### 2014-09-15 documents/inclination/inclination.tex
start

\documentclass[12pt, preprint]{aastex}

\begin{document}

\title{Removing inclination noise}
\author{some combination of DWH, DFM, and others}
\date{}

\begin{abstract}
Many observations of dynamical systems---galactic black holes, stellar
rotation, and exoplanets, for examples---suffer from an inclination
uncertainty.
When the system is unresolved the observable contains a sine ($\sin
i$) of the inclination ($i$).
Here we show that it is possible to infer the true distribution of
rotation velocities $v$ from noisy, censored measurements of $v\,\sin
i$ (or the true distribution of masses $M$ from measurements of
$M\,\sin i$).
This is a classic problem in non-blind ``deconvolution''.
We frame the problem as a hierarchical probabilistic inference; in
this formulation, the whole distribution of the observable $v\,\sin i$
is compared to that expected from a distribution of latent ``true''
values $v$ and the expected inclination distribution and other noise
sources and censoring.
This permits us to write a likelihood function for the catalog of
observed values, given a parameterized or non-parametric model for the
distribution of latent values.
We show that for realistic simulated rotation velocity data, the
method returns reliable inferences for the distribution of true
rotation velocities, even when the velocity distribution model used in
the inference does not include the model with which the velocities
were originally drawn.
One interesting consequence or application of the probabilistic model
is that it provides informative posterior information, for each object
in the catalog, about its true inclination.
\end{abstract}

\section{Introduction}

\section{Method}

\section{Experiments}

\section{Discussion}

\acknowledgements
It is a pleasure to thank...
Funding...
Code...

\end{document}

### 2014-09-15 documents/inclination/inclination.tex
equationdump

@@
 \documentclass[12pt, preprint]{aastex}
+\usepackage{bm}
+\input{vc}
+
+\newcommand{\setof}[1]{\left\{{#1}\right\}}
+\newcommand{\given}{\,|\,}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\catalog}{\bm{Q}}
+\newcommand{\pars}{\bm{\theta}}
 
@@
 \author{some combination of DWH, DFM, and others}
-\date{}
+\date{NOT READY / \texttt{\githash}}
 
 \begin{abstract}
-Many observations of dynamical systems---galactic black holes, stellar
-rotation, and exoplanets, for examples---suffer from an inclination
+Many observations of kinematic systems (such as galactic black holes,
+stellar rotation, and exoplanets) suffer from an inclination
 uncertainty.
-When the system is unresolved the observable contains a sine ($\sin
-i$) of the inclination ($i$).
+When the system is unresolved the observable contains a sine of the
+inclination ($\sin i$).
 Here we show that it is possible to infer the true distribution of
@@
 $M\,\sin i$).
-This is a classic problem in non-blind ``deconvolution''.
+This is a classic problem in ``non-blind deconvolution''.
 We frame the problem as a hierarchical probabilistic inference; in
 this formulation, the whole distribution of the observable $v\,\sin i$
-is compared to that expected from a distribution of latent ``true''
+is compared to that expected from a distribution of latent true
 values $v$ and the expected inclination distribution and other noise
@@
 
+...Equation dump...
+\begin{eqnarray}
+Q &\equiv& v\,\sin i
+\\
+f(Q\given\pars) &=& \int P(Q)\,p(Q\given v,i)\,f(v\given\pars)\,p(i)\,\dd i\,\dd v
+\\
+\int p(x)\,\dd x &=& 1
+\\
+\int f(x)\,\dd x &=& E[N]
+\\
+\ln p(\catalog\given\pars) &=& \sum_{n=1}^N f(Q_n\given\pars) - \ln \int f(Q\given\pars)\,\dd Q
+\\
+\catalog &\equiv& \setof{Q_n}_{n=1}^N
+\\
+p(\pars\given\catalog) &=& \frac{1}{Z}\,p(\catalog\given\pars)\,p(\pars)
+\\
+p(i_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
+\\
+p(i_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd v_n
+\\
+p(v_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
+\\
+p(v_n\given\pars) &=& \frac{1}{Z_n}\,\int p(Q_n\given v_n,i_n)\,f(v_n\given\pars)\,p(i_n)\,\dd i_n
+\end{eqnarray}
+
 \section{Experiments}

### 2014-09-15 documents/inclination/inclination.tex
notesToSelf

@@
 
+...For specificity we will consider stellar rotation.
+
 \section{Method}
@@
 \\
-p(v_n\given\catalog) &=& \int p(i_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
+p(v_n\given\catalog) &=& \int p(v_n\given\pars)\,p(\pars\given\catalog)\,\dd\pars
 \\
@@
 
+...To make an experiment, we need to generate fake data from some true
+distribution, and add some noise.
+We \emph{also} have to choose a form for the latent distribution
+$f(Q\given pars)$; that is, a parameterization $\theta$
+Once we have chosen both, we have an experiment.
+
 \section{Discussion}
+
+...Method generalizes to more complex situations; for example when the
+censoring depends on variables beyond $Q$, or when the direct
+observable is not precisely $Q$ but something intermediate.
 

### 2014-09-16 tiltshift/fakedata.py
Added module to generate fake data

@@ -1,0 +1,70 @@
+# coding: utf-8
+
+from __future__ import division, print_function
+
+__author__ = "adrn <adrn@astro.columbia.edu>"
+
+# Standard library
+import os, sys
+
+# Third-party
+import numpy as np
+import numexpr
+from astropy import log as logger
+import astropy.units as u
+
+# Project
+# ...
+
+__all__ = ['']
+
+def generate_data(N, v_func, v_func_kwargs=dict(), sigma=5., censor="Q > 5*sigma"):
+    """ Generate fake measurements of $Q = v \sin i$ (e.g., stellar rotation, or
+        radial velocity of a binary component). `sigma` controls the measurement
+        uncertainty (in units of km/s), `v_func` specifies the function to draw
+        true velocities from, and `censor` specifies an expression to censor the
+        data with.
+
+        Parameters
+        ----------
+        N : int
+            Number of data points to generate.
+        v_func : function
+            Function to sample from to get true velocities. For example,
+            `np.random.lognormal`.
+        v_func_kwargs : dict (optional)
+            Any kwargs that need to be passed to the function to sample the
+            true velicities. For example, for `lognormal()`, need to specify
+            `mean` and `sigma`. Size is added automatically by `N`.
+        sigma : float, numeric (optional)
+            Observational uncertainty in the observed $v \sin i$ in km/s. Default
+            is 5 km/s.
+        censor : str (optional)
+            An expression (as a string) that specifies how to censor the data.
+            Default is to only accept velocitie measured >5 times the velocity
+            uncertainty.
+
+    """
+
+    v_func_kwargs['size'] = N
+    v = v_func(**v_func_kwargs)
+
+    # v = np.random.lognormal(5, sigma=0.01, size=N)
+    # v = np.random.lognormal(5, sigma=0.25, size=N)
+    sini = np.sin(np.arccos(np.random.uniform(0.,1.,size=N)))
+    Q = v*sini
+
+    if isinstance(sigma, float):
+        sigma = np.ones(N)*sigma
+    else:
+        sigma = np.array(sigma)
+
+    if sigma.shape != Q.shape:
+        raise ValueError("Shape of sigma is invalid. Must be a scalar, or length N")
+
+    Q = Q + np.random.normal(0., sigma)
+
+    mask = numexpr.evaluate(censor)  # censor the data
+    logger.debug("Fraction of censored objects: {}".format((~mask).sum() / float(N)))
+
+    return v[mask], Q[mask], sigma[mask]

### 2014-09-16 tiltshift/fakedata.py
git rid of shite imports

@@ -4,19 +4,15 @@ from __future__ import division, print_function
 
 __author__ = "adrn <adrn@astro.columbia.edu>"
 
-# Standard library
-import os, sys
-
 # Third-party
 import numpy as np
 import numexpr
 from astropy import log as logger
-import astropy.units as u
 
 # Project
 # ...
 
-__all__ = ['']
+__all__ = ['generate_data']
 
 def generate_data(N, v_func, v_func_kwargs=dict(), sigma=5., censor="Q > 5*sigma"):
     """ Generate fake measurements of $Q = v \sin i$ (e.g., stellar rotation, or

### 2014-09-16 tiltshift/fakedata.py
more import nuking

@@ -9,9 +9,6 @@ import numpy as np
 import numexpr
 from astropy import log as logger
 
-# Project
-# ...
-
 __all__ = ['generate_data']
 
 def generate_data(N, v_func, v_func_kwargs=dict(), sigma=5., censor="Q > 5*sigma"):

### 2014-09-17 tiltshift/model.py
code up model

@@ -1,0 +1,100 @@
+# coding: utf-8
+
+from __future__ import division, print_function
+
+__author__ = "adrn <adrn@astro.columbia.edu>"
+
+# Standard library
+import os, sys
+
+# Third-party
+import numpy as np
+from astropy import log as logger
+import astropy.units as u
+from scipy.misc import logsumexp
+
+# Project
+# ...
+
+__all__ = ['']
+
+def ln_integrand(x, mu, sigma, i):
+    return -0.5*((x-mu*np.sin(i))/sigma)**2 - 0.5*np.log(2*np.pi) \
+        - np.log(sigma) + np.log(np.sin(i))
+
+def ln_prior(a_k):
+    """ Using the prior
+
+            p(a_k) ∝ 1/a_k
+            ln(p) = -ln(a_k)
+    """
+
+    if np.any(a_k < 0.):
+        return -np.inf
+
+    return -np.sum(np.log(a_k))
+
+def _ln_likelihood_explicit(a_k, v_k, Q, sigma_Q):
+    """ Directly turn sums into loops"""
+
+    neyes = 100
+    eyes = np.linspace(0., np.pi/2., neyes)  # grid of inclination angles [rad]
+    di = eyes[1] - eyes[0]
+
+    l = 0.
+    for a,v in zip(a_k,v_k):
+        rs = np.zeros_like(eyes)
+        for j,eye in enumerate(eyes):
+            r = np.exp(ln_integrand(Q,v,sigma_Q,eye))
+            rs[j] = r
+
+        l += a * di * rs.sum() / sigma_Q / np.sqrt(2*np.pi)
+
+    ll = np.log(l)
+
+    if np.isnan(ll):
+        return -np.inf
+
+    return ll
+
+def ln_likelihood_explicit(a_k, v_k, Qs, sigma_Qs):
+    N = len(Qs)
+    rs = np.zeros_like(Qs)
+    for n in range(N):
+        rs[n] = _ln_likelihood_explicit(a_k, v_k, Qs[n], sigma_Qs[n])
+    return np.sum(rs)
+
+def ln_likelihood_fast(a_k, v_k, Qs, sigma_Qs):
+    """ """
+
+    J = 128  # number of i's to use in dumb-ass integration
+    K = len(a_k)  # number of mixture components
+    N = len(Qs)  # number of data points
[…]

### 2014-09-17 scripts/test_infer.py
test explicit vs fast

@@ -1,0 +1,75 @@
+# coding: utf-8
+
+"""  """
+
+from __future__ import division, print_function
+
+__author__ = "adrn <adrn@astro.columbia.edu>"
+
+# Standard library
+import os, sys
+# HACK:
+sys.path.append("/Users/adrian/projects/tilt-shift/")
+
+# Third-party
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy import log as logger
+
+# Project
+from tiltshift.model import ln_likelihood_explicit, ln_likelihood_fast
+from tiltshift.fakedata import generate_data
+
+# TODO: make plot of f(Q | {a_k}) for some choice of a_k's
+def main():
+    np.random.seed(42)
+
+    N = 100
+    sigma = 5.  # km/s
+    v_func = np.random.lognormal
+    v_func_args = dict(mean=5., sigma=0.01)
+    v,Q,sigma_Q = generate_data(N, v_func, v_func_kwargs=v_func_args,
+                                sigma=sigma, censor="Q > 5*sigma")
+
+    a_k = np.array([0.4, 0.5, 0.6])
+    v_k = np.array([100, 150, 200.])
+
+    ll = ln_likelihood_fast(a_k, v_k, Q, sigma_Q)
+    print(ll.sum())
+    ll = ln_likelihood_explicit(a_k, v_k, Q, sigma_Q)
+    print(ll)
+
+    QQs = np.linspace(50., 250., 100)
+    sigma_QQs = np.ones_like(QQs)*sigma_Q[0]
+    lls = ln_likelihood_fast(a_k, v_k, QQs, sigma_QQs)
+
+    plt.plot(QQs, np.exp(lls-lls.max()))
+    plt.show()
+
+if __name__ == '__main__':
+    from argparse import ArgumentParser
+    import logging
+
+    # Define parser object
+    parser = ArgumentParser(description="")
+    parser.add_argument("-v", "--verbose", action="store_true", dest="verbose",
+                        default=False, help="Be chatty! (default = False)")
+    parser.add_argument("-q", "--quiet", action="store_true", dest="quiet",
+                        default=False, help="Be quiet! (default = False)")
+
+    # parser.add_argument("-f", dest="field_id", default=None, required=True,
+    #                     type=int, help="Field ID")
+    # parser.add_argument("-p", dest="plot", action="store_true", default=False,
+    #                     help="Plot or not")
+
+    args = parser.parse_args()
+
[…]

### 2014-09-17 scripts/test_infer.py
add plot option

@@ -21,7 +21,7 @@ from tiltshift.model import ln_likelihood_explicit, ln_likelihood_fast
 from tiltshift.fakedata import generate_data
 
 # TODO: make plot of f(Q | {a_k}) for some choice of a_k's
-def main():
+def main(plot=False):
     np.random.seed(42)
 
     N = 100
@@ -34,17 +34,21 @@ def main():
     a_k = np.array([0.4, 0.5, 0.6])
     v_k = np.array([100, 150, 200.])
 
-    ll = ln_likelihood_fast(a_k, v_k, Q, sigma_Q)
-    print(ll.sum())
-    ll = ln_likelihood_explicit(a_k, v_k, Q, sigma_Q)
-    print(ll)
+    ll1 = ln_likelihood_fast(a_k, v_k, Q, sigma_Q)
+    ll1 = ll1.sum()
+
+    ll2 = ln_likelihood_explicit(a_k, v_k, Q, sigma_Q)
+
+    assert np.allclose(ll1, ll2, rtol=1E-1)
 
     QQs = np.linspace(50., 250., 100)
     sigma_QQs = np.ones_like(QQs)*sigma_Q[0]
     lls = ln_likelihood_fast(a_k, v_k, QQs, sigma_QQs)
 
-    plt.plot(QQs, np.exp(lls-lls.max()))
-    plt.show()
+    if plot:
+        plt.clf()
+        plt.plot(QQs, np.exp(lls-lls.max()))
+        plt.show()
 
 if __name__ == '__main__':
     from argparse import ArgumentParser
@@ -59,8 +63,8 @@ if __name__ == '__main__':
 
     # parser.add_argument("-f", dest="field_id", default=None, required=True,
     #                     type=int, help="Field ID")
-    # parser.add_argument("-p", dest="plot", action="store_true", default=False,
-    #                     help="Plot or not")
+    parser.add_argument("-p", dest="plot", action="store_true", default=False,
+                        help="Plot or not")
 
     args = parser.parse_args()
 
@@ -72,4 +76,4 @@ if __name__ == '__main__':
     else:
         logger.setLevel(logging.INFO)
 
-    main()
+    main(plot=args.plot)

### 2014-09-17 scripts/test_infer.py
added pool support

@@ -7,21 +7,23 @@ from __future__ import division, print_function
 __author__ = "adrn <adrn@astro.columbia.edu>"
 
 # Standard library
-import os, sys
+import sys
 # HACK:
 sys.path.append("/Users/adrian/projects/tilt-shift/")
 
 # Third-party
+import emcee
 import matplotlib.pyplot as plt
 import numpy as np
 from astropy import log as logger
+from streamteam.util import get_pool
 
 # Project
-from tiltshift.model import ln_likelihood_explicit, ln_likelihood_fast
+from tiltshift.model import ln_likelihood_explicit, ln_likelihood_fast, ln_posterior
 from tiltshift.fakedata import generate_data
 
 # TODO: make plot of f(Q | {a_k}) for some choice of a_k's
-def main(plot=False):
+def main(pool, plot=False):
     np.random.seed(42)
 
     N = 100
@@ -50,6 +52,57 @@ def main(plot=False):
         plt.plot(QQs, np.exp(lls-lls.max()))
         plt.show()
 
+    # ------------------------------------------------------------------------
+    # Now try actually sampling
+    K = 10
+    v_k = np.linspace(5., 200., K)
+    logger.debug("v_ks: {}".format(v_k))
+
+    nwalkers = 64
+    ndim = K
+    sampler = emcee.EnsembleSampler(nwalkers, dim=ndim,
+                                    lnpostfn=ln_posterior,
+                                    args=(v_k,Q,sigma_Q),
+                                    pool=pool)
+    p0 = np.random.normal(0.5,0.05,size=(nwalkers,ndim))
+    p0 = p0 * N / p0.sum(axis=1)[:,np.newaxis]
+    if np.any(p0 <= 0.):
+        raise ValueError("Dumby.")
+
+    logger.debug("Running sampler to burn in...")
+    pos,prob,state = sampler.run_mcmc(p0, 100)
+
+    sampler.reset()
+    logger.debug("Running sampler for main sampling...")
+    pos,prob,state = sampler.run_mcmc(pos, 100)
+    logger.debug("Done sampling!")
+
+    pool.close()
+    sys.exit(0)
+
+    for j in range(ndim):
+        plt.clf()
+        for walker in sampler.chain[...,j]:
+            plt.plot(walker)
+        plt.ylim(0,sampler.flatchain.max())
+        plt.xlabel("Step number")
+        plt.savefig("{}.png".format(j))
+
+    nbins = 25
[…]

### 2014-09-17 scripts/test_infer.py
move sys exit

@@ -19,7 +19,8 @@ from astropy import log as logger
 from streamteam.util import get_pool
 
 # Project
-from tiltshift.model import ln_likelihood_explicit, ln_likelihood_fast, ln_posterior
+from tiltshift.model import ln_posterior, ln_likelihood
+from tiltshift.explicitmodel import ln_likelihood as ln_likelihood_explicit
 from tiltshift.fakedata import generate_data
 
 # TODO: make plot of f(Q | {a_k}) for some choice of a_k's
@@ -36,7 +37,7 @@ def main(pool, plot=False):
     a_k = np.array([0.4, 0.5, 0.6])
     v_k = np.array([100, 150, 200.])
 
-    ll1 = ln_likelihood_fast(a_k, v_k, Q, sigma_Q)
+    ll1 = ln_likelihood(a_k, v_k, Q, sigma_Q)
     ll1 = ll1.sum()
 
     ll2 = ln_likelihood_explicit(a_k, v_k, Q, sigma_Q)
@@ -45,7 +46,7 @@ def main(pool, plot=False):
 
     QQs = np.linspace(50., 250., 100)
     sigma_QQs = np.ones_like(QQs)*sigma_Q[0]
-    lls = ln_likelihood_fast(a_k, v_k, QQs, sigma_QQs)
+    lls = ln_likelihood(a_k, v_k, QQs, sigma_QQs)
 
     if plot:
         plt.clf()
@@ -78,7 +79,6 @@ def main(pool, plot=False):
     logger.debug("Done sampling!")
 
     pool.close()
-    sys.exit(0)
 
     for j in range(ndim):
         plt.clf()
@@ -135,3 +135,4 @@ if __name__ == '__main__':
 
     pool = get_pool(mpi=args.mpi, threads=args.threads)
     main(pool, plot=args.plot)
+    sys.exit(0)

### 2014-09-17 tiltshift/explicitmodel.py
separated models

@@ -1,0 +1,66 @@
+# coding: utf-8
+
+from __future__ import division, print_function
+
+__author__ = "adrn <adrn@astro.columbia.edu>"
+
+# Third-party
+import numpy as np
+
+# Project
+from .model import ln_integrand
+
+__all__ = ['ln_prior', 'ln_likelihood', 'ln_posterior']
+
+def ln_prior(a_k):
+    """ Using the prior
+
+            p(a_k) ∝ 1/a_k
+            ln(p) = -ln(a_k)
+    """
+
+    if np.any(a_k <= 0.):
+        return -np.inf
+
+    return -np.sum(np.log(a_k))
+
+def _ln_likelihood_explicit(a_k, v_k, Q, sigma_Q):
+    """ Directly turn sums into loops"""
+
+    neyes = 100
+    eyes = np.linspace(0., np.pi/2., neyes)  # grid of inclination angles [rad]
+    di = eyes[1] - eyes[0]
+
+    l = 0.
+    for a,v in zip(a_k,v_k):
+        rs = np.zeros_like(eyes)
+        for j,eye in enumerate(eyes):
+            r = np.exp(ln_integrand(Q,v,sigma_Q,eye))
+            rs[j] = r
+
+        l += a * di * rs.sum() / sigma_Q / np.sqrt(2*np.pi)
+
+    ll = np.log(l)
+
+    if np.isnan(ll):
+        return -np.inf
+
+    return ll
+
+def ln_likelihood(a_k, v_k, Qs, sigma_Qs):
+    N = len(Qs)
+    rs = np.zeros_like(Qs)
+    for n in range(N):
+        rs[n] = _ln_likelihood_explicit(a_k, v_k, Qs[n], sigma_Qs[n])
+    return np.sum(rs)
+
+def ln_posterior(a_k, v_k, Q, sigma_Q):
+    lp = ln_prior(a_k)
+    if np.any(np.isinf(lp)):
+        return -np.inf
+
+    ll = ln_likelihood(a_k, v_k, Q, sigma_Q).sum()
+    if np.any(np.isinf(ll)):
+        return -np.inf
+
+    return lp + ll

### 2014-09-17 tiltshift/model.py

@@ -4,19 +4,11 @@ from __future__ import division, print_function
 
 __author__ = "adrn <adrn@astro.columbia.edu>"
 
-# Standard library
-import os, sys
-
 # Third-party
 import numpy as np
-from astropy import log as logger
-import astropy.units as u
 from scipy.misc import logsumexp
 
-# Project
-# ...
-
-__all__ = ['']
+__all__ = ['ln_prior', 'ln_likelihood', 'ln_posterior']
 
 def ln_integrand(x, mu, sigma, i):
     return -0.5*((x-mu*np.sin(i))/sigma)**2 - 0.5*np.log(2*np.pi) \
@@ -29,42 +21,12 @@ def ln_prior(a_k):
             ln(p) = -ln(a_k)
     """
 
-    if np.any(a_k < 0.):
+    if np.any(a_k <= 0.):
         return -np.inf
 
     return -np.sum(np.log(a_k))
 
-def _ln_likelihood_explicit(a_k, v_k, Q, sigma_Q):
-    """ Directly turn sums into loops"""
-
-    neyes = 100
-    eyes = np.linspace(0., np.pi/2., neyes)  # grid of inclination angles [rad]
-    di = eyes[1] - eyes[0]
-
-    l = 0.
-    for a,v in zip(a_k,v_k):
-        rs = np.zeros_like(eyes)
-        for j,eye in enumerate(eyes):
-            r = np.exp(ln_integrand(Q,v,sigma_Q,eye))
-            rs[j] = r
-
-        l += a * di * rs.sum() / sigma_Q / np.sqrt(2*np.pi)
-
-    ll = np.log(l)
-
-    if np.isnan(ll):
-        return -np.inf
-
-    return ll
-
-def ln_likelihood_explicit(a_k, v_k, Qs, sigma_Qs):
-    N = len(Qs)
-    rs = np.zeros_like(Qs)
-    for n in range(N):
-        rs[n] = _ln_likelihood_explicit(a_k, v_k, Qs[n], sigma_Qs[n])
-    return np.sum(rs)
-
-def ln_likelihood_fast(a_k, v_k, Qs, sigma_Qs):
+def ln_likelihood(a_k, v_k, Qs, sigma_Qs):
     """ """
 
     J = 128  # number of i's to use in dumb-ass integration
@@ -93,7 +55,7 @@ def ln_posterior(a_k, v_k, Q, sigma_Q):
[…]

### 2014-09-17 scripts/test_infer.py
change number of steps

@@ -71,11 +71,11 @@ def main(pool, plot=False):
         raise ValueError("Dumby.")
 
     logger.debug("Running sampler to burn in...")
-    pos,prob,state = sampler.run_mcmc(p0, 100)
+    pos,prob,state = sampler.run_mcmc(p0, 1000)
 
     sampler.reset()
     logger.debug("Running sampler for main sampling...")
-    pos,prob,state = sampler.run_mcmc(pos, 100)
+    pos,prob,state = sampler.run_mcmc(pos, 5000)
     logger.debug("Done sampling!")
 
     pool.close()

### 2014-09-17 scripts/test_infer.py
plot path

@@ -23,12 +23,13 @@ from tiltshift.model import ln_posterior, ln_likelihood
 from tiltshift.explicitmodel import ln_likelihood as ln_likelihood_explicit
 from tiltshift.fakedata import generate_data
 
-# TODO: make plot of f(Q | {a_k}) for some choice of a_k's
+plot_path = "/vega/astro/users/amp2217/projects/tilt-shift"
+
 def main(pool, plot=False):
     np.random.seed(42)
 
-    N = 100
-    sigma = 5.  # km/s
+    N = 256
+    sigma = 1.  # km/s
     v_func = np.random.lognormal
     # v_func_args = dict(mean=5., sigma=0.01)  # tight v
     v_func_args = dict(mean=5., sigma=0.25)  # wide v
@@ -56,11 +57,11 @@ def main(pool, plot=False):
 
     # ------------------------------------------------------------------------
     # Now try actually sampling
-    K = 10
+    K = 32
     v_k = np.linspace(5., 200., K)
     logger.debug("v_ks: {}".format(v_k))
 
-    nwalkers = 64
+    nwalkers = 128
     ndim = K
     sampler = emcee.EnsembleSampler(nwalkers, dim=ndim,
                                     lnpostfn=ln_posterior,
@@ -87,7 +88,7 @@ def main(pool, plot=False):
             plt.plot(walker)
         plt.ylim(0,sampler.flatchain.max())
         plt.xlabel("Step number")
-        plt.savefig("{}.png".format(j))
+        plt.savefig(os.path.join(plot_path, "{}.png".format(j)))
 
     nbins = 25
     bins = np.linspace(0,200,nbins)
@@ -98,11 +99,11 @@ def main(pool, plot=False):
     axes[0].set_xlabel(r'True $v$ [km s$^{-1}$]')
 
     median_a = np.median(sampler.flatchain, axis=0)
-    vs = np.random.choice(v_k, p=median_a/np.sum(median_a), size=1000)
-    axes[1].hist(vs, bins=bins)
+    # vs = np.random.choice(v_k, p=median_a/np.sum(median_a), size=1000)
+    axes[1].plot(v_k, median_a, linestyle='none', marker='o') # hist(vs, bins=bins)
     axes[1].set_xlim(bins.min(), bins.max())
     axes[1].set_xlabel(r'Model')
-    fig.savefig("compare.png")
+    fig.savefig(os.path.join(plot_path, "compare.png"))
 
 if __name__ == '__main__':
     from argparse import ArgumentParser

### 2014-09-18 scripts/run.py
no testing foos

@@ -1,0 +1,144 @@
+# coding: utf-8
+
+""" Given observations of Q = v sin i for some sample of objects, model the
+    distribution of v as a mixture of components and infer parameters of those
+    components. Essentially a deconvolution of sin i.
+"""
+
+from __future__ import division, print_function
+
+__author__ = "adrn <adrn@astro.columbia.edu>"
+
+# Standard library
+import os
+import sys
+import socket
+
+# Third-party
+import emcee
+import matplotlib.pyplot as plt
+import numpy as np
+from astropy import log as logger
+from streamteam.util import get_pool
+
+# Project
+from tiltshift.model import ln_posterior
+from tiltshift.fakedata import generate_data
+
+def main(pool, path, plot=False):
+
+    N = 256  # Number of fake data points
+    J = 128  # Number of steps to use when integrating over i
+    K = 32  # Number of mixture components
+
+    base_save_path = os.path.join(path, "cache")
+    save_path = os.path.join(base_save_path, "N{}_J{}_K{}".format(N,J,K))
+    if not os.path.exists(save_path):
+        os.makedirs(save_path)
+
+    # -------------------------------------------------------------------------
+    # Generate fake data
+    #
+
+    np.random.seed(42)
+    sigma = 1.  # km/s
+    v_func = np.random.lognormal
+    # v_func_args = dict(mean=5., sigma=0.01)  # tight v
+    v_func_args = dict(mean=5., sigma=0.25)  # wide v
+    v,Q,sigma_Q = generate_data(N, v_func, v_func_kwargs=v_func_args,
+                                sigma=sigma, censor="Q > 5*sigma")
+
+    # -------------------------------------------------------------------------
+    # Now try sampling
+    #
+
+    # fix the positions of the mixture components
+    v_k = np.linspace(5., 250., K)
+    logger.debug("v_ks: {}".format(v_k))
+
+    nwalkers = K*4
+    ndim = K
+    sampler = emcee.EnsembleSampler(nwalkers, dim=ndim,
+                                    lnpostfn=ln_posterior,
+                                    args=(v_k,Q,sigma_Q),
+                                    pool=pool)
+    p0 = np.random.normal(0.5,0.05,size=(nwalkers,ndim))
+    p0 = p0 * N / p0.sum(axis=1)[:,np.newaxis]
+    if np.any(p0 <= 0.):
+        raise ValueError("Dumby.")
+
[…]

### 2014-09-18 scripts/run.py
imports and paths

@@ -21,11 +21,10 @@ import numpy as np
 from astropy import log as logger
 from streamteam.util import get_pool
 
-# Project
-from tiltshift.model import ln_posterior
-from tiltshift.fakedata import generate_data
-
 def main(pool, path, plot=False):
+    # Project
+    from tiltshift.model import ln_posterior
+    from tiltshift.fakedata import generate_data
 
     N = 256  # Number of fake data points
     J = 128  # Number of steps to use when integrating over i
@@ -138,7 +137,8 @@ if __name__ == '__main__':
         base_path = "/Users/adrian/projects/tilt-shift"
     else:
         logger.info("Assuming we're on yeti...")
-        base_path = ""
+        base_path = "/vega/astro/users/amp2217/projects/tilt-shift"
 
+    sys.path.append(base_path)
     main(pool, path=base_path, plot=args.plot)
     sys.exit(0)

### 2014-09-18 scripts/run.py
changed N

@@ -28,7 +28,7 @@ def main(pool, path, plot=False):
 
     N = 256  # Number of fake data points
     J = 128  # Number of steps to use when integrating over i
-    K = 32  # Number of mixture components
+    K = 16  # Number of mixture components
 
     base_save_path = os.path.join(path, "cache")
     save_path = os.path.join(base_save_path, "N{}_J{}_K{}".format(N,J,K))

### 2014-09-18 scripts/run.py
bad walkers

@@ -18,6 +18,7 @@ import socket
 import emcee
 import matplotlib.pyplot as plt
 import numpy as np
+from astropy.stats import median_absolute_deviation
 from astropy import log as logger
 from streamteam.util import get_pool
 
@@ -69,7 +70,13 @@ def main(pool, path, plot=False):
     logger.debug("Running sampler to burn in...")
     pos,prob,state = sampler.run_mcmc(p0, 1000)
 
+    bad_walkers = sampler.acceptance_fraction < 0.1
+    pos[bad_walkers] = np.random.normal(np.median(pos[~bad_walkers]),
+                                        median_absolute_deviation(pos[~bad_walkers]),
+                                        size=bad_walkers.sum())
+
     sampler.reset()
+
     logger.debug("Running sampler for main sampling...")
     pos,prob,state = sampler.run_mcmc(pos, 5000)
     logger.debug("Done sampling!")

### 2014-09-18 scripts/run.py
bad walkers

@@ -68,12 +68,13 @@ def main(pool, path, plot=False):
         raise ValueError("Dumby.")
 
     logger.debug("Running sampler to burn in...")
-    pos,prob,state = sampler.run_mcmc(p0, 1000)
+    # pos,prob,state = sampler.run_mcmc(p0, 1000)
+    pos,prob,state = sampler.run_mcmc(p0, 100) # HACK
 
     bad_walkers = sampler.acceptance_fraction < 0.1
-    pos[bad_walkers] = np.random.normal(np.median(pos[~bad_walkers]),
-                                        median_absolute_deviation(pos[~bad_walkers]),
-                                        size=bad_walkers.sum())
+    pos[bad_walkers] = np.random.normal(np.median(pos[~bad_walkers],axis=0),
+                                        median_absolute_deviation(pos[~bad_walkers],axis=0),
+                                        size=(bad_walkers.sum(), ndim))
 
     sampler.reset()
 

### 2014-09-28 documents/letter/ms.tex
added manuscript to repo

%\documentclass{emulateapj}
\documentclass[letterpaper,12pt,preprint]{aastex}

% packages
\usepackage{amssymb,amsmath,amsbsy}

% commands
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transpose}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inverse}[1]{{#1}^{-1}}
\newcommand{\Msun}{\mathrm{M}_\odot}

\begin{document}

\title{The Companion Mass Distribution to the ELM WD Sample}
\author{Jeff Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}

% Affiliations
\newcommand{\colum}{1}
\altaffiltext{\colum}{Department of Astronomy, 
		              Columbia University, 
		              550 W 120th St., 
		              New York, NY 10027, USA}
% \altaffiltext{\adrn}{To whom correspondence should be addressed: adrn@astro.columbia.edu}

\begin{abstract}
Determining component masses of single-line spectroscopic binary stars
is impossible because of the unknown inclination angle. Even when the
mass of the bright star can be derived, only a lower limit can be placed
on the mass of the unseen companion. However, since the probability of
any inclination angle scales with sin $i$, for a large enough, unbiased
population, the companion mass distribution can be deconvolved from the
inclination angle. We develop a Bayesian technique to handle this
deconvolution and place it within a Markov Chain Monte Carlo framework.
We then apply our method to the sample of 55 extremely low mass (ELM)
WDs with radial velocity variations. Modeling the companion mass
distribution as a Gaussian with a variable neutron star component, we
find the companion population is well modeled by a mean of 0.65 and a
standard deviation of 0.3 . Our model indicates a neutron star (NS)
fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
\end{abstract}

%\keywords{
%  cosmology: dark matter
%  ---
%  Galaxy: structure
%  ---
%  Galaxy: halo
%}

%\begin{figure*}[!h]
%\begin{center}
%\includegraphics[width=\textwidth]{PATH}
%\caption{ CAPTION }\label{fig:FIGNAME}
%\end{center}
%\end{figure*}

\section{Introduction}

The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from the Data Release 7 (DR7) in the Sloan Digital Sky Survey (SDSS), containing some 20,000 confirmed WDs (Kleinman et al 2013). While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number (6\%) of low mass WDs was observed, with $M<0.4~\Msun$.

These Low Mass WDs (LMWDs) comprise an astrophysically unique population. Except in special cases of extreme metallicity (Kilic et al 2007), the Galaxy is not old enough to produce WDs with mass $<0.5~\Msun$ through single star evolution. In their seminal work, Marsh, Dhillon, \& Duck (1995) discovered companions around five LMWDs, cementing the requirement that these objects be formed through binary evolution. In addition to SDSS, LMWDs have been observed in similar numbers in the Palomar Green Survey (Liebert et al 2005).

Using a reduced proper motion selection criterion, the Extrememly Low Mass (ELM) WD Survey specifically searched for LMWDs in SDSS. After their initial investigation found 11 of 12 LMWDs had close binary companions (Brown et al. 2010), further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity variations (Kilic et al 2011, 2012, Brown et al 2012, 2013).

While the orbital periods and radial velocities indicated the companions were most likely WDs, it was realized that these LMWDs could have NS companions (van Leeuwen et al 2007). However this and other radio searches for pulsed emission were fruitless (Agueros et al 2009a, 2009b). X-ray observations provide more stringent limits on the presence of a NS, and searches using {\it XMM-Newton} and {\it Chandra} have all yielded non-detections. Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars. Because of the resources required for these targeted observations, selecting the most likely candidates for multiwavelength follow-up is crucial. We outline the standard technique below.

For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($P_{\rm orb}$), WD mass ($M_1$), and projected orbital velocity ($K$). Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:

\begin{equation}
	\frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 \label{eq:massfunc}
\end{equation}

The righthand side of this equation is the well-known mass function. $M_2$ is minimized for an edge-on orbit, with $i = 90^{\circ}$. For any individual system, deriving the likelihood of a $M_2$ for that system ($P(M_2)$) involves solving Equation 1 for $M_2$ for different values for $i$, weighting the inclination angle by sin $i$. A basic calculation for the probability that the companion to any individual system is a NS can therefore be calculated:

\begin{equation}
P({\rm NS}) = \int_{0^{\circ}}^{i_{\rm NS}} {\rm sin}\ i\ {\rm d}i
\end{equation}

Where $i_{\rm NS}$ is the inclination angle from Equation 1 when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$. However, implicit in this calculation is that all companion masses are equally likely a priori. Clearly this is not the case as evidenced by e.g. SDSS (kleinman et al 2013) who show the WD mass distribution is strongly peaked around $0.6~\Msun$. Including this as a prior on the companion mass does not improve the situation since it is unlikely that the mass distribution of single WDs and WDs in binaries is the same. Equation 2 should therefore be used only as an approximation for the NS probability of a companion.

With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the population is large enough to be modeled. Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased. In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses (i.e. one Gaussian)? 2.\ How many NSs are implied by the distribution of $M_{2,min}$'s? 3.\ Can we determine the likelihood of any individual system including a NS companion, based on the most likely models? 4.\ Are the six systems without detected radial velocity variations consistent with the population as a whole, or are these a fundamentally separate population (i.e. single ELM WDs)? 7.\ Can our model place limits on the space density of ELM WD binaries with NS companions?

In Section 2 we build the mathematical framework that we employ in our model described in Section 3. Section 4 shows the results of our model, while Section 5 gives a discussion. We conclude in Section 6.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample. The three eclipsing systems, with known $M_2$ are shown by the filled circles. Arrows indicate the masses of ELM WDs without detected radial velocity variation. Triangles indicate the positions of the known WD-NS binaries. From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
\end{center}
\end{figure}

\section{Methods (?)}

We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$ --- for the distribution of ELM WD companion masses, $M_2$.  For each system, we assume we are given $K$, $T$, and $M_1$ and therefore have a measurement of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}). In this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$ and therefore $m_f$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$. We would therefore like to find posterior constraints on the parameters, $\boldsymbol{theta}$, given the ``observed'' mass functions, $m_f$. Using Bayes' rule,
\begin{equation}
    p(\bs{\theta} \given m_f, M_1) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
\end{equation}
The likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the unobserved inclination angle, $i$, and companion mass, $M_2$
\begin{equation}
    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
\end{equation}

and can derive a distribution over possible $M_2$'s -- the 'true' $M_2$ (a $\delta$-function) convolved with the distribution over possible inclination angles, $i$ (Figure?). We would like to infer some parameters, $\boldsymbol{\theta}$, of a model for the true companion mass distribution, 
\begin{equation}
    p(\boldsymbol{\theta} \,|\, K, T, M_1) = \int p(\boldsymbol{\theta} \,|\, K, T, M_1, i)\,p(i)\,di.
\end{equation}
For this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$.

\begin{align}
    p(D\,|\,M_2,i)\,p(M_2\,|\,\boldsymbol{\theta})\,p(i)
\end{align}

We are interested in determining the probability of any given model to have produced the observations, abstractly represented by the conditional probability, $P(M|D)$, where $M$ represents our model and $D$ represents our data. We first use Bayes's Theorem:

\begin{equation}
P(M|D) = \frac{P(D|M)P(M)}{P(D)}
\end{equation}

where $P(M)$ is the Bayesian prior on the model and $P(D)$ is the known as the "evidence". The conditional probability $P(D|M)$ requires a "generative model". We choose to represent our model, $M$, as $\mathbf{\Theta}$ and our combined data, $D$, as a set of individual systems, $\vec{D}$. Since each system is an independent data point, the combined probability can be represented as a product of the individual system likelihoods:

\begin{equation}
P(\vec{D}|\mathbf{\Theta}) = \prod^{\vec{D}}P(D | \mathbf{\Theta})
\end{equation}

We choose to model the log of the likelihood:

\begin{equation}
{\rm log}\ P(\vec{D}|\mathbf{\Theta}) = \sum^{\vec{D}} {\rm log}\ P(D | \mathbf{\Theta})
\end{equation}

To determine the individual system likelihoods, we first marginalize over $M_2$:

\begin{equation}
P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\infty} P(D |\mathbf{\Theta}, M_2) P(M_2|\mathbf{\Theta})\ dM_2 
\end{equation}

where $A$ is a normalization constant. We further marginalize over the inclination angle, $i$:

\begin{equation}
P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\pi/2} \int_{M_{2,min}}^{\infty} P(D | \mathbf{\Theta}, M_2, i) P(M_2|\mathbf{\Theta}, i) P(i | \mathbf{\Theta})\ {\rm d}M_2\ {\rm d}i
\end{equation}

Since only a single value for $M_{2,min}$ is allowed for a given $M_1$, $M_2$, and $i$, $P(D | \mathbf{\Theta}, M_2, i)$ reduces to a delta function:

\begin{equation}
P(D | \mathbf{\Theta}, M_2, i) = \delta \left(M_{2,min} - f(M_1,M_2,i) \right)
\end{equation}

where $f(M_1,M_2,i)$ is the root of equation {\bf XXXXX}. Furthermore, the inclination angle is independent of other parameters:

\begin{eqnarray}
P(i | \mathbf{\Theta}) &=& P(i) \\
  &=& {\rm sin}\ i \\
  &=& \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2}
\end{eqnarray}

where in the last equation, we used equation {\bf XXX}. Combining equations {\bf XXX}, {\bf XXX}, and {\bf XXX} and evaluating the integral over $i$ we produce the following result:

\begin{equation}
P(D|\mathbf{\Theta}) = \frac{1}{A} \int_{M_{2,min}}^{\infty}  P(M_2|\mathbf{\Theta},i_{M_2}) \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2
\end{equation}

where $i_{M_2}$ is a function of $M_2$, determined from Equation {\bf XXX}. The final parameter left to be determined is the normalization constant, $A$. This parameter requires an additional integral, over all $M_{2,min}$:

\begin{equation}
A = \int_0^{\infty} \int_{M_{2,min}}^{\infty} P(M_2|\mathbf{\Theta}, i_{M_2}) \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2\ {\rm d}M_{2,min}
\end{equation}

Finally, $P(M_2|\mathbf{\Theta},i_{M_2})$ is our model. We choose to model the masses of the WD companions as a Gaussian, with an additional NS component. This model is independent of the inclination angle and can be expressed in the following way:

\begin{eqnarray}
P(M_2|\mathbf{\Theta},i) &=& P(M_2 | \mathbf{\Theta}) \\
  &=& \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} + \mathcal{f}_{NS} \delta \left( M_2 - M_{NS} \right)
\end{eqnarray}

where $\mathcal{f}_{NS}$ represents the NS fraction in the model, and $\mathcal{N}(\mu , \sigma)$ represents a Gaussian with mean, $\mu$, and standard deviation, $\sigma$. The NS component is modeled by a delta function around $M_{NS}$ which we take to be $1.35 ~\Msun$. Combining this with equation {\bf XXX}, we can separate the integrand into a WD and a NS component:

\begin{equation}
P(D|\mathbf{\Theta}) = P_{WD} + P_{NS}
\end{equation}

where the WD component is:

\begin{equation}
P_{WD} = \frac{1}{A} \int_{M_{2,min}}^{\infty} \left[ \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} \right]  \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2 
\end{equation}

and the NS component is:

\begin{equation}
P_{NS} = \frac{1}{A} \mathcal{f}_{NS}\left( \frac{M_1 + M_{NS}}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_{NS}}
\end{equation}

The normalization constant can likewise be reduced into a WD and a NS component, with the integral over d$M_{2,min}$ performed separately on both:

\begin{equation}
A = A_{WD} + A_{NS}
\end{equation}

where the WD component is:

\begin{equation}
A_{WD} = \int_0^{\infty} \int_{M_{2,min}}^{\infty} \left[ \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} \right]  \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2}\ {\rm d}M_2\ {\rm d}M_{2,min}
\end{equation}

and the NS component is:

\begin{equation}
A_{NS} = \int_0^{\infty} \mathcal{f}_{NS}\left( \frac{M_1 + M_{NS}}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} \delta \left( M_2 - M_{NS} \right) {\rm d}M_{2,min}
\end{equation}

which can be evaluated analytically, using integration by parts:

\begin{equation}
A_{NS} = 3 \left(M_1+M_{NS}\right)^{2/3} \left[  \frac{M_{2,min}}{M_{NS}} \left( M_1+M_{2,min} \right)^{1/3} - \frac{3}{4} \frac{ \left( M_1 + M_{2,min} \right)^{4/3} }{M_{NS}} \right] |_{M_{2,min}=0}^{M_{2,min}=M_{NS}}
\end{equation}

Using these equations, we can now calculate the likelihood of a given set of model parameters ($\mu$, $\sigma$, and $\mathcal{f}_{NS}$). In general, these integrals must be evaluated numerically. Furthermore, since each system has a different $M_1$ and $M_{2,min}$ and therefore must be calculated separately, these formulae become quite computationally expensive, particularly calculating the double integral in $A_{WD}$.

It is also straightforward to determine, for a particular $\Theta$, the probability of any individual system being composed of a NS:

\begin{equation}
P(NS) = \frac{P_{NS}}{P_{WD} + P_{NS}}
\end{equation}

where $P_{NS}$ and $P_{WD}$ are calculated from equation {\bf XXX} and {\bf XXX}, respectively.

In future work we will extend this analysis to incorporate uncertainties and non-detections.

\section{Our model}

Maximizing the likelihood now requires a numerical technique to probe the parameter space. We have chosen to use a Markov Chain Monte Carlo (MCMC) technique. Because we only have three parameters, we can use a standard Metropolis-Hastings acceptance-rejection technique. Using this technique, we randomly generate new model parameters based on the old model parameters, using a proposal distribution, $K(\mathbf{\Theta '} | \mathbf{\Theta})$. So that the proposal distribution is symmetric ($K(\mathbf{\Theta '} | \mathbf{\Theta})$ = $K(\mathbf{\Theta} | \mathbf{\Theta '})$), we follow the standard prescription and adopt a Gaussian distribution for $K(\mathbf{\Theta '} | \mathbf{\Theta})$, centered on $\Theta$. After a "burn-in" of 500 steps, we use 10 separate chains to determine the posterior probability, $P(\mathbf{\Theta} | \vec{D})$.

To test the performance of our model, we apply it to three separate sets of mock data, each with 100 systems. These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution then applying a randomly drawn inclination angle. We apply our model to the distribution of resulting $M_{2,min}$ and $M_1$ values, attempting to recover the initial model parameters.

Our first set of mock data, shown in the top three panels of Figure 2 is composed of a Gaussian distribution centered at $0.7~\Msun$, with a standard deviation of $0.2~\Msun$. We give these binaries random inclination angles. The distribution of the mock observations for $M_{2,min}$ are shown by the histogram in the left panel. The red line shows the theoretical distribution, determined by numerically evaluating the integral in Equation {\bf XXX}, substituting $\mathcal{N}(0.7,0.2)$ for $P(M_2|\mathbf{\Theta})$. We apply our model to the data and obtain the posterior distribution shown in the middle panel. Contours indicate 1, 2, and 3-$\sigma$ confidence levels. The overplotted "X" shows the input mean and standard deviation for our randomly selected sample. The right panel shows that the one dimensional posterior distribution for the NS probability is strongly peaked at zero. For this simple data set, our model correctly identifies the population mean, standard deviation, and NS probability.

Our second set of mock data is drawn from the same distribution as the first (with $\mu = 0.7$ and $\sigma = 0.2$) except it includes 10 NS, each given a mass of $1.35~\Msun$. Comparing the analytic distribution in the top left panel with the middle left panel shows that adding a NS component most strongly affects the high end tail of the distribution. The sample of "observed" $M_{2,min}$ shows that only five of the ten NS have masses greater than $1.0~\Msun$; the other five NS companions have $M_{2,min}$ measurements indistinguishable from that of WD companions. The middle panel in Figure {\bf XXX} shows the posterior distribution for the mean and standard deviation of the sample. The NS component clearly skews the distribution toward larger distributions, however the true values (designated by the "X") are still within the 1-$\sigma$ confidence level. The ability of our model to correctly identify the NS fraction, shown in the right panel, is most interesting. The peak of the posterior distribution is centered at 10\%. {\bf Come up with confidence levels here.}

The third set of mock data tests the ability of our model to match non-Gaussian distributions. Here, we generated a sample of WD companions from a flat mass distribution $M_{WD} = [0.3:1.1]~\Msun$, combined with a NS fraction of 10\%. The theoretical expectation for the distribution of $M_{2,min}$, shown by the red line in the bottom left panel, was produced by numerically integrating equation {\bf XXX}, where we substitute a flat distribution for $P(M_2 | \mathbf{\Theta},i)$:

\begin{equation}
P(M_2 | \mathbf{\Theta},i) = \left( 1 - \mathcal{f}_{NS} \right) \frac{1}{M_{WD,max} - M_{WD,min}} + \mathcal{f}_{NS} \delta(M_2 - M_{NS})
\end{equation}

where $M_{WD,min}=0.3~\Msun$ and $M_{WD,max} = 1.1~\Msun$. The histogram shows that this distribution results in a larger number of WDs with very low $M_{2,min}$. The resulting posterior distribution in $\mu$ and $\sigma$ is shown by the bottom middle panel. Since our model is attempting to derive a Gaussian mass distribution from an initially non-Gaussian distribution, the posterior is not as well formed as our previous two test cases. Furthermore, the resulting NS probability, shown in the bottom right panel of Figure {\bf XXX}, is not as well formed. This is because, on the one hand, the distribution of $M_{2,min}$ has a large component at very low masses, skewing the resulting $\mu$ distribution toward lower masses, with a larger NS fraction. On the other hand, the portion of the sample at large $M_{2,min}$ is pushing the distribution toward larger masses, with a smaller NS fraction. The competition between these two effects spreads the posterior distributions in all three of our model parameters.

It is clear that our model can recover the initial distribution of companion masses and NS fraction with a fairly high degree of accuracy, when the population is well represented by a Gaussian. Our third test case shows that when our initial population significantly deviates from a Gaussian, our model is much more imprecise. However this uniform distribution, with a relatively low $M_{WD,min}$ of $0.3~\Msun$ and high $M_{WD,max}$ of $1.1~\Msun$ is a very difficult distribution to fit with a Gaussian because the high mass WDs can easily be confused with NSs and vice versa. Unfortunately, the posterior NS probability did not converge on a single value. Nevertheless, our model indicates that, despite the "wrong" choice of model, the NS fraction is non-negligible.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{figures/model_post1/model_post.jpg}
\caption{Replace this text with your caption}
\end{center}
\end{figure}

\section{Results}

We apply our model to the ELM WD sample, however there are some slight differences worth mentioning in the population of ELM WDs and our test cases above.

First, there are 55 systems with radial velocity measurements in the ELM sample, while the test cases above were each produced with 100 systems. Second, the masses of the primaries in our test cases were all $0.25~\Msun$, while in the ELM sample, the masses vary between 0.16 and $0.49~\Msun$. Also, the orbital periods of the systems in our test case were all 12 hours, while in the ELM sample the orbital periods vary between 12 minutes and just over a day. Since our model does not depend on the $M_2$ or $P_{\rm orb}$, its accuracy will not be affected.

In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$1748: $M_2=0.72~\Msun$, J0651$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$). These are taken into account in our model through equation {\bf XXX}. Since the inclination angle cannot vary, these systems will strongly affect the likelihood of any particular model.

Finally, six systems in the ELM WD sample lack radial velocity variations down upper limits of $\sim$50 km s$^{-1}$. While some of these may be in binaries with radial velocities below the detection limit, they may also be single ELM WDs. In principle we could add to our model the possibility that each of these WDs is actually a single ELM WD. Because this requires an additional six free parameters, one for each ELM WD without radial velocity variations, including these in our model becomes too computationally expensive. The result is that we can run our model on the 55 ELM systems with orbital solutions.

We apply our model to the ELM WD data set, using 10 indepedent Markov chains, each run for 100,000 steps. The acceptance fraction is {\bf XXX}. We determine an autocorrelation length of {\bf XXX} steps, and correspondingly, only include every {\bf XXX} samples for our posterior distributions. {\bf Is there anything else we need to say about the applying the method to the data set?}

The results of our model are shown in Figure {\bf XXX}. The first panel shows the distribution of $M_{2,min}$ for the data set. It is fairly similar to the distribution of $M_{2,min}$ in the test cases above, with a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$. The second panel shows the posterior distribution of $\mu$ and $\sigma$; contours indicate 1, 2, and 3-$\sigma$ confidence levels. The single high probability region indicates the models converged {\bf (Is this reasonable to say?)}. The best fit Gaussian model has a mean of 0.66 $\substack{+0.12 \\ -0.09}~\Msun$ and a standard deviation of 0.27$\substack{+0.09 \\ -0.07}~\Msun$. The third panel shows the NS fraction is strongly peaked toward low probabilities. Our model indicates a NS fraction of 1.4$\substack{+7.0 \\ -1.4}$\% at the 68\% confidence level, however there is a non-negligible tail toward higher NS probabilities. This is further indicated by the fourth panel in Figure {\bf XXX} which shows a histogram of NS probabilities for individual systems. These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system. Although a few systems have high probabilities, the distribution is strongly clustered below 20\%.

\section{Discussion}

How does the companion mass distribution compare to the single WD mass distribution? Based on their population of $\sim$ 14,000 spectroscopically confirmed DA WDs in SDSS, Kleinman et al (2013) found that WDs are well approximated by a four component Gaussian mixture model. Their mixture model is dominated by two Gaussians with means $\sim0.6~\Msun$, containing over 75\% of all WDs. Figure {\bf XXX} shows that the best fit Gaussian to our distribution of WD companion masses is also centered around $\sim0.6!\Msun$. However, our distribution is significantly wider ($\sigma \approx 0.3~\Msun$ compared with $\sigma \approx 0.1~\Msun$). This could be due to our simplistic assumption of a single Gaussian mass distribution. A more complicated model would include multiple Gaussians with varying weights, however adding only one more Gaussian component doubles the number of free parameters from three to six. Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.

There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve. However, the posterior distribution in $\mu$ and $\sigma$ is well behaved, with a clear high probability region, similar to the posterior distributions for $\mu$ and $\sigma$ for our first two test cases shown in Figure {\bf XXX}. The part of the distribution with a low $\mu$ and high $\sigma$ is indicative of a low mass WD component. A low mass component is expected from binary evolution theory; recent population synthesis work predicts more than half of all He WDs in DWDs will have He WD companions (Toonen et al 2012). Our results here suggest that this is not the case, our posterior suggests a Gaussian distribution centered around $0.6~\Msun$, firmly in the mass range for CO WDs. This suggests that our results on the companion masses of the secondaries in these systems could constrain population synthesis models. We plan on exploring this in a future work.

Systems with NS companions cannot be differentiated from those with WD companions through orbital period and ELM WD mass alone. Our model attempts to suggest a NS fraction for the population as a whole. This is an improvement over NS probabilities for individual companions calculated through equation {\bf XXX}. The third panel in Figure {\bf XXX} indicates a NS fraction of a few percent. For 55 systems with observed radial velocity variations, this corresponds to a 1-2 systems with NS companions. However, the top left panel in Figure {\bf XXX} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass tail of a Gaussian distribution. Furthermore, in their Gaussian mixture fit to the SDSS DA WD mass distribution, Kleinman et al (2013) found a high mass WD component extending above $1~\Msun$. Our single Gaussian model does not include this high mass component. It is not guaranteed that any ELM WDs have NS companions. Nevertheless, a quite firm result of our model is an upper limit on the fraction of ELM WDs with NS companions of {\bf XXXX}\%.

If we combine our result of a NS fraction of {\bf XXX} with the ELM WD space density as determined from the Palomar Green Survey: $4\times10^{-14}$pc$^{-3}$yr$^{-1}$ (Liebert et al 2005) {\bf Is there a more recent estimate?} we can get a space density of ELM WD + NS binaries. This suggests that there are {\bf XXX} such binaries within a few kpc of us. Compare to the number of known MSP+LMWDs.

The fourth panel in Figure {\bf XXX} shows  that only two systems have $P(NS)$ above 50\%: J0811$0225 (67\%) and J1741$6526 (53\%). These systems are ideal candidates for searches for NS companions in radio and X-ray. Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio. However, all NS give off blackbody radiation as X-rays, and therefore X-ray follow-up provides a more stringent test on the potential for a NS companion.

Non-detections? What does that imply about the existence of single ELM WDs?

\begin{figure}[h!]
\begin{center}
\includegraphics[width=1\columnwidth]{figures/ELM_post1/ELM_post1.jpg}
\caption{Replace this text with your caption}
\end{center}
\end{figure}

\subsection{Non-detections}

Six systems in the ELM WD sample have non-detections of companions, down to an upper limit on the transverse velocity. We include these systems in our model, too, as in principle they could be binary systems at with low inclination angles or long period orbits or both. We can estimate the number of binaries with inclination angles too low to produce observable radial velocity variations:

\begin{equation}
P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} \int_0^{i_{\rm max}} P(M_2|\mathbf{\Theta})\ {\rm sin}\ i\ {\rm d}i\ {\rm d}M_2
\end{equation}

which reduces to:

\begin{equation}
P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} P(M_2|\mathbf{\Theta})\ \left( 1 - {\rm cos}\ i_{\rm max}\right)\ {\rm d}M_2
\end{equation}

where $i_{\rm max}$ is the smallest inclination angle that would still produce an unobservable binary, found by solving equation 1, using $K_{\rm max}$ for $K$. For an estimate of the expected fraction of unobserable binaries, we adopt $0.25~\Msun$ for $M_1$, an orbital period of 0.5 days, and a limiting velocity of 50 km s$^{-1}$. For our best fit model, with $\mu=0.6$, $\sigma=0.3$, and $\mathcal{f}=0.03$, we numerically calculate the integral above, and find that we would expect $\sim$2\% and $\sim$7\% of systems to have radial velocity variations below 25 km s$^{-1}$ and 50 km s$^{-1}$, respectively. If we increase the fiducial orbital period to 1.0 day, those numbers increases to 3\% and 10\%, respectively. For the ELM sample with 61 systems, this corresponds to 2 and 6 systems, consistent with the number of non-detections observed. Although we caution that this result is based on our imperfect model, it suggests that the number of non-detections observed is consistent with binaries at low inclination angles (albeit at slightly larger orbital periods than that of the observed population).

\section{Conclusions}

\begin{enumerate}
\item We have created a mathematical description to describe the companion mass distribution of a set of single-lined spectoscopic binaries. \\
\item We have used that mathematical framework to build a Markov Chain Monte Carlo model and applied it to the set of WDs from the ELM survey. \\
\item Our model suggests that the majority of ELM WDs have CO-core WDs. {\bf We should check this.} \\
\item Our model indicates that the fraction of ELM WDs with NS companions is of order a few percent. Specifically, J0811$+$0225 and J1741$+$6526 have probabilities of having NS companions greater than 50\%. \\
\item This NS fraction implies an ELM+WD space density of {\bf XXX} which suggests there are {\bf XXX} systems withing a few kiloparsecs.
\end{enumerate}

\acknowledgements
APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance. \\

\bibliographystyle{apj}
\bibliography{refs}

\end{document}

### 2014-09-28 documents/letter/ms.tex
changes to methods

@@
 \newcommand{\Msun}{\mathrm{M}_\odot}
+\newcommand{\bs}[1]{\boldsymbol{#1}}
 
@@
 
-We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$ --- for the distribution of ELM WD companion masses, $M_2$.
-For each system, we assume we are given $K$, $T$, and $M_1$ and therefore have a measurement of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
-In this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$ and therefore $m_f$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$.
-We would therefore like to find posterior constraints on the parameters, $\boldsymbol{theta}$, given the ``observed'' mass functions, $m_f$.
+We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} --- for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta}})$.
+For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).\footnote{In this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$ and therefore $m_f$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$.} We would like to find posterior constraints on the parameters, $\boldsymbol{\theta}$, given all of the known mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,
@@
 \end{equation}
-The likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the unobserved inclination angle, $i$, and companion mass, $M_2$
+The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
 \begin{equation}
     p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
+\end{equation}
+where we, again, neglect observational uncertainties in the mass function, and assume the inclination angles, $i$, are isotropically distributed
+\begin{align}
+	p(m_f \given M_1, M_2, i) &= \delta(m_f - f(M_1, M_2, i))\\
+	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
+	p(i) &= \sin i.
+\end{align}
+For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$.
+With the above assumptions, the marginal likelihood integral is reduced to
+\begin{equation}
+    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~\delta(m_f - f(M_1, M_2, i))~p(M_2 \given \bs{\theta})~p(i).
 \end{equation}

### 2014-09-29 documents/letter/ms.tex
so many maths

@@
 We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} --- for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta}})$.
-For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).\footnote{In this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$ and therefore $m_f$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$.} We would like to find posterior constraints on the parameters, $\boldsymbol{\theta}$, given all of the known mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
+We would like to find posterior constraints on the parameters, $\boldsymbol{\theta}$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,
@@
 \end{equation}
-where we, again, neglect observational uncertainties in the mass function, and assume the inclination angles, $i$, are isotropically distributed
+where we neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles, $i$, are isotropically distributed
 \begin{align}
@@
 \end{align}
-For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$.
-With the above assumptions, the marginal likelihood integral is reduced to
+For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
+\begin{align}
+    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta(m_f - f(M_1, M_2, i))~\sin i\\
+    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta(g(M_1,M_2,i))\label{eq:delta}
+\end{align}
+where
 \begin{equation}
-    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~\delta(m_f - f(M_1, M_2, i))~p(M_2 \given \bs{\theta})~p(i).
+	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - m_f.
 \end{equation}
-
-and can derive a distribution over possible $M_2$'s -- the 'true' $M_2$ (a $\delta$-function) convolved with the distribution over possible inclination angles, $i$ (Figure?).
-We would like to infer some parameters, $\boldsymbol{\theta}$, of a model for the true companion mass distribution,
+The inner integral (over $i$) has the form
 \begin{equation}
-    p(\boldsymbol{\theta} \,|\, K, T, M_1) = \int p(\boldsymbol{\theta} \,|\, K, T, M_1, i)\,p(i)\,di.
+    \int dx~F(x)~\delta{(G(x)}) = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
 \end{equation}
-For this work, we neglect the uncertainties in the catalog parameters ($K$, $T$, $M_1$) because the relative uncertainties in these quantities are small, $\sigma_x / x \sim XXX$.
-
+where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative, $g'(M_1,M_2,i)$, of the argument of the delta function in Equation~\ref{eq:delta} are 
 \begin{align}
-    p(D\,|\,M_2,i)\,p(M_2\,|\,\boldsymbol{\theta})\,p(i)
+	i^* &= \sin^{-1}\alpha\\
+	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
+	g'(M_1,M_2,i) &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
+	g'(M_1,M_2,i^*) &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
 \end{align}
 
-We are interested in determining the probability of any given model to have produced the observations, abstractly represented by the conditional probability, $P(M|D)$, where $M$ represents our model and $D$ represents our data.
-We first use Bayes's Theorem:
+With this in mind,
+\begin{align}
+	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
+	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1} 
+\end{align}
 
-\begin{equation}
-P(M|D) = \frac{P(D|M)P(M)}{P(D)}
-\end{equation}
-
-where $P(M)$ is the Bayesian prior on the model and $P(D)$ is the known as the "evidence".
-The conditional probability $P(D|M)$ requires a "generative model".
-We choose to represent our model, $M$, as $\mathbf{\Theta}$ and our combined data, $D$, as a set of individual systems, $\vec{D}$.
-Since each system is an independent data point, the combined probability can be represented as a product of the individual system likelihoods:
-
-\begin{equation}
-P(\vec{D}|\mathbf{\Theta}) = \prod^{\vec{D}}P(D | \mathbf{\Theta})
-\end{equation}
-
-We choose to model the log of the likelihood:
-
-\begin{equation}
-{\rm log}\ P(\vec{D}|\mathbf{\Theta}) = \sum^{\vec{D}} {\rm log}\ P(D | \mathbf{\Theta})
-\end{equation}
+\vspace{2em}
+\hrule
 

### 2014-09-29 documents/letter/ms.tex
marginalization

@@
 \end{align}
-
-With this in mind,
+With this in mind, we may write the marginal likelihood as
 \begin{align}
 	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
-	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1} 
+	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{M_2(M_1+M_2)^{4/3}}{3m_f^{1/3}\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\label{eq:fullm2}
 \end{align}
+where the bottom bound in the integral in Equation~\ref{eq:fullm2} is the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.
 

### 2014-09-29 documents/letter/ms.tex
Figures added, Eqn 18 fixed

@@
 \begin{center}
-\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
+\includegraphics[width=0.7\columnwidth]{Porb_M1.eps}
 \caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
@@
 
-We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} --- for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta}})$.
+We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} --- for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.
 For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
@@
 	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{M_2(M_1+M_2)^{4/3}}{3m_f^{1/3}\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\label{eq:fullm2}
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\label{eq:fullm2}
 \end{align}
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{figures/model_post1/model_post.jpg}
+\includegraphics[width=1\columnwidth]{model_post.eps}
 \caption{Replace this text with your caption}
@@
 
-In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$1748: $M_2=0.72~\Msun$, J0651$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$).
+In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$).
 These are taken into account in our model through equation {\bf XXX}.
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{figures/ELM_post1/ELM_post1.jpg}
+\includegraphics[width=1\columnwidth]{ELM_post.eps}
 \caption{Replace this text with your caption}

### 2014-09-30 documents/letter/ms.tex
note to self

--- 2014-09-29 documents/letter/ms.tex
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
-\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
+%\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
 The three eclipsing systems, with known $M_2$ are shown by the filled circles.
@@
 From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
-\end{center}
-\end{figure}
+%\end{center}
+%\end{figure}
 
@@
 \begin{equation}
-    p(\bs{\theta} \given m_f, M_1) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
+    p(\bs{\theta} \given m_f) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
 \end{equation}
-The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
+[APW: Write about $\mathcal{Z}$] The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
 \begin{equation}
@@
 \begin{equation}
-P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\infty} P(D |\mathbf{\Theta}, M_2) P(M_2|\mathbf{\Theta})\ dM_2 
+P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\infty} P(D |\mathbf{\Theta}, M_2) P	(M_2|\mathbf{\Theta})\ dM_2 
 \end{equation}

### 2014-09-30 documents/letter/ms.tex

--- 2014-09-29 documents/letter/ms.tex
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=0.7\columnwidth]{Porb_M1.eps}
-\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
+%\begin{figure}[h!]
+%\begin{center}
+%\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
+%\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
 The three eclipsing systems, with known $M_2$ are shown by the filled circles.

### 2014-10-02 documents/letter/ms.tex
equation refs

--- 2014-09-29 documents/letter/ms.tex
@@
 \begin{center}
-\includegraphics[width=0.7\columnwidth]{Porb_M1.eps}
+\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
 \caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
@@
 \begin{equation}
-    p(\bs{\theta} \given m_f, M_1) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
+    p(\bs{\theta} \given m_f) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
 \end{equation}
+where $p(m_f \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
 The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
@@
 \end{equation}
-where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative, $g'(M_1,M_2,i)$, of the argument of the delta function in Equation~\ref{eq:delta} are 
+where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in Equation~\ref{eq:delta} are 
 \begin{align}
@@
 	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
-	g'(M_1,M_2,i) &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
-	g'(M_1,M_2,i^*) &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
+	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
+	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
 \end{align}

### 2014-10-02 scripts/run.py
dunno

@@ -5,6 +5,8 @@
     components. Essentially a deconvolution of sin i.
 """
 
+# TODO: I think the model is wrong - need to fix P(Q) and check logsumexp
+
 from __future__ import division, print_function
 
 __author__ = "adrn <adrn@astro.columbia.edu>"
@@ -37,7 +39,7 @@ def main(pool, path, N, J, K, plot=False, nsteps=1000):
     #
 
     np.random.seed(42)
-    sigma = 1.  # km/s
+    sigma = 0.01  # km/s
     v_func = np.random.lognormal
     # v_func_args = dict(mean=5., sigma=0.01)  # tight v
     v_func_args = dict(mean=5., sigma=0.25)  # wide v
@@ -76,7 +78,7 @@ def main(pool, path, N, J, K, plot=False, nsteps=1000):
         pos,prob,state = sampler.run_mcmc(pos, nsteps//10)
 
     sampler.reset()
-
+    logger.debug("Pos: {}".format())
     logger.debug("Running sampler for main sampling...")
     pos,prob,state = sampler.run_mcmc(pos, nsteps)
     logger.debug("Done sampling!")

### 2014-10-02 scripts/run.py
remove old code that doesn't work

@@ -1,164 +1,0 @@
-# coding: utf-8
-
-""" Given observations of Q = v sin i for some sample of objects, model the
-    distribution of v as a mixture of components and infer parameters of those
-    components. Essentially a deconvolution of sin i.
-"""
-
-# TODO: I think the model is wrong - need to fix P(Q) and check logsumexp
-
-from __future__ import division, print_function
-
-__author__ = "adrn <adrn@astro.columbia.edu>"
-
-# Standard library
-import os
-import sys
-import socket
-
-# Third-party
-import emcee
-import matplotlib.pyplot as plt
-import numpy as np
-from astropy.stats import median_absolute_deviation
-from astropy import log as logger
-from streamteam.util import get_pool
-
-def main(pool, path, N, J, K, plot=False, nsteps=1000):
-    # Project
-    from tiltshift.model import ln_posterior
-    from tiltshift.fakedata import generate_data
-
-    base_save_path = os.path.join(path, "cache")
-    save_path = os.path.join(base_save_path, "N{}_J{}_K{}".format(N,J,K))
-    if not os.path.exists(save_path):
-        os.makedirs(save_path)
-
-    # -------------------------------------------------------------------------
-    # Generate fake data
-    #
-
-    np.random.seed(42)
-    sigma = 0.01  # km/s
-    v_func = np.random.lognormal
-    # v_func_args = dict(mean=5., sigma=0.01)  # tight v
-    v_func_args = dict(mean=5., sigma=0.25)  # wide v
-    v,Q,sigma_Q = generate_data(N, v_func, v_func_kwargs=v_func_args,
-                                sigma=sigma, censor="Q > 5*sigma")
-
-    # -------------------------------------------------------------------------
-    # Now try sampling
-    #
-
-    # fix the positions of the mixture components
-    v_k = np.linspace(5., 250., K)
-    logger.debug("v_ks: {}".format(v_k))
-
-    nwalkers = K*8
-    ndim = K
-    sampler = emcee.EnsembleSampler(nwalkers, dim=ndim,
-                                    lnpostfn=ln_posterior,
-                                    args=(v_k,Q,sigma_Q),
-                                    pool=pool)
-    p0 = np.random.normal(0.5,0.05,size=(nwalkers,ndim))
-    p0 = p0 * N / p0.sum(axis=1)[:,np.newaxis]
-    if np.any(p0 <= 0.):
-        raise ValueError("Dumby.")
-
[…]

### 2014-10-02 scripts/test_infer.py

@@ -1,140 +1,0 @@
-# coding: utf-8
-
-"""  """
-
-from __future__ import division, print_function
-
-__author__ = "adrn <adrn@astro.columbia.edu>"
-
-# Standard library
-import sys
-# HACK:
-sys.path.append("/Users/adrian/projects/tilt-shift/")
-
-# Third-party
-import emcee
-import matplotlib.pyplot as plt
-import numpy as np
-from astropy import log as logger
-from streamteam.util import get_pool
-
-# Project
-from tiltshift.model import ln_posterior, ln_likelihood
-from tiltshift.explicitmodel import ln_likelihood as ln_likelihood_explicit
-from tiltshift.fakedata import generate_data
-
-plot_path = "/vega/astro/users/amp2217/projects/tilt-shift"
-
-def main(pool, plot=False):
-    np.random.seed(42)
-
-    N = 256
-    sigma = 1.  # km/s
-    v_func = np.random.lognormal
-    # v_func_args = dict(mean=5., sigma=0.01)  # tight v
-    v_func_args = dict(mean=5., sigma=0.25)  # wide v
-    v,Q,sigma_Q = generate_data(N, v_func, v_func_kwargs=v_func_args,
-                                sigma=sigma, censor="Q > 5*sigma")
-
-    a_k = np.array([0.4, 0.5, 0.6])
-    v_k = np.array([100, 150, 200.])
-
-    ll1 = ln_likelihood(a_k, v_k, Q, sigma_Q)
-    ll1 = ll1.sum()
-
-    ll2 = ln_likelihood_explicit(a_k, v_k, Q, sigma_Q)
-
-    assert np.allclose(ll1, ll2, rtol=1E-1)
-
-    QQs = np.linspace(50., 250., 100)
-    sigma_QQs = np.ones_like(QQs)*sigma_Q[0]
-    lls = ln_likelihood(a_k, v_k, QQs, sigma_QQs)
-
-    if plot:
-        plt.clf()
-        plt.plot(QQs, np.exp(lls-lls.max()))
-        plt.show()
-
-    # ------------------------------------------------------------------------
-    # Now try actually sampling
-    K = 32
-    v_k = np.linspace(5., 200., K)
-    logger.debug("v_ks: {}".format(v_k))
-
-    nwalkers = 128
-    ndim = K
-    sampler = emcee.EnsembleSampler(nwalkers, dim=ndim,
-                                    lnpostfn=ln_posterior,
-                                    args=(v_k,Q,sigma_Q),
-                                    pool=pool)
[…]

### 2014-10-02 tiltshift/explicitmodel.py

@@ -1,66 +1,0 @@
-# coding: utf-8
-
-from __future__ import division, print_function
-
-__author__ = "adrn <adrn@astro.columbia.edu>"
-
-# Third-party
-import numpy as np
-
-# Project
-from .model import ln_integrand
-
-__all__ = ['ln_prior', 'ln_likelihood', 'ln_posterior']
-
-def ln_prior(a_k):
-    """ Using the prior
-
-            p(a_k) ∝ 1/a_k
-            ln(p) = -ln(a_k)
-    """
-
-    if np.any(a_k <= 0.):
-        return -np.inf
-
-    return -np.sum(np.log(a_k))
-
-def _ln_likelihood_explicit(a_k, v_k, Q, sigma_Q):
-    """ Directly turn sums into loops"""
-
-    neyes = 100
-    eyes = np.linspace(0., np.pi/2., neyes)  # grid of inclination angles [rad]
-    di = eyes[1] - eyes[0]
-
-    l = 0.
-    for a,v in zip(a_k,v_k):
-        rs = np.zeros_like(eyes)
-        for j,eye in enumerate(eyes):
-            r = np.exp(ln_integrand(Q,v,sigma_Q,eye))
-            rs[j] = r
-
-        l += a * di * rs.sum() / sigma_Q / np.sqrt(2*np.pi)
-
-    ll = np.log(l)
-
-    if np.isnan(ll):
-        return -np.inf
-
-    return ll
-
-def ln_likelihood(a_k, v_k, Qs, sigma_Qs):
-    N = len(Qs)
-    rs = np.zeros_like(Qs)
-    for n in range(N):
-        rs[n] = _ln_likelihood_explicit(a_k, v_k, Qs[n], sigma_Qs[n])
-    return np.sum(rs)
-
-def ln_posterior(a_k, v_k, Q, sigma_Q):
-    lp = ln_prior(a_k)
-    if np.any(np.isinf(lp)):
-        return -np.inf
-
-    ll = ln_likelihood(a_k, v_k, Q, sigma_Q).sum()
-    if np.any(np.isinf(ll)):
-        return -np.inf
-
-    return lp + ll

### 2014-10-02 tiltshift/fakedata.py

@@ -1,63 +1,0 @@
-# coding: utf-8
-
-from __future__ import division, print_function
-
-__author__ = "adrn <adrn@astro.columbia.edu>"
-
-# Third-party
-import numpy as np
-import numexpr
-from astropy import log as logger
-
-__all__ = ['generate_data']
-
-def generate_data(N, v_func, v_func_kwargs=dict(), sigma=5., censor="Q > 5*sigma"):
-    """ Generate fake measurements of $Q = v \sin i$ (e.g., stellar rotation, or
-        radial velocity of a binary component). `sigma` controls the measurement
-        uncertainty (in units of km/s), `v_func` specifies the function to draw
-        true velocities from, and `censor` specifies an expression to censor the
-        data with.
-
-        Parameters
-        ----------
-        N : int
-            Number of data points to generate.
-        v_func : function
-            Function to sample from to get true velocities. For example,
-            `np.random.lognormal`.
-        v_func_kwargs : dict (optional)
-            Any kwargs that need to be passed to the function to sample the
-            true velicities. For example, for `lognormal()`, need to specify
-            `mean` and `sigma`. Size is added automatically by `N`.
-        sigma : float, numeric (optional)
-            Observational uncertainty in the observed $v \sin i$ in km/s. Default
-            is 5 km/s.
-        censor : str (optional)
-            An expression (as a string) that specifies how to censor the data.
-            Default is to only accept velocitie measured >5 times the velocity
-            uncertainty.
-
-    """
-
-    v_func_kwargs['size'] = N
-    v = v_func(**v_func_kwargs)
-
-    # v = np.random.lognormal(5, sigma=0.01, size=N)
-    # v = np.random.lognormal(5, sigma=0.25, size=N)
-    sini = np.sin(np.arccos(np.random.uniform(0.,1.,size=N)))
-    Q = v*sini
-
-    if isinstance(sigma, float):
-        sigma = np.ones(N)*sigma
-    else:
-        sigma = np.array(sigma)
-
-    if sigma.shape != Q.shape:
-        raise ValueError("Shape of sigma is invalid. Must be a scalar, or length N")
-
-    Q = Q + np.random.normal(0., sigma)
-
-    mask = numexpr.evaluate(censor)  # censor the data
-    logger.debug("Fraction of censored objects: {}".format((~mask).sum() / float(N)))
-
-    return v[mask], Q[mask], sigma[mask]

### 2014-10-02 tiltshift/model.py

@@ -1,61 +1,0 @@
-# coding: utf-8
-
-from __future__ import division, print_function
-
-__author__ = "adrn <adrn@astro.columbia.edu>"
-
-# Third-party
-import numpy as np
-from scipy.misc import logsumexp
-
-__all__ = ['ln_prior', 'ln_likelihood', 'ln_posterior']
-
-def ln_integrand(x, mu, sigma, i):
-    return -0.5*((x-mu*np.sin(i))/sigma)**2 - 0.5*np.log(2*np.pi) \
-        - np.log(sigma) + np.log(np.sin(i))
-
-def ln_prior(a_k):
-    """ Using the prior
-
-            p(a_k) ∝ 1/a_k^2
-            ln(p) = -2*ln(a_k)
-    """
-
-    if np.any(a_k <= 0.):
-        return -np.inf
-
-    return -2*np.sum(np.log(a_k))
-
-def ln_likelihood(a_k, v_k, Qs, sigma_Qs):
-    """ """
-
-    J = 128  # number of i's to use in dumb-ass integration
-    K = len(a_k)  # number of mixture components
-    N = len(Qs)  # number of data points
-    eyes = np.linspace(0., np.pi/2., J)  # grid of inclination angles [rad]
-    di = (eyes[1] - eyes[0])
-
-    # N,K,J
-    a_k = a_k[np.newaxis,:,np.newaxis]
-    v_k = v_k[np.newaxis,:,np.newaxis]
-    eyes = eyes[np.newaxis,np.newaxis,:]
-    Qs = Qs[:,np.newaxis,np.newaxis]
-    sigma_Qs = sigma_Qs[:,np.newaxis,np.newaxis]
-
-    ln_int = ln_integrand(Qs,v_k,sigma_Qs,eyes).reshape(N, J*K)
-    coeff = np.repeat(a_k*di/sigma_Qs/np.sqrt(2*np.pi), J, axis=2)
-    coeff = coeff.reshape(ln_int.shape)
-    ll = logsumexp(ln_int, b=coeff, axis=1)
-
-    return ll
-
-def ln_posterior(a_k, v_k, Q, sigma_Q):
-    lp = ln_prior(a_k)
-    if np.any(np.isinf(lp)):
-        return -np.inf
-
-    ll = ln_likelihood(a_k, v_k, Q, sigma_Q).sum()
-    if np.any(~np.isfinite(ll)):
-        return -np.inf
-
-    return lp + ll

### 2014-10-02 documents/letter/ms.tex
acknowledgements and shiii

@@
 
-We construct a statistical model to derive constraints on a parametric model --- parametrized by the vector $\bs{\theta}$\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} --- for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.
+We construct a statistical model to derive constraints on a parametric model, parametrized by the vector $\bs{\theta}$,\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.
 For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
@@
 
-\vspace{2em}
-\hrule
-
-To determine the individual system likelihoods, we first marginalize over $M_2$:
-
-\begin{equation}
-P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\infty} P(D |\mathbf{\Theta}, M_2) P	(M_2|\mathbf{\Theta})\ dM_2 
-\end{equation}
-
-where $A$ is a normalization constant. We further marginalize over the inclination angle, $i$:
-
-\begin{equation}
-P(D|\mathbf{\Theta}) = \frac{1}{A} \int_0^{\pi/2} \int_{M_{2,min}}^{\infty} P(D | \mathbf{\Theta}, M_2, i) P(M_2|\mathbf{\Theta}, i) P(i | \mathbf{\Theta})\ {\rm d}M_2\ {\rm d}i
-\end{equation}
-
-Since only a single value for $M_{2,min}$ is allowed for a given $M_1$, $M_2$, and $i$, $P(D | \mathbf{\Theta}, M_2, i)$ reduces to a delta function:
-
-\begin{equation}
-P(D | \mathbf{\Theta}, M_2, i) = \delta \left(M_{2,min} - f(M_1,M_2,i) \right)
-\end{equation}
-
-where $f(M_1,M_2,i)$ is the root of equation {\bf XXXXX}. Furthermore, the inclination angle is independent of other parameters:
-
-\begin{eqnarray}
-P(i | \mathbf{\Theta}) &=& P(i) \\
-  &=& {\rm sin}\ i \\
-  &=& \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2}
-\end{eqnarray}
-
-where in the last equation, we used equation {\bf XXX}. Combining equations {\bf XXX}, {\bf XXX}, and {\bf XXX} and evaluating the integral over $i$ we produce the following result:
-
-\begin{equation}
-P(D|\mathbf{\Theta}) = \frac{1}{A} \int_{M_{2,min}}^{\infty}  P(M_2|\mathbf{\Theta},i_{M_2}) \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2
-\end{equation}
-
-where $i_{M_2}$ is a function of $M_2$, determined from Equation {\bf XXX}.
-The final parameter left to be determined is the normalization constant, $A$.
-This parameter requires an additional integral, over all $M_{2,min}$:
-
-\begin{equation}
-A = \int_0^{\infty} \int_{M_{2,min}}^{\infty} P(M_2|\mathbf{\Theta}, i_{M_2}) \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2\ {\rm d}M_{2,min}
-\end{equation}
-
-Finally, $P(M_2|\mathbf{\Theta},i_{M_2})$ is our model.
-We choose to model the masses of the WD companions as a Gaussian, with an additional NS component.
-This model is independent of the inclination angle and can be expressed in the following way:
-
-\begin{eqnarray}
-P(M_2|\mathbf{\Theta},i) &=& P(M_2 | \mathbf{\Theta}) \\
-  &=& \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} + \mathcal{f}_{NS} \delta \left( M_2 - M_{NS} \right)
-\end{eqnarray}
-
-where $\mathcal{f}_{NS}$ represents the NS fraction in the model, and $\mathcal{N}(\mu , \sigma)$ represents a Gaussian with mean, $\mu$, and standard deviation, $\sigma$.
-The NS component is modeled by a delta function around $M_{NS}$ which we take to be $1.35 ~\Msun$.
-Combining this with equation {\bf XXX}, we can separate the integrand into a WD and a NS component:
-
-\begin{equation}
-P(D|\mathbf{\Theta}) = P_{WD} + P_{NS}
-\end{equation}
-
-where the WD component is:
-
-\begin{equation}
-P_{WD} = \frac{1}{A} \int_{M_{2,min}}^{\infty} \left[ \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} \right]  \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} {\rm d}M_2
-\end{equation}
-
-and the NS component is:
-
-\begin{equation}
-P_{NS} = \frac{1}{A} \mathcal{f}_{NS}\left( \frac{M_1 + M_{NS}}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_{NS}}
-\end{equation}
-
-The normalization constant can likewise be reduced into a WD and a NS component, with the integral over d$M_{2,min}$ performed separately on both:
-
-\begin{equation}
-A = A_{WD} + A_{NS}
-\end{equation}
-
-where the WD component is:
-
-\begin{equation}
-A_{WD} = \int_0^{\infty} \int_{M_{2,min}}^{\infty} \left[ \left( 1-\mathcal{f}_{NS} \right) \mathcal{N}(\mu , \sigma)|_{M_2} \right]  \left( \frac{M_1 + M_2}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2}\ {\rm d}M_2\ {\rm d}M_{2,min}
-\end{equation}
-
-and the NS component is:
-
-\begin{equation}
-A_{NS} = \int_0^{\infty} \mathcal{f}_{NS}\left( \frac{M_1 + M_{NS}}{M_1 + M_{2,min}} \right)^{2/3} \frac{M_{2,min}}{M_2} \delta \left( M_2 - M_{NS} \right) {\rm d}M_{2,min}
-\end{equation}
-
-which can be evaluated analytically, using integration by parts:
-
-\begin{equation}
-A_{NS} = 3 \left(M_1+M_{NS}\right)^{2/3} \left[  \frac{M_{2,min}}{M_{NS}} \left( M_1+M_{2,min} \right)^{1/3} - \frac{3}{4} \frac{ \left( M_1 + M_{2,min} \right)^{4/3} }{M_{NS}} \right] |_{M_{2,min}=0}^{M_{2,min}=M_{NS}}
-\end{equation}
-
-Using these equations, we can now calculate the likelihood of a given set of model parameters ($\mu$, $\sigma$, and $\mathcal{f}_{NS}$).
-In general, these integrals must be evaluated numerically.
-Furthermore, since each system has a different $M_1$ and $M_{2,min}$ and therefore must be calculated separately, these formulae become quite computationally expensive, particularly calculating the double integral in $A_{WD}$.
-
-It is also straightforward to determine, for a particular $\Theta$, the probability of any individual system being composed of a NS:
-
-\begin{equation}
-P(NS) = \frac{P_{NS}}{P_{WD} + P_{NS}}
-\end{equation}
-
-where $P_{NS}$ and $P_{WD}$ are calculated from equation {\bf XXX} and {\bf XXX}, respectively.
+[TODO: put in $p(M_2\given ...), description of models in separate subsection?]
 
@@
 \acknowledgements
+The authors wish to acknowledge David Hogg (NYU) for useful discussions, and the organizing committee of the \emph{AstroData Hack Week} (2014). 
 APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 

### 2014-10-02 documents/letter/ms.tex
experiments

@@
 \usepackage{amssymb,amsmath,amsbsy}
+\usepackage{booktabs}
 
@@
 \begin{equation}
-	\frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 \label{eq:massfunc}
+	m_f = \frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 \label{eq:massfunc}
 \end{equation}
@@
 From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
-\end{center}
-\end{figure}
+%\end{center}
+%\end{figure}
 
-\section{Methods (?)}
+\section{Methods}
 
-We construct a statistical model to derive constraints on a parametric model, parametrized by the vector $\bs{\theta}$,\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.
-For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
-We would like to find posterior constraints on the parameters, $\boldsymbol{\theta}$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
+We would like to find posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,
@@
 \end{align}
-where the bottom bound in the integral in Equation~\ref{eq:fullm2} is the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.
+where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.
 
-[TODO: put in $p(M_2\given ...), description of models in separate subsection?]
+\section{Experiments} \label{sec:experiments}
 
-In future work we will extend this analysis to incorporate uncertainties and non-detections.
+We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$.
+For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data.
+However, in tests below, we generate test data with a variety of mixture component forms.
+The likelihood with a Gaussian mixture model is
+\begin{align}
+	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\\
+	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
+	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}) \\
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})
+\end{align}
+where $\mathcal{N}$ is the normal distribution with mean $\mu$ and variance $\sigma^2$. In this work, we fix the mean and variance of the neutron star distribution to
+\begin{align}
+	\mu_{\rm NS} &= 1.4~\Msun\\
+	\sigma^2_{\rm NS} &= (0.2~\Msun)^2
+\end{align}
+given the uncertainties in neutron star mass, birth channels, and mass accretion scenarios \citep{refs} [TODO: Jeff, references].
+Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
 
-\section{Our model}
+We choose standard priors on these parameters.
+For the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$.
+We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.~\Msun$.
+We use a uniform distribution over the dimensionless neutron star fraction from $0-1$.
+The model parameters are summarized in Table~\ref{tbl:parameters}.
+
+\begin{table*}[ht]
+\begin{center}
+	\begin{tabular}{l c c l} \toprule
+		Parameter & Prior \\\toprule
+		$f_{\rm NS}$ & $\mathcal{U}(0, 1)$ \\ 
+		$\mu_{\rm WD}$ & $\mathcal{U}(0.2, 1.4)$ \\ 
+		$\sigma_{\rm WD}$ & $\frac{1}{\ln(40)\sigma}$ $(0.05 < \sigma < 2~\Msun)$ \\ 
+		$\mu_{\rm NS}$ & 1.4~$\Msun$ (fixed) \\ 
+		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) \\
+		\bottomrule
+		\end{tabular}
+	\caption{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}.
+$\mathcal{U}$ is the uniform distribution.
+There are 3 free parameters.
+\label{tbl:parameters}}
+\end{center}
+\end{table*}
+
+\subsection{Single Gaussian (white dwarf)}
+
+\subsection{Two Gaussians (white dwarf + neutron star)}
+
+\subsection{Uniform (white dwarf) + Gaussian (neutron star)}
+
+\hrule{4em}
 

### 2014-10-02 documents/letter/ms.tex
describing experiments

@@
 However, in tests below, we generate test data with a variety of mixture component forms.
+We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,1.4)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1,2)~\Msun$.
 The likelihood with a Gaussian mixture model is
@@
 	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
-	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}) \\
-	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})
+	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,(0.2 < M_2 < 1.4~\Msun) \\
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\,(1.4 < M_2 < 2~\Msun)
 \end{align}
-where $\mathcal{N}$ is the normal distribution with mean $\mu$ and variance $\sigma^2$. In this work, we fix the mean and variance of the neutron star distribution to
+where $\mathcal{N}$ is the (truncated, but normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
+In this work, we fix the mean and variance of the neutron star distribution to
 \begin{align}
 	\mu_{\rm NS} &= 1.4~\Msun\\
-	\sigma^2_{\rm NS} &= (0.2~\Msun)^2
+	\sigma^2_{\rm NS} &= (0.1~\Msun)^2
 \end{align}
@@
 
+To test the performance of this Gaussian mixture model, we apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
+These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $m_f$.
+We draw primary masses from a uniform distribution, $M_1 \sim \mathcal{U}(0.2,0.4)~\Msun$.
+We apply the same Gaussian mixture model to all test datasets to infer the parameters of the white dwarf mixture component and neutron star fraction.
+
+In each experiment below, we use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
+The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We run the walkers for an initial, burn-in period of 1000 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
+We then re-initialized the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
+We compute the autocorrelation time for each parameter to confirm they have converged.
+
 \subsection{Single Gaussian (white dwarf)}
+
+As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with mean, variance, and bounds
+\begin{align}
+	\mu_{\rm WD, true} &= 0.7~\Msun\\
+	\sigma^2_{\rm WD, true} &= (0.2~\Msun)^2\\
+	0.2 < M_2& < 1.4~\Msun.
+\end{align}
+The distribution of mock observations of the mass function, $m_f$, are shown by the top-left panel of Figure~\ref{}.
 
@@
 \hrule{4em}
-
-Maximizing the likelihood now requires a numerical technique to probe the parameter space.
-We have chosen to use a Markov Chain Monte Carlo (MCMC) technique.
-Because we only have three parameters, we can use a standard Metropolis-Hastings acceptance-rejection technique.
-Using this technique, we randomly generate new model parameters based on the old model parameters, using a proposal distribution, $K(\mathbf{\Theta '} | \mathbf{\Theta})$.
-So that the proposal distribution is symmetric ($K(\mathbf{\Theta '} | \mathbf{\Theta})$ = $K(\mathbf{\Theta} | \mathbf{\Theta '})$), we follow the standard prescription and adopt a Gaussian distribution for $K(\mathbf{\Theta '} | \mathbf{\Theta})$, centered on $\Theta$.
-After a "burn-in" of 500 steps, we use 10 separate chains to determine the posterior probability, $P(\mathbf{\Theta} | \vec{D})$.
-
-To test the performance of our model, we apply it to three separate sets of mock data, each with 100 systems.
-These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution then applying a randomly drawn inclination angle.
-We apply our model to the distribution of resulting $M_{2,min}$ and $M_1$ values, attempting to recover the initial model parameters.
 

### 2014-10-02 documents/letter/ms.tex
more words in experiments

@@
 
-\subsection{Single Gaussian (white dwarf)}
+\subsection{Single Gaussian (white dwarf)} \label{sec:exp1}
 
@@
 \end{align}
+This is equivalent to setting the neutron star fraction to $f_{\rm NS} = 0$.
 The distribution of mock observations of the mass function, $m_f$, are shown by the top-left panel of Figure~\ref{}.
+We use MCMC (see description above) to ...
 
-\subsection{Two Gaussians (white dwarf + neutron star)}
+\subsection{Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
+For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters
+\begin{align}
+	\mu_{\rm NS, true} &= 1.4~\Msun\\
+	\sigma^2_{\rm NS, true} &= (0.1~\Msun)^2\\
+	1.4 < M_2& < 2.~\Msun.
+\end{align}
+We set the neutron star fraction to $f_{\rm NS} = 0.1$.
+The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{}.
+We use MCMC (see description above) to ...
 
-\subsection{Uniform (white dwarf) + Gaussian (neutron star)}
+[TODO: We have also tried changing the mean and variance of the true neutron star distribution while keeping the fitting parameters fixed and found ...]
 
-\hrule{4em}
-
-Our first set of mock data, shown in the top three panels of Figure 2 is composed of a Gaussian distribution centered at $0.7~\Msun$, with a standard deviation of $0.2~\Msun$.
-We give these binaries random inclination angles.
-The distribution of the mock observations for $M_{2,min}$ are shown by the histogram in the left panel.
-The red line shows the theoretical distribution, determined by numerically evaluating the integral in Equation {\bf XXX}, substituting $\mathcal{N}(0.7,0.2)$ for $P(M_2|\mathbf{\Theta})$.
-We apply our model to the data and obtain the posterior distribution shown in the middle panel.
-Contours indicate 1, 2, and 3-$\sigma$ confidence levels.
-The overplotted "X" shows the input mean and standard deviation for our randomly selected sample.
-The right panel shows that the one dimensional posterior distribution for the NS probability is strongly peaked at zero.
-For this simple data set, our model correctly identifies the population mean, standard deviation, and NS probability.
-
-Our second set of mock data is drawn from the same distribution as the first (with $\mu = 0.7$ and $\sigma = 0.2$) except it includes 10 NS, each given a mass of $1.35~\Msun$.
-Comparing the analytic distribution in the top left panel with the middle left panel shows that adding a NS component most strongly affects the high end tail of the distribution.
-The sample of "observed" $M_{2,min}$ shows that only five of the ten NS have masses greater than $1.0~\Msun$; the other five NS companions have $M_{2,min}$ measurements indistinguishable from that of WD companions.
-The middle panel in Figure {\bf XXX} shows the posterior distribution for the mean and standard deviation of the sample.
-The NS component clearly skews the distribution toward larger distributions, however the true values (designated by the "X") are still within the 1-$\sigma$ confidence level.
-The ability of our model to correctly identify the NS fraction, shown in the right panel, is most interesting.
-The peak of the posterior distribution is centered at 10\%.
-{\bf Come up with confidence levels here.}
-
-The third set of mock data tests the ability of our model to match non-Gaussian distributions.
-Here, we generated a sample of WD companions from a flat mass distribution $M_{WD} = [0.3:1.1]~\Msun$, combined with a NS fraction of 10\%.
-The theoretical expectation for the distribution of $M_{2,min}$, shown by the red line in the bottom left panel, was produced by numerically integrating equation {\bf XXX}, where we substitute a flat distribution for $P(M_2 | \mathbf{\Theta},i)$:
-
-\begin{equation}
-P(M_2 | \mathbf{\Theta},i) = \left( 1 - \mathcal{f}_{NS} \right) \frac{1}{M_{WD,max} - M_{WD,min}} + \mathcal{f}_{NS} \delta(M_2 - M_{NS})
-\end{equation}
-
-where $M_{WD,min}=0.3~\Msun$ and $M_{WD,max} = 1.1~\Msun$.
-The histogram shows that this distribution results in a larger number of WDs with very low $M_{2,min}$.
-The resulting posterior distribution in $\mu$ and $\sigma$ is shown by the bottom middle panel.
-Since our model is attempting to derive a Gaussian mass distribution from an initially non-Gaussian distribution, the posterior is not as well formed as our previous two test cases.
-Furthermore, the resulting NS probability, shown in the bottom right panel of Figure {\bf XXX}, is not as well formed.
-This is because, on the one hand, the distribution of $M_{2,min}$ has a large component at very low masses, skewing the resulting $\mu$ distribution toward lower masses, with a larger NS fraction.
-On the other hand, the portion of the sample at large $M_{2,min}$ is pushing the distribution toward larger masses, with a smaller NS fraction.
-The competition between these two effects spreads the posterior distributions in all three of our model parameters.
-
-It is clear that our model can recover the initial distribution of companion masses and NS fraction with a fairly high degree of accuracy, when the population is well represented by a Gaussian.
-Our third test case shows that when our initial population significantly deviates from a Gaussian, our model is much more imprecise.
-However this uniform distribution, with a relatively low $M_{WD,min}$ of $0.3~\Msun$ and high $M_{WD,max}$ of $1.1~\Msun$ is a very difficult distribution to fit with a Gaussian because the high mass WDs can easily be confused with NSs and vice versa.
-Unfortunately, the posterior NS probability did not converge on a single value.
-Nevertheless, our model indicates that, despite the "wrong" choice of model, the NS fraction is non-negligible.
+\subsection{Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
+For a final test, we use the same neutron star component as in Section~\ref{sec:exp2}, but now generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$.
+We keep the neutron star fraction fixed to $f_{\rm NS}=0.1$.
+The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{}.
+We use MCMC (see description above) to ...
 

### 2014-10-04 documents/letter/ms.tex
Updated intro, added references

@@
 		              New York, NY 10027, USA}
-% \altaffiltext{\adrn}{To whom correspondence should be addressed: adrn@astro.columbia.edu}
 
@@
 
-%\keywords{
-%  cosmology: dark matter
-%  ---
-%  Galaxy: structure
-%  ---
-%  Galaxy: halo
-%}
-
-%\begin{figure*}[!h]
-%\begin{center}
-%\includegraphics[width=\textwidth]{PATH}
-%\caption{ CAPTION }\label{fig:FIGNAME}
-%\end{center}
-%\end{figure*}
-
 \section{Introduction}
 
-The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from the Data Release 7 (DR7) in the Sloan Digital Sky Survey (SDSS), containing some 20,000 confirmed WDs (Kleinman et al 2013).
-While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number (6\%) of low mass WDs was observed, with $M<0.4~\Msun$.
+The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from the Data Release 7 (DR7) in the Sloan Digital Sky Survey (SDSS), containing some 20,000 confirmed WDs \citet{kleinman13}.
+While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number (6\%) of low mass WDs (LMWD) was observed, with $M<0.4~\Msun$.
+In addition to SDSS, LMWDs have been observed in similar numbers elsewhere \citep[e.g.
+the Palomar Green Survey][]{liebert05}.
 
-These Low Mass WDs (LMWDs) comprise an astrophysically unique population.
-Except in special cases of extreme metallicity (Kilic et al 2007), the Galaxy is not old enough to produce WDs with mass $<0.5~\Msun$ through single star evolution.
-In their seminal work, Marsh, Dhillon, \& Duck (1995) discovered companions around five LMWDs, cementing the requirement that these objects be formed through binary evolution.
-In addition to SDSS, LMWDs have been observed in similar numbers in the Palomar Green Survey (Liebert et al 2005).
+Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce these LMWD through single star evolution.
+These objects are formed through dynamical interactions with another star, in which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
+After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a helium core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98}.
 
-Using a reduced proper motion selection criterion, the Extrememly Low Mass (ELM) WD Survey specifically searched for LMWDs in SDSS.
-After their initial investigation found 11 of 12 LMWDs had close binary companions (Brown et al.
-2010), further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity variations (Kilic et al 2011, 2012, Brown et al 2012, 2013).
+In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, cementing LMWDs as fruitful targets for close binary searches.
+Using a reduced proper motion selection criterion, the Extremely Low Mass (ELM) WD Survey specifically searched for LMWDs in SDSS using a photometric constraint combined with a reduced proper motion constraint.
+After their initial investigation found 11 of 12 LMWDs had close binary companions \citep{ELMI}, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity variations \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
-While the orbital periods and radial velocities indicated the companions were most likely WDs, it was realized that these LMWDs could have NS companions (van Leeuwen et al 2007).
-However this and other radio searches for pulsed emission were fruitless (Agueros et al 2009a, 2009b).
-X-ray observations provide more stringent limits on the presence of a NS, and searches using {\it XMM-Newton} and {\it Chandra} have all yielded non-detections.
+While the orbital periods and radial velocities indicated the companions were most likely WDs, it was realized that these LMWDs could have NS companions \citep{vLeeuwen07}.
+However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been fruitless \citet{agueros09a,agueros09b,kilic13}.
 Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars.
-Because of the resources required for these targeted observations, selecting the most likely candidates for multiwavelength follow-up is crucial.
+Since the orbital solutions provided by the ELM survey combined with the precision of radio data would overconstrain the system, finding even one system would be extraordinarily interesting.
+The NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses, allowing for an understanding of the binary evolution processes forming these systems \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
+The resources required for these targeted observations, selecting the most likely candidates for multiwavelength follow-up is crucial.
 We outline the standard technique below.
@@
 \begin{equation}
-	m_f = \frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 \label{eq:massfunc}
+	\frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 = m_f \label{eq:massfunc}
 \end{equation}
 
-The righthand side of this equation is the well-known mass function.
+The righthand side of this equation is the well-known mass function ($M_f$).
 $M_2$ is minimized for an edge-on orbit, with $i = 90^{\circ}$.
@@
 However, implicit in this calculation is that all companion masses are equally likely a priori.
-Clearly this is not the case as evidenced by e.g.
-SDSS (kleinman et al 2013) who show the WD mass distribution is strongly peaked around $0.6~\Msun$.
+Clearly this is not the case as evidenced by \citep{kleinman13} who show the WD mass distribution in SDSS is strongly peaked around $0.6~\Msun$.
 Including this as a prior on the companion mass does not improve the situation since it is unlikely that the mass distribution of single WDs and WDs in binaries is the same.
@@
 
-With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the population is large enough to be modeled.
+With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled.
 Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
-In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses (i.e.
-one Gaussian)?
-2.\ How many NSs are implied by the distribution of $M_{2,min}$'s?
-3.\ Can we determine the likelihood of any individual system including a NS companion, based on the most likely models?
+In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
+2.\ How many NSs does our simplistic model imply?
+3.\ Can we determine the improved likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
 4.\ Are the six systems without detected radial velocity variations consistent with the population as a whole, or are these a fundamentally separate population (i.e.
 single ELM WDs)?
-7.\ Can our model place limits on the space density of ELM WD binaries with NS companions?
+5.\ Can our model place limits on the space density of ELM WD binaries with NS companions?
 
@@
 
-%\begin{figure}[h!]
-%\begin{center}
-%\includegraphics[width=0.7\columnwidth]{figures/Porb_M1/Porb_M1.jpg}
-%\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[angle=90,width=0.7\columnwidth]{Porb_M1.eps}
+\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
 The three eclipsing systems, with known $M_2$ are shown by the filled circles.
@@
 From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
-%\end{center}
-%\end{figure}
+\end{center}
+\end{figure}
 
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{model_post.eps}
+\includegraphics[angle=90,width=1\columnwidth]{model_post.eps}
 \caption{Replace this text with your caption}
@@
 
-In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$).
+In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$) {\bf Cite something here}.
 These are taken into account in our model through equation {\bf XXX}.
@@
 
-We apply our model to the ELM WD data set, using 10 indepedent Markov chains, each run for 100,000 steps.
+We apply our model to the ELM WD data set, using 10 independent Markov chains, each run for 100,000 steps.
 The acceptance fraction is {\bf XXX}.
@@
 How does the companion mass distribution compare to the single WD mass distribution?
-Based on their population of $\sim$ 14,000 spectroscopically confirmed DA WDs in SDSS, Kleinman et al (2013) found that WDs are well approximated by a four component Gaussian mixture model.
+Based on their population of $\sim$ 14,000 spectroscopically confirmed DA WDs in SDSS, \citet{kleinman13} found that WDs are well approximated by a four component Gaussian mixture model.
 Their mixture model is dominated by two Gaussians with means $\sim0.6~\Msun$, containing over 75\% of all WDs.
@@
 The part of the distribution with a low $\mu$ and high $\sigma$ is indicative of a low mass WD component.
-A low mass component is expected from binary evolution theory; recent population synthesis work predicts more than half of all He WDs in DWDs will have He WD companions (Toonen et al 2012).
+A low mass component is expected from binary evolution theory; recent population synthesis work predicts more than half of all He WDs in DWDs will have He WD companions \citet{toonen12}.
 Our results here suggest that this is not the case, our posterior suggests a Gaussian distribution centered around $0.6~\Msun$, firmly in the mass range for CO WDs.
@@
 However, the top left panel in Figure {\bf XXX} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass tail of a Gaussian distribution.
-Furthermore, in their Gaussian mixture fit to the SDSS DA WD mass distribution, Kleinman et al (2013) found a high mass WD component extending above $1~\Msun$.
+Furthermore, in their Gaussian mixture fit to the SDSS DA WD mass distribution, \citet{kleinman13} found a high mass WD component extending above $1~\Msun$.
 Our single Gaussian model does not include this high mass component.
@@
 
-If we combine our result of a NS fraction of {\bf XXX} with the ELM WD space density as determined from the Palomar Green Survey: $4\times10^{-14}$pc$^{-3}$yr$^{-1}$ (Liebert et al 2005) {\bf Is there a more recent estimate?} we can get a space density of ELM WD + NS binaries.
+If we combine our result of a NS fraction of {\bf XXX} with the ELM WD space density as determined from the Palomar Green Survey: $4\times10^{-14}$pc$^{-3}$yr$^{-1}$ \cite{liebert05} {\bf Is there a more recent estimate?} we can get a space density of ELM WD + NS binaries.
 This suggests that there are {\bf XXX} such binaries within a few kpc of us.
@@
 \begin{center}
-\includegraphics[width=1\columnwidth]{ELM_post.eps}
+\includegraphics[angle=90,width=1\columnwidth]{ELM_post.eps}
 \caption{Replace this text with your caption}
@@
 
+\bibitem[Goodman~\&\ Weare(2010)]{goodman10}
+Goodman,~J. \& Weare,\ J.,
+2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
+
 \end{document}

### 2014-10-08 documents/letter/ms.tex

@@
 While the orbital periods and radial velocities indicated the companions were most likely WDs, it was realized that these LMWDs could have NS companions \citep{vLeeuwen07}.
-However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been fruitless \citet{agueros09a,agueros09b,kilic13}.
+However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been fruitless \citep{agueros09a,agueros09b,kilic13}.
 Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars.
@@
 \begin{equation}
-P({\rm NS}) = \int_{0^{\circ}}^{i_{\rm NS}} {\rm sin}\ i\ {\rm d}i
+P({\rm NS}) = \int_{0^{\circ}}^{i_{\rm NS}} {\rm sin}\ i\ {\rm d}i \label{eq:P_NS_approx}
 \end{equation}
@@
 \caption{Replace this text with your caption}
+\label{fig:tests}
 \end{center}
@@
 
-We apply our model to the ELM WD sample, however there are some slight differences worth mentioning in the population of ELM WDs and our test cases above.
-
-First, there are 55 systems with radial velocity measurements in the ELM sample, while the test cases above were each produced with 100 systems.
-Second, the masses of the primaries in our test cases were all $0.25~\Msun$, while in the ELM sample, the masses vary between 0.16 and $0.49~\Msun$.
-Also, the orbital periods of the systems in our test case were all 12 hours, while in the ELM sample the orbital periods vary between 12 minutes and just over a day.
-Since our model does not depend on the $M_2$ or $P_{\rm orb}$, its accuracy will not be affected.
-
-In the ELM sample three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$) {\bf Cite something here}.
+The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, providing precise measurements for $P_{\rm orb}$ and $K$.
+Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$.
+We use the spectroscopic solutions found in \citet{Gianninas14}.
+Furthermore, three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$).
 These are taken into account in our model through equation {\bf XXX}.
@@
 
-Finally, six systems in the ELM WD sample lack radial velocity variations down upper limits of $\sim$50 km s$^{-1}$.
-While some of these may be in binaries with radial velocities below the detection limit, they may also be single ELM WDs.
-In principle we could add to our model the possibility that each of these WDs is actually a single ELM WD.
+Finally, six systems in the ELM WD sample lack radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$.
+Some of these may be in binaries with radial velocities below the detection limit, due to low inclination angle, however studies by {\bf XXX} suggest there may also be a population of single LMWDs.
+Because of the uncertainty in their formation, we restrict these from our sample.
+
+%In principle we could add to our model the possibility that each of these WDs is actually a single ELM WD.
 Because this requires an additional six free parameters, one for each ELM WD without radial velocity variations, including these in our model becomes too computationally expensive.
-The result is that we can run our model on the 55 ELM systems with orbital solutions.
 
-We apply our model to the ELM WD data set, using 10 independent Markov chains, each run for 100,000 steps.
+%We apply our model to the ELM WD data set, using 10 independent Markov chains, each run for 100,000 steps.
 The acceptance fraction is {\bf XXX}.
@@
 
-The results of our model are shown in Figure {\bf XXX}.
-The first panel shows the distribution of $M_{2,min}$ for the data set.
-It is fairly similar to the distribution of $M_{2,min}$ in the test cases above, with a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$.
+The results of our model are shown in Figure \ref{fig:ELM_post}.
+The first panel shows the distribution of $M_{2,min}$ for the data set, showing a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$.
 The second panel shows the posterior distribution of $\mu$ and $\sigma$; contours indicate 1, 2, and 3-$\sigma$ confidence levels.
-The single high probability region indicates the models converged {\bf (Is this reasonable to say?)}.
 The best fit Gaussian model has a mean of 0.66 $\substack{+0.12 \\ -0.09}~\Msun$ and a standard deviation of 0.27$\substack{+0.09 \\ -0.07}~\Msun$.
@@
 Our model indicates a NS fraction of 1.4$\substack{+7.0 \\ -1.4}$\% at the 68\% confidence level, however there is a non-negligible tail toward higher NS probabilities.
-This is further indicated by the fourth panel in Figure {\bf XXX} which shows a histogram of NS probabilities for individual systems.
+This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows a histogram of NS probabilities for individual systems.
 These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system.
@@
 
-How does the companion mass distribution compare to the single WD mass distribution?
-Based on their population of $\sim$ 14,000 spectroscopically confirmed DA WDs in SDSS, \citet{kleinman13} found that WDs are well approximated by a four component Gaussian mixture model.
-Their mixture model is dominated by two Gaussians with means $\sim0.6~\Msun$, containing over 75\% of all WDs.
-Figure {\bf XXX} shows that the best fit Gaussian to our distribution of WD companion masses is also centered around $\sim0.6!\Msun$.
-However, our distribution is significantly wider ($\sigma \approx 0.3~\Msun$ compared with $\sigma \approx 0.1~\Msun$).
-This could be due to our simplistic assumption of a single Gaussian mass distribution.
-A more complicated model would include multiple Gaussians with varying weights, however adding only one more Gaussian component doubles the number of free parameters from three to six.
+Our results indicate that the best fit Gaussian for the companions to the ELM WD sample is very similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+However, our distribution is significantly wider ($\sigma \approx 0.3~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+Furthermore, population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs.
+The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep{toonen12}.
+Our method here could be extended to include multiple Gaussians with varying weights, however adding only one more Gaussian component doubles the number of free parameters from three to six.
 Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.
+In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models.
+It remains to be seen whether such a model can place such constraints with 55 measured systems.
+We plan to explore this in a future work, however it may require a larger data set.
 
 There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve.
-However, the posterior distribution in $\mu$ and $\sigma$ is well behaved, with a clear high probability region, similar to the posterior distributions for $\mu$ and $\sigma$ for our first two test cases shown in Figure {\bf XXX}.
+However, the posterior distribution in $\mu$ and $\sigma$ is well behaved, with a clear high probability region, similar to the posterior distributions for $\mu$ and $\sigma$ for our first two test cases shown in Figure \ref{fig:ELM_post}.
 The part of the distribution with a low $\mu$ and high $\sigma$ is indicative of a low mass WD component.
-A low mass component is expected from binary evolution theory; recent population synthesis work predicts more than half of all He WDs in DWDs will have He WD companions \citet{toonen12}.
-Our results here suggest that this is not the case, our posterior suggests a Gaussian distribution centered around $0.6~\Msun$, firmly in the mass range for CO WDs.
-This suggests that our results on the companion masses of the secondaries in these systems could constrain population synthesis models.
-We plan on exploring this in a future work.
 
 Systems with NS companions cannot be differentiated from those with WD companions through orbital period and ELM WD mass alone.
-Our model attempts to suggest a NS fraction for the population as a whole.
-This is an improvement over NS probabilities for individual companions calculated through equation {\bf XXX}.
-The third panel in Figure {\bf XXX} indicates a NS fraction of a few percent.
+Our model attempts to determine a NS fraction for the population as a whole.
+This is an improvement over NS probabilities for individual companions calculated through Equation \ref{P_NS_approx}.
+The third panel in Figure \ref{fig:ELM_post} indicates a NS fraction of a few percent.
 For 55 systems with observed radial velocity variations, this corresponds to a 1-2 systems with NS companions.
-However, the top left panel in Figure {\bf XXX} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass tail of a Gaussian distribution.
-Furthermore, in their Gaussian mixture fit to the SDSS DA WD mass distribution, \citet{kleinman13} found a high mass WD component extending above $1~\Msun$.
-Our single Gaussian model does not include this high mass component.
-It is not guaranteed that any ELM WDs have NS companions.
-Nevertheless, a quite firm result of our model is an upper limit on the fraction of ELM WDs with NS companions of {\bf XXXX}\%.
+However, the top left panel in Figure \ref{fig:tests} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass wing of our Gaussian distribution.
+It is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
+Nevertheless, our model indicates a NS fraction of {\bf XXX\%}, corresponding to zero to four systems.
 
@@
 
-The fourth panel in Figure {\bf XXX} shows  that only two systems have $P(NS)$ above 50\%: J0811$0225 (67\%) and J1741$6526 (53\%).
+The fourth panel in Figure {\bf XXX} shows  that only two systems have $P(NS)$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
 These systems are ideal candidates for searches for NS companions in radio and X-ray.
 Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio.
-However, all NS give off blackbody radiation as X-rays, and therefore X-ray follow-up provides a more stringent test on the potential for a NS companion.
-
-Non-detections? What does that imply about the existence of single ELM WDs?
+However, all NS give off blackbody radiation as X-rays, and X-ray follow-up provides a more stringent test on the potential for a NS companion.
 
@@
 \caption{Replace this text with your caption}
+\label{fig:ELM_post}
 \end{center}

### 2014-10-08 documents/letter/ms.tex
Updated .tex

@@
-%\documentclass{emulateapj}
-\documentclass[letterpaper,12pt,preprint]{aastex}
+\documentclass[apjl]{emulateapj}
+%\documentclass[letterpaper,12pt,preprint]{aastex}
 
@@
 \newcommand{\inverse}[1]{{#1}^{-1}}
-\newcommand{\Msun}{\mathrm{M}_\odot}
+\newcommand{\Msun}{\ifmmode {{\rm M}_{\odot}}\else M$_{\odot}$\fi}
 \newcommand{\bs}[1]{\boldsymbol{#1}}
@@
 mass of the bright star can be derived, only a lower limit can be placed
-on the mass of the unseen companion. However, since the probability of
+on the mass of the unseen companion. However since the probability of
 any inclination angle scales with sin $i$, for a large enough, unbiased
-population, the companion mass distribution can be deconvolved from the
-inclination angle. We develop a Bayesian technique to handle this
+sample, the companion mass distribution can be deconvolved from the
+inclination angle distribution. We develop a Bayesian technique to handle this
 deconvolution and place it within a Markov Chain Monte Carlo framework.
@@
 distribution as a Gaussian with a variable neutron star component, we
-find the companion population is well modeled by a mean of 0.65 and a
-standard deviation of 0.3 . Our model indicates a neutron star (NS)
+find the companion population is well modeled by a mean of 0.74 \Msun\ and a
+standard deviation of 0.26 \Msun. Our model indicates a neutron star (NS)
 fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
@@
 In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
-2.\ How many NSs does our simplistic model imply?
-3.\ Can we determine the improved likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
-4.\ Are the six systems without detected radial velocity variations consistent with the population as a whole, or are these a fundamentally separate population (i.e.
-single ELM WDs)?
-5.\ Can our model place limits on the space density of ELM WD binaries with NS companions?
+2.\ What is the rate of NS implied by our model?
+3.\ Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
 
@@
 \begin{center}
-\includegraphics[angle=90,width=0.7\columnwidth]{Porb_M1.eps}
+\includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
 \caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
@@
 \begin{align}
-	p(m_f \given M_1, M_2, i) &= \delta(m_f - f(M_1, M_2, i))\\
+	p(m_f \given M_1, M_2, i) &= \delta \left[m_f - f(M_1, M_2, i) \right]\\
 	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
@@
 \begin{align}
-    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta(m_f - f(M_1, M_2, i))~\sin i\\
-    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta(g(M_1,M_2,i))\label{eq:delta}
+    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta \left[m_f - f(M_1, M_2, i)\right]~\sin i\\
+    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
 \end{align}
@@
 	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\label{eq:fullm2}
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\label{eq:fullm2}
 \end{align}
@@
 \begin{align}
-	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\\
+	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\\
 	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
@@
 given the uncertainties in neutron star mass, birth channels, and mass accretion scenarios \citep{refs} [TODO: Jeff, references].
+
+The probability of any particular system having a NS companion $P({\rm NS})$ is then:
+
+\begin{equation}
+P({\rm NS}) = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, m_f, M_1) \label{eq:P_NS_full}
+\end{equation}
+
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-
 We choose standard priors on these parameters.
@@
 
-\begin{table*}[ht]
+\begin{table}[ht]
 \begin{center}
@@
 \end{center}
-\end{table*}
+\end{table}
 
@@
 We compute the autocorrelation time for each parameter to confirm they have converged.
+
+\begin{figure*}[h!]
+\begin{center}
+\includegraphics[angle=90,width=0.95\textwidth]{model_post.eps}
+\caption{Replace this text with your caption}
+\label{fig:tests}
+\end{center}
+\end{figure*}
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[angle=90,width=1\columnwidth]{model_post.eps}
-\caption{Replace this text with your caption}
-\label{fig:tests}
-\end{center}
-\end{figure}
-
 \section{Results}
@@
 Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$.
-We use the spectroscopic solutions found in \citet{Gianninas14}.
-Furthermore, three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$).
+We use the spectroscopic solutions found in \citet{gianninas14}.
+Three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$ \citep{kaplan14}, J0651$+$2844: $M_2=0.50~\Msun$ \citep{brown11b}, and J0751$-$0141: $M_2=0.97~\Msun$ \citep{kilic14}).
 These are taken into account in our model through equation {\bf XXX}.
-Since the inclination angle cannot vary, these systems will strongly affect the likelihood of any particular model.
-
-Finally, six systems in the ELM WD sample lack radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$.
-Some of these may be in binaries with radial velocities below the detection limit, due to low inclination angle, however studies by {\bf XXX} suggest there may also be a population of single LMWDs.
-Because of the uncertainty in their formation, we restrict these from our sample.
-
-%In principle we could add to our model the possibility that each of these WDs is actually a single ELM WD.
-Because this requires an additional six free parameters, one for each ELM WD without radial velocity variations, including these in our model becomes too computationally expensive.
-
-%We apply our model to the ELM WD data set, using 10 independent Markov chains, each run for 100,000 steps.
-The acceptance fraction is {\bf XXX}.
-We determine an autocorrelation length of {\bf XXX} steps, and correspondingly, only include every {\bf XXX} samples for our posterior distributions.
-{\bf Is there anything else we need to say about the applying the method to the data set?}
+Furthermore, six systems in the ELM WD sample show no radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$.
+Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
+These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit.
+Because of the uncertainties in their formation, we restrict these from our sample.
 
@@
 The first panel shows the distribution of $M_{2,min}$ for the data set, showing a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$.
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; contours indicate 1, 2, and 3-$\sigma$ confidence levels.
-The best fit Gaussian model has a mean of 0.66 $\substack{+0.12 \\ -0.09}~\Msun$ and a standard deviation of 0.27$\substack{+0.09 \\ -0.07}~\Msun$.
-The third panel shows the NS fraction is strongly peaked toward low probabilities.
-Our model indicates a NS fraction of 1.4$\substack{+7.0 \\ -1.4}$\% at the 68\% confidence level, however there is a non-negligible tail toward higher NS probabilities.
+The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
+The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
 This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows a histogram of NS probabilities for individual systems.
 These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system.
-Although a few systems have high probabilities, the distribution is strongly clustered below 20\%.
+Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
 
@@
 
+There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve.
+However, the posterior distribution in $\mu$ and $\sigma$ is strongly peaked, indicating that our naive Gaussian model is a good descriptor of the companion mass distribution.
 Our results indicate that the best fit Gaussian for the companions to the ELM WD sample is very similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-However, our distribution is significantly wider ($\sigma \approx 0.3~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
-Furthermore, population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs.
-The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep{toonen12}.
-Our method here could be extended to include multiple Gaussians with varying weights, however adding only one more Gaussian component doubles the number of free parameters from three to six.
+However, our distribution is significantly wider ($\sigma \approx 0.26~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+
+Population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs.
+The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see e.g., ][]{toonen12}.
+In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models.
+However adding only one more Gaussian component doubles the number of free parameters from three to six.
 Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.
-In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models.
-It remains to be seen whether such a model can place such constraints with 55 measured systems.
-We plan to explore this in a future work, however it may require a larger data set.
+It remains to be seen whether constraints can be placed with 55 measured systems using such a model.
+We plan to explore this in a future work, as well as a comparison with population synthesis models.
 
-There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve.
-However, the posterior distribution in $\mu$ and $\sigma$ is well behaved, with a clear high probability region, similar to the posterior distributions for $\mu$ and $\sigma$ for our first two test cases shown in Figure \ref{fig:ELM_post}.
-The part of the distribution with a low $\mu$ and high $\sigma$ is indicative of a low mass WD component.
+While we were writing this work, we became aware of recent high-speed photometric observations by \citet{hermes14}.
+Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
+For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
+Including these observations in our model is non-trivial and remains outside the scope of this work, however we plan to explore this in a future work.
 
-Systems with NS companions cannot be differentiated from those with WD companions through orbital period and ELM WD mass alone.
+\begin{figure*}[h!]
+\begin{center}
+\includegraphics[angle=90,width=0.95\textwidth]{ELM_post.eps}
+\caption{Replace this text with your caption}
+\label{fig:ELM_post}
+\end{center}
+\end{figure*}
+
+\subsection{NS Companion Probability}
+
+Systems with NS companions cannot be differentiated from those with WD companions through the mass function and LMWD mass alone.
 Our model attempts to determine a NS fraction for the population as a whole.
@@
 
-If we combine our result of a NS fraction of {\bf XXX} with the ELM WD space density as determined from the Palomar Green Survey: $4\times10^{-14}$pc$^{-3}$yr$^{-1}$ \cite{liebert05} {\bf Is there a more recent estimate?} we can get a space density of ELM WD + NS binaries.
-This suggests that there are {\bf XXX} such binaries within a few kpc of us.
+The probability of any particular ELM WD having a NS companion will vary depending on the NS fraction of the sample.
+This is not taken into account in Equation~\ref{eq:P_NS_approx}.
+When the NS mass is approximated as a delta function, this can be evaluated analytically, $P(NS)$ reduces to calculating $f_{\rm NS} \times h(M_{\rm NS},m_f,M_1)$:
+
+\begin{equation}
+P({\rm NS}) = f_{\rm NS} \frac{(M_1+M_{\rm NS})^{4/3}}{3m_f^{1/3}M_{\rm NS}\sqrt{M_{\rm NS}^2 - \left[m_f(M_1+M_{\rm NS})^2 \right]^{2/3}}} \label{eq:P_NS}
+\end{equation}
+
+This equation, approximating the NS population as a delta function around $M=1.4$~\Msun\ instead of the full integral around the Gaussian NS distribution defined in Equation~\ref{eq:P_NS_full}, is accurate to $\sim${\bf XXX}\%.
+We therefore suggest using this equation, combined with the $f_{\rm NS}$ determined here to provide future estimates for the probability of a NS companion to any LMWD system with a measured $m_f$ and $M_1$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% If we do this calculation, we need to think more about it
+% 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Combining our resulting NS fraction of {\bf 5\%} with the ELM WD space density of 40 kpc$^{-3}$ as determined by \citet{brown11a}, we can find a space density of ELM WD + NS binaries of 2 kpc$^{-3}$.
+If we assume an exponential disk with a scale height of 250 pc, this suggests that there are $\approx$  such binaries within a two kpc of us.
 Compare to the number of known MSP+LMWDs.
 
-The fourth panel in Figure {\bf XXX} shows  that only two systems have $P(NS)$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
+The fourth panel in Figure {\bf XXX} shows  that only two systems have $P({\rm NS})$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
 These systems are ideal candidates for searches for NS companions in radio and X-ray.
 Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio.
-However, all NS give off blackbody radiation as X-rays, and X-ray follow-up provides a more stringent test on the potential for a NS companion.
+All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion.
+Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all those sources have a low probability of hosting a NS companion.
+If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then stringent constraints can be placed on $f_{\rm NS}$.
+In principle, our model can also include the non-detection of radio and X-rays for those systems in which searches have already been performed.
+We leave this to a future work.
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[angle=90,width=1\columnwidth]{ELM_post.eps}
-\caption{Replace this text with your caption}
-\label{fig:ELM_post}
-\end{center}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  If we say anything about non-detections, we need to fix up the
+% math below. I suggest we wait and discuss these in a future work
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\subsection{Non-detections}
+%\subsection{Non-detections}
 
-Six systems in the ELM WD sample have non-detections of companions, down to an upper limit on the transverse velocity.
+%Six systems in the ELM WD sample have non-detections of companions, down to an upper limit on the transverse velocity.
 We include these systems in our model, too, as in principle they could be binary systems at with low inclination angles or long period orbits or both.
@@
 
-\begin{equation}
-P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} \int_0^{i_{\rm max}} P(M_2|\mathbf{\Theta})\ {\rm sin}\ i\ {\rm d}i\ {\rm d}M_2
-\end{equation}
+%\begin{equation}
+%P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} \int_0^{i_{\rm max}} P(M_2|\mathbf{\Theta})\ {\rm sin}\ i\ {\rm d}i\ {\rm d}M_2
+%\end{equation}
 
-which reduces to:
+%which reduces to:
 
-\begin{equation}
-P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} P(M_2|\mathbf{\Theta})\ \left( 1 - {\rm cos}\ i_{\rm max}\right)\ {\rm d}M_2
-\end{equation}
+%\begin{equation}
+%P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} P(M_2|\mathbf{\Theta})\ \left( 1 - {\rm cos}\ i_{\rm max}\right)\ {\rm d}M_2
+%\end{equation}
 
-where $i_{\rm max}$ is the smallest inclination angle that would still produce an unobservable binary, found by solving equation 1, using $K_{\rm max}$ for $K$.
+%where $i_{\rm max}$ is the smallest inclination angle that would still produce an unobservable binary, found by solving equation 1, using $K_{\rm max}$ for $K$.
 For an estimate of the expected fraction of unobserable binaries, we adopt $0.25~\Msun$ for $M_1$, an orbital period of 0.5 days, and a limiting velocity of 50 km s$^{-1}$.
@@
 \begin{enumerate}
-\item We have created a mathematical description to describe the companion mass distribution of a set of single-lined spectoscopic binaries. \\
-\item We have used that mathematical framework to build a Markov Chain Monte Carlo model and applied it to the set of WDs from the ELM survey. \\
-\item Our model suggests that the majority of ELM WDs have CO-core WDs. {\bf We should check this.} \\
+\item We have created a mathematical description to describe the companion mass distribution of a set of unbiased single-lined spectroscopic binaries. \\
+\item We have used that mathematical framework to build a Markov Chain Monte Carlo model and applied it to the set of WDs from the ELM WD survey. \\
+\item Our model suggests that the majority of ELM WDs have CO-core WDs.
+This is in contrast to predictions from population synthesis models.
+In a future work, we plan to quantify the ratio of He+He core WDs to He+CO core WDs.
+\\
 \item Our model indicates that the fraction of ELM WDs with NS companions is of order a few percent.
-Specifically, J0811$+$0225 and J1741$+$6526 have probabilities of having NS companions greater than 50\%.
+We provide an updated formula for determining the probability of any particular LMWD having a NS companion.
+We further identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion with {\bf XXX\%} and {\bf XXX\%}, respectively.
 \\
-\item This NS fraction implies an ELM+WD space density of {\bf XXX} which suggests there are {\bf XXX} systems withing a few kiloparsecs.
 \end{enumerate}
@@
 This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
-This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance. \\
+This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.
+These clusters includes support from New York State Empire State Development, Division of Science Technology and Innovation (NYSTAR) Contract C090171.
+\\
 

### 2014-10-09 documents/letter/ms.tex
properly

--- 2014-10-08 documents/letter/ms.tex
@@
 \end{align}
-where $\mathcal{N}$ is the (truncated, but normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
+where $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
 In this work, we fix the mean and variance of the neutron star distribution to

### 2014-10-09 documents/letter/ms.tex
Updated Equations

--- 2014-10-08 documents/letter/ms.tex
@@
 deconvolution and place it within a Markov Chain Monte Carlo framework.
-We then apply our method to the sample of 55 extremely low mass (ELM)
-WDs with radial velocity variations. Modeling the companion mass
+We then apply our method to the sample of 61 white dwarfs in the extremely low mass (ELM) white dwarf
+survey. Modeling the companion mass
 distribution as a Gaussian with a variable neutron star component, we
@@
 fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
+We make the posterior distribution from our simulations publicly available and provide a python script so that the probability of any future detected LMWD containing a NS can be determined.
 \end{abstract}
@@
 The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from the Data Release 7 (DR7) in the Sloan Digital Sky Survey (SDSS), containing some 20,000 confirmed WDs \citet{kleinman13}.
-While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number (6\%) of low mass WDs (LMWD) was observed, with $M<0.4~\Msun$.
+While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\approx$6\%) of low mass WDs (LMWD) is observed, with $M<0.4~\Msun$.
 In addition to SDSS, LMWDs have been observed in similar numbers elsewhere \citep[e.g.
@@
 These objects are formed through dynamical interactions with another star, in which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
-After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a helium core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98}.
+After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a He-core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98}.
 
-In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, cementing LMWDs as fruitful targets for close binary searches.
-Using a reduced proper motion selection criterion, the Extremely Low Mass (ELM) WD Survey specifically searched for LMWDs in SDSS using a photometric constraint combined with a reduced proper motion constraint.
-After their initial investigation found 11 of 12 LMWDs had close binary companions \citep{ELMI}, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity variations \citep{ELMII, ELMIII, ELMIV, ELMV}.
+In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations and cementing LMWDs as fruitful targets for binary searches.
+The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up using a photometric constraint combined with a reduced proper motion constraint \citep{ELMI}.
+After their initial investigation found 11 of 12 LMWDs had close binary companions, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
-While the orbital periods and radial velocities indicated the companions were most likely WDs, it was realized that these LMWDs could have NS companions \citep{vLeeuwen07}.
-However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been fruitless \citep{agueros09a,agueros09b,kilic13}.
-Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars.
-Since the orbital solutions provided by the ELM survey combined with the precision of radio data would overconstrain the system, finding even one system would be extraordinarily interesting.
-The NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses, allowing for an understanding of the binary evolution processes forming these systems \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-The resources required for these targeted observations, selecting the most likely candidates for multiwavelength follow-up is crucial.
-We outline the standard technique below.
+While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the uncertain inclination angle, these LMWDs could have NS companions \citep{vLeeuwen07}.
+However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
+Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
+Finding even one system would be extremely interesting; the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses, allowing for an understanding of the binary evolution processes forming these systems .
 
+Selecting the most likely candidates for multiwavelength follow-up is crucial.
 For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($P_{\rm orb}$), WD mass ($M_1$), and projected orbital velocity ($K$).
@@
 $M_2$ is minimized for an edge-on orbit, with $i = 90^{\circ}$.
-For any individual system, deriving the likelihood of a $M_2$ for that system ($P(M_2)$) involves solving Equation 1 for $M_2$ for different values for $i$, weighting the inclination angle by sin $i$.
+For any individual system, deriving the likelihood of a $M_2$ for that system ($P(M_2)$) involves solving Equation \ref{eq:massfunc} for $M_2$ for different values for $i$, weighting the inclination angle by sin $i$.
 A basic calculation for the probability that the companion to any individual system is a NS can therefore be calculated:
@@
 
-Where $i_{\rm NS}$ is the inclination angle from Equation 1 when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$.
+Where $i_{\rm NS}$ is the inclination angle from Equation \ref{eq:massfunc} when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$.
 However, implicit in this calculation is that all companion masses are equally likely a priori.
@@
 Including this as a prior on the companion mass does not improve the situation since it is unlikely that the mass distribution of single WDs and WDs in binaries is the same.
-Equation 2 should therefore be used only as an approximation for the NS probability of a companion.
+Equation \ref{eq:P_NS_approx} should therefore be used only as an approximation for the NS probability of a companion.
 
-With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled.
+With 55 of the 61 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled.
 Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
 In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
-2.\ What is the rate of NS implied by our model?
-3.\ Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
+2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
+3.\ What is the rate of NS implied by our model?
+4.\ Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
 
-In Section 2 we build the mathematical framework that we employ in our model described in Section 3.
+Toward these goals, we build the mathematical framework in Section 2 that we employ in our model described in Section 3.
 Section 4 shows the results of our model, while Section 5 gives a discussion.
@@
 where $p(m_f \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
-The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
-\begin{equation}
-    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
-\end{equation}
-where we neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles, $i$, are isotropically distributed
+The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and $M_2$,
+\begin{align}
+    p(m_f \given \bs{\theta}) &= \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2  \nonumber \\
+      & \qquad {} \times p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
+\end{align}
+We neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles are isotropically distributed
 \begin{align}
@@
 \begin{align}
-    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta \left[m_f - f(M_1, M_2, i)\right]~\sin i\\
-    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
+%    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di \nonumber \\
+%    & \qquad {} \times \delta \left[m_f - f(M_1, M_2, i)\right]~\sin i\\
+    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di  \nonumber \\
+    & \qquad {} \times ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
 \end{align}
@@
 \begin{equation}
-    \int dx~F(x)~\delta{(G(x)}) = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
+    \int dx~F(x)~\delta \left[ G(x) \right] = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
 \end{equation}
@@
 \begin{align}
-	i^* &= \sin^{-1}\alpha\\
-	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
-	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
-	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
+%	\sin i^* &= \alpha\\
+%	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
+	\sin i^* &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
+%	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
+%	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
+	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \sin^2 i^* \sqrt{1 - \sin^2 i^*}
 \end{align}
@@
 	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
-	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\label{eq:fullm2}
+%	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta}) h(M_2, m_f, M_1) \label{eq:fullm2}
 \end{align}
-where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.
+
+where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90$ in Equation~\ref{eq:massfunc} and solving for $M_2$), and
+
+\begin{equation}
+h(M_2, m_f, M_1) = \frac{(M_1+M_2)^{4/3}}{3\ m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}
+\end{equation}
 
@@
 \begin{align}
-	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\\
-	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
-	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,(0.2 < M_2 < 1.4~\Msun) \\
-	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\,(1.4 < M_2 < 2~\Msun)
+%	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\\
+%	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
+	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right] 
 \end{align}
-where $\mathcal{N}$ is the (truncated, but normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
+
+where
+
+\begin{equation}
+	p_{\rm WD} = \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,\left[ 0.2 < \frac{M_2}{\Msun} < 1.4 \right] 
+\end{equation}
+
+and
+
+\begin{equation}
+	p_{\rm NS} = \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\, \left[1.4 < \frac{M_2}{\Msun} < 2 \right].
+\end{equation}
+
+$\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
 In this work, we fix the mean and variance of the neutron star distribution to
@@
 \end{align}
-given the uncertainties in neutron star mass, birth channels, and mass accretion scenarios \citep{refs} [TODO: Jeff, references].
+based on indications that NSs with WD companions may be somewhat more massive than the canonical NS mass of 1.35 \Msun \citep{smedley14}.
 
-The probability of any particular system having a NS companion $P({\rm NS})$ is then:
+%The probability of any particular system having a NS companion $P({\rm NS})$ is then:
 
-\begin{equation}
-P({\rm NS}) = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, m_f, M_1) \label{eq:P_NS_full}
-\end{equation}
+%\begin{equation}
+%P({\rm NS}) = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, m_f, M_1) \label{eq:P_NS_full}
+%\end{equation}
 
@@
 
-\begin{table}[ht]
-\begin{center}
-	\begin{tabular}{l c c l} \toprule
-		Parameter & Prior \\\toprule
+\begin{deluxetable}{cc}
+	\tablecaption{Model Parameters \label{tbl:parameters}}
+
+	\tablehead{
+		\colhead{Parameter} &
+		\colhead{Prior}
+	}
+
+	\startdata
 		$f_{\rm NS}$ & $\mathcal{U}(0, 1)$ \\ 
@@
 		$\mu_{\rm NS}$ & 1.4~$\Msun$ (fixed) \\ 
-		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) \\
-		\bottomrule
-		\end{tabular}
-	\caption{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}.
+		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) 
+	\enddata
+
+	\tablecomments{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}.
 $\mathcal{U}$ is the uniform distribution.
 There are 3 free parameters.
-\label{tbl:parameters}}
-\end{center}
-\end{table}
+}\
+
+\end{deluxetable}
 
@@
 \begin{center}
-\includegraphics[angle=90,width=0.95\textwidth]{model_post.eps}
+\includegraphics[width=0.95\textwidth]{many-panel.pdf}
 \caption{Replace this text with your caption}
@@
 	\sigma^2_{\rm WD, true} &= (0.2~\Msun)^2\\
-	0.2 < M_2& < 1.4~\Msun.
+	0.2 < &\frac{M_2}{\Msun} < 1.4.
 \end{align}
 This is equivalent to setting the neutron star fraction to $f_{\rm NS} = 0$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the top-left panel of Figure~\ref{}.
+The distribution of mock observations of the mass function, $m_f$, are shown by the top-left panel of Figure~\ref{fig:tests}.
 We use MCMC (see description above) to ...
@@
 	\sigma^2_{\rm NS, true} &= (0.1~\Msun)^2\\
-	1.4 < M_2& < 2.~\Msun.
+	1.4 < & \frac{M_2}{\Msun} < 2.
 \end{align}
 We set the neutron star fraction to $f_{\rm NS} = 0.1$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{}.
+The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{fig:tests}.
 We use MCMC (see description above) to ...
@@
 We keep the neutron star fraction fixed to $f_{\rm NS}=0.1$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{}.
+The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{fig:tests}.
 We use MCMC (see description above) to ...
@@
 \begin{center}
-\includegraphics[angle=90,width=0.95\textwidth]{ELM_post.eps}
+\includegraphics[width=0.95\textwidth]{real-data.pdf}
 \caption{Replace this text with your caption}

### 2014-10-10 documents/letter/ms.tex
Updated results/conclusions

@@
 
-Toward these goals, we build the mathematical framework in Section 2 that we employ in our model described in Section 3.
-Section 4 shows the results of our model, while Section 5 gives a discussion.
-We conclude in Section 6.
+Toward these goals, we build the mathematical framework in Section 2 that we employ in our model described in Section 3. We give the results and discussion in Section 4, and conclude in Section 5.
 
@@
 
-\section{Experiments} \label{sec:experiments}
+\section{Our Model} \label{sec:experiments}
 
@@
 
+In our model, we use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
+The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We run the walkers for an initial, burn-in period of 1000 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
+We then re-initialized the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
+We compute the autocorrelation time for each parameter to confirm they have converged.
+
+\subsection{Test Cases}
 To test the performance of this Gaussian mixture model, we apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
@@
 We apply the same Gaussian mixture model to all test datasets to infer the parameters of the white dwarf mixture component and neutron star fraction.
-
-In each experiment below, we use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
-The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
-We run the walkers for an initial, burn-in period of 1000 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
-We then re-initialized the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
-We compute the autocorrelation time for each parameter to confirm they have converged.
 
@@
 
-\subsection{Single Gaussian (white dwarf)} \label{sec:exp1}
+\subsubsection{Test 1: Single Gaussian (white dwarf)} \label{sec:exp1}
 
@@
 
-\subsection{Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
+\subsubsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
 For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters
@@
 
-\subsection{Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
+\subsubsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
 For a final test, we use the same neutron star component as in Section~\ref{sec:exp2}, but now generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$.
@@
 
-\section{Results}
+\subsection{The ELM Sample}
 
@@
 Three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$ \citep{kaplan14}, J0651$+$2844: $M_2=0.50~\Msun$ \citep{brown11b}, and J0751$-$0141: $M_2=0.97~\Msun$ \citep{kilic14}).
-These are taken into account in our model through equation {\bf XXX}.
-Furthermore, six systems in the ELM WD sample show no radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$.
+For these systems, our marginal likelihood reduces to:
+
+\begin{equation}
+p(m_f \given \theta) = (1-f_{\rm NS}) \mathcal{N}(M_2^* \given \mu_{\rm WD}, \sigma^2_{\rm WD})
+\end{equation}
+
+where $M_2^*$ is the mass of the WD companion in these three systems.
+
+Furthermore, six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
 Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
 These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit.
-Because of the uncertainties in their formation, we restrict these from our sample.
-
-The results of our model are shown in Figure \ref{fig:ELM_post}.
-The first panel shows the distribution of $M_{2,min}$ for the data set, showing a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$.
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
-The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
-This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows a histogram of NS probabilities for individual systems.
-These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system.
-Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
-
-\section{Discussion}
-
-There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve.
-However, the posterior distribution in $\mu$ and $\sigma$ is strongly peaked, indicating that our naive Gaussian model is a good descriptor of the companion mass distribution.
-Our results indicate that the best fit Gaussian for the companions to the ELM WD sample is very similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-However, our distribution is significantly wider ($\sigma \approx 0.26~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
-
-Population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs.
-The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see e.g., ][]{toonen12}.
-In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models.
-However adding only one more Gaussian component doubles the number of free parameters from three to six.
-Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.
-It remains to be seen whether constraints can be placed with 55 measured systems using such a model.
-We plan to explore this in a future work, as well as a comparison with population synthesis models.
-
-While we were writing this work, we became aware of recent high-speed photometric observations by \citet{hermes14}.
-Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
-For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
-Including these observations in our model is non-trivial and remains outside the scope of this work, however we plan to explore this in a future work.
+Because of the uncertainties in their formation, we remove these from our analysis.
 
@@
 \includegraphics[width=0.95\textwidth]{real-data.pdf}
-\caption{Replace this text with your caption}
+\caption{The posteriors for our model applied to the ELM WDs.
+The first panel shows the distribution of $M_2$ for the data set.
+The black line gives the maximum a posteriori value, while the fainter lines show a set of randomly selected realizations from our model.
+The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
+The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
+This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows the relation between $M_f$ and $P({\rm NS})$ for individual systems.
+}
 \label{fig:ELM_post}
@@
 
-\subsection{NS Companion Probability}
+\section{Results and Discussion}
 
-Systems with NS companions cannot be differentiated from those with WD companions through the mass function and LMWD mass alone.
-Our model attempts to determine a NS fraction for the population as a whole.
-This is an improvement over NS probabilities for individual companions calculated through Equation \ref{P_NS_approx}.
-The third panel in Figure \ref{fig:ELM_post} indicates a NS fraction of a few percent.
-For 55 systems with observed radial velocity variations, this corresponds to a 1-2 systems with NS companions.
-However, the top left panel in Figure \ref{fig:tests} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass wing of our Gaussian distribution.
-It is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
-Nevertheless, our model indicates a NS fraction of {\bf XXX\%}, corresponding to zero to four systems.
+The results of our model are shown in Figure \ref{fig:ELM_post}.
+The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
+While the well-defined peak in the posterior distribution demonstrates convergence of the model the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
+However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+Our distribution is significantly wider ($\sigma \approx 0.26~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+
+Our results are independent of astrophysical expectations since they do not include any priors on $\mu$ and $\sigma$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and 1.4 \Msun (based on the Chandrasekhar mass).
+In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWD, composed of CO and He core WDs \citep{han98}.
+The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in e.g., ][]{toonen12}.
+
+Our model could be expanded to include a two Gaussian model one for each WD population.
+The ratio of these populations could be determined, and potentially place an important constraint on population synthesis models.
+However adding only one more Gaussian component doubles the number of free parameters from three to six.
+Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.
+It remains to be seen whether constraints can be placed with 55 measured systems using such a model.
+
+The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
+Our model does indicate an upper limit to the NS fraction of {\bf XXX\%} at the 95\% confidence level.
+For 55 systems with observed radial velocity variations, this corresponds to a {\bf 0-4?} systems with NS companions.
+These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $P({\rm NS})$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
+With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P({\rm NS})$ of $\substack{+4 \\ -2}\%$.
+
+Since our results are still consistent with a 0\% NS fraction, it is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
+However the fourth panel in Figure \ref{fig:ELM_post} indicates which ELM WDs have the highest probability of hosting NS companions.
+Here, we show the relation between $m_f$ and $P({\rm NS})$ for individual systems.
+This panel shows that $P({\rm NS})$ only starts to significantly deviate from zero for $m_f\approx0.6 \Msun$ Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
+
+The two systems with $P({\rm NS})$ above 10\% are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
+These systems are ideal candidates for searches for NS companions in radio and X-ray.
+Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable in radio \citep{vLeeuwen07}.
+All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
+Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all those sources have a low probability of hosting a NS companion.
+If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
+In a future work, we plan to combine our model results here with radio and x-ray non-detections, placing more stringent constraints on $P({\rm NS})$.
+
+It is worth noting that the fourth panels in our test cases in Figure~\ref{fig:tests} shows that our model is fairly good at identifying those systems most likely to host NS's.
+However it also shows that roughly half of the LMWDs with NS companions may appear with a deceptively low $f_{\rm NS}$.
+Systems with NS companions cannot all be differentiated from those with WD companions through the mass function and LMWD mass alone.
+Therefore {\it any} LMWD could host a NS companion.
 
@@
 This is not taken into account in Equation~\ref{eq:P_NS_approx}.
-When the NS mass is approximated as a delta function, this can be evaluated analytically, $P(NS)$ reduces to calculating $f_{\rm NS} \times h(M_{\rm NS},m_f,M_1)$:
+{\bf TEXT ON USING PYTHON SCRIPT FOR DETERMINING P-NS FOR FUTURE DISCOVERED LMWDs.}
 
-\begin{equation}
-P({\rm NS}) = f_{\rm NS} \frac{(M_1+M_{\rm NS})^{4/3}}{3m_f^{1/3}M_{\rm NS}\sqrt{M_{\rm NS}^2 - \left[m_f(M_1+M_{\rm NS})^2 \right]^{2/3}}} \label{eq:P_NS}
-\end{equation}
-
-This equation, approximating the NS population as a delta function around $M=1.4$~\Msun\ instead of the full integral around the Gaussian NS distribution defined in Equation~\ref{eq:P_NS_full}, is accurate to $\sim${\bf XXX}\%.
-We therefore suggest using this equation, combined with the $f_{\rm NS}$ determined here to provide future estimates for the probability of a NS companion to any LMWD system with a measured $m_f$ and $M_1$.
+Recently, high-speed photometric observations by \citet{hermes14}.
+Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
+For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
+Including these observations in our model is non-trivial and remains outside the scope of this work, however we plan to explore this in a future work.
 
@@
 Compare to the number of known MSP+LMWDs.
-
-The fourth panel in Figure {\bf XXX} shows  that only two systems have $P({\rm NS})$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
-These systems are ideal candidates for searches for NS companions in radio and X-ray.
-Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio.
-All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion.
-Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all those sources have a low probability of hosting a NS companion.
-If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then stringent constraints can be placed on $f_{\rm NS}$.
-In principle, our model can also include the non-detection of radio and X-rays for those systems in which searches have already been performed.
-We leave this to a future work.
 

### 2014-10-11 documents/letter/ms.tex

@@
 \newcommand{\bs}[1]{\boldsymbol{#1}}
+\newcommand{\degree}{^{\circ}}
 
@@
 The righthand side of this equation is the well-known mass function ($M_f$).
-$M_2$ is minimized for an edge-on orbit, with $i = 90^{\circ}$.
+$M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
 For any individual system, deriving the likelihood of a $M_2$ for that system ($P(M_2)$) involves solving Equation \ref{eq:massfunc} for $M_2$ for different values for $i$, weighting the inclination angle by sin $i$.
@@
 
-Where $i_{\rm NS}$ is the inclination angle from Equation \ref{eq:massfunc} when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$.
+Where $i_{\rm NS}$ is the inclination angle from Equation \ref{eq:massfunc} when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$ \citep{thorsett99}.
 However, implicit in this calculation is that all companion masses are equally likely a priori.
@@
 Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
-In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
+In this work we develop a Bayesian model to determine the mass distribution of companions to ELM WDs.
+Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries.
+We focus on several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
@@
 
-Toward these goals, we build the mathematical framework in Section 2 that we employ in our model described in Section 3. We give the results and discussion in Section 4, and conclude in Section 5.
+To answer these questions, we build the mathematical framework in Section 2 that we employ in our model described in Section 3.
+We give the results and discussion in Section 4, and conclude in Section 5.
 
@@
 
-where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90$ in Equation~\ref{eq:massfunc} and solving for $M_2$), and
+where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90\degree$ in Equation~\ref{eq:massfunc} and solving for $M_2$), and
 
@@
 \end{align}
-based on indications that NSs with WD companions may be somewhat more massive than the canonical NS mass of 1.35 \Msun \citep{smedley14}.
+based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun \citep{kiziltan13,smedley14}.
 
@@
 
-\subsection{Test Cases}
+\subsection{Test Cases} \label{sec:tests}
 To test the performance of this Gaussian mixture model, we apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
@@
 \includegraphics[width=0.95\textwidth]{many-panel.pdf}
-\caption{Replace this text with your caption}
+\caption{The model results of our three tests described in Section~\ref{sec:tests}.
+The left-most panel shows a histogram of the $M_2$ drawn from each of our test distributions.
+Overplotted as a solid line is posterior distribution using the maximum a posteriori parameter values, resulting from our model.
+The second panel shows the posterior distributions for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The dashed lines in the top two panels show the true values that the sample systems were drawn from.
+Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
+The third panel shows the convolved posterior histogram for $f_{\rm NS}$, with the dashed lines in the bottom two panels showing the true value of 10\%.
+Finally, the rightmost panels show the NS probability for individual systems as a function of $m_f$.
+The error bars in $P_{\rm NS}$ enclose the interquartile range.}
 \label{fig:tests}

### 2014-10-11 documents/letter/ms.tex
Updated .tex

@@
-\documentclass[apjl]{emulateapj}
-%\documentclass[letterpaper,12pt,preprint]{aastex}
+%\documentclass[apjl]{emulateapj}
+\documentclass[letterpaper,12pt,preprint]{aastex}
 
@@
 distribution as a Gaussian with a variable neutron star component, we
-find the companion population is well modeled by a mean of 0.74 \Msun\ and a
-standard deviation of 0.26 \Msun. Our model indicates a neutron star (NS)
-fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
+find the companion population is well modeled by a mean of {\bf 0.74} \Msun\ and a
+standard deviation of {\bf 0.26} \Msun. Our model indicates a neutron star (NS)
+fraction of {\bf 1.4$\substack{+7.0 \\ -1.4}$\%}.
 We make the posterior distribution from our simulations publicly available and provide a python script so that the probability of any future detected LMWD containing a NS can be determined.
@@
 %	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
-	\sin i^* &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
+	\sin i^* &= \frac{ \left[m_f(M_1+M_2)^2 \right]^{1/3}}{M_2}\\
 %	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
@@
 %	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta}) h(M_2, m_f, M_1) \label{eq:fullm2}
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, m_f, M_1) \label{eq:fullm2}
 \end{align}
@@
 For the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$.
-We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.~\Msun$.
+We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.0~\Msun$.
 We use a uniform distribution over the dimensionless neutron star fraction from $0-1$.
@@
 The results of our model are shown in Figure \ref{fig:ELM_post}.
-The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
-While the well-defined peak in the posterior distribution demonstrates convergence of the model the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
+The maximum a posteriori Gaussian model has a mean of {\bf 0.74} \Msun\ and a standard deviation of {\bf 0.26} \Msun.
+While the well-defined peak in the posterior distribution demonstrates convergence of the model, the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
 However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-Our distribution is significantly wider ($\sigma \approx 0.26~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
 
@@
 Our model could be expanded to include a two Gaussian model one for each WD population.
-The ratio of these populations could be determined, and potentially place an important constraint on population synthesis models.
+The ratio of these populations could potentially place an important constraint on population synthesis models.
 However adding only one more Gaussian component doubles the number of free parameters from three to six.
@@
 These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $P({\rm NS})$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
-With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P({\rm NS})$ of $\substack{+4 \\ -2}\%$.
+With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P({\rm NS})$ of $10\substack{+4 \\ -2}\%$.
 
@@
 Here, we show the relation between $m_f$ and $P({\rm NS})$ for individual systems.
-This panel shows that $P({\rm NS})$ only starts to significantly deviate from zero for $m_f\approx0.6 \Msun$ Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
+This panel shows that $P({\rm NS})$ only starts to significantly deviate from zero for {\bf $m_f\approx0.6 \Msun$} Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
 
-The two systems with $P({\rm NS})$ above 10\% are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
+The two systems with $P({\rm NS})$ above {\bf 10\%} are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
 These systems are ideal candidates for searches for NS companions in radio and X-ray.
@@
 Systems with NS companions cannot all be differentiated from those with WD companions through the mass function and LMWD mass alone.
-Therefore {\it any} LMWD could host a NS companion.
+Therefore {\it any} LMWD could host a NS companion, and is a valuable target for radio and X-ray follow-up observations.
 

### 2014-10-12 documents/letter/ms.tex
oops figures back in

@@
 \newcommand{\degree}{^{\circ}}
+\newcommand{\eqn}{Equation~}
+
+% Symbols
+\newcommand{\period}{T_{\rm orb}}
+\newcommand{\mf}{M_f}
+\newcommand{\wdupper}{1.44}
 
@@
 
-\title{The Companion Mass Distribution to the ELM WD Sample}
+\title{The Companion Mass Distribution of extremely low-mass white dwarfs}
 \author{Jeff Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}
@@
 \begin{abstract}
-Determining component masses of single-line spectroscopic binary stars
-is impossible because of the unknown inclination angle. Even when the
-mass of the bright star can be derived, only a lower limit can be placed
-on the mass of the unseen companion. However since the probability of
-any inclination angle scales with sin $i$, for a large enough, unbiased
-sample, the companion mass distribution can be deconvolved from the
-inclination angle distribution. We develop a Bayesian technique to handle this
-deconvolution and place it within a Markov Chain Monte Carlo framework.
-We then apply our method to the sample of 61 white dwarfs in the extremely low mass (ELM) white dwarf
-survey. Modeling the companion mass
-distribution as a Gaussian with a variable neutron star component, we
-find the companion population is well modeled by a mean of {\bf 0.74} \Msun\ and a
-standard deviation of {\bf 0.26} \Msun. Our model indicates a neutron star (NS)
-fraction of {\bf 1.4$\substack{+7.0 \\ -1.4}$\%}.
-We make the posterior distribution from our simulations publicly available and provide a python script so that the probability of any future detected LMWD containing a NS can be determined.
+Measuring the masses of companions to single-line spectroscopic binary stars
+is (in general) not possible because of the unknown orbital plane inclination angles. 
+Even when the mass of the visible star can be measured, only a lower limit can be placed
+on the mass of the unseen companion. However, since the systems should be isotropically
+distributed in the inclination angle, for a large enough, unbiased sample, the 
+companion mass distribution can be deconvolved from the distributions of observables.
+In this work, we construct a hierarchical probabilistic model to infer properties of unseen 
+companion stars given kinematic measurements of the primary. We use a mixture of 
+(two) Gaussians to model the true companion mass distribution, meant to represent 
+populations of white dwarfs (WD) and neutron stars (NS). We run this model on mock data generated
+both with and without the same functional form as the fitting model in order to test the
+robustness of our inferences. We then apply our model to 55 of the 61 white dwarfs in 
+the extremely low mass (ELM) WD survey. We find maximum a posteriori (MAP) parameters for
+the WD companion population of $\mu_{\rm WD} = 0.73~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
+with a NS fraction consistent with zero, $f_{\rm NS} = 0$. However, the marginal posterior 
+distribution over NS fraction has a significant tail up to $f_{\rm NS} \sim 0.12$.
+We make samples from the posterior distribution publicly available and provide a  
+script for computing the probability that a ... in the context of our model.
 \end{abstract}
@@
 
-The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from the Data Release 7 (DR7) in the Sloan Digital Sky Survey (SDSS), containing some 20,000 confirmed WDs \citet{kleinman13}.
-While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\approx$6\%) of low mass WDs (LMWD) is observed, with $M<0.4~\Msun$.
-In addition to SDSS, LMWDs have been observed in similar numbers elsewhere \citep[e.g.
-the Palomar Green Survey][]{liebert05}.
+The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from Data Release 7 (DR7) of the Sloan Digital Sky Survey (SDSS), which contains $\sim$20,000 confirmed WDs \citep{kleinman13}.
+While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\sim$6\%) of low mass WDs (LMWD) is observed with $M<0.4~\Msun$.
+In addition to SDSS, LMWDs have been observed in similar numbers elsewhere \citep[e.g., the Palomar Green Survey;][]{liebert05}.
 
@@
 In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations and cementing LMWDs as fruitful targets for binary searches.
-The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up using a photometric constraint combined with a reduced proper motion constraint \citep{ELMI}.
+The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up using combined constraints on photometry and reduced proper motions \citep{ELMI}.
 After their initial investigation found 11 of 12 LMWDs had close binary companions, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
-While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the uncertain inclination angle, these LMWDs could have NS companions \citep{vLeeuwen07}.
-However this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
+While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could have NS companions \citep{vLeeuwen07}.
+However, this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
 Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-Finding even one system would be extremely interesting; the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses, allowing for an understanding of the binary evolution processes forming these systems .
+Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems .
 
 Selecting the most likely candidates for multiwavelength follow-up is crucial.
-For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($P_{\rm orb}$), WD mass ($M_1$), and projected orbital velocity ($K$).
+For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($\period$), WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
 Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:
+\begin{equation}
+	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3 = \mf \label{eq:massfunc}
+\end{equation}
+The righthand side of this equation is the well-known mass function ($\mf$). $M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
 
-\begin{equation}
-	\frac{M_2^3}{\left(M_1+M_2\right)^2} {\rm sin}^3 i = \frac{P_{\rm orb}}{2\pi G} K^3 = m_f \label{eq:massfunc}
-\end{equation}
-
-The righthand side of this equation is the well-known mass function ($M_f$).
-$M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
-For any individual system, deriving the likelihood of a $M_2$ for that system ($P(M_2)$) involves solving Equation \ref{eq:massfunc} for $M_2$ for different values for $i$, weighting the inclination angle by sin $i$.
-A basic calculation for the probability that the companion to any individual system is a NS can therefore be calculated:
-
-\begin{equation}
-P({\rm NS}) = \int_{0^{\circ}}^{i_{\rm NS}} {\rm sin}\ i\ {\rm d}i \label{eq:P_NS_approx}
-\end{equation}
-
-Where $i_{\rm NS}$ is the inclination angle from Equation \ref{eq:massfunc} when $M_2$ is the mass of a NS, typically $\approx1.35~\Msun$ \citep{thorsett99}.
-However, implicit in this calculation is that all companion masses are equally likely a priori.
-Clearly this is not the case as evidenced by \citep{kleinman13} who show the WD mass distribution in SDSS is strongly peaked around $0.6~\Msun$.
-Including this as a prior on the companion mass does not improve the situation since it is unlikely that the mass distribution of single WDs and WDs in binaries is the same.
-Equation \ref{eq:P_NS_approx} should therefore be used only as an approximation for the NS probability of a companion.
-
-With 55 of the 61 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled.
-Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
-In this work we develop a Bayesian model to determine the mass distribution of companions to ELM WDs.
+55 of the 61 systems have precise $M_1$, $\period$, and $K$ measured; we refer to this as the ELM sample.
+Since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
+In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries.
@@
 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
-3.\ What is the rate of NS implied by our model?
-4.\ Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
+3.\ What is the rate of NS-LMWD binaries implied by our model?
+4.\ {\bf [Jeff: I propose nixing this question...
+]} Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
 
@@
 \includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
-\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample.
+\caption{The $\period$ - $M_1$ distribution of the ELM WD sample.
 The three eclipsing systems, with known $M_2$ are shown by the filled circles.
@@
 Triangles indicate the positions of the known WD-NS binaries.
-From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
+From $\period$ and $M_1$ alone, the two populations are indistinguishable.}
 \end{center}
@@
 
-We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}).
-We would like to find posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
+We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,
 \begin{equation}
-    p(\bs{\theta} \given m_f) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
+    p(\bs{\theta} \given \mf) = \frac{1}{\mathcal{Z}}~p(\mf \given \bs{\theta})~p(\bs{\theta}).
 \end{equation}
-where $p(m_f \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
-The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and $M_2$,
+where $p(\mf \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
+The marginal likelihood, $p(\mf \given \bs{\theta})$, involves integrals over the latent variables $i$ and $M_2$,
 \begin{align}
-    p(m_f \given \bs{\theta}) &= \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2  \nonumber \\
-      & \qquad {} \times p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
+    p(\mf \given \bs{\theta}) &= \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2  \nonumber \\
+      & \qquad {} \times p(\mf \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
 \end{align}
-We neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles are isotropically distributed
+We neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles are isotropically distributed
 \begin{align}
-	p(m_f \given M_1, M_2, i) &= \delta \left[m_f - f(M_1, M_2, i) \right]\\
+	p(\mf \given M_1, M_2, i) &= \delta \left[\mf - f(M_1, M_2, i) \right]\\
 	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
@@
 \begin{align}
-%    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di \nonumber \\
-%    & \qquad {} \times \delta \left[m_f - f(M_1, M_2, i)\right]~\sin i\\
-    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di  \nonumber \\
+%    p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di \nonumber \\
+%    & \qquad {} \times \delta \left[\mf - f(M_1, M_2, i)\right]~\sin i\\
+    p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di  \nonumber \\
     & \qquad {} \times ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
@@
 \begin{equation}
-	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - m_f.
+	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - \mf.
 \end{equation}
@@
 \end{equation}
-where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in Equation~\ref{eq:delta} are 
+where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in \eqn\ref{eq:delta} are 
 \begin{align}
 %	\sin i^* &= \alpha\\
-%	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
-	\sin i^* &= \frac{ \left[m_f(M_1+M_2)^2 \right]^{1/3}}{M_2}\\
+%	\alpha &= \frac{(\mf(M_1+M_2)^2)^{1/3}}{M_2}\\
+	\sin i^* &= \frac{ \left[\mf(M_1+M_2)^2 \right]^{1/3}}{M_2}\\
 %	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
@@
 \begin{align}
-	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
+	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\sin i^* \left(\frac{\partial g}{\partial i}\bigg\rvert_{i^*}\right)^{-1}\\
 %	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, m_f, M_1) \label{eq:fullm2}
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, \mf, M_1) \label{eq:fullm2}
 \end{align}
 
-where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90\degree$ in Equation~\ref{eq:massfunc} and solving for $M_2$), and
+where the bottom bound in the integral in \eqn\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90\degree$ in \eqn\ref{eq:massfunc} and solving for $M_2$), and
 
 \begin{equation}
-h(M_2, m_f, M_1) = \frac{(M_1+M_2)^{4/3}}{3\ m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}
+h(M_2, \mf, M_1) = \frac{(M_1+M_2)^{4/3}}{3\ \mf^{1/3}M_2\sqrt{M_2^2 - \left[ \mf(M_1+M_2)^2 \right]^{2/3}}}
 \end{equation}
 
-\section{Our Model} \label{sec:experiments}
+\subsection{Our Model} \label{sec:experiments}
 
@@
 However, in tests below, we generate test data with a variety of mixture component forms.
-We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,1.4)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1,2)~\Msun$.
-The likelihood with a Gaussian mixture model is
+We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1.3,2)~\Msun$,
 \begin{align}
-%	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\\
-%	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
+%	h(M_2, \mf, M_1) &= \frac{(M_1+M_2)^{4/3}}{3\mf^{1/3}M_2\sqrt{M_2^2 - \left[ \mf(M_1+M_2)^2 \right]^{2/3}}}\\
+%	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, \mf, M_1)\\
 	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right] 
 \end{align}
-
 where 
-
-\begin{equation}
-	p_{\rm WD} = \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,\left[ 0.2 < \frac{M_2}{\Msun} < 1.4 \right] 
-\end{equation}
-
-and
-
-\begin{equation}
-	p_{\rm NS} = \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\, \left[1.4 < \frac{M_2}{\Msun} < 2 \right].
-\end{equation}
-
-$\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
+\begin{align}
+	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,\left[ 0.2 < \frac{M_2}{\Msun} < \wdupper \right] \\
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\, \left[1.3 < \frac{M_2}{\Msun} < 2 \right].
+\end{align}
+and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
 In this work, we fix the mean and variance of the neutron star distribution to
@@
 	\mu_{\rm NS} &= 1.4~\Msun\\
-	\sigma^2_{\rm NS} &= (0.1~\Msun)^2
+	\sigma^2_{\rm NS} &= (0.05~\Msun)^2
 \end{align}
@@
 
-%The probability of any particular system having a NS companion $P({\rm NS})$ is then:
+%The probability of any particular system having a NS companion $P_{\rm NS}$ is then:
 
 %\begin{equation}
-%P({\rm NS}) = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, m_f, M_1) \label{eq:P_NS_full}
+%P_{\rm NS} = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, \mf, M_1) \label{eq:P_NS_full}
 %\end{equation}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-We choose standard priors on these parameters.
-For the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$.
-We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.0~\Msun$.
-We use a uniform distribution over the dimensionless neutron star fraction from $0-1$.
+We choose standard priors on these parameters: for the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$; we use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
@@
 
-In our model, we use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
+We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
 The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
@@
 
-\subsection{Test Cases} \label{sec:tests}
+\section{Test Cases} \label{sec:tests}
 To test the performance of this Gaussian mixture model, we apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
-These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $m_f$.
+These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $\mf$.
 We draw primary masses from a uniform distribution, $M_1 \sim \mathcal{U}(0.2,0.4)~\Msun$.
@@
 The third panel shows the convolved posterior histogram for $f_{\rm NS}$, with the dashed lines in the bottom two panels showing the true value of 10\%.
-Finally, the rightmost panels show the NS probability for individual systems as a function of $m_f$.
+Finally, the rightmost panels show the NS probability for individual systems as a function of $\mf$.
 The error bars in $P_{\rm NS}$ enclose the interquartile range.}
@@
 
-\subsubsection{Test 1: Single Gaussian (white dwarf)} \label{sec:exp1}
+\subsection{Test 1: Single Gaussian (white dwarf)} \label{sec:exp1}
 
@@
 	\sigma^2_{\rm WD, true} &= (0.2~\Msun)^2\\
-	0.2 < &\frac{M_2}{\Msun} < 1.4.
+	0.2 < &\frac{M_2}{\Msun} < \wdupper.
 \end{align}
 This is equivalent to setting the neutron star fraction to $f_{\rm NS} = 0$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the top-left panel of Figure~\ref{fig:tests}.
-We use MCMC (see description above) to ...
 
-\subsubsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
+\subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
 For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters
@@
 	\mu_{\rm NS, true} &= 1.4~\Msun\\
-	\sigma^2_{\rm NS, true} &= (0.1~\Msun)^2\\
-	1.4 < & \frac{M_2}{\Msun} < 2.
+	\sigma^2_{\rm NS, true} &= (0.05~\Msun)^2\\
+	1.3 < & \frac{M_2}{\Msun} < 2.
 \end{align}
 We set the neutron star fraction to $f_{\rm NS} = 0.1$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{fig:tests}.
-We use MCMC (see description above) to ...
 
-[TODO: We have also tried changing the mean and variance of the true neutron star distribution while keeping the fitting parameters fixed and found ...]
+% [TODO: We have also tried changing the mean and variance of the true neutron star distribution while keeping the fitting parameters fixed and found ...]
 
-\subsubsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
+\subsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
 For a final test, we use the same neutron star component as in Section~\ref{sec:exp2}, but now generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$.
 We keep the neutron star fraction fixed to $f_{\rm NS}=0.1$.
-The distribution of mock observations of the mass function, $m_f$, are shown by the middle-left panel of Figure~\ref{fig:tests}.
-We use MCMC (see description above) to ...
 
-\subsection{The ELM Sample}
+\subsection{Test results}
+The test results are summarized by Figure~\ref{fig:tests}.
+Each row corresponds to one of the three tests described above.
+The left-most column shows the true distribution of $M_2$'s, over-plotted with the maximum a posteriori (MAP) model from our posterior samples, inferred from mock observations of the mass functions, $\mf$, and primary masses, $M_1$, of the mock data.
+The middle panels show samples from the posterior in two projections (grey points), along with contours that contain 68\% and 95\% of the samples.
+The final column shows the probability that any given test object is a neutron star, as computed for 512 samples from the posterior.
 
-The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, providing precise measurements for $P_{\rm orb}$ and $K$.
-Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$.
+\section{The ELM Sample}
+
+The ELM WD sample is composed of 55 of 61 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
+{\bf [Jeff: this sentence looks incomplete]} Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$.
 We use the spectroscopic solutions found in \citet{gianninas14}.
 Three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$ \citep{kaplan14}, J0651$+$2844: $M_2=0.50~\Msun$ \citep{brown11b}, and J0751$-$0141: $M_2=0.97~\Msun$ \citep{kilic14}).
-For these systems, our marginal likelihood reduces to:
-
+For these systems, the likelihood reduces to:
 \begin{equation}
-p(m_f \given \theta) = (1-f_{\rm NS}) \mathcal{N}(M_2^* \given \mu_{\rm WD}, \sigma^2_{\rm WD})
+p(\mf \given \theta) = (1-f_{\rm NS}) \mathcal{N}(M_2^* \given \mu_{\rm WD}, \sigma^2_{\rm WD})
 \end{equation}
-
 where $M_2^*$ is the mass of the WD companion in these three systems.
 
-Furthermore, six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
+The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\sim$20-50 km s$^{-1}$.
 Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
@@
 The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
-This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows the relation between $M_f$ and $P({\rm NS})$ for individual systems.
+This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows the relation between $\mf$ and $P_{\rm NS}$ for individual systems.
 }
@@
 While the well-defined peak in the posterior distribution demonstrates convergence of the model, the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
-However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA {\bf [Jeff: DA?
+I don't think we ever defined that acronym]} WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
 Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
 
-Our results are independent of astrophysical expectations since they do not include any priors on $\mu$ and $\sigma$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and 1.4 \Msun (based on the Chandrasekhar mass).
-In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWD, composed of CO and He core WDs \citep{han98}.
-The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in e.g., ][]{toonen12}.
+Our results are independent of astrophysical expectations since they do not include any priors on $\mu$ and $\sigma$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper \Msun (based on the Chandrasekhar mass).
+In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
+The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
+Our model could be expanded to include a two Gaussian model --- one for each WD population.
+The ratio of these populations could potentially place an important constraint on population synthesis models.
+However, we have found that there is not enough data to motivate adding additional freedom to the model in the form of a second WD component.
 
-Our model could be expanded to include a two Gaussian model one for each WD population.
-The ratio of these populations could potentially place an important constraint on population synthesis models.
-However adding only one more Gaussian component doubles the number of free parameters from three to six.
-Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.
-It remains to be seen whether constraints can be placed with 55 measured systems using such a model.
-
-The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
+The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a significant tail toward higher NS probabilities.
 Our model does indicate an upper limit to the NS fraction of {\bf XXX\%} at the 95\% confidence level.
 For 55 systems with observed radial velocity variations, this corresponds to a {\bf 0-4?} systems with NS companions.
-These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $P({\rm NS})$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
-With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P({\rm NS})$ of $10\substack{+4 \\ -2}\%$.
+These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $P_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
+With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P_{\rm NS}$ of $10\substack{+4 \\ -2}\%$.
 
@@
 However the fourth panel in Figure \ref{fig:ELM_post} indicates which ELM WDs have the highest probability of hosting NS companions.
-Here, we show the relation between $m_f$ and $P({\rm NS})$ for individual systems.
-This panel shows that $P({\rm NS})$ only starts to significantly deviate from zero for {\bf $m_f\approx0.6 \Msun$} Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
+Here, we show the relation between $\mf$ and $P_{\rm NS}$ for individual systems.
+This panel shows that $P_{\rm NS}$ only starts to significantly deviate from zero for {\bf $\mf\approx0.6 \Msun$} Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
 
-The two systems with $P({\rm NS})$ above {\bf 10\%} are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
+The two systems with $P_{\rm NS}$ above {\bf 10\%} are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
 These systems are ideal candidates for searches for NS companions in radio and X-ray.
@@
 If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
-In a future work, we plan to combine our model results here with radio and x-ray non-detections, placing more stringent constraints on $P({\rm NS})$.
+In future work, we plan to combine these results with radio and x-ray non-detections to further constrain $P_{\rm NS}$ for each system.
 
 It is worth noting that the fourth panels in our test cases in Figure~\ref{fig:tests} shows that our model is fairly good at identifying those systems most likely to host NS's.
-However it also shows that roughly half of the LMWDs with NS companions may appear with a deceptively low $f_{\rm NS}$.
+However it also shows that roughly half of the LMWDs with NS companions may appear with a deceptively low $f_{\rm NS}$ due to the inclination angle.
 Systems with NS companions cannot all be differentiated from those with WD companions through the mass function and LMWD mass alone.
 Therefore {\it any} LMWD could host a NS companion, and is a valuable target for radio and X-ray follow-up observations.
+{\bf [Jeff: maybe cut the last sentence here because this kind of contradicts one of the points of the paper!]}
 
 The probability of any particular ELM WD having a NS companion will vary depending on the NS fraction of the sample.
-This is not taken into account in Equation~\ref{eq:P_NS_approx}.
+This is not taken into account in \eqn\ref{eq:P_NS_approx}.
 {\bf TEXT ON USING PYTHON SCRIPT FOR DETERMINING P-NS FOR FUTURE DISCOVERED LMWDs.}
 
-Recently, high-speed photometric observations by \citet{hermes14}.
+{\bf [Jeff: first sentence is a stub]} Recently, high-speed photometric observations by \citet{hermes14}.
 Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
 For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
-Including these observations in our model is non-trivial and remains outside the scope of this work, however we plan to explore this in a future work.
+We have not included these observations in our model, but we plan to explore this in future work.
 
@@
 \acknowledgements
-The authors wish to acknowledge David Hogg (NYU) for useful discussions, and the organizing committee of the \emph{AstroData Hack Week} (2014). 
+The authors wish to acknowledge David Hogg (NYU) for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
 APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
-This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
-This work additionally relied on Columbia University's \emph{Hotfoot} and \emph{Yeti} compute clusters, and we acknowledge the Columbia HPC support staff for assistance.
-These clusters includes support from New York State Empire State Development, Division of Science Technology and Innovation (NYSTAR) Contract C090171.
-\\
+This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}. \\
 

### 2014-10-14 documents/letter/ms.tex

@@
 \usepackage{booktabs}
+\usepackage{multirow}
 
@@
 Even when the mass of the visible star can be measured, only a lower limit can be placed
-on the mass of the unseen companion. However, since the systems should be isotropically
-distributed in the inclination angle, for a large enough, unbiased sample, the 
+on the mass of the unseen companion. However, since the orbital geometry of the systems should be isotropically
+distributed, for a large enough, unbiased sample, the 
 companion mass distribution can be deconvolved from the distributions of observables.
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen 
-companion stars given kinematic measurements of the primary. We use a mixture of 
-(two) Gaussians to model the true companion mass distribution, meant to represent 
-populations of white dwarfs (WD) and neutron stars (NS). We run this model on mock data generated
-both with and without the same functional form as the fitting model in order to test the
+companion stars given orbital period and projected radial velocity measurements of the primary. We use a mixture of 
+two Gaussians to model the true companion mass distribution to represent 
+populations of white dwarfs (WD) and neutron stars (NS). We run this model on mock data sets in order to test the
 robustness of our inferences. We then apply our model to 55 of the 61 white dwarfs in 
@@
 the WD companion population of $\mu_{\rm WD} = 0.73~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
-with a NS fraction consistent with zero, $f_{\rm NS} = 0$. However, the marginal posterior 
-distribution over NS fraction has a significant tail up to $f_{\rm NS} \sim 0.12$.
+with a NS fraction consistent with zero, $f_{\rm NS} = 0\%$. However, the marginal posterior 
+distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 12\%$.
 We make samples from the posterior distribution publicly available and provide a  
@@
 The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from Data Release 7 (DR7) of the Sloan Digital Sky Survey (SDSS), which contains $\sim$20,000 confirmed WDs \citep{kleinman13}.
-While the distribution of WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\sim$6\%) of low mass WDs (LMWD) is observed with $M<0.4~\Msun$.
-In addition to SDSS, LMWDs have been observed in similar numbers elsewhere \citep[e.g., the Palomar Green Survey;][]{liebert05}.
+While the distribution of hydrogen atmosphere (DA) WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\approx$6\%) are seen as low mass WDs (LMWD) with $M<0.4~\Msun$ both in SDSS and elsewhere \citep[e.g., the Palomar Green Survey;][]{liebert05}.
 
-Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce these LMWD through single star evolution.
+Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce WDs with $M<0.5 \Msun$ through single star evolution.
 These objects are formed through dynamical interactions with another star, in which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
-After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a He-core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98}.
+After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a He-core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98,nelemans00,nelemans01}.
 
@@
 While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could have NS companions \citep{vLeeuwen07}.
-However, this and other radio searches for pulsed emission, as well as searches for blackbody X-ray emission using {\it XMM-Newton} and {\it Chandra}, have all been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
+However, all radio searches for pulsed emission, as well as searches for blackbody X-ray emission from a NS surface have been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
 Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems .
+Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}
 
@@
 \end{equation}
-The righthand side of this equation is the well-known mass function ($\mf$). $M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
+The righthand side of this equation is the well-known mass function ($\mf$).
+$M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
+Because of the dependence on $i$, the nature of the companion cannot usually be determined based on $\mf$ alone.
+Figure~\ref{fig:Porb-M1} shows that the population of LMWD with pulsar companions (triangles) occupy the same region in $M_1 - \period$ space as those with WD companions (circles).
+Therefore, barring rare circumstances (such as an edge-on, eclipsing system), individual LMWDs with NS companions cannot be readily identified.
 
@@
 3.\ What is the rate of NS-LMWD binaries implied by our model?
-4.\ {\bf [Jeff: I propose nixing this question...
-]} Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?
+4.\ What are the resulting distributions of NS probabilities for individual systems in the ELM sample?
 
@@
 From $\period$ and $M_1$ alone, the two populations are indistinguishable.}
+\label{fig:Porb-M1}
 \end{center}
@@
 \end{align}
-We neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles are isotropically distributed
+We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$.} and assume the inclination angles are isotropically distributed
 \begin{align}
@@
 
-\begin{deluxetable}{cc}
+\begin{deluxetable}{ccccc}
 	\tablecaption{Model Parameters \label{tbl:parameters}}
@@
 	\tablehead{
-		\colhead{Parameter} &
-		\colhead{Prior}
+		\multicolumn{2}{c}{} &
+		\colhead{$\mu_{\rm WD}$} & 
+		\colhead{$\sigma_{\rm WD}$} &
+		\colhead{$f_{\rm NS}$} \\
+		\colhead{} &
+		\colhead{} &
+		\colhead{[\Msun]} &
+		\colhead{[\Msun]} &
+		\colhead{}
 	}
@@
 	\startdata
-		$f_{\rm NS}$ & $\mathcal{U}(0, 1)$ \\ 
-		$\mu_{\rm WD}$ & $\mathcal{U}(0.2, 1.4)$ \\ 
-		$\sigma_{\rm WD}$ & $\frac{1}{\ln(40)\sigma}$ $(0.05 < \sigma < 2~\Msun)$ \\ 
-		$\mu_{\rm NS}$ & 1.4~$\Msun$ (fixed) \\ 
-		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) 
+		\multicolumn{2}{c}{Priors} & $\mathcal{U}(0.2, 1.4)$ & $\left[\ln(40)\sigma\right]^{-1}$ $(0.05 < \sigma/\Msun < 2)$ & $\mathcal{U}(0, 1)$ \\
+		\cutinhead{Test Cases}
+		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
+		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 \hline
+		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
+		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 \hline
+		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
+		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 \cutinhead{ELM Sample}
+		 & MAP & 0.73 & 0.26 & {\bf 5\%?}
 	\enddata
@@
 There are 3 free parameters.
-}\
+We additionally fix the NS distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.1~\Msun.$}\
 
@@
 The ELM WD sample is composed of 55 of 61 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-{\bf [Jeff: this sentence looks incomplete]} Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$.
+Fitting the sample's high S/N spectra to templates provides precisely determine $M_1$ values.
 We use the spectroscopic solutions found in \citet{gianninas14}.
@@
 
-The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\sim$20-50 km s$^{-1}$.
-Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
+The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
+Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
 These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit.
@@
 The black line gives the maximum a posteriori value, while the fainter lines show a set of randomly selected realizations from our model.
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun.
-The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities.
+The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= 0.74~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
+The third panel shows a NS fraction consistent with zero, however with a non-negligible tail toward higher NS probabilities.
 This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows the relation between $\mf$ and $P_{\rm NS}$ for individual systems.
@@
 The results of our model are shown in Figure \ref{fig:ELM_post}.
-The maximum a posteriori Gaussian model has a mean of {\bf 0.74} \Msun\ and a standard deviation of {\bf 0.26} \Msun.
+The maximum a posteriori Gaussian model has $mu_{\rm WD} = {\bf 0.74} \Msun$ and $\sigma_{\rm WD} = {\bf 0.26}~\Msun$.
 While the well-defined peak in the posterior distribution demonstrates convergence of the model, the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
-However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA {\bf [Jeff: DA?
-I don't think we ever defined that acronym]} WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
 Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
 
-Our results are independent of astrophysical expectations since they do not include any priors on $\mu$ and $\sigma$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper \Msun (based on the Chandrasekhar mass).
+Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper \Msun (based on the Chandrasekhar mass).
 In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
@@
 For 55 systems with observed radial velocity variations, this corresponds to a {\bf 0-4?} systems with NS companions.
-These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $P_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
-With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $P_{\rm NS}$ of $10\substack{+4 \\ -2}\%$.
+These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $f_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
+With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $f_{\rm NS}$ of $10\substack{+4 \\ -2}\%$.
 
@@
 Systems with NS companions cannot all be differentiated from those with WD companions through the mass function and LMWD mass alone.
-Therefore {\it any} LMWD could host a NS companion, and is a valuable target for radio and X-ray follow-up observations.
-{\bf [Jeff: maybe cut the last sentence here because this kind of contradicts one of the points of the paper!]}
+Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.
 
@@
 
-{\bf [Jeff: first sentence is a stub]} Recently, high-speed photometric observations by \citet{hermes14}.
-Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
+Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample to search for eclipses.
+They placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
 For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.

### 2014-10-15 documents/letter/ms.tex
Updated table
Updated intro, Section 3

@@
-%\documentclass[apjl]{emulateapj}
-\documentclass[letterpaper,12pt,preprint]{aastex}
+\documentclass[apjl]{emulateapj}
+%\documentclass[letterpaper,12pt,preprint]{aastex}
 
@@
 % Symbols
-\newcommand{\period}{T_{\rm orb}}
-\newcommand{\mf}{M_f}
+\newcommand{\period}{T}
+\newcommand{\mf}{m_f}
 \newcommand{\wdupper}{1.44}
@@
 
-The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from Data Release 7 (DR7) of the Sloan Digital Sky Survey (SDSS), which contains $\sim$20,000 confirmed WDs \citep{kleinman13}.
+%The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from Data Release 7 (DR7) of the Sloan Digital Sky Survey (SDSS), which contains $\sim$20,000 confirmed WDs \citep{kleinman13}.
 While the distribution of hydrogen atmosphere (DA) WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\approx$6\%) are seen as low mass WDs (LMWD) with $M<0.4~\Msun$ both in SDSS and elsewhere \citep[e.g., the Palomar Green Survey;][]{liebert05}.
 
-Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce WDs with $M<0.5 \Msun$ through single star evolution.
-These objects are formed through dynamical interactions with another star, in which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
+Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce WDs with $M\lesssim0.45~ \Msun$ through single star evolution.
+These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems.
+\citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
+%which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
 After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a He-core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98,nelemans00,nelemans01}.
-
 In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations and cementing LMWDs as fruitful targets for binary searches.
-The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up using combined constraints on photometry and reduced proper motions \citep{ELMI}.
+The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up
+% using combined constraints on photometry and reduced proper motions 
+\citep{ELMI}.
 After their initial investigation found 11 of 12 LMWDs had close binary companions, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
-While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could have NS companions \citep{vLeeuwen07}.
+While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could host NS companions \citep{vLeeuwen07}.
 However, all radio searches for pulsed emission, as well as searches for blackbody X-ray emission from a NS surface have been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
@@
 
+%\setlength{\tabcolsep}{2pt}
+\renewcommand{\arraystretch}{1.405}
 \begin{deluxetable}{ccccc}
-	\tablecaption{Model Parameters \label{tbl:parameters}}
+	\tablecaption{Model Results \label{tbl:parameters}}
 
@@
 	\startdata
-		\multicolumn{2}{c}{Priors} & $\mathcal{U}(0.2, 1.4)$ & $\left[\ln(40)\sigma\right]^{-1}$ $(0.05 < \sigma/\Msun < 2)$ & $\mathcal{U}(0, 1)$ \\
+		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1.4)$ & $\left[\ln(40)\sigma\right]^{-1}$  & $\mathcal{U}(0, 1)$ \\
+		\multicolumn{2}{c}{} & & $(0.05 < \sigma/\Msun < 2)$ & \\
 		\cutinhead{Test Cases}
@@
 The left-most panel shows a histogram of the $M_2$ drawn from each of our test distributions.
-Overplotted as a solid line is posterior distribution using the maximum a posteriori parameter values, resulting from our model.
+Overplotted as a solid line is MAP distribution.
 The second panel shows the posterior distributions for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
@@
 Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
-The third panel shows the convolved posterior histogram for $f_{\rm NS}$, with the dashed lines in the bottom two panels showing the true value of 10\%.
-Finally, the rightmost panels show the NS probability for individual systems as a function of $\mf$.
-The error bars in $P_{\rm NS}$ enclose the interquartile range.}
+The third panel shows the posterior distribution for $f_{\rm NS}$ and $\sigma_{\rm WD}$, again with the dashed lines showing the true values.
+Finally, the rightmost panels list the individual systems and show each of their corresponding NS probabilities.
+The systems are ordered by increasing $\mf$.
+}
 \label{fig:tests}
@@
 
-As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with mean, variance, and bounds
-\begin{align}
-	\mu_{\rm WD, true} &= 0.7~\Msun\\
-	\sigma^2_{\rm WD, true} &= (0.2~\Msun)^2\\
-	0.2 < &\frac{M_2}{\Msun} < \wdupper.
-\end{align}
-This is equivalent to setting the neutron star fraction to $f_{\rm NS} = 0$.
+As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in \ref{tbl:parameters}.
+This test sample contains no NSs.
+The leftmost panel in Figure~\ref{fig:ELM_post} shows that the MAP $M_2$ distribution qualitatively matches the input distribution, while the second panel shows the posterior distribution quantitatively matches the input values shown as dashed lines.
+The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\approx 10$\%.
+Nevertheless, our model closely recovers the input parameters.
+The fourth panel lists individual systems, ordered by $\mf$, and provides the distribution of $P_{\rm NS}$ values for each.
+Few systems have $P_{\rm NS}$ values higher than $\approx$5\%, consistent with our input distribution of $f_{\rm NS}=$0\%.
 
 \subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters
-\begin{align}
-	\mu_{\rm NS, true} &= 1.4~\Msun\\
-	\sigma^2_{\rm NS, true} &= (0.05~\Msun)^2\\
-	1.3 < & \frac{M_2}{\Msun} < 2.
-\end{align}
-We set the neutron star fraction to $f_{\rm NS} = 0.1$.
+For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters, setting $f_{\rm NS} =$ 10\%.
+The panels are the same as in Test 1 described above.
+Again, our model recovers the input values for $\mu{\rm WD}$ and $\sigma_{\rm WD}$.
+Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior again shows a tail toward higher probabilities.
+The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS.
+However, this accounts for only roughly half of the systems with NSs in the sample, and the other half may found with low $\mf$ due to a low inclination angle.
+Although our model can correctly identify the $f_{\rm NS}$ within a factor of $\approx2$, it can only identify some LMWDs as having NS companions.
 
@@
 \subsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
-For a final test, we use the same neutron star component as in Section~\ref{sec:exp2}, but now generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$.
-We keep the neutron star fraction fixed to $f_{\rm NS}=0.1$.
-
-\subsection{Test results}
-The test results are summarized by Figure~\ref{fig:tests}.
-Each row corresponds to one of the three tests described above.
-The left-most column shows the true distribution of $M_2$'s, over-plotted with the maximum a posteriori (MAP) model from our posterior samples, inferred from mock observations of the mass functions, $\mf$, and primary masses, $M_1$, of the mock data.
-The middle panels show samples from the posterior in two projections (grey points), along with contours that contain 68\% and 95\% of the samples.
-The final column shows the probability that any given test object is a neutron star, as computed for 512 samples from the posterior.
+For a final test, we generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, while keeping $f_{\rm NS}=$10\%.
+Again, the panels are the same as in Test 1 described above.
+The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm sigma}$.
+Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$, approximately as accurately as in Test 2.
+%The rightmost panel shows that despite accurately finding $f_{\rm NS}$, our model is not as good at identifying exactly which WDs are NSs.
 
@@
 \caption{The posteriors for our model applied to the ELM WDs.
-The first panel shows the distribution of $M_2$ for the data set.
-The black line gives the maximum a posteriori value, while the fainter lines show a set of randomly selected realizations from our model.
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= 0.74~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
-The third panel shows a NS fraction consistent with zero, however with a non-negligible tail toward higher NS probabilities.
-This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows the relation between $\mf$ and $P_{\rm NS}$ for individual systems.
-}
+The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
+The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.74}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
+The third panel the posterior distribution of $\mu$ and $f_{\rm NS}$.
+The last panel lists individual LMWDs in the ELM sample and shows each of their corresponding NS probabilities.
+The systems are ordered by increasing $\mf$.
+The three systems with $P_{\rm NS}=$0\% are the three eclipsing systems.}
 \label{fig:ELM_post}
@@
 
-The two systems with $P_{\rm NS}$ above {\bf 10\%} are J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%).
+The two systems with the highest $P_{\rm NS}$ are J0811$+$0225 and J1741$+$6526.
 These systems are ideal candidates for searches for NS companions in radio and X-ray.
@@
 For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
-We have not included these observations in our model, but we plan to explore this in future work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% If we do this calculation, we need to think more about it
-% 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Combining our resulting NS fraction of {\bf 5\%} with the ELM WD space density of 40 kpc$^{-3}$ as determined by \citet{brown11a}, we can find a space density of ELM WD + NS binaries of 2 kpc$^{-3}$.
-If we assume an exponential disk with a scale height of 250 pc, this suggests that there are $\approx$  such binaries within a two kpc of us.
-Compare to the number of known MSP+LMWDs.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  If we say anything about non-detections, we need to fix up the
-% math below. I suggest we wait and discuss these in a future work
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{Non-detections}
-
-%Six systems in the ELM WD sample have non-detections of companions, down to an upper limit on the transverse velocity.
-We include these systems in our model, too, as in principle they could be binary systems at with low inclination angles or long period orbits or both.
-We can estimate the number of binaries with inclination angles too low to produce observable radial velocity variations:
-
-%\begin{equation}
-%P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} \int_0^{i_{\rm max}} P(M_2|\mathbf{\Theta})\ {\rm sin}\ i\ {\rm d}i\ {\rm d}M_2
-%\end{equation}
-
-%which reduces to:
-
-%\begin{equation}
-%P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} P(M_2|\mathbf{\Theta})\ \left( 1 - {\rm cos}\ i_{\rm max}\right)\ {\rm d}M_2
-%\end{equation}
-
-%where $i_{\rm max}$ is the smallest inclination angle that would still produce an unobservable binary, found by solving equation 1, using $K_{\rm max}$ for $K$.
-For an estimate of the expected fraction of unobserable binaries, we adopt $0.25~\Msun$ for $M_1$, an orbital period of 0.5 days, and a limiting velocity of 50 km s$^{-1}$.
-For our best fit model, with $\mu=0.6$, $\sigma=0.3$, and $\mathcal{f}=0.03$, we numerically calculate the integral above, and find that we would expect $\sim$2\% and $\sim$7\% of systems to have radial velocity variations below 25 km s$^{-1}$ and 50 km s$^{-1}$, respectively.
-If we increase the fiducial orbital period to 1.0 day, those numbers increases to 3\% and 10\%, respectively.
-For the ELM sample with 61 systems, this corresponds to 2 and 6 systems, consistent with the number of non-detections observed.
-Although we caution that this result is based on our imperfect model, it suggests that the number of non-detections observed is consistent with binaries at low inclination angles (albeit at slightly larger orbital periods than that of the observed population).
+We have not included these observations in our model, but we plan to explore this in a future work.
 
@@
 
-\begin{enumerate}
-\item We have created a mathematical description to describe the companion mass distribution of a set of unbiased single-lined spectroscopic binaries. \\
-\item We have used that mathematical framework to build a Markov Chain Monte Carlo model and applied it to the set of WDs from the ELM WD survey. \\
-\item Our model suggests that the majority of ELM WDs have CO-core WDs.
-This is in contrast to predictions from population synthesis models.
-In a future work, we plan to quantify the ratio of He+He core WDs to He+CO core WDs.
-\\
-\item Our model indicates that the fraction of ELM WDs with NS companions is of order a few percent.
-We provide an updated formula for determining the probability of any particular LMWD having a NS companion.
-We further identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion with {\bf XXX\%} and {\bf XXX\%}, respectively.
-\\
-\end{enumerate}
+We have created a mathematical description using a Bayesian framework to describe the companion mass distribution of a set of unbiased single-lined spectroscopic binaries.
+We have used that mathematical framework to build a Markov Chain Monte Carlo model.
+Our model recovers the input parameters for three separate test cases with WD and NS companion masses drawn from different distributions.
+In particular, even if the companion mass distribution is not drawn from a Gaussian distribution, our model can still determine the NS fraction within a factor of $\approx2$.
+
+We then applied our model to the set of WDs from the ELM WD survey.
+Our model indicates that the fraction of ELM WDs with NS companions is of order a few percent.
+We identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion, and suggest the multi-wavelength follow-up is warranted.
+Our model further suggests that the majority of ELM WDs have CO-core WD companions.
+This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs.
+
+There are several ways in which this model can be expanded.
+First, our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
+Applying this method to various populations can help to constrain the formation of particularly classes of binaries.
+In particular, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
 
@@
 \bibliographystyle{apj}
-\bibliography{refs}
+
+\begin{thebibliography}{35}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{a}}){Ag{\"u}eros}, {Camilo},
+  {Silvestri}, {Kleinman}, {Anderson}, \& {Liebert}}]{agueros09b}
+{Ag{\"u}eros}, M.~A., {Camilo}, F., {Silvestri}, N.~M., {Kleinman}, S.~J.,
+  {Anderson}, S.~F., \& {Liebert}, J.~W. 2009{\natexlab{a}}, \apj, 697, 283
+
+\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{b}}){Ag{\"u}eros}, {Heinke},
+  {Camilo}, {Kilic}, {Anderson}, {Freire}, {Kleinman}, {Liebert}, \&
+  {Silvestri}}]{agueros09a}
+{Ag{\"u}eros}, M.~A. {et~al.} 2009{\natexlab{b}}, \apjl, 700, L123
+
+\bibitem[{{Antoniadis} {et~al.}(2012){Antoniadis}, {van Kerkwijk}, {Koester},
+  {Freire}, {Wex}, {Tauris}, {Kramer}, \& {Bassa}}]{antoniadis12}
+{Antoniadis}, J., {van Kerkwijk}, M.~H., {Koester}, D., {Freire}, P.~C.~C.,
+  {Wex}, N., {Tauris}, T.~M., {Kramer}, M., \& {Bassa}, C.~G. 2012, \mnras,
+  423, 3316
+
+\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
+  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
+  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
+  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
+  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
+  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
+  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
+  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy13}
+{Astropy Collaboration} {et~al.} 2013, \aap, 558, A33
+
+\bibitem[{{Bassa} {et~al.}(2006){Bassa}, {van Kerkwijk}, {Koester}, \&
+  {Verbunt}}]{bassa06}
+{Bassa}, C.~G., {van Kerkwijk}, M.~H., {Koester}, D., \& {Verbunt}, F. 2006,
+  \aap, 456, 295
+
+\bibitem[{{Benvenuto} \& {De Vito}(2005)}]{benvenuto05}
+{Benvenuto}, O.~G., \& {De Vito}, M.~A. 2005, \mnras, 362, 891
+
+\bibitem[{{Brown} {et~al.}(2013){Brown}, {Kilic}, {Allende Prieto},
+  {Gianninas}, \& {Kenyon}}]{ELMV}
+{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., {Gianninas}, A., \&
+  {Kenyon}, S.~J. 2013, \apj, 769, 66
+
+\bibitem[{{Brown} {et~al.}(2010){Brown}, {Kilic}, {Allende Prieto}, \&
+  {Kenyon}}]{ELMI}
+{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., \& {Kenyon}, S.~J. 2010,
+  \apj, 723, 1072
+
+\bibitem[{{Brown} {et~al.}(2012){Brown}, {Kilic}, {Allende Prieto}, \&
+  {Kenyon}}]{ELMIII}
+---. 2012, \apj, 744, 142
+
+\bibitem[{{Brown} {et~al.}(2011){Brown}, {Kilic}, {Hermes}, {Allende Prieto},
+  {Kenyon}, \& {Winget}}]{brown11b}
+{Brown}, W.~R., {Kilic}, M., {Hermes}, J.~J., {Allende Prieto}, C., {Kenyon},
+  S.~J., \& {Winget}, D.~E. 2011, \apjl, 737, L23
+
+\bibitem[{{Callanan} {et~al.}(1998){Callanan}, {Garnavich}, \&
+  {Koester}}]{callanan98}
+{Callanan}, P.~J., {Garnavich}, P.~M., \& {Koester}, D. 1998, \mnras, 298, 207
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{foremanmackey13}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Gianninas} {et~al.}(2014){Gianninas}, {Dufour}, {Kilic}, {Brown},
+  {Bergeron}, \& {Hermes}}]{gianninas14}
+{Gianninas}, A., {Dufour}, P., {Kilic}, M., {Brown}, W.~R., {Bergeron}, P., \&
+  {Hermes}, J.~J. 2014, \apj, 794, 35
+
+\bibitem[{{Han}(1998)}]{han98}
+{Han}, Z. 1998, \mnras, 296, 1019
+
+\bibitem[{{Hermes} {et~al.}(2014){Hermes}, {Brown}, {Kilic}, {Gianninas},
+  {Chote}, {Sullivan}, {Winget}, {Bell}, {Falcon}, {Winget}, {Mason},
+  {Harrold}, \& {Montgomery}}]{hermes14}
+{Hermes}, J.~J. {et~al.} 2014, \apj, 792, 39
+
+\bibitem[{{Jia} \& {Li}(2014)}]{jia14}
+{Jia}, K., \& {Li}, X.-D. 2014, \apj, 791, 127
+
+\bibitem[{{Kaplan} {et~al.}(2014){Kaplan}, {Marsh}, {Walker}, {Bildsten},
+  {Bours}, {Breedt}, {Copperwheat}, {Dhillon}, {Howell}, {Littlefair},
+  {Shporer}, \& {Steinfadt}}]{kaplan14}
+{Kaplan}, D.~L. {et~al.} 2014, \apj, 780, 167
+
+\bibitem[{{Kilic} {et~al.}(2011){Kilic}, {Brown}, {Allende Prieto},
+  {Ag{\"u}eros}, {Heinke}, \& {Kenyon}}]{ELMII}
+{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Ag{\"u}eros}, M.~A.,
+  {Heinke}, C., \& {Kenyon}, S.~J. 2011, \apj, 727, 3
+
+\bibitem[{{Kilic} {et~al.}(2012){Kilic}, {Brown}, {Allende Prieto}, {Kenyon},
+  {Heinke}, {Ag{\"u}eros}, \& {Kleinman}}]{ELMIV}
+{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Kenyon}, S.~J., {Heinke},
+  C.~O., {Ag{\"u}eros}, M.~A., \& {Kleinman}, S.~J. 2012, \apj, 751, 141
+
+\bibitem[{{Kilic} {et~al.}(2013){Kilic}, {Gianninas}, {Brown}, {Harris},
+  {Dahn}, {Ag{\"u}eros}, {Heinke}, {Kenyon}, {Panei}, \& {Camilo}}]{kilic13}
+{Kilic}, M. {et~al.} 2013, \mnras, 434, 3582
+
+\bibitem[{{Kilic} {et~al.}(2014){Kilic}, {Hermes}, {Gianninas}, {Brown},
+  {Heinke}, {Ag{\"u}eros}, {Chote}, {Sullivan}, {Bell}, \& {Harrold}}]{kilic14}
+---. 2014, \mnras, 438, L26
+
+\bibitem[{{Kilic} {et~al.}(2007){Kilic}, {Stanek}, \& {Pinsonneault}}]{kilic07}
+{Kilic}, M., {Stanek}, K.~Z., \& {Pinsonneault}, M.~H. 2007, \apj, 671, 761
+
+\bibitem[{{Kiziltan} {et~al.}(2013){Kiziltan}, {Kottas}, {De Yoreo}, \&
+  {Thorsett}}]{kiziltan13}
+{Kiziltan}, B., {Kottas}, A., {De Yoreo}, M., \& {Thorsett}, S.~E. 2013, \apj,
+  778, 66
+
+\bibitem[{{Kleinman} {et~al.}(2013){Kleinman}, {Kepler}, {Koester}, {Pelisoli},
+  {Pe{\c c}anha}, {Nitta}, {Costa}, {Krzesinski}, {Dufour}, {Lachapelle},
+  {Bergeron}, {Yip}, {Harris}, {Eisenstein}, {Althaus}, \&
+  {C{\'o}rsico}}]{kleinman13}
+{Kleinman}, S.~J. {et~al.} 2013, \apjs, 204, 5
+
+\bibitem[{{Liebert} {et~al.}(2005){Liebert}, {Bergeron}, \&
+  {Holberg}}]{liebert05}
+{Liebert}, J., {Bergeron}, P., \& {Holberg}, J.~B. 2005, \apjs, 156, 47
+
+\bibitem[{{Marsh} {et~al.}(1995){Marsh}, {Dhillon}, \& {Duck}}]{marsh95}
+{Marsh}, T.~R., {Dhillon}, V.~S., \& {Duck}, S.~R. 1995, \mnras, 275, 828
+
+\bibitem[{{Nelemans} {et~al.}(2000){Nelemans}, {Verbunt}, {Yungelson}, \&
+  {Portegies Zwart}}]{nelemans00}
+{Nelemans}, G., {Verbunt}, F., {Yungelson}, L.~R., \& {Portegies Zwart}, S.~F.
+  2000, \aap, 360, 1011
+
+\bibitem[{{Nelemans} {et~al.}(2001){Nelemans}, {Yungelson}, {Portegies Zwart},
+  \& {Verbunt}}]{nelemans01}
+{Nelemans}, G., {Yungelson}, L.~R., {Portegies Zwart}, S.~F., \& {Verbunt}, F.
+  2001, \aap, 365, 491
+
+\bibitem[{{{\"O}zel} {et~al.}(2012){{\"O}zel}, {Psaltis}, {Narayan}, \& {Santos
+  Villarreal}}]{ozel12}
+{{\"O}zel}, F., {Psaltis}, D., {Narayan}, R., \& {Santos Villarreal}, A. 2012,
+  \apj, 757, 55
+
+\bibitem[{{Smedley} {et~al.}(2014){Smedley}, {Tout}, {Ferrario}, \&
+  {Wickramasinghe}}]{smedley14}
+{Smedley}, S.~L., {Tout}, C.~A., {Ferrario}, L., \& {Wickramasinghe}, D.~T.
+  2014, \mnras, 437, 2217
+
+\bibitem[{{Toonen} {et~al.}(2012){Toonen}, {Nelemans}, \& {Portegies
+  Zwart}}]{toonen12}
+{Toonen}, S., {Nelemans}, G., \& {Portegies Zwart}, S. 2012, \aap, 546, A70
+
+\bibitem[{{van der Sluys} {et~al.}(2006){van der Sluys}, {Verbunt}, \&
+  {Pols}}]{vdSluys06}
+{van der Sluys}, M.~V., {Verbunt}, F., \& {Pols}, O.~R. 2006, \aap, 460, 209
+
+\bibitem[{{van Kerkwijk} {et~al.}(1996){van Kerkwijk}, {Bergeron}, \&
+  {Kulkarni}}]{vKerkwijk96}
+{van Kerkwijk}, M.~H., {Bergeron}, P., \& {Kulkarni}, S.~R. 1996, \apjl, 467,
+  L89
+
+\bibitem[{{van Leeuwen} {et~al.}(2007){van Leeuwen}, {Ferdman}, {Meyer}, \&
+  {Stairs}}]{vLeeuwen07}
+{van Leeuwen}, J., {Ferdman}, R.~D., {Meyer}, S., \& {Stairs}, I. 2007, \mnras,
+  374, 1437
+
+\bibitem[{{Woods} {et~al.}(2012){Woods}, {Ivanova}, {van der Sluys}, \&
+  {Chaichenets}}]{woods12}
+{Woods}, T.~E., {Ivanova}, N., {van der Sluys}, M.~V., \& {Chaichenets}, S.
+  2012, \apj, 744, 12
+
+%\bibliography{refs}
 
@@
 
+\end{thebibliography}
+
 \end{document}

### 2014-10-15 documents/letter/ms.tex
Added product equation

@@
 
-We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
+We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
 We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
@@
 \begin{equation}
-    p(\bs{\theta} \given \mf) = \frac{1}{\mathcal{Z}}~p(\mf \given \bs{\theta})~p(\bs{\theta}).
+    p(\bs{\theta} \given \bs{\mf}) = \frac{1}{\mathcal{Z}}~p(\bs{\mf} \given \bs{\theta})~p(\bs{\theta}).
 \end{equation}
-where $p(\mf \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
-The marginal likelihood, $p(\mf \given \bs{\theta})$, involves integrals over the latent variables $i$ and $M_2$,
+where $p(\bs{\mf} \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data.
+The likelihood, $p(\bs{\mf} \given \bs{\theta})$, can be split into a product over the likelihoods of individual systems:
+
+\begin{equation}
+p(\bs{\mf} \given \bs{\theta}) = \prod_j p(\mf \given \bs{\theta})
+\end{equation}
+
+where the product is over all each of the $j$ systems.  The marginal likelihood involves integrals over the latent variables $i$ and $M_2$,
 \begin{align}

### 2014-10-15 documents/letter/ms.tex
Added figshare description

@@
 \usepackage{multirow}
+\usepackage{url}
 
@@
 We make samples from the posterior distribution publicly available and provide a  
-script for computing the probability that a ... in the context of our model.
+script for computing the companion mass distribution and the NS probability for newly discovered low mass WDs given a measured WD mass and mass function.
 \end{abstract}
@@
 
-\section{Test Cases} \label{sec:tests}
-To test the performance of this Gaussian mixture model, we apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
+\section{Applying Our Model} \label{sec:tests}
+To test the performance of this Gaussian mixture model, we first apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
 These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $\mf$.
@@
 
-\section{The ELM Sample}
+\subsection{The ELM Sample}
 
@@
 
-The probability of any particular ELM WD having a NS companion will vary depending on the NS fraction of the sample.
-This is not taken into account in \eqn\ref{eq:P_NS_approx}.
-{\bf TEXT ON USING PYTHON SCRIPT FOR DETERMINING P-NS FOR FUTURE DISCOVERED LMWDs.}
+To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share} \footnote{\url{http://figshare.com/authors/Jeff\_Andrews/644768}}.
+We further provide a {\tt python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
+This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
 

### 2014-10-16 documents/letter/ms.tex
Added figshare description
update MAP numbers

@@
 Even when the mass of the visible star can be measured, only a lower limit can be placed
-on the mass of the unseen companion. However, since the orbital geometry of the systems should be isotropically
+on the mass of the unseen companion. However, since these inclination angles should be isotropically
 distributed, for a large enough, unbiased sample, the 
@@
 the extremely low mass (ELM) WD survey. We find maximum a posteriori (MAP) parameters for
-the WD companion population of $\mu_{\rm WD} = 0.73~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
+the WD companion population of $\mu_{\rm WD} = 0.71~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
 with a NS fraction consistent with zero, $f_{\rm NS} = 0\%$. However, the marginal posterior 
-distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 12\%$.
-We make samples from the posterior distribution publicly available and provide a  
-script for computing the companion mass distribution and the NS probability for newly discovered low mass WDs given a measured WD mass and mass function.
+distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
+We make samples from the posterior distribution publicly available so that future observational
+efforts may compute the NS probability for newly discovered low mass WDs given a measured 
+WD mass and mass function.
 \end{abstract}
@@
 	\startdata
-		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1.4)$ & $\left[\ln(40)\sigma\right]^{-1}$  & $\mathcal{U}(0, 1)$ \\
-		\multicolumn{2}{c}{} & & $(0.05 < \sigma/\Msun < 2)$ & \\
+		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\left[\ln(100)\sigma\right]^{-1}$  & $\mathcal{U}(0, 1)$ \\
+		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2)$ & \\
 		\cutinhead{Test Cases}
 		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
-		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 & MAP & {\bf 0.74} & {\bf 0.18} & {\bf 0.0} \\
 		 \hline
 		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
-		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 & MAP & {\bf 0.76} & {\bf 0.17} & {\bf 0.12} \\
 		 \hline
 		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
-		 & MAP & {\bf XXX} & {\bf XXX} & {\bf XXX} \\
+		 & MAP & {\bf 0.80} & {\bf 0.39} & {\bf 0.12} \\
 		 \cutinhead{ELM Sample}
-		 & MAP & 0.73 & 0.26 & {\bf 5\%?}
+		 & MAP & 0.71 & 0.26 & {\bf 0.0?}
 	\enddata
@@
 The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
-We run the walkers for an initial, burn-in period of 1000 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
+We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
 We then re-initialized the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
@@
 
-As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in \ref{tbl:parameters}.
+As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
 This test sample contains no NSs.
-The leftmost panel in Figure~\ref{fig:ELM_post} shows that the MAP $M_2$ distribution qualitatively matches the input distribution, while the second panel shows the posterior distribution quantitatively matches the input values shown as dashed lines.
-The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\approx 10$\%.
-Nevertheless, our model closely recovers the input parameters.
-The fourth panel lists individual systems, ordered by $\mf$, and provides the distribution of $P_{\rm NS}$ values for each.
-Few systems have $P_{\rm NS}$ values higher than $\approx$5\%, consistent with our input distribution of $f_{\rm NS}=$0\%.
+The leftmost panel in Figure~\ref{fig:ELM_post} shows that the MAP $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
+The second panel shows samples from the posterior distribution and the contours contain 68\% and 95\% of the samples.
+The input values lie cleanly within the inner contour in both projections of the posterior shown.
+The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim 10$\%.
+Nevertheless, our model recovers the input parameters for the white dwarf companion population.
+The fourth panel lists individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+Few systems have $P_{\rm NS}$ values higher than $\sim$5\%.
 
 \subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with parameters, setting $f_{\rm NS} =$ 10\%.
+For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with $f_{\rm NS} =$ 10\% and parameters described in Section~\ref{sec:experiments}.
 The panels are the same as in Test 1 described above.
@@
 The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS.
-However, this accounts for only roughly half of the systems with NSs in the sample, and the other half may found with low $\mf$ due to a low inclination angle.
-Although our model can correctly identify the $f_{\rm NS}$ within a factor of $\approx2$, it can only identify some LMWDs as having NS companions.
-
-% [TODO: We have also tried changing the mean and variance of the true neutron star distribution while keeping the fitting parameters fixed and found ...]
+However, this accounts for only roughly half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
 
@@
 For a final test, we generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, while keeping $f_{\rm NS}=$10\%.
-Again, the panels are the same as in Test 1 described above.
+The panels are the same as in Test 1 described above.
 The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm sigma}$.
-Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$, approximately as accurately as in Test 2.
+Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
 %The rightmost panel shows that despite accurately finding $f_{\rm NS}$, our model is not as good at identifying exactly which WDs are NSs.
@@
 The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.74}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
+The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.71}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
 The third panel the posterior distribution of $\mu$ and $f_{\rm NS}$.
@@
 
-The results of our model are shown in Figure \ref{fig:ELM_post}.
-The maximum a posteriori Gaussian model has $mu_{\rm WD} = {\bf 0.74} \Msun$ and $\sigma_{\rm WD} = {\bf 0.26}~\Msun$.
-While the well-defined peak in the posterior distribution demonstrates convergence of the model, the extended distribution toward larger variances could indicate that the true distribution does not match a Gaussian.
-However it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+The results of using our model on the ELM sample are shown in Figure \ref{fig:ELM_post}.
+The maximum a posteriori model has parameters $\mu_{\rm WD} = {\bf 0.71} \Msun$, $\sigma_{\rm WD} = {\bf 0.26}~\Msun$, and $f_{\rm NS} = 0\%$.
+The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution is not exactly Gaussian.
+However, it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
 
@@
 The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a significant tail toward higher NS probabilities.
-Our model does indicate an upper limit to the NS fraction of {\bf XXX\%} at the 95\% confidence level.
+Our model indicates an upper limit to the NS fraction of {\bf 25\%} at the 95\% confidence level.
 For 55 systems with observed radial velocity variations, this corresponds to a {\bf 0-4?} systems with NS companions.
-These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $f_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
+{\bf [Jeff: TODO -- this probably needs to be updated?]} These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $f_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
 With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $f_{\rm NS}$ of $10\substack{+4 \\ -2}\%$.
 
-Since our results are still consistent with a 0\% NS fraction, it is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
+%Since our results are still consistent with a 0\% NS fraction, it is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
 However the fourth panel in Figure \ref{fig:ELM_post} indicates which ELM WDs have the highest probability of hosting NS companions.
-Here, we show the relation between $\mf$ and $P_{\rm NS}$ for individual systems.
+Here, we show the distributions of $P_{\rm NS}$ for each system, ordered by $\mf$.
 This panel shows that $P_{\rm NS}$ only starts to significantly deviate from zero for {\bf $\mf\approx0.6 \Msun$} Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
@@
 If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
-In future work, we plan to combine these results with radio and x-ray non-detections to further constrain $P_{\rm NS}$ for each system.
+% In future work, we plan to combine these results with radio and x-ray non-detections to further constrain $P_{\rm NS}$ for each system.
 
@@
 
+{\bf Jeff: change your mind, or is this old?}
 To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share} \footnote{\url{http://figshare.com/authors/Jeff\_Andrews/644768}}.
@@
 
+\bibitem[Goodman~\&\ Weare(2010)]{goodman10}
+Goodman,~J. \& Weare,\ J.,
+2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
+
 \bibitem[{{Han}(1998)}]{han98}
@@
 
-\bibitem[Goodman~\&\ Weare(2010)]{goodman10}
-Goodman,~J. \& Weare,\ J.,
-2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
-
 \end{thebibliography}

### 2014-10-17 documents/letter/ms.tex
APW tweaks

@@
 We make samples from the posterior distribution publicly available so that future observational
-efforts may compute the NS probability for newly discovered low mass WDs given a measured 
-WD mass and mass function.
+efforts may compute the NS probability for newly discovered low mass WDs.
 \end{abstract}
@@
 Selecting the most likely candidates for multiwavelength follow-up is crucial.
-For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($\period$), WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
+For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
 Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:
@@
 \end{equation}
-The righthand side of this equation is the well-known mass function ($\mf$).
+The righthand side of this equation is the mass function ($\mf$).
 $M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
@@
 
-To answer these questions, we build the mathematical framework in Section 2 that we employ in our model described in Section 3.
+To answer these questions, we build the mathematical framework in Section 2, then apply our model to test and real data in Section 3.
 We give the results and discussion in Section 4, and conclude in Section 5.
@@
 
-where the product is over all each of the $j$ systems.  The marginal likelihood involves integrals over the latent variables $i$ and $M_2$,
+where the product is over each of the $j$ systems.  This marginal likelihood involves integrals over the latent variables $i$ and $M_2$,
 \begin{align}
@@
 \end{align}
-We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$.} and assume the inclination angles are isotropically distributed
+We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{The fractional uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$.} and assume the inclination angles are isotropically distributed
 \begin{align}
@@
 For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data.
-However, in tests below, we generate test data with a variety of mixture component forms.
+However, in tests below, we generate test data with different mixture component forms.
 We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1.3,2)~\Msun$,
@@
 We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
-We then re-initialized the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
+We then re-initialize the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
 We compute the autocorrelation time for each parameter to confirm they have converged.
@@
 \includegraphics[width=0.95\textwidth]{many-panel.pdf}
-\caption{The model results of our three tests described in Section~\ref{sec:tests}.
-The left-most panel shows a histogram of the $M_2$ drawn from each of our test distributions.
-Overplotted as a solid line is MAP distribution.
-The second panel shows the posterior distributions for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+\caption{Results from the three tests described in Section~\ref{sec:tests}.
+The left-most column shows histograms of $M_2$'s drawn from each of our test distributions.
+Overplotted as solid lines are the MAP models.
+The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 The dashed lines in the top two panels show the true values that the sample systems were drawn from.
 Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
-The third panel shows the posterior distribution for $f_{\rm NS}$ and $\sigma_{\rm WD}$, again with the dashed lines showing the true values.
+The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$, again the dashed lines show the input values.
 Finally, the rightmost panels list the individual systems and show each of their corresponding NS probabilities.
@@
 This test sample contains no NSs.
-The leftmost panel in Figure~\ref{fig:ELM_post} shows that the MAP $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
-The second panel shows samples from the posterior distribution and the contours contain 68\% and 95\% of the samples.
+The leftmost panel in Figure~\ref{fig:ELM_post} shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
+The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
 The input values lie cleanly within the inner contour in both projections of the posterior shown.
-The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim 10$\%.
+The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
 Nevertheless, our model recovers the input parameters for the white dwarf companion population.
@@
 \subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with $f_{\rm NS} =$ 10\% and parameters described in Section~\ref{sec:experiments}.
+For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
 The panels are the same as in Test 1 described above.
-Again, our model recovers the input values for $\mu{\rm WD}$ and $\sigma_{\rm WD}$.
+Again, our model recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior again shows a tail toward higher probabilities.
@@
 The panels are the same as in Test 1 described above.
-The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm sigma}$.
+The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
@@
 These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit.
-Because of the uncertainties in their formation, we remove these from our analysis.
+We do not include these systems in our analysis.
 
@@
 \includegraphics[width=0.95\textwidth]{real-data.pdf}
-\caption{The posteriors for our model applied to the ELM WDs.
+\caption{Results from applying our model to the ELM WDs.
 The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
-The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.71}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
-The third panel the posterior distribution of $\mu$ and $f_{\rm NS}$.
+The second panel shows posterior samples of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.71}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
+The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$.
 The last panel lists individual LMWDs in the ELM sample and shows each of their corresponding NS probabilities.
 The systems are ordered by increasing $\mf$.
-The three systems with $P_{\rm NS}=$0\% are the three eclipsing systems.}
+The three systems with $P_{\rm NS}=$0\% are the three eclipsing systems with known $M_2$'s.}
 \label{fig:ELM_post}
@@
 
-The results of using our model on the ELM sample are shown in Figure \ref{fig:ELM_post}.
-The maximum a posteriori model has parameters $\mu_{\rm WD} = {\bf 0.71} \Msun$, $\sigma_{\rm WD} = {\bf 0.26}~\Msun$, and $f_{\rm NS} = 0\%$.
+The results from applying our model to the ELM sample are shown in Figure \ref{fig:ELM_post}.
+The MAP model has parameters $\mu_{\rm WD} = {\bf 0.71}~\Msun$, $\sigma_{\rm WD} = {\bf 0.26}~\Msun$, and $f_{\rm NS} = 0\%$.
 The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution is not exactly Gaussian.
@@
 
-Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper \Msun (based on the Chandrasekhar mass).
+Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
 In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
@@
 The two systems with the highest $P_{\rm NS}$ are J0811$+$0225 and J1741$+$6526.
-These systems are ideal candidates for searches for NS companions in radio and X-ray.
-Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable in radio \citep{vLeeuwen07}.
+These systems are ideal candidates for radio and X-ray searches for NS companions.
+Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
 All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
-Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all those sources have a low probability of hosting a NS companion.
+Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all of those sources have a low probability of hosting a NS companion.
 If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
@@
 
-We have created a mathematical description using a Bayesian framework to describe the companion mass distribution of a set of unbiased single-lined spectroscopic binaries.
-We have used that mathematical framework to build a Markov Chain Monte Carlo model.
-Our model recovers the input parameters for three separate test cases with WD and NS companion masses drawn from different distributions.
-In particular, even if the companion mass distribution is not drawn from a Gaussian distribution, our model can still determine the NS fraction within a factor of $\approx2$.
+We have developed a statistical model to infer the companion mass distribution for a set of unbiased, single-lined, spectroscopic binaries.
+Our model recovers the correct input parameters for three separate test cases with WD and NS companion masses drawn from different distributions.
+In particular, even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
 
 We then applied our model to the set of WDs from the ELM WD survey.
-Our model indicates that the fraction of ELM WDs with NS companions is of order a few percent.
+Our model indicates that the fraction of ELM WDs with NS companions is consistent with zero, but could be up to $\sim$16\% (within 1-$\sigma$).
 We identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion, and suggest the multi-wavelength follow-up is warranted.

### 2014-10-17 documents/letter/ms.tex
N_words = 3498

@@
 
-\title{The Companion Mass Distribution of extremely low-mass white dwarfs}
+\title{The mass distribution of companions to extremely low-mass white dwarfs}
 \author{Jeff Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}
@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen 
-companion stars given orbital period and projected radial velocity measurements of the primary. We use a mixture of 
+companion stars to low mass white dwarfs (LMWD) given orbital period and projected radial velocity measurements of the primary. We use a mixture of 
 two Gaussians to model the true companion mass distribution to represent 
-populations of white dwarfs (WD) and neutron stars (NS). We run this model on mock data sets in order to test the
-robustness of our inferences. We then apply our model to 55 of the 61 white dwarfs in 
+populations of white dwarfs (WD) and neutron stars (NS). 
+Our model successfully recovers the initial parameters of several mock data sets.
+We then apply our model to 55 of the 61 white dwarfs in 
 the extremely low mass (ELM) WD survey. We find maximum a posteriori (MAP) parameters for
@@
 
+\keywords{binaries: general --- binaries: spectroscopic --- methods: statistical --- white dwarfs}
+
 \section{Introduction}
-
-%The dramatic increase in the number of spectroscopically confirmed white dwarfs (WDs) is seen in the most recently compiled sample from Data Release 7 (DR7) of the Sloan Digital Sky Survey (SDSS), which contains $\sim$20,000 confirmed WDs \citep{kleinman13}.
-While the distribution of hydrogen atmosphere (DA) WD masses is strongly peaked at $0.6~\Msun$, a small but non-negligible number ($\approx$6\%) are seen as low mass WDs (LMWD) with $M<0.4~\Msun$ both in SDSS and elsewhere \citep[e.g., the Palomar Green Survey;][]{liebert05}.
 
@@
 \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
-%which the primary overfills its Roche lobe in either an unstable, common envelope \citep{vdSluys06}, or a phase of stable but non-conservative mass transfer \citep{woods12}.
-After the primary has become a WD, the secondary overfills its Roche lobe, forming a common envelope prior to core helium ignition, leaving a He-core WD secondary in a tight orbit with either a He- or CO- core WD \citep{han98,nelemans00,nelemans01}.
-In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations and cementing LMWDs as fruitful targets for binary searches.
-The Extremely Low Mass (ELM) WD Survey identifies LMWDs in SDSS for spectroscopic follow-up
-% using combined constraints on photometry and reduced proper motions 
-\citep{ELMI}.
-After their initial investigation found 11 of 12 LMWDs had close binary companions, further radial velocity follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
+In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations.
+The ELM WD Survey identifies LMWDs in SDSS for spectroscopic follow-up \citep{ELMI}.
+After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
@@
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries.
-We focus on several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
+We focus on several specific astrophysical questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
@@
 \includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
-\caption{The $\period$ - $M_1$ distribution of the ELM WD sample.
-The three eclipsing systems, with known $M_2$ are shown by the filled circles.
-Arrows indicate the masses of ELM WDs without detected radial velocity variation.
-Triangles indicate the positions of the known WD-NS binaries.
+\caption{The $\period$ - $M_1$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
+The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the ELM WDs without detected radial velocity variations are shown by the arrows.
 From $\period$ and $M_1$ alone, the two populations are indistinguishable.}
@@
 \begin{equation}
-	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - \mf.
+	g(M_1,M_2,i) = \mf - \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i.
 \end{equation}
@@
 %	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, \mf, M_1)\\
-	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right] 
+	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] 
 \end{align}
@@
 	\startdata
-		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\left[\ln(100)\sigma\right]^{-1}$  & $\mathcal{U}(0, 1)$ \\
+		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\propto \sigma^{-1}$  & $\mathcal{U}(0, 1)$ \\
 		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2)$ & \\
@@
 		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
-		 & MAP & {\bf 0.74} & {\bf 0.18} & {\bf 0.0} \\
+		 & MAP & 0.74 & 0.18 & 0.0 \\
 		 \hline
 		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
-		 & MAP & {\bf 0.76} & {\bf 0.17} & {\bf 0.12} \\
+		 & MAP & 0.76 & 0.17 & 0.12 \\
 		 \hline
 		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
-		 & MAP & {\bf 0.80} & {\bf 0.39} & {\bf 0.12} \\
+		 & MAP & 0.80 & 0.39 & 0.12 \\
 		 \cutinhead{ELM Sample}
-		 & MAP & 0.71 & 0.26 & {\bf 0.0?}
+		 & MAP & 0.71 & 0.26 & 0.0
 	\enddata
@@
 There are 3 free parameters.
-We additionally fix the NS distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.1~\Msun.$}\
+We additionally fix the NS distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
 
@@
 We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
-The algorithm is implemented in the \texttt{Python} programming language \citep{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+The algorithm is implemented in the \texttt{Python} programming language \citep[{\tt emcee};][]{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
 We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
@@
 The dashed lines in the top two panels show the true values that the sample systems were drawn from.
+Contours designate the 68\% and 95\% contours.
 Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
 The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$, again the dashed lines show the input values.
-Finally, the rightmost panels list the individual systems and show each of their corresponding NS probabilities.
-The systems are ordered by increasing $\mf$.
+Finally, the rightmost panels list the individual systems (ordered by increasing $\mf$) and show each of their corresponding NS probabilities.
 }
@@
 \subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the white dwarf component as the previous example (Section~\ref{sec:exp1}), but we now add an additional neutron star component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
+For our next test, we use the same Gaussian distribution to generate companion masses for the WD component as the previous example (Section~\ref{sec:exp1}), but we now add an additional NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
 The panels are the same as in Test 1 described above.
@@
 The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS.
-However, this accounts for only roughly half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
+However, this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
 
 \subsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
-For a final test, we generate companion masses for the white dwarf component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, while keeping $f_{\rm NS}=$10\%.
+For a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, while keeping $f_{\rm NS}=$10\%.
 The panels are the same as in Test 1 described above.
@@
 Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-%The rightmost panel shows that despite accurately finding $f_{\rm NS}$, our model is not as good at identifying exactly which WDs are NSs.
 
@@
 Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
-These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit.
+These LMWDs could also have companions at systematically longer orbital periods resulting in orbital velocities below the detection limit.
 We do not include these systems in our analysis.
@@
 The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
-The second panel shows posterior samples of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has $\mu_{\rm WD}= {\bf 0.71}~\Msun$ and $\sigma_{\rm WD}= {\bf 0.26}~\Msun$.
+The second panel shows posterior samples of $\mu$ and $\sigma$; The MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
 The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$.
-The last panel lists individual LMWDs in the ELM sample and shows each of their corresponding NS probabilities.
-The systems are ordered by increasing $\mf$.
-The three systems with $P_{\rm NS}=$0\% are the three eclipsing systems with known $M_2$'s.}
+The last panel lists individual LMWDs in the ELM sample (ordered by increasing $\mf$) and shows each of their corresponding NS probabilities.
+The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with known $M_2$'s.}
 \label{fig:ELM_post}
@@
 The results from applying our model to the ELM sample are shown in Figure \ref{fig:ELM_post}.
-The MAP model has parameters $\mu_{\rm WD} = {\bf 0.71}~\Msun$, $\sigma_{\rm WD} = {\bf 0.26}~\Msun$, and $f_{\rm NS} = 0\%$.
+The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$.
 The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution is not exactly Gaussian.
-However, it is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
 Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
@@
 The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
+Our results here suggest the companion sample is composed mainly of CO WDs.
 Our model could be expanded to include a two Gaussian model --- one for each WD population.
@@
 The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a significant tail toward higher NS probabilities.
-Our model indicates an upper limit to the NS fraction of {\bf 25\%} at the 95\% confidence level.
-For 55 systems with observed radial velocity variations, this corresponds to a {\bf 0-4?} systems with NS companions.
-{\bf [Jeff: TODO -- this probably needs to be updated?]} These results are in agreement with independent constraints from \citet{vLeeuwen07} who set an upper limit on $f_{\rm NS}$ of 18$\pm5$\% based on the non-detection of radio emission from eight LMWD targets.
-With non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample, \citet{agueros09b} place a more stringent upper limit on $f_{\rm NS}$ of $10\substack{+4 \\ -2}\%$.
-
-%Since our results are still consistent with a 0\% NS fraction, it is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions.
-However the fourth panel in Figure \ref{fig:ELM_post} indicates which ELM WDs have the highest probability of hosting NS companions.
-Here, we show the distributions of $P_{\rm NS}$ for each system, ordered by $\mf$.
-This panel shows that $P_{\rm NS}$ only starts to significantly deviate from zero for {\bf $\mf\approx0.6 \Msun$} Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.
-
-The two systems with the highest $P_{\rm NS}$ are J0811$+$0225 and J1741$+$6526.
-These systems are ideal candidates for radio and X-ray searches for NS companions.
-Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%) based on the non-detection of radio emission from eight LMWD targets and \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}\%$) based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
+Because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
 All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
 Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all of those sources have a low probability of hosting a NS companion.
-If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
-% In future work, we plan to combine these results with radio and x-ray non-detections to further constrain $P_{\rm NS}$ for each system.
+If the two systems with the highest $P_{\rm NS}$, J0811$+$0225 and J1741$+$6526, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
+It is worth noting that systems with NS companions cannot necessarily be differentiated from those with WD companions through the mass function and LMWD mass alone.
+Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.
+%These systems are ideal candidates for radio and X-ray searches for NS companions. 
+%Radio observations of these objects are in progress, however
 
-It is worth noting that the fourth panels in our test cases in Figure~\ref{fig:tests} shows that our model is fairly good at identifying those systems most likely to host NS's.
+%It is worth noting that the fourth panels in our test cases in Figure~\ref{fig:tests} shows that our model is fairly good at identifying those systems most likely to host NS's.
 However it also shows that roughly half of the LMWDs with NS companions may appear with a deceptively low $f_{\rm NS}$ due to the inclination angle.
-Systems with NS companions cannot all be differentiated from those with WD companions through the mass function and LMWD mass alone.
-Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.
 
-{\bf Jeff: change your mind, or is this old?}
-To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share} \footnote{\url{http://figshare.com/authors/Jeff\_Andrews/644768}}.
+To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}}.
 We further provide a {\tt python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
@@
 
-Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample to search for eclipses.
+Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
+Based on non-detection of eclipses and modeling of photometric variability, they set limits on the inclination angles of these systems.
+We have not included these observations in our model, but we plan to explore this in a future work.
+
+%Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample to search for eclipses.
 They placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
@@
 Our model indicates that the fraction of ELM WDs with NS companions is consistent with zero, but could be up to $\sim$16\% (within 1-$\sigma$).
-We identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion, and suggest the multi-wavelength follow-up is warranted.
+We identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
 Our model further suggests that the majority of ELM WDs have CO-core WD companions.
-This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs.
+This is in contrast to recent predictions from population synthesis models which predict the dominant companion population should be He-core WDs.
 
 There are several ways in which this model can be expanded.
-First, our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
+Our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
 Applying this method to various populations can help to constrain the formation of particularly classes of binaries.
@@
 \acknowledgements
-The authors wish to acknowledge David Hogg (NYU) for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
+The authors wish to acknowledge David Hogg and DJ D'Orazio for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
 APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
@@
 
-\begin{thebibliography}{35}
+\begin{thebibliography}{36}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

### 2014-10-22 documents/letter/ms.tex
Updated .tex

@@
 
-\title{The mass distribution of companions to extremely low-mass white dwarfs}
-\author{Jeff Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}
+\title{The mass distribution of companions to low-mass white dwarfs}
+\author{Jeff J. Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}
 
@@
 We then apply our model to 55 of the 61 white dwarfs in 
-the extremely low mass (ELM) WD survey. We find maximum a posteriori (MAP) parameters for
+the extremely low mass (ELM) WD survey. We find maximum a posteriori parameters for
 the WD companion population of $\mu_{\rm WD} = 0.71~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
@@
 
-Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce WDs with $M\lesssim0.45~ \Msun$ through single star evolution.
-These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems.
-\citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
+Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution.
+These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
 In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations.
-The ELM WD Survey identifies LMWDs in SDSS for spectroscopic follow-up \citep{ELMI}.
+The ELM WD Survey identifies LMWDs in SDSS and elsewhere for spectroscopic follow-up, focusing in particular on extremely low mass WDs ($M\lesssim0.3~ \Msun$) \citep{ELMI}.
 After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
@@
 However, all radio searches for pulsed emission, as well as searches for blackbody X-ray emission from a NS surface have been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
-Yet, such systems must exist since LMWDs are observed as companions around millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}
+Yet, such systems must exist since LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
+Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
 
-Selecting the most likely candidates for multiwavelength follow-up is crucial.
+%Selecting the most likely candidates for multiwavelength follow-up is crucial. 
 For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
@@
 55 of the 61 systems have precise $M_1$, $\period$, and $K$ measured; we refer to this as the ELM sample.
-Since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries.
+Instead of spectroscopic fits to component masses, their constraints are based on the measured post-Keplerian parameters in their sample.
 We focus on several specific astrophysical questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
@@
 \begin{align}
-    p(\mf \given \bs{\theta}) &= \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2  \nonumber \\
+    p(\mf \given \bs{\theta}) &= \int_{-\infty}^\infty dM_2 \int_0^{\pi/2} di  \nonumber \\
       & \qquad {} \times p(\mf \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
@@
 We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{The fractional uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$.} and assume the inclination angles are isotropically distributed
-\begin{align}
-	p(\mf \given M_1, M_2, i) &= \delta \left[\mf - f(M_1, M_2, i) \right]\\
-	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
-	p(i) &= \sin i.
-\end{align}
-For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
+\begin{equation}
+	p(\mf \given M_1, M_2, i) = \delta \left[\mf - f(M_1, M_2, i) \right]
+\end{equation}
+where
+\begin{equation}
+	f(M_1, M_2, i) = \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}
+\end{equation}
+and
+\begin{equation}
+	p(i) = \sin i.
+\end{equation}
+For now, we do not specify a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
 \begin{align}
@@
 %    & \qquad {} \times \delta \left[\mf - f(M_1, M_2, i)\right]~\sin i\\
-    p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di  \nonumber \\
-    & \qquad {} \times ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
+    p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta})  \nonumber \\
+    & \qquad {} \times \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
 \end{align}
@@
 \end{align}
-With this in mind, we may write the marginal likelihood as
+We may rewrite the marginal likelihood as
 \begin{align}
@@
 For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data.
-However, in tests below, we generate test data with different mixture component forms.
+In tests below, we generate test data with different mixture component forms.
 We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1.3,2)~\Msun$,
@@
 \begin{align}
-	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,\left[ 0.2 < \frac{M_2}{\Msun} < \wdupper \right] \\
-	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\, \left[1.3 < \frac{M_2}{\Msun} < 2 \right].
+	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper \\
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2.
 \end{align}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-We choose standard priors on these parameters: for the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$; we use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
+We choose uninformative priors on these parameters: for the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$; we use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
@@
 We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
-We then re-initialize the walkers from their positions at the end of this run, throw out the burn-in samples, and run again for 1000 steps.
-We compute the autocorrelation time for each parameter to confirm they have converged.
+We then re-initialize the walkers from their positions at the end of this run and run again for 1000 steps.
+We throw out the burn-in samples to eliminate any effects from our choice of initial conditions.
+The autocorrelation times for each parameter confirm they have converged.
 
@@
 These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $\mf$.
-We draw primary masses from a uniform distribution, $M_1 \sim \mathcal{U}(0.2,0.4)~\Msun$.
+We draw primary masses from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
 We apply the same Gaussian mixture model to all test datasets to infer the parameters of the white dwarf mixture component and neutron star fraction.
@@
 \caption{Results from the three tests described in Section~\ref{sec:tests}.
-The left-most column shows histograms of $M_2$'s drawn from each of our test distributions.
+The left-most column shows histograms of $M_2$ drawn from each of our test distributions.
 Overplotted as solid lines are the MAP models.
@@
 
-\subsection{Test 1: Single Gaussian (white dwarf)} \label{sec:exp1}
+\subsection{Test 1: Single Gaussian (WD)} \label{sec:exp1}
 
-As a first test, we generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
+As a first test, we generate $M_2$ by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
 This test sample contains no NSs.
-The leftmost panel in Figure~\ref{fig:ELM_post} shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
+In the top row of Figure~\ref{fig:ELM_post}, the leftmost panel shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
 The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
@@
 
-\subsection{Test 2: Two Gaussians (white dwarf + neutron star)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the WD component as the previous example (Section~\ref{sec:exp1}), but we now add an additional NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
-The panels are the same as in Test 1 described above.
-Again, our model recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+\subsection{Test 2: Two Gaussians (WD + NS)} \label{sec:exp2}
+For our next test, we use the same Gaussian distribution to generate companion masses for the WD component as the previous example, but we add an additional NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
+The middle row of Figure~\ref{fig:ELM_post} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior again shows a tail toward higher probabilities.
-The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS.
-However, this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
+The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS, however this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
 
-\subsection{Test 3: Uniform (white dwarf) + Gaussian (neutron star)} \label{sec:exp3}
-For a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, while keeping $f_{\rm NS}=$10\%.
-The panels are the same as in Test 1 described above.
+\subsection{Test 3: Uniform (WD) + Gaussian (NS)} \label{sec:exp3}
+As a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$ while keeping $f_{\rm NS}=$10\%.
+The bottom row of Figure~\ref{fig:ELM_post} shows the results of this test.
 The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
@@
 
-The ELM WD sample is composed of 55 of 61 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
+The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
 Fitting the sample's high S/N spectra to templates provides precisely determine $M_1$ values.
 We use the spectroscopic solutions found in \citet{gianninas14}.
-Three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$ \citep{kaplan14}, J0651$+$2844: $M_2=0.50~\Msun$ \citep{brown11b}, and J0751$-$0141: $M_2=0.97~\Msun$ \citep{kilic14}).
+Three systems are eclipsing binaries, with known companion masses (NLTT 11748: $M_2=0.72~\Msun$ \citep{kaplan14}, SDSS J065133.3$+$284423.3: $M_2=0.50~\Msun$ \citep{brown11b}, and SDSS J075141.2$-$014120.9: $M_2=0.97~\Msun$ \citep{kilic14}).
 For these systems, the likelihood reduces to:
@@
 where $M_2^*$ is the mass of the WD companion in these three systems.
+
+Since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
 
@@
 The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
-The second panel shows posterior samples of $\mu$ and $\sigma$; The MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
+The second panel shows posterior samples of $\mu$ and $\sigma$; the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
 The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$.
 The last panel lists individual LMWDs in the ELM sample (ordered by increasing $\mf$) and shows each of their corresponding NS probabilities.
-The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with known $M_2$'s.}
+The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.}
 \label{fig:ELM_post}
@@
 
-Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun (based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
-In principle, priors could be added based on population synthesis models which suggest there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
+Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
+In principle, priors could be added based on population synthesis models that suggest that there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
 The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
@@
 
-The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward zero, however there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%) based on the non-detection of radio emission from eight LMWD targets and \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}\%$) based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
-Because a NS companion may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
-All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
-Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all of those sources have a low probability of hosting a NS companion.
-If the two systems with the highest $P_{\rm NS}$, J0811$+$0225 and J1741$+$6526, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
+The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward 0.
+However, there is a significant tail toward higher NS probabilities.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%), based on the non-detection of radio emission from eight LMWD targets, and from \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}\%$), based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
+Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
+All NSs give off blackbody radiation peaked in X-ray wavelengths, so X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
+Previous searches for LMWDs with X-ray counterparts have all been non-detections \citep{ELMII,ELMIV,kilic13}.
+However, we show here that all of those sources have a low probability of hosting a NS companion.
+If the two systems with the highest $P_{\rm NS}$, SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
+
 It is worth noting that systems with NS companions cannot necessarily be differentiated from those with WD companions through the mass function and LMWD mass alone.
 Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.
+
 %These systems are ideal candidates for radio and X-ray searches for NS companions. 
@@
 
-To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}}.
-We further provide a {\tt python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
+To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
 This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
-
-Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
-Based on non-detection of eclipses and modeling of photometric variability, they set limits on the inclination angles of these systems.
-We have not included these observations in our model, but we plan to explore this in a future work.
 
@@
 Our model indicates that the fraction of ELM WDs with NS companions is consistent with zero, but could be up to $\sim$16\% (within 1-$\sigma$).
-We identify J0811$+$0225 and J1741$+$6526 as having the highest probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
+We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
 Our model further suggests that the majority of ELM WDs have CO-core WD companions.
-This is in contrast to recent predictions from population synthesis models which predict the dominant companion population should be He-core WDs.
+This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep{toonen12}.
 
@@
 In particular, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
+
+Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
+Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems.
+We have not included these observations in our model, but we plan to explore this in the future.
 
@@
 
-\begin{thebibliography}{36}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{a}}){Ag{\"u}eros}, {Camilo},
-  {Silvestri}, {Kleinman}, {Anderson}, \& {Liebert}}]{agueros09b}
-{Ag{\"u}eros}, M.~A., {Camilo}, F., {Silvestri}, N.~M., {Kleinman}, S.~J.,
-  {Anderson}, S.~F., \& {Liebert}, J.~W. 2009{\natexlab{a}}, \apj, 697, 283
-
-\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{b}}){Ag{\"u}eros}, {Heinke},
-  {Camilo}, {Kilic}, {Anderson}, {Freire}, {Kleinman}, {Liebert}, \&
-  {Silvestri}}]{agueros09a}
-{Ag{\"u}eros}, M.~A. {et~al.} 2009{\natexlab{b}}, \apjl, 700, L123
-
-\bibitem[{{Antoniadis} {et~al.}(2012){Antoniadis}, {van Kerkwijk}, {Koester},
-  {Freire}, {Wex}, {Tauris}, {Kramer}, \& {Bassa}}]{antoniadis12}
-{Antoniadis}, J., {van Kerkwijk}, M.~H., {Koester}, D., {Freire}, P.~C.~C.,
-  {Wex}, N., {Tauris}, T.~M., {Kramer}, M., \& {Bassa}, C.~G. 2012, \mnras,
-  423, 3316
-
-\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
-  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
-  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
-  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
-  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
-  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
-  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
-  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy13}
-{Astropy Collaboration} {et~al.} 2013, \aap, 558, A33
-
-\bibitem[{{Bassa} {et~al.}(2006){Bassa}, {van Kerkwijk}, {Koester}, \&
-  {Verbunt}}]{bassa06}
-{Bassa}, C.~G., {van Kerkwijk}, M.~H., {Koester}, D., \& {Verbunt}, F. 2006,
-  \aap, 456, 295
-
-\bibitem[{{Benvenuto} \& {De Vito}(2005)}]{benvenuto05}
-{Benvenuto}, O.~G., \& {De Vito}, M.~A. 2005, \mnras, 362, 891
-
-\bibitem[{{Brown} {et~al.}(2013){Brown}, {Kilic}, {Allende Prieto},
-  {Gianninas}, \& {Kenyon}}]{ELMV}
-{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., {Gianninas}, A., \&
-  {Kenyon}, S.~J. 2013, \apj, 769, 66
-
-\bibitem[{{Brown} {et~al.}(2010){Brown}, {Kilic}, {Allende Prieto}, \&
-  {Kenyon}}]{ELMI}
-{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., \& {Kenyon}, S.~J. 2010,
-  \apj, 723, 1072
-
-\bibitem[{{Brown} {et~al.}(2012){Brown}, {Kilic}, {Allende Prieto}, \&
-  {Kenyon}}]{ELMIII}
----. 2012, \apj, 744, 142
-
-\bibitem[{{Brown} {et~al.}(2011){Brown}, {Kilic}, {Hermes}, {Allende Prieto},
-  {Kenyon}, \& {Winget}}]{brown11b}
-{Brown}, W.~R., {Kilic}, M., {Hermes}, J.~J., {Allende Prieto}, C., {Kenyon},
-  S.~J., \& {Winget}, D.~E. 2011, \apjl, 737, L23
-
-\bibitem[{{Callanan} {et~al.}(1998){Callanan}, {Garnavich}, \&
-  {Koester}}]{callanan98}
-{Callanan}, P.~J., {Garnavich}, P.~M., \& {Koester}, D. 1998, \mnras, 298, 207
-
-\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
-  {Goodman}}]{foremanmackey13}
-{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
-  125, 306
-
-\bibitem[{{Gianninas} {et~al.}(2014){Gianninas}, {Dufour}, {Kilic}, {Brown},
-  {Bergeron}, \& {Hermes}}]{gianninas14}
-{Gianninas}, A., {Dufour}, P., {Kilic}, M., {Brown}, W.~R., {Bergeron}, P., \&
-  {Hermes}, J.~J. 2014, \apj, 794, 35
+\bibliography{refs}
 
@@
 
-\bibitem[{{Han}(1998)}]{han98}
-{Han}, Z. 1998, \mnras, 296, 1019
-
-\bibitem[{{Hermes} {et~al.}(2014){Hermes}, {Brown}, {Kilic}, {Gianninas},
-  {Chote}, {Sullivan}, {Winget}, {Bell}, {Falcon}, {Winget}, {Mason},
-  {Harrold}, \& {Montgomery}}]{hermes14}
-{Hermes}, J.~J. {et~al.} 2014, \apj, 792, 39
-
-\bibitem[{{Jia} \& {Li}(2014)}]{jia14}
-{Jia}, K., \& {Li}, X.-D. 2014, \apj, 791, 127
-
-\bibitem[{{Kaplan} {et~al.}(2014){Kaplan}, {Marsh}, {Walker}, {Bildsten},
-  {Bours}, {Breedt}, {Copperwheat}, {Dhillon}, {Howell}, {Littlefair},
-  {Shporer}, \& {Steinfadt}}]{kaplan14}
-{Kaplan}, D.~L. {et~al.} 2014, \apj, 780, 167
-
-\bibitem[{{Kilic} {et~al.}(2011){Kilic}, {Brown}, {Allende Prieto},
-  {Ag{\"u}eros}, {Heinke}, \& {Kenyon}}]{ELMII}
-{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Ag{\"u}eros}, M.~A.,
-  {Heinke}, C., \& {Kenyon}, S.~J. 2011, \apj, 727, 3
-
-\bibitem[{{Kilic} {et~al.}(2012){Kilic}, {Brown}, {Allende Prieto}, {Kenyon},
-  {Heinke}, {Ag{\"u}eros}, \& {Kleinman}}]{ELMIV}
-{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Kenyon}, S.~J., {Heinke},
-  C.~O., {Ag{\"u}eros}, M.~A., \& {Kleinman}, S.~J. 2012, \apj, 751, 141
-
-\bibitem[{{Kilic} {et~al.}(2013){Kilic}, {Gianninas}, {Brown}, {Harris},
-  {Dahn}, {Ag{\"u}eros}, {Heinke}, {Kenyon}, {Panei}, \& {Camilo}}]{kilic13}
-{Kilic}, M. {et~al.} 2013, \mnras, 434, 3582
-
-\bibitem[{{Kilic} {et~al.}(2014){Kilic}, {Hermes}, {Gianninas}, {Brown},
-  {Heinke}, {Ag{\"u}eros}, {Chote}, {Sullivan}, {Bell}, \& {Harrold}}]{kilic14}
----. 2014, \mnras, 438, L26
-
-\bibitem[{{Kilic} {et~al.}(2007){Kilic}, {Stanek}, \& {Pinsonneault}}]{kilic07}
-{Kilic}, M., {Stanek}, K.~Z., \& {Pinsonneault}, M.~H. 2007, \apj, 671, 761
-
-\bibitem[{{Kiziltan} {et~al.}(2013){Kiziltan}, {Kottas}, {De Yoreo}, \&
-  {Thorsett}}]{kiziltan13}
-{Kiziltan}, B., {Kottas}, A., {De Yoreo}, M., \& {Thorsett}, S.~E. 2013, \apj,
-  778, 66
-
-\bibitem[{{Kleinman} {et~al.}(2013){Kleinman}, {Kepler}, {Koester}, {Pelisoli},
-  {Pe{\c c}anha}, {Nitta}, {Costa}, {Krzesinski}, {Dufour}, {Lachapelle},
-  {Bergeron}, {Yip}, {Harris}, {Eisenstein}, {Althaus}, \&
-  {C{\'o}rsico}}]{kleinman13}
-{Kleinman}, S.~J. {et~al.} 2013, \apjs, 204, 5
-
-\bibitem[{{Liebert} {et~al.}(2005){Liebert}, {Bergeron}, \&
-  {Holberg}}]{liebert05}
-{Liebert}, J., {Bergeron}, P., \& {Holberg}, J.~B. 2005, \apjs, 156, 47
-
-\bibitem[{{Marsh} {et~al.}(1995){Marsh}, {Dhillon}, \& {Duck}}]{marsh95}
-{Marsh}, T.~R., {Dhillon}, V.~S., \& {Duck}, S.~R. 1995, \mnras, 275, 828
-
-\bibitem[{{Nelemans} {et~al.}(2000){Nelemans}, {Verbunt}, {Yungelson}, \&
-  {Portegies Zwart}}]{nelemans00}
-{Nelemans}, G., {Verbunt}, F., {Yungelson}, L.~R., \& {Portegies Zwart}, S.~F.
-  2000, \aap, 360, 1011
-
-\bibitem[{{Nelemans} {et~al.}(2001){Nelemans}, {Yungelson}, {Portegies Zwart},
-  \& {Verbunt}}]{nelemans01}
-{Nelemans}, G., {Yungelson}, L.~R., {Portegies Zwart}, S.~F., \& {Verbunt}, F.
-  2001, \aap, 365, 491
-
-\bibitem[{{{\"O}zel} {et~al.}(2012){{\"O}zel}, {Psaltis}, {Narayan}, \& {Santos
-  Villarreal}}]{ozel12}
-{{\"O}zel}, F., {Psaltis}, D., {Narayan}, R., \& {Santos Villarreal}, A. 2012,
-  \apj, 757, 55
-
-\bibitem[{{Smedley} {et~al.}(2014){Smedley}, {Tout}, {Ferrario}, \&
-  {Wickramasinghe}}]{smedley14}
-{Smedley}, S.~L., {Tout}, C.~A., {Ferrario}, L., \& {Wickramasinghe}, D.~T.
-  2014, \mnras, 437, 2217
-
-\bibitem[{{Toonen} {et~al.}(2012){Toonen}, {Nelemans}, \& {Portegies
-  Zwart}}]{toonen12}
-{Toonen}, S., {Nelemans}, G., \& {Portegies Zwart}, S. 2012, \aap, 546, A70
-
-\bibitem[{{van der Sluys} {et~al.}(2006){van der Sluys}, {Verbunt}, \&
-  {Pols}}]{vdSluys06}
-{van der Sluys}, M.~V., {Verbunt}, F., \& {Pols}, O.~R. 2006, \aap, 460, 209
-
-\bibitem[{{van Kerkwijk} {et~al.}(1996){van Kerkwijk}, {Bergeron}, \&
-  {Kulkarni}}]{vKerkwijk96}
-{van Kerkwijk}, M.~H., {Bergeron}, P., \& {Kulkarni}, S.~R. 1996, \apjl, 467,
-  L89
-
-\bibitem[{{van Leeuwen} {et~al.}(2007){van Leeuwen}, {Ferdman}, {Meyer}, \&
-  {Stairs}}]{vLeeuwen07}
-{van Leeuwen}, J., {Ferdman}, R.~D., {Meyer}, S., \& {Stairs}, I. 2007, \mnras,
-  374, 1437
-
-\bibitem[{{Woods} {et~al.}(2012){Woods}, {Ivanova}, {van der Sluys}, \&
-  {Chaichenets}}]{woods12}
-{Woods}, T.~E., {Ivanova}, N., {van der Sluys}, M.~V., \& {Chaichenets}, S.
-  2012, \apj, 744, 12
-
-%\bibliography{refs}
-
-\end{thebibliography}
-
 \end{document}

### 2014-10-23 documents/letter/ms.tex
updated bibliography

@@
 
-\bibliography{refs}
+\begin{thebibliography}{36}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{a}}){Ag{\"u}eros}, {Camilo},
+  {Silvestri}, {Kleinman}, {Anderson}, \& {Liebert}}]{agueros09b}
+{Ag{\"u}eros}, M.~A., {Camilo}, F., {Silvestri}, N.~M., {Kleinman}, S.~J.,
+  {Anderson}, S.~F., \& {Liebert}, J.~W. 2009{\natexlab{a}}, \apj, 697, 283
+
+\bibitem[{{Ag{\"u}eros} {et~al.}(2009{\natexlab{b}}){Ag{\"u}eros}, {Heinke},
+  {Camilo}, {Kilic}, {Anderson}, {Freire}, {Kleinman}, {Liebert}, \&
+  {Silvestri}}]{agueros09a}
+{Ag{\"u}eros}, M.~A. {et~al.} 2009{\natexlab{b}}, \apjl, 700, L123
+
+\bibitem[{{Antoniadis} {et~al.}(2012){Antoniadis}, {van Kerkwijk}, {Koester},
+  {Freire}, {Wex}, {Tauris}, {Kramer}, \& {Bassa}}]{antoniadis12}
+{Antoniadis}, J., {van Kerkwijk}, M.~H., {Koester}, D., {Freire}, P.~C.~C.,
+  {Wex}, N., {Tauris}, T.~M., {Kramer}, M., \& {Bassa}, C.~G. 2012, \mnras,
+  423, 3316
+
+\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
+  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
+  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
+  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
+  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
+  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
+  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
+  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy13}
+{Astropy Collaboration} {et~al.} 2013, \aap, 558, A33
+
+\bibitem[{{Bassa} {et~al.}(2006){Bassa}, {van Kerkwijk}, {Koester}, \&
+  {Verbunt}}]{bassa06}
+{Bassa}, C.~G., {van Kerkwijk}, M.~H., {Koester}, D., \& {Verbunt}, F. 2006,
+  \aap, 456, 295
+
+\bibitem[{{Benvenuto} \& {De Vito}(2005)}]{benvenuto05}
+{Benvenuto}, O.~G., \& {De Vito}, M.~A. 2005, \mnras, 362, 891
+
+\bibitem[{{Brown} {et~al.}(2013){Brown}, {Kilic}, {Allende Prieto},
+  {Gianninas}, \& {Kenyon}}]{ELMV}
+{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., {Gianninas}, A., \&
+  {Kenyon}, S.~J. 2013, \apj, 769, 66
+
+\bibitem[{{Brown} {et~al.}(2010){Brown}, {Kilic}, {Allende Prieto}, \&
+  {Kenyon}}]{ELMI}
+{Brown}, W.~R., {Kilic}, M., {Allende Prieto}, C., \& {Kenyon}, S.~J. 2010,
+  \apj, 723, 1072
+
+\bibitem[{{Brown} {et~al.}(2012){Brown}, {Kilic}, {Allende Prieto}, \&
+  {Kenyon}}]{ELMIII}
+---. 2012, \apj, 744, 142
+
+\bibitem[{{Brown} {et~al.}(2011){Brown}, {Kilic}, {Hermes}, {Allende Prieto},
+  {Kenyon}, \& {Winget}}]{brown11b}
+{Brown}, W.~R., {Kilic}, M., {Hermes}, J.~J., {Allende Prieto}, C., {Kenyon},
+  S.~J., \& {Winget}, D.~E. 2011, \apjl, 737, L23
+
+\bibitem[{{Callanan} {et~al.}(1998){Callanan}, {Garnavich}, \&
+  {Koester}}]{callanan98}
+{Callanan}, P.~J., {Garnavich}, P.~M., \& {Koester}, D. 1998, \mnras, 298, 207
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{foremanmackey13}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Gianninas} {et~al.}(2014){Gianninas}, {Dufour}, {Kilic}, {Brown},
+  {Bergeron}, \& {Hermes}}]{gianninas14}
+{Gianninas}, A., {Dufour}, P., {Kilic}, M., {Brown}, W.~R., {Bergeron}, P., \&
+  {Hermes}, J.~J. 2014, \apj, 794, 35
 
@@
 
+\bibitem[{{Han}(1998)}]{han98}
+{Han}, Z. 1998, \mnras, 296, 1019
+
+\bibitem[{{Hermes} {et~al.}(2014){Hermes}, {Brown}, {Kilic}, {Gianninas},
+  {Chote}, {Sullivan}, {Winget}, {Bell}, {Falcon}, {Winget}, {Mason},
+  {Harrold}, \& {Montgomery}}]{hermes14}
+{Hermes}, J.~J. {et~al.} 2014, \apj, 792, 39
+
+\bibitem[{{Jia} \& {Li}(2014)}]{jia14}
+{Jia}, K., \& {Li}, X.-D. 2014, \apj, 791, 127
+
+\bibitem[{{Kaplan} {et~al.}(2014){Kaplan}, {Marsh}, {Walker}, {Bildsten},
+  {Bours}, {Breedt}, {Copperwheat}, {Dhillon}, {Howell}, {Littlefair},
+  {Shporer}, \& {Steinfadt}}]{kaplan14}
+{Kaplan}, D.~L. {et~al.} 2014, \apj, 780, 167
+
+\bibitem[{{Kilic} {et~al.}(2011){Kilic}, {Brown}, {Allende Prieto},
+  {Ag{\"u}eros}, {Heinke}, \& {Kenyon}}]{ELMII}
+{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Ag{\"u}eros}, M.~A.,
+  {Heinke}, C., \& {Kenyon}, S.~J. 2011, \apj, 727, 3
+
+\bibitem[{{Kilic} {et~al.}(2012){Kilic}, {Brown}, {Allende Prieto}, {Kenyon},
+  {Heinke}, {Ag{\"u}eros}, \& {Kleinman}}]{ELMIV}
+{Kilic}, M., {Brown}, W.~R., {Allende Prieto}, C., {Kenyon}, S.~J., {Heinke},
+  C.~O., {Ag{\"u}eros}, M.~A., \& {Kleinman}, S.~J. 2012, \apj, 751, 141
+
+\bibitem[{{Kilic} {et~al.}(2013){Kilic}, {Gianninas}, {Brown}, {Harris},
+  {Dahn}, {Ag{\"u}eros}, {Heinke}, {Kenyon}, {Panei}, \& {Camilo}}]{kilic13}
+{Kilic}, M. {et~al.} 2013, \mnras, 434, 3582
+
+\bibitem[{{Kilic} {et~al.}(2014){Kilic}, {Hermes}, {Gianninas}, {Brown},
+  {Heinke}, {Ag{\"u}eros}, {Chote}, {Sullivan}, {Bell}, \& {Harrold}}]{kilic14}
+---. 2014, \mnras, 438, L26
+
+\bibitem[{{Kilic} {et~al.}(2007){Kilic}, {Stanek}, \& {Pinsonneault}}]{kilic07}
+{Kilic}, M., {Stanek}, K.~Z., \& {Pinsonneault}, M.~H. 2007, \apj, 671, 761
+
+\bibitem[{{Kiziltan} {et~al.}(2013){Kiziltan}, {Kottas}, {De Yoreo}, \&
+  {Thorsett}}]{kiziltan13}
+{Kiziltan}, B., {Kottas}, A., {De Yoreo}, M., \& {Thorsett}, S.~E. 2013, \apj,
+  778, 66
+
+\bibitem[{{Kleinman} {et~al.}(2013){Kleinman}, {Kepler}, {Koester}, {Pelisoli},
+  {Pe{\c c}anha}, {Nitta}, {Costa}, {Krzesinski}, {Dufour}, {Lachapelle},
+  {Bergeron}, {Yip}, {Harris}, {Eisenstein}, {Althaus}, \&
+  {C{\'o}rsico}}]{kleinman13}
+{Kleinman}, S.~J. {et~al.} 2013, \apjs, 204, 5
+
+\bibitem[{{Liebert} {et~al.}(2005){Liebert}, {Bergeron}, \&
+  {Holberg}}]{liebert05}
+{Liebert}, J., {Bergeron}, P., \& {Holberg}, J.~B. 2005, \apjs, 156, 47
+
+\bibitem[{{Marsh} {et~al.}(1995){Marsh}, {Dhillon}, \& {Duck}}]{marsh95}
+{Marsh}, T.~R., {Dhillon}, V.~S., \& {Duck}, S.~R. 1995, \mnras, 275, 828
+
+\bibitem[{{Nelemans} {et~al.}(2000){Nelemans}, {Verbunt}, {Yungelson}, \&
+  {Portegies Zwart}}]{nelemans00}
+{Nelemans}, G., {Verbunt}, F., {Yungelson}, L.~R., \& {Portegies Zwart}, S.~F.
+  2000, \aap, 360, 1011
+
+\bibitem[{{Nelemans} {et~al.}(2001){Nelemans}, {Yungelson}, {Portegies Zwart},
+  \& {Verbunt}}]{nelemans01}
+{Nelemans}, G., {Yungelson}, L.~R., {Portegies Zwart}, S.~F., \& {Verbunt}, F.
+  2001, \aap, 365, 491
+
+\bibitem[{{{\"O}zel} {et~al.}(2012){{\"O}zel}, {Psaltis}, {Narayan}, \& {Santos
+  Villarreal}}]{ozel12}
+{{\"O}zel}, F., {Psaltis}, D., {Narayan}, R., \& {Santos Villarreal}, A. 2012,
+  \apj, 757, 55
+
+\bibitem[{{Smedley} {et~al.}(2014){Smedley}, {Tout}, {Ferrario}, \&
+  {Wickramasinghe}}]{smedley14}
+{Smedley}, S.~L., {Tout}, C.~A., {Ferrario}, L., \& {Wickramasinghe}, D.~T.
+  2014, \mnras, 437, 2217
+
+\bibitem[{{Toonen} {et~al.}(2012){Toonen}, {Nelemans}, \& {Portegies
+  Zwart}}]{toonen12}
+{Toonen}, S., {Nelemans}, G., \& {Portegies Zwart}, S. 2012, \aap, 546, A70
+
+\bibitem[{{van der Sluys} {et~al.}(2006){van der Sluys}, {Verbunt}, \&
+  {Pols}}]{vdSluys06}
+{van der Sluys}, M.~V., {Verbunt}, F., \& {Pols}, O.~R. 2006, \aap, 460, 209
+
+\bibitem[{{van Kerkwijk} {et~al.}(1996){van Kerkwijk}, {Bergeron}, \&
+  {Kulkarni}}]{vKerkwijk96}
+{van Kerkwijk}, M.~H., {Bergeron}, P., \& {Kulkarni}, S.~R. 1996, \apjl, 467,
+  L89
+
+\bibitem[{{van Leeuwen} {et~al.}(2007){van Leeuwen}, {Ferdman}, {Meyer}, \&
+  {Stairs}}]{vLeeuwen07}
+{van Leeuwen}, J., {Ferdman}, R.~D., {Meyer}, S., \& {Stairs}, I. 2007, \mnras,
+  374, 1437
+
+\bibitem[{{Woods} {et~al.}(2012){Woods}, {Ivanova}, {van der Sluys}, \&
+  {Chaichenets}}]{woods12}
+{Woods}, T.~E., {Ivanova}, N., {van der Sluys}, M.~V., \& {Chaichenets}, S.
+  2012, \apj, 744, 12
+
+\end{thebibliography}
+
+%\bibliography{refs}
+
 \end{document}

### 2014-10-23 documents/letter/ms.tex
Updated .tex

@@
 The ELM WD Survey identifies LMWDs in SDSS and elsewhere for spectroscopic follow-up, focusing in particular on extremely low mass WDs ($M\lesssim0.3~ \Msun$) \citep{ELMI}.
-After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
+After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods; we refer to this as the ELM sample \citep{ELMII, ELMIII, ELMIV, ELMV}.
 
 While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could host NS companions \citep{vLeeuwen07}.
+Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
 However, all radio searches for pulsed emission, as well as searches for blackbody X-ray emission from a NS surface have been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
-Yet, such systems must exist since LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-Finding even one system would be extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
+
+%Such systems are extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
 
 %Selecting the most likely candidates for multiwavelength follow-up is crucial.
-For each WD in a single-line spectroscopic binary, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
+
+Spectroscopic fits determine which systems are ideal candidates for spectroscopic follow-up; for each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
 Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:
@@
 
-55 of the 61 systems have precise $M_1$, $\period$, and $K$ measured; we refer to this as the ELM sample.
+The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction can be statistically constrained.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
-Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries.
-Instead of spectroscopic fits to component masses, their constraints are based on the measured post-Keplerian parameters in their sample.
+Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
 We focus on several specific astrophysical questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
@@
 \end{align}
-based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun \citep{kiziltan13,smedley14}.
-
-%The probability of any particular system having a NS companion $P_{\rm NS}$ is then:
-
-%\begin{equation}
-%P_{\rm NS} = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, \mf, M_1) \label{eq:P_NS_full}
-%\end{equation}
+based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}.
+The probability of any particular system having a NS companion $P_{\rm NS}$ is then:
+\begin{equation}
+P_{\rm NS} = \int_{0}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1) \label{eq:P_NS}
+\end{equation}
 
@@
 These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $\mf$.
-We draw primary masses from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
+We draw $M_1$ from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
 We apply the same Gaussian mixture model to all test datasets to infer the parameters of the white dwarf mixture component and neutron star fraction.
@@
 The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
-The input values lie cleanly within the inner contour in both projections of the posterior shown.
+The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated mass distribution.
 The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
-Nevertheless, our model recovers the input parameters for the white dwarf companion population.
+%Nevertheless, our model recovers the input parameters for the white dwarf companion population. 
+For any set of model parameters, Equation~\ref{eq:P_NS} gives the probability of an individual system hosting a NS.
+using samples from our posteriors, we can determine the distribution of $P_{\rm NS}$ for each system.
 The fourth panel lists individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
-Few systems have $P_{\rm NS}$ values higher than $\sim$5\%.
+Most systems have their entire distribution of $P_{\rm NS}$ values less than $\sim$5\%.
 
@@
 The middle row of Figure~\ref{fig:ELM_post} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
-Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior again shows a tail toward higher probabilities.
-The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NS, however this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
+As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution.
+Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior shows a substantial tail toward higher probabilities.
+The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NSs.
+However this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
+Such systems are impossible to statistically differentiate them from those with WD companions.
 
@@
 The bottom row of Figure~\ref{fig:ELM_post} shows the results of this test.
-The posterior distribution in the second panel shows that the systems have difficulty converging on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
-Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
+The posterior distribution in the second panel shows that the model does not converge on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The preference toward larger $\sigma_{\rm WD}$ is expected as it flattens the distribution to match it with the input uniform distribution.
+The third panel shows that the posterior distribution is spread out in $\sigma_{\rm WD}$.
+Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
+The fourth panel again shows that, compared to Test 2, our model is not as effective at identifying which LMWDs host NS companions.
 
 \subsection{The ELM Sample}
+
+The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06} \citep[it also includes previously identified LMWDs in SDSS; ][]{eisenstein06,liebert04}.
+Objects are identified for spectroscopic follow-up by their $u-g$ versus $g-r$ colors.
+Since the survey is designed to find low surface gravity WDs by color, the detection probability is independent of both the mass and nature of the companion.
+Therefore, at least with regard to the inclination angle and companion mass, the population is unbiased.
 
@@
 where $M_2^*$ is the mass of the WD companion in these three systems.
-
-Since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased.
 
@@
 However, there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%), based on the non-detection of radio emission from eight LMWD targets, and from \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}\%$), based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%), based on the non-detection of radio emission from eight LMWD targets, and from \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}~\%$), based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
 Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
 All NSs give off blackbody radiation peaked in X-ray wavelengths, so X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
-Previous searches for LMWDs with X-ray counterparts have all been non-detections \citep{ELMII,ELMIV,kilic13}.
+Previous searches for LMWDs with X-ray counterparts have all been non-detections \citep{ELMII,ELMIV,kilic13,kilic14}.
 However, we show here that all of those sources have a low probability of hosting a NS companion.
@@
 
-%Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample to search for eclipses.
-They placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses.
-For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming.
-We have not included these observations in our model, but we plan to explore this in a future work.
-
 \section{Conclusions}
 
-We have developed a statistical model to infer the companion mass distribution for a set of unbiased, single-lined, spectroscopic binaries.
-Our model recovers the correct input parameters for three separate test cases with WD and NS companion masses drawn from different distributions.
-In particular, even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
+We have developed a statistical model to infer the companion mass distribution for a sample of single-lined, spectroscopic binaries.
+This model can be applied to any such sample with measured $M_1$.
+When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the correct input parameters; even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
 
 We then applied our model to the set of WDs from the ELM WD survey.
-Our model indicates that the fraction of ELM WDs with NS companions is consistent with zero, but could be up to $\sim$16\% (within 1-$\sigma$).
+Our model indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
 We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
@@
 
+%In particular, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
+
 There are several ways in which this model can be expanded.
-Our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
+Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
+Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems, which could be included in our model.
+Furthermore, tighter constraints can be placed on $f_{\rm NS}$ by including radio and X-ray non-detection data.
+Finally, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
+
+%Our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
 Applying this method to various populations can help to constrain the formation of particularly classes of binaries.
-In particular, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
-
-Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
-Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems.
-We have not included these observations in our model, but we plan to explore this in the future.
 

### 2014-10-23 documents/letter/ms.tex
Updated .tex

@@
 
-\bibitem[{{Benvenuto} \& {De Vito}(2005)}]{benvenuto05}
-{Benvenuto}, O.~G., \& {De Vito}, M.~A. 2005, \mnras, 362, 891
+\bibitem[{{Brown} {et~al.}(2006){Brown}, {Geller}, {Kenyon}, \&
+  {Kurtz}}]{brown06}
+{Brown}, W.~R., {Geller}, M.~J., {Kenyon}, S.~J., \& {Kurtz}, M.~J. 2006, \apj,
+  647, 303
 
@@
 
+\bibitem[{{Eisenstein} {et~al.}(2006){Eisenstein}, {Liebert}, {Harris},
+  {Kleinman}, {Nitta}, {Silvestri}, {Anderson}, {Barentine}, {Brewington},
+  {Brinkmann}, {Harvanek}, {Krzesi{\'n}ski}, {Neilsen}, {Long}, {Schneider}, \&
+  {Snedden}}]{eisenstein06}
+{Eisenstein}, D.~J. {et~al.} 2006, \apjs, 167, 40
+
 \bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
@@
 {Hermes}, J.~J. {et~al.} 2014, \apj, 792, 39
-
-\bibitem[{{Jia} \& {Li}(2014)}]{jia14}
-{Jia}, K., \& {Li}, X.-D. 2014, \apj, 791, 127
 
@@
 
-\bibitem[{{Liebert} {et~al.}(2005){Liebert}, {Bergeron}, \&
-  {Holberg}}]{liebert05}
-{Liebert}, J., {Bergeron}, P., \& {Holberg}, J.~B. 2005, \apjs, 156, 47
+\bibitem[{{Liebert} {et~al.}(2004){Liebert}, {Bergeron}, {Eisenstein},
+  {Harris}, {Kleinman}, {Nitta}, \& {Krzesinski}}]{liebert04}
+{Liebert}, J., {Bergeron}, P., {Eisenstein}, D., {Harris}, H.~C., {Kleinman},
+  S.~J., {Nitta}, A., \& {Krzesinski}, J. 2004, \apjl, 606, L147
 

### 2014-10-24 documents/letter/ms.tex
text changes

@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen 
-companion stars to low mass white dwarfs (LMWD) given orbital period and projected radial velocity measurements of the primary. We use a mixture of 
+companion stars given observations of the orbital period and projected radial velocity of the primary star. 
+We then apply this model to a sample of low mass white dwarfs (LMWD).
+We use a mixture of 
 two Gaussians to model the true companion mass distribution to represent 
@@
 
-The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction can be statistically constrained.
+The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
@@
 
-where the product is over each of the $j$ systems.  This marginal likelihood involves integrals over the latent variables $i$ and $M_2$,
+where the product is over each of the $j$ systems.  This marginal likelihood involves integrals over the unobserved quantities $i$ and $M_2$,
 \begin{align}
@@
 based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}.
-The probability of any particular system having a NS companion $P_{\rm NS}$ is then:
+The probability of any particular system having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the companion mass distribution:
 \begin{equation}
-P_{\rm NS} = \int_{0}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1) \label{eq:P_NS}
+P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] ~ h(M_2, \mf, M_1)}\label{eq:P_NS}
 \end{equation}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-We choose uninformative priors on these parameters: for the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$; we use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
+For the mean of the white dwarf component, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
@@
 We throw out the burn-in samples to eliminate any effects from our choice of initial conditions.
-The autocorrelation times for each parameter confirm they have converged.
+The autocorrelation times for each parameter indicate that they have converged.
 
@@
 The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
-The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated mass distribution.
+The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated test sample.
 The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
@@
 For any set of model parameters, Equation~\ref{eq:P_NS} gives the probability of an individual system hosting a NS.
-using samples from our posteriors, we can determine the distribution of $P_{\rm NS}$ for each system.
+Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
 The fourth panel lists individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
-Most systems have their entire distribution of $P_{\rm NS}$ values less than $\sim$5\%.
+For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
 
@@
 However this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
-Such systems are impossible to statistically differentiate them from those with WD companions.
+Such systems are impossible to statistically differentiate from those with WD companions.
 
 \subsection{Test 3: Uniform (WD) + Gaussian (NS)} \label{sec:exp3}
-As a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$ while keeping $f_{\rm NS}=$10\%.
+As a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, again with $f_{\rm NS}=$10\%.
 The bottom row of Figure~\ref{fig:ELM_post} shows the results of this test.
-The posterior distribution in the second panel shows that the model does not converge on any one solution for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The posterior distribution in the second panel shows that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained, as expected.
 The preference toward larger $\sigma_{\rm WD}$ is expected as it flattens the distribution to match it with the input uniform distribution.
@@
 The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$.
-The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution is not exactly Gaussian.
+The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution may not be exactly Gaussian.
 It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
@@
 Previous searches for LMWDs with X-ray counterparts have all been non-detections \citep{ELMII,ELMIV,kilic13,kilic14}.
-However, we show here that all of those sources have a low probability of hosting a NS companion.
-If the two systems with the highest $P_{\rm NS}$, SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
+However, based on our model, all of those sources have a low probability of hosting a NS companion.
+%If the two systems with the highest $P_{\rm NS}$, SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
 
@@
 
-We have developed a statistical model to infer the companion mass distribution for a sample of single-lined, spectroscopic binaries.
-This model can be applied to any such sample with measured $M_1$.
-When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the correct input parameters; even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
+We have developed a statistical model to infer the companion mass distribution for a sample of single-line, spectroscopic binaries.
+This model can be applied to any such sample with measured $M_1$ and mass function.
+When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the input parameters; even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
 
@@
 Our model indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
-We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
+We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest median probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
 Our model further suggests that the majority of ELM WDs have CO-core WD companions.

### 2014-10-24 documents/letter/ms.tex

@@
 \begin{equation}
-P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] ~ h(M_2, \mf, M_1)}\label{eq:P_NS}
+P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{p(\mf \given \bs{\theta})}\label{eq:P_NS}
 \end{equation}
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{many-panel.pdf}
+\includegraphics[width=0.95\textwidth]{many-panel.png}
 \caption{Results from the three tests described in Section~\ref{sec:tests}.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{real-data.pdf}
+\includegraphics[width=0.95\textwidth]{real-data.png}
 \caption{Results from applying our model to the ELM WDs.
@@
 Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%), based on the non-detection of radio emission from eight LMWD targets, and from \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}~\%$), based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
-Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
+% Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
 All NSs give off blackbody radiation peaked in X-ray wavelengths, so X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
@@
 
-It is worth noting that systems with NS companions cannot necessarily be differentiated from those with WD companions through the mass function and LMWD mass alone.
+% It is worth noting that systems with NS companions cannot necessarily be differentiated from those with WD companions through the mass function and LMWD mass alone.
 Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.

### 2014-10-28 documents/letter/ms.tex
png to pdf
update MAP params
Updated .tex

@@
 \title{The mass distribution of companions to low-mass white dwarfs}
-\author{Jeff J. Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel Ag\"ueros\altaffilmark{\colum}}
+\author{Jeff J. Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel A. Ag\"ueros\altaffilmark{\colum}}
 
@@
 \begin{abstract}
-Measuring the masses of companions to single-line spectroscopic binary stars
-is (in general) not possible because of the unknown orbital plane inclination angles. 
-Even when the mass of the visible star can be measured, only a lower limit can be placed
-on the mass of the unseen companion. However, since these inclination angles should be isotropically
-distributed, for a large enough, unbiased sample, the 
-companion mass distribution can be deconvolved from the distributions of observables.
-In this work, we construct a hierarchical probabilistic model to infer properties of unseen 
-companion stars given observations of the orbital period and projected radial velocity of the primary star. 
-We then apply this model to a sample of low mass white dwarfs (LMWD).
-We use a mixture of 
-two Gaussians to model the true companion mass distribution to represent 
-populations of white dwarfs (WD) and neutron stars (NS). 
+Measuring the masses of companions to single-line spectroscopic binary stars is (in general) not possible because of the unknown orbital plane inclination angles.
+Even when the mass of the visible star can be measured, only a lower limit can be placed on the mass of the unseen companion.
+However, since these inclination angles should be isotropically distributed, for a large enough, unbiased sample, the  companion mass distribution can be deconvolved from the distributions of observables.
+In this work, we construct a hierarchical probabilistic model to infer properties of unseen  companion stars given observations of the orbital period and projected radial velocity of the primary star.
+We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWD; $M\lesssim0.45\Msun$).
+We use a mixture of two Gaussians to model the white dwarf (WD) and neutron star (NS) companion mass distributions.
 Our model successfully recovers the initial parameters of several mock data sets.
-We then apply our model to 55 of the 61 white dwarfs in 
-the extremely low mass (ELM) WD survey. We find maximum a posteriori parameters for
-the WD companion population of $\mu_{\rm WD} = 0.71~\Msun$ and $\sigma_{\rm WD} = 0.26~\Msun$ 
-with a NS fraction consistent with zero, $f_{\rm NS} = 0\%$. However, the marginal posterior 
-distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
-We make samples from the posterior distribution publicly available so that future observational
-efforts may compute the NS probability for newly discovered low mass WDs.
+We then apply our model to 55 of the 61 white dwarfs in the extremely low mass (ELM) WD Survey.
+Our maximum a posteriori model for the WD companion population has a mean $\mu_{\rm WD} = 0.71~\Msun$ and standard deviation $\sigma_{\rm WD} = 0.26~\Msun$ with a NS fraction consistent with zero, $f_{\rm NS} = 0\%$.
+However, the marginal posterior distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
+We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered low mass WDs.
 \end{abstract}
@@
 In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations.
-The ELM WD Survey identifies LMWDs in SDSS and elsewhere for spectroscopic follow-up, focusing in particular on extremely low mass WDs ($M\lesssim0.3~ \Msun$) \citep{ELMI}.
-After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods; we refer to this as the ELM sample \citep{ELMII, ELMIII, ELMIV, ELMV}.
+The ELM WD Survey identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing in particular on extremely low mass WDs \citep[$M\lesssim0.3~ \Msun$;][]{ELMI}.
+After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
+We refer to this as the ELM sample.
 
-While the orbital periods and radial velocities indicated the companions were most likely WDs, due to the unmeasured inclination angle, these LMWDs could host NS companions \citep{vLeeuwen07}.
+While the orbital periods and radial velocities indicate the companions are most likely WDs, due to the unmeasured inclination angle, LMWDs can host NS companions \citep{vLeeuwen07}.
 Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-However, all radio searches for pulsed emission, as well as searches for blackbody X-ray emission from a NS surface have been unsuccessful \citep{agueros09a,agueros09b,kilic13}.
+However, all radio searches for pulsed emission, as well as searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
 
-%Such systems are extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
-
-%Selecting the most likely candidates for multiwavelength follow-up is crucial.
-
-Spectroscopic fits determine which systems are ideal candidates for spectroscopic follow-up; for each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
+For each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
 Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:
 \begin{equation}
-	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3 = \mf \label{eq:massfunc}
+	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3 \label{eq:massfunc}
 \end{equation}
@@
 $M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
-Because of the dependence on $i$, the nature of the companion cannot usually be determined based on $\mf$ alone.
-Figure~\ref{fig:Porb-M1} shows that the population of LMWD with pulsar companions (triangles) occupy the same region in $M_1 - \period$ space as those with WD companions (circles).
+Because of this dependence on $i$, the nature of the companion cannot usually be determined based on $\mf$ alone.
+Figure~\ref{fig:Porb-M1} shows that the population of LMWD with pulsar companions (triangles) occupies the same region in $M_1 - \period$ space as those with WD companions (circles).
 Therefore, barring rare circumstances (such as an edge-on, eclipsing system), individual LMWDs with NS companions cannot be readily identified.
@@
 The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained. 
+%Such systems are extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
-We focus on several specific astrophysical questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
+We focus on several specific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
@@
 To answer these questions, we build the mathematical framework in Section 2, then apply our model to test and real data in Section 3.
-We give the results and discussion in Section 4, and conclude in Section 5.
+We give the discuss the results in Section 4, and conclude in Section 5.
 
@@
 \caption{The $\period$ - $M_1$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
-The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the ELM WDs without detected radial velocity variations are shown by the arrows.
+The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected radial velocity variations are shown by the arrows.
 From $\period$ and $M_1$ alone, the two populations are indistinguishable.}
@@
 \end{align}
-We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{The fractional uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$.} and assume the inclination angles are isotropically distributed
+We neglect observational uncertainties in $\mf$ and $M_1$,\footnote{The fractional uncertainties in these quantities are small, $\sigma_x / x \sim 0.05-0.1$ \citep{gianninas14}.} and assume the inclination angles are isotropically distributed:
 \begin{equation}
@@
 \end{equation}
-For now, we do not specify a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
+For now, we do not specify a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is:
 \begin{align}
@@
 \end{equation}
-The inner integral (over $i$) has the form
+The inner integral (over $i$) has the form:
 \begin{equation}
@@
 \end{equation}
-where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in \eqn\ref{eq:delta} are 
+where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in \eqn\ref{eq:delta} are: 
 \begin{align}
@@
 \end{align}
-We may rewrite the marginal likelihood as
+We may rewrite the marginal likelihood as:
 \begin{align}
@@
 \end{align}
-
 where the bottom bound in the integral in \eqn\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90\degree$ in \eqn\ref{eq:massfunc} and solving for $M_2$), and
@@
 We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$.
-For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data.
-In tests below, we generate test data with different mixture component forms.
-We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1.3,2)~\Msun$,
+For all experiments -- including that with the real data -- we use a two-component Gaussian mixture model to fit the data.
+We generate test data with different mixture component forms.
+We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the NS component is restricted to $M_2\in (1.3,2)~\Msun$.
+We then have:
 \begin{align}
@@
 \begin{align}
-	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper \\
-	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2.
+	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper, \\
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2,
 \end{align}
-and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified.
-In this work, we fix the mean and variance of the neutron star distribution to
+and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified.
+We fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
 \begin{align}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-For the mean of the white dwarf component, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for the variance of the white dwarf component over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless neutron star fraction from $0-1$.
+For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
@@
 		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
-		 & MAP & 0.76 & 0.17 & 0.12 \\
+		 & MAP & 0.74 & 0.2 & 0.11 \\
 		 \hline
 		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
-		 & MAP & 0.80 & 0.39 & 0.12 \\
+		 & MAP & 0.64 & 0.5 & 0.14 \\
 		 \cutinhead{ELM Sample}
@@
 $\mathcal{U}$ is the uniform distribution.
-There are 3 free parameters.
+There are three free parameters.
 We additionally fix the NS distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
@@
 
-We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.
-The algorithm is implemented in the \texttt{Python} programming language \citep[{\tt emcee};][]{foremanmackey13} and uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$\footnote{Our model uses {\tt emcee}, implemented in the \texttt{Python} programming language \citep{foremanmackey13}}.
+The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
 We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
@@
 
-\section{Applying Our Model} \label{sec:tests}
+\section{Testing Our Model} \label{sec:tests}
 To test the performance of this Gaussian mixture model, we first apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
-These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle and primary mass, $M_1$, to compute the mass function, $\mf$.
+These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle, $i$, and primary mass, $M_1$, to compute the mass function, $\mf$.
 We draw $M_1$ from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
-We apply the same Gaussian mixture model to all test datasets to infer the parameters of the white dwarf mixture component and neutron star fraction.
+We apply the same Gaussian mixture model to all test datasets to infer the parameters of the WD mixture component and $f_{\rm NS}$.
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{many-panel.png}
+\includegraphics[width=0.95\textwidth]{many-panel.pdf}
 \caption{Results from the three tests described in Section~\ref{sec:tests}.
-The left-most column shows histograms of $M_2$ drawn from each of our test distributions.
+The leftmost column shows histograms of $M_2$ drawn from each of our test distributions.
 Overplotted as solid lines are the MAP models.
@@
 Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
-The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$, again the dashed lines show the input values.
-Finally, the rightmost panels list the individual systems (ordered by increasing $\mf$) and show each of their corresponding NS probabilities.
+The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; again the dashed lines show the input values.
+Finally, the rightmost panels include all the individual LMWD systems (ordered by increasing $\mf$) and show here their corresponding $P_{\rm NS}$.
 }
@@
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
-The fourth panel lists individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+The fourth panel includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
 For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
@@
 \subsection{Test 2: Two Gaussians (WD + NS)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the WD component as the previous example, but we add an additional NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
+For our next test, we use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
 The middle row of Figure~\ref{fig:ELM_post} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution.
-Importantly, the third panel shows that it also recovers $f_{\rm NS}$, however the posterior shows a substantial tail toward higher probabilities.
+Importantly, the third panel shows that it also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
 The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NSs.
-However this accounts for less than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
+However, this accounts for fewer than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
 Such systems are impossible to statistically differentiate from those with WD companions.
@@
 \subsection{Test 3: Uniform (WD) + Gaussian (NS)} \label{sec:exp3}
-As a final test, we generate companion masses for the WD component by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, again with $f_{\rm NS}=$10\%.
+As a final test, we generate companion masses for the WDs by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, again with $f_{\rm NS}=$10\%.
 The bottom row of Figure~\ref{fig:ELM_post} shows the results of this test.
@@
 Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-The fourth panel again shows that, compared to Test 2, our model is not as effective at identifying which LMWDs host NS companions.
+The fourth panel shows that, compared to Test 2, our model is not as effective at identifying which LMWDs host NS companions.
 
@@
 
-The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06} \citep[it also includes previously identified LMWDs in SDSS; ][]{eisenstein06,liebert04}.
+The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06}; it also includes previously identified LMWDs in SDSS \citep{eisenstein06,liebert04}.
 Objects are identified for spectroscopic follow-up by their $u-g$ versus $g-r$ colors.
-Since the survey is designed to find low surface gravity WDs by color, the detection probability is independent of both the mass and nature of the companion.
+Since the survey is designed to select low surface gravity WDs by color, the detection probability is independent of both the mass and nature of any putative companion.
 Therefore, at least with regard to the inclination angle and companion mass, the population is unbiased.
@@
 The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-Fitting the sample's high S/N spectra to templates provides precisely determine $M_1$ values.
-We use the spectroscopic solutions found in \citet{gianninas14}.
-Three systems are eclipsing binaries, with known companion masses (NLTT 11748: $M_2=0.72~\Msun$ \citep{kaplan14}, SDSS J065133.3$+$284423.3: $M_2=0.50~\Msun$ \citep{brown11b}, and SDSS J075141.2$-$014120.9: $M_2=0.97~\Msun$ \citep{kilic14}).
+Fitting the WDs' spectra to templates provides precisely determine $M_1$ values.
+We use the spectroscopic solutions of \citet{gianninas14}.
+Three systems are eclipsing binaries, with known companion masses: NLTT 11748 \citep[$M_2=0.72~\Msun$;][]{kaplan14}, SDSS J065133.3$+$284423.3 \citep[$M_2=0.50~\Msun$;][]{brown11b}, and SDSS J075141.2$-$014120.9 \citep[$M_2=0.97~\Msun$;][]{kilic14}.
 For these systems, the likelihood reduces to:
@@
 The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
-Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
+Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
 These LMWDs could also have companions at systematically longer orbital periods resulting in orbital velocities below the detection limit.
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{real-data.png}
+\includegraphics[width=0.95\textwidth]{real-data.pdf}
 \caption{Results from applying our model to the ELM WDs.
@@
 The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$.
-The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail towards larger variances, which could indicate that the true WD distribution may not be exactly Gaussian.
-It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail toward larger $\sigma_{\rm WD}$, which could indicate that the true WD distribution may not be exactly Gaussian.
+It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}.
 Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
 
-Our results are independent of astrophysical expectations since they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
+Our results are independent of astrophysical expectations, as they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
 In principle, priors could be added based on population synthesis models that suggest that there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
-The ratio and distribution of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
+The ratio and distribution of these two populations depend on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
 Our results here suggest the companion sample is composed mainly of CO WDs.
@@
 The ratio of these populations could potentially place an important constraint on population synthesis models.
-However, we have found that there is not enough data to motivate adding additional freedom to the model in the form of a second WD component.
+However, we have found that there are not enough data to motivate adding additional freedom to the model in the form of a second WD component.
 
@@
 However, there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet{vLeeuwen07} ($f_{\rm NS}<18\pm5$\%), based on the non-detection of radio emission from eight LMWD targets, and from \citet{agueros09b} ($f_{\rm NS}<10\substack{+4 \\ -2}~\%$), based on non-detections of radio emission from an expanded sample of 15 LMWD targets in the ELM WD sample.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07}, based on the non-detection of radio emission from eight LMWD targets, and from \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, based on non-detections of radio emission from an expanded sample of 15 LMWD targets.
 % Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
@@
 
-To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
+To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt Python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
 This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
@@
 This model can be applied to any such sample with measured $M_1$ and mass function.
-When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the input parameters; even if the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
+When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the input parameters.
+Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
 
@@
 We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest median probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
-Our model further suggests that the majority of ELM WDs have CO-core WD companions.
+We further suggest that the majority of ELM WDs have CO-core WD companions.
 This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep{toonen12}.

### 2014-11-04 documents/letter/ms.tex

@@
 \begin{abstract}
-Measuring the masses of companions to single-line spectroscopic binary stars is (in general) not possible because of the unknown orbital plane inclination angles.
+Measuring the masses of companions to single-line spectroscopic binary stars is (in general) not possible because of the unknown orbital plane inclination.
 Even when the mass of the visible star can be measured, only a lower limit can be placed on the mass of the unseen companion.
-However, since these inclination angles should be isotropically distributed, for a large enough, unbiased sample, the  companion mass distribution can be deconvolved from the distributions of observables.
+However, since these inclination angles should be isotropically distributed, for a large enough, unbiased sample, the  companion mass distribution can be deconvolved from the distribution of observables.
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen  companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWD; $M\lesssim0.45\Msun$).
+We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWD; $M\lesssim0.45~\Msun$).
 We use a mixture of two Gaussians to model the white dwarf (WD) and neutron star (NS) companion mass distributions.
@@
 We then apply our model to 55 of the 61 white dwarfs in the extremely low mass (ELM) WD Survey.
-Our maximum a posteriori model for the WD companion population has a mean $\mu_{\rm WD} = 0.71~\Msun$ and standard deviation $\sigma_{\rm WD} = 0.26~\Msun$ with a NS fraction consistent with zero, $f_{\rm NS} = 0\%$.
+Our maximum a posteriori model for the WD companion population has a mean, $\mu_{\rm WD}$ of $0.71~\Msun$ and standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$ with a NS fraction, $f_{\rm NS}$, consistent with zero.
 However, the marginal posterior distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
@@
 
-To answer these questions, we build the mathematical framework in Section 2, then apply our model to test and real data in Section 3.
-We give the discuss the results in Section 4, and conclude in Section 5.
+To answer these questions, we build the mathematical framework in Section 2, then test our model in Section 3. We apply our model to the ELM WD sample in Section 4 and conclude in Section 5.
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{many-panel.pdf}
+\includegraphics[width=0.75\textwidth]{many-panel.pdf}
 \caption{Results from the three tests described in Section~\ref{sec:tests}.
@@
 The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; again the dashed lines show the input values.
-Finally, the rightmost panels include all the individual LMWD systems (ordered by increasing $\mf$) and show here their corresponding $P_{\rm NS}$.
 }
@@
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
-The fourth panel includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+Figure~\ref{fig:P_NS} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
 For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
@@
 Importantly, the third panel shows that it also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
-The fourth panel indicates that some systems have near unity $P_{\rm NS}$ values; our model correctly identifies these as true NSs.
-However, this accounts for fewer than half of the systems with NSs in the simulated sample; the other half have low $\mf$'s due to low inclination angles.
-Such systems are impossible to statistically differentiate from those with WD companions.
+Figure~\ref{fig:P_NS} indicates that some systems have near unity $P_{\rm NS}$ values; tick marks, which indicate "true" NSs, indicate that our model correctly identifies these as true NSs.
+However, more than half of the systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
 
@@
 Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-The fourth panel shows that, compared to Test 2, our model is not as effective at identifying which LMWDs host NS companions.
+Figure~\ref{fig:P_NS} shows that, compared to Test 2, our model is not as effective at identifying exactly which LMWDs host NS companions.
+
+\begin{figure*}[h!]
+\begin{center}
+\includegraphics[width=0.75\textwidth]{PNS.pdf}
+\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks show those systems that are true NSs.}
+\label{fig:P_NS}
+\end{center}
+\end{figure*}
 
@@
 
-\section{Results and Discussion}
+\section{Applying our Model}
 
@@
 Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07}, based on the non-detection of radio emission from eight LMWD targets, and from \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, based on non-detections of radio emission from an expanded sample of 15 LMWD targets.
+
+The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$ probabilities: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7.
+X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}.
+Searches for radio and x-ray emission from SDSS J081133.6$+$022556.8 are ongoing.
+
 % Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
@@
 This model can be applied to any such sample with measured $M_1$ and mass function.
-When applied to three separate test cases with WD and NS companion masses drawn from different distributions, our model recovers the input parameters.
+When applied to three separate test cases with unseen WD and NS companions to LMWDs, our model recovers the input parameters.
 Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
 
-We then applied our model to the set of WDs from the ELM WD survey.
+We then applied our model to the set of LMWDs from the ELM WD survey.
 Our model indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
-We identify SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7 as having the highest median probabilities of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
+Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
+This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
+
+%We identify SDSS J081133.6$+$022556.8 %and SDSS J174140.5$+$652638.7 
+%as having the highest median probability of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
 We further suggest that the majority of ELM WDs have CO-core WD companions.
-This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep{toonen12}.
+This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
 
@@
 
+\bibitem[{{York} {et~al.}(2000){York}, {Adelman}, {Anderson}, {Anderson},
+  {Annis}, {Bahcall}, {Bakken}, {Barkhouser}, {Bastian}, {Berman}, {Boroski},
+  {Bracker}, {Briegel}, {Briggs}, {Brinkmann}, {Brunner}, {Burles}, {Carey},
+  {Carr}, {Castander}, {Chen}, {Colestock}, {Connolly}, {Crocker}, {Csabai},
+  {Czarapata}, {Davis}, {Doi}, {Dombeck}, {Eisenstein}, {Ellman}, {Elms},
+  {Evans}, {Fan}, {Federwitz}, {Fiscelli}, {Friedman}, {Frieman}, {Fukugita},
+  {Gillespie}, {Gunn}, {Gurbani}, {de Haas}, {Haldeman}, {Harris}, {Hayes},
+  {Heckman}, {Hennessy}, {Hindsley}, {Holm}, {Holmgren}, {Huang}, {Hull},
+  {Husby}, {Ichikawa}, {Ichikawa}, {Ivezi{\'c}}, {Kent}, {Kim}, {Kinney},
+  {Klaene}, {Kleinman}, {Kleinman}, {Knapp}, {Korienek}, {Kron}, {Kunszt},
+  {Lamb}, {Lee}, {Leger}, {Limmongkol}, {Lindenmeyer}, {Long}, {Loomis},
+  {Loveday}, {Lucinio}, {Lupton}, {MacKinnon}, {Mannery}, {Mantsch}, {Margon},
+  {McGehee}, {McKay}, {Meiksin}, {Merelli}, {Monet}, {Munn}, {Narayanan},
+  {Nash}, {Neilsen}, {Neswold}, {Newberg}, {Nichol}, {Nicinski}, {Nonino},
+  {Okada}, {Okamura}, {Ostriker}, {Owen}, {Pauls}, {Peoples}, {Peterson},
+  {Petravick}, {Pier}, {Pope}, {Pordes}, {Prosapio}, {Rechenmacher}, {Quinn},
+  {Richards}, {Richmond}, {Rivetta}, {Rockosi}, {Ruthmansdorfer}, {Sandford},
+  {Schlegel}, {Schneider}, {Sekiguchi}, {Sergey}, {Shimasaku}, {Siegmund},
+  {Smee}, {Smith}, {Snedden}, {Stone}, {Stoughton}, {Strauss}, {Stubbs},
+  {SubbaRao}, {Szalay}, {Szapudi}, {Szokoly}, {Thakar}, {Tremonti}, {Tucker},
+  {Uomoto}, {Vanden Berk}, {Vogeley}, {Waddell}, {Wang}, {Watanabe},
+  {Weinberg}, {Yanny}, {Yasuda}, \& {SDSS Collaboration}}]{york00}
+{York}, D.~G. {et~al.} 2000, \aj, 120, 1579
+
 \end{thebibliography}
@@
 
+%\bibitem[Goodman~\&\ Weare(2010)]{goodman10}
+%Goodman,~J. \& Weare,\ J.,
+%2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
+
 \end{document}

### 2014-11-04 documents/letter/ms.tex

@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWD; $M\lesssim0.45~\Msun$).
-We use a mixture of two Gaussians to model the white dwarf (WD) and neutron star (NS) companion mass distributions.
+We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
+We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions.
 Our model successfully recovers the initial parameters of several mock data sets.
-We then apply our model to 55 of the 61 white dwarfs in the extremely low mass (ELM) WD Survey.
-Our maximum a posteriori model for the WD companion population has a mean, $\mu_{\rm WD}$ of $0.71~\Msun$ and standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$ with a NS fraction, $f_{\rm NS}$, consistent with zero.
-However, the marginal posterior distribution over NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
+We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey.
+Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.71~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$; the fraction of NS companions, $f_{\rm NS}$, is consistent with zero.
+However, the marginal posterior distribution over the NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
 We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered low mass WDs.
@@
 These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
-In their seminal work, \citet{marsh95} discovered companions around five LMWDs in their sample of seven objects, confirming these theoretical expectations.
-The ELM WD Survey identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing in particular on extremely low mass WDs \citep[$M\lesssim0.3~ \Msun$;][]{ELMI}.
-After their initial investigation found 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
-We refer to this as the ELM sample.
+In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations.
+The ELM WD Survey identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs \citep[$M\lesssim0.3~ \Msun$;][]{ELMI}.
+After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
+We refer to these 55 systems as the ELM sample.
 
-While the orbital periods and radial velocities indicate the companions are most likely WDs, due to the unmeasured inclination angle, LMWDs can host NS companions \citep{vLeeuwen07}.
+While the orbital periods and radial velocities indicate the companions are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}.
 Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
@@
 For each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
-Using Kepler's third law, we can write the relation between these quantities and the unknown inclination angle as:
+Using Kepler's third law, we can write the relation between these quantities, the unknown inclination angle ($i$), and the companion mass ($M_2$) as:
 \begin{equation}
@@
 \end{equation}
-The righthand side of this equation is the mass function ($\mf$).
-$M_2$ is minimized for an edge-on orbit, with $i = 90\degree$.
+The righthand side of this equation is the mass function $\mf$.
+$M_2$ is minimized for an edge-on orbit with $i = 90\degree$.
 Because of this dependence on $i$, the nature of the companion cannot usually be determined based on $\mf$ alone.
-Figure~\ref{fig:Porb-M1} shows that the population of LMWD with pulsar companions (triangles) occupies the same region in $M_1 - \period$ space as those with WD companions (circles).
-Therefore, barring rare circumstances (such as an edge-on, eclipsing system), individual LMWDs with NS companions cannot be readily identified.
+Figure~\ref{fig:Porb-M1} shows that the population of LMWDs with pulsar companions occupies the same region in $M_1 - \period$ space as those with WD companions.
+Therefore, barring rare circumstances (such as an edge-on, eclipsing system), individual LMWDs with NS companions cannot be identified from optical observations alone.
 
@@
 %Such systems are extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
-In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to ELM WDs.
+In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
@@
 \includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
-\caption{The $\period$ - $M_1$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
+\caption{The $M_1$ - $\period$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
 The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected radial velocity variations are shown by the arrows.
-From $\period$ and $M_1$ alone, the two populations are indistinguishable.}
+From $M_1$ and $\period$ alone, the two populations are indistinguishable.}
 \label{fig:Porb-M1}
@@
 
-We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
+We construct a statistical model to derive constraints on a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
 We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
@@
 For all experiments -- including that with the real data -- we use a two-component Gaussian mixture model to fit the data.
-We generate test data with different mixture component forms.
-We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in (0.2,\wdupper)~\Msun$ and the NS component is restricted to $M_2\in (1.3,2)~\Msun$.
+We generate mock data with different mixture component forms.
+We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$.
 We then have:
@@
 There are three free parameters.
-We additionally fix the NS distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
+We additionally fix the NS mass distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
 
@@
 
-We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$\footnote{Our model uses {\tt emcee}, implemented in the \texttt{Python} programming language \citep{foremanmackey13}}.
+We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}}.
 The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
@@
 We throw out the burn-in samples to eliminate any effects from our choice of initial conditions.
-The autocorrelation times for each parameter indicate that they have converged.
 
@@
 To test the performance of this Gaussian mixture model, we first apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
-These data are generated by randomly drawing the companion mass, $M_2$, from a particular distribution, then using a randomly drawn inclination angle, $i$, and primary mass, $M_1$, to compute the mass function, $\mf$.
+These mock data are generated by randomly drawing the companion mass from a particular distribution, then using a randomly drawn inclination angle and primary mass to compute the mass function.
 We draw $M_1$ from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
-We apply the same Gaussian mixture model to all test datasets to infer the parameters of the WD mixture component and $f_{\rm NS}$.
+We apply the same Gaussian mixture model to all mock datasets to infer the parameters of the WD mixture component and $f_{\rm NS}$.
 
@@
 As a first test, we generate $M_2$ by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
-This test sample contains no NSs.
-In the top row of Figure~\ref{fig:ELM_post}, the leftmost panel shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
+This mock sample contains no NSs.
+In the top row of Figure~\ref{fig:tests}, the leftmost panel shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
 The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
-The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated test sample.
+The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated mock sample.
 The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
 %Nevertheless, our model recovers the input parameters for the white dwarf companion population.
+
 For any set of model parameters, Equation~\ref{eq:P_NS} gives the probability of an individual system hosting a NS.
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
-Figure~\ref{fig:P_NS} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+The leftmost panel in Figure~\ref{fig:P_NS} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
 For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
@@
 For our next test, we use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
-The middle row of Figure~\ref{fig:ELM_post} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The middle row of Figure~\ref{fig:tests} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution.
-Importantly, the third panel shows that it also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
-Figure~\ref{fig:P_NS} indicates that some systems have near unity $P_{\rm NS}$ values; tick marks, which indicate "true" NSs, indicate that our model correctly identifies these as true NSs.
+Importantly, the third panel shows that our model also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
+Tick marks in the middle panel of Figure~\ref{fig:P_NS} indicate ''true" NSs in our mock data.
+Our model correctly assigns high $P_{\rm NS}$ to roughly half of these.
+However, many systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
+
+%Figure~\ref{fig:P_NS} indicates that some systems have near unity $P_{\rm NS}$ values; tick marks, which indicate ''true" NSs, indicate that our model correctly identifies these as true NSs.
 However, more than half of the systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
@@
 \subsection{Test 3: Uniform (WD) + Gaussian (NS)} \label{sec:exp3}
-As a final test, we generate companion masses for the WDs by sampling from a uniform distribution over the range $(0.2,1.2)~\Msun$, again with $f_{\rm NS}=$10\%.
-The bottom row of Figure~\ref{fig:ELM_post} shows the results of this test.
+As a final test, we generate companion masses for the WDs by sampling from a uniform distribution over the range $[0.2,1.2]~\Msun$, again with $f_{\rm NS}=$10\%.
+The bottom row of Figure~\ref{fig:tests} shows the results of this test.
 The posterior distribution in the second panel shows that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained, as expected.
-The preference toward larger $\sigma_{\rm WD}$ is expected as it flattens the distribution to match it with the input uniform distribution.
+The preference toward larger $\sigma_{\rm WD}$ is expected as the model flattens the distribution to match it with the input uniform distribution.
 The third panel shows that the posterior distribution is spread out in $\sigma_{\rm WD}$.
 Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-Figure~\ref{fig:P_NS} shows that, compared to Test 2, our model is not as effective at identifying exactly which LMWDs host NS companions.
+Furthermore, Figure~\ref{fig:P_NS} shows that our model is still effective at identifying exactly which LMWDs host NS companions.
 
@@
 
-The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06}; it also includes previously identified LMWDs in SDSS \citep{eisenstein06,liebert04}.
+The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06}.
+The ELM sample also includes previously identified LMWDs in SDSS \citep{eisenstein06,liebert04}.
 Objects are identified for spectroscopic follow-up by their $u-g$ versus $g-r$ colors.
@@
 The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-Fitting the WDs' spectra to templates provides precisely determine $M_1$ values.
-We use the spectroscopic solutions of \citet{gianninas14}.
+Fitting the WDs' spectra to templates provides precisely determine $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.
+
 Three systems are eclipsing binaries, with known companion masses: NLTT 11748 \citep[$M_2=0.72~\Msun$;][]{kaplan14}, SDSS J065133.3$+$284423.3 \citep[$M_2=0.50~\Msun$;][]{brown11b}, and SDSS J075141.2$-$014120.9 \citep[$M_2=0.97~\Msun$;][]{kilic14}.
@@
 Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
-These LMWDs could also have companions at systematically longer orbital periods resulting in orbital velocities below the detection limit.
+These LMWDs could also have companions at systematically longer orbital periods, resulting in orbital velocities below the detection limit.
 We do not include these systems in our analysis.
@@
 Our results are independent of astrophysical expectations, as they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
-In principle, priors could be added based on population synthesis models that suggest that there are two dominant companion populations to LMWDs, composed of CO and He core WDs \citep{han98}.
+In principle, priors could be added based on population synthesis models, which suggest that there are two dominant companion populations to LMWDs composed of CO and He core WDs \citep{han98}.
 The ratio and distribution of these two populations depend on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
@@
 
-The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward 0.
+The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward 0\%.
 However, there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07}, based on the non-detection of radio emission from eight LMWD targets, and from \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, based on non-detections of radio emission from an expanded sample of 15 LMWD targets.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07}, based on the non-detection of radio emission from eight LMWD targets, and from \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, based on non-detections of radio emission from an expanded sample of 15 LMWDs.
 
@@
 When applied to three separate test cases with unseen WD and NS companions to LMWDs, our model recovers the input parameters.
-Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction within a few percent.
+Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction to within a few percent.
 
 We then applied our model to the set of LMWDs from the ELM WD survey.
-Our model indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
-Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
+It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case.
+Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
 This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
-
-%We identify SDSS J081133.6$+$022556.8 %and SDSS J174140.5$+$652638.7 
-%as having the highest median probability of hosting a NS companion and suggest that X-ray and radio follow-up is warranted.
+Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
+Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
+%and SDSS J174140.5$+$652638.7 
+% and suggest that X-ray and radio follow-up is warranted.
 We further suggest that the majority of ELM WDs have CO-core WD companions.

### 2014-11-04 documents/letter/ms.tex
Upated .tex

@@
 
-	\tablecomments{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}.
+	\tablecomments{Parameter information for the form of the companion mass distribution used in the tests of Section~\ref{sec:tests}.
 $\mathcal{U}$ is the uniform distribution.
@@
 We then applied our model to the set of LMWDs from the ELM WD survey.
-It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case.
+It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the mass distribution of LMWD companions is well-described by our model.
 Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.

### 2014-11-05 documents/letter/ms.tex
Updated .tex and Porb_M1

@@
 
-Except in special cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution.
+Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution.
 These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
 In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations.
-The ELM WD Survey identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs \citep[$M\lesssim0.3~ \Msun$;][]{ELMI}.
+The ELM WD Survey \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$).
 After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
@@
 
-While the orbital periods and radial velocities indicate the companions are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}.
+While the orbital periods and radial velocities indicate the companions to these LMWDs are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}.
 Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-However, all radio searches for pulsed emission, as well as searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
+However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
 
-For each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$).
-Using Kepler's third law, we can write the relation between these quantities, the unknown inclination angle ($i$), and the companion mass ($M_2$) as:
+For each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$), where $i$ is the unknown inclination angle.
+Using Kepler's third law, we can write the relation between these quantities and the companion mass ($M_2$) as:
 \begin{equation}
@@
 
-To answer these questions, we build the mathematical framework in Section 2, then test our model in Section 3. We apply our model to the ELM WD sample in Section 4 and conclude in Section 5.
+To answer these questions, we build the mathematical framework in Section 2, then test our resulting model in Section 3. We apply our model to the ELM WD sample in Section 4 and conclude in Section 5.
 
@@
 
-\section{Methods}
+\section{Building our model}
 
@@
 
-We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}}.
-The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}} The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
 We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
@@
 Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
-The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; again the dashed lines show the input values.
+The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; here again the dashed lines show the input values.
 }
@@
 Importantly, the third panel shows that our model also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
-Tick marks in the middle panel of Figure~\ref{fig:P_NS} indicate ''true" NSs in our mock data.
+Tick marks in the middle panel of Figure~\ref{fig:P_NS} indicate ``true" NSs in our mock data.
 Our model correctly assigns high $P_{\rm NS}$ to roughly half of these.
@@
 The posterior distribution in the second panel shows that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained, as expected.
-The preference toward larger $\sigma_{\rm WD}$ is expected as the model flattens the distribution to match it with the input uniform distribution.
+The preference for larger $\sigma_{\rm WD}$ is expected as the model flattens the distribution to match it with the input uniform distribution.
 The third panel shows that the posterior distribution is spread out in $\sigma_{\rm WD}$.
 Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-Furthermore, Figure~\ref{fig:P_NS} shows that our model is still effective at identifying exactly which LMWDs host NS companions.
+Furthermore, the rightmost panel of Figure~\ref{fig:P_NS} shows that our model is still effective at identifying exactly which LMWDs host NS companions.
 
@@
 \includegraphics[width=0.75\textwidth]{PNS.pdf}
-\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks show those systems that are true NSs.}
+\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks along the bottom show those systems that are true NSs.}
 \label{fig:P_NS}
@@
 \end{figure*}
+
+\section{Applying our model}
 
@@
 The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
-Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
+Some of these systems may be in low inclination-angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
 These LMWDs could also have companions at systematically longer orbital periods, resulting in orbital velocities below the detection limit.
@@
 
-\section{Applying our Model}
+\subsection{Results and Discussion}
 
@@
 
-The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$ probabilities: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7.
+The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7.
 X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}.
-Searches for radio and x-ray emission from SDSS J081133.6$+$022556.8 are ongoing.
+Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are ongoing.
 
@@
 
-To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt Python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
-This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
-
 \section{Conclusions}
@@
 We have developed a statistical model to infer the companion mass distribution for a sample of single-line, spectroscopic binaries.
-This model can be applied to any such sample with measured $M_1$ and mass function.
+This model can be applied to any such sample with measured $M_1$ and $\mf$.
 When applied to three separate test cases with unseen WD and NS companions to LMWDs, our model recovers the input parameters.
@@
 Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
-This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
-Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$).
+This is in contrast to predictions from population synthesis models, which find that the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
+Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\approx$16\% (within 1-$\sigma$).
 Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
@@
 
-There are several ways in which this model can be expanded.
+To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt Python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
+This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
+
+There are several ways in which our model can be expanded.
 Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.

### 2014-11-05 documents/letter/ms.tex
Submitted version

@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to a single-line spectroscopic sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
+We then apply this model to a sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
 We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions.
@@
 The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained.
-%Such systems are extremely interesting: the NS binaries with WD companions bright enough to detect spectroscopic radial velocity variations have precisely determined NS masses which provide useful insights into the binary evolution processes that form these systems \citep{benvenuto05,smedley14,jia14}.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
@@
 We construct a statistical model to derive constraints on a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
-We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m_f}$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,
@@
 \end{equation}
-
 where the product is over each of the $j$ systems.  This marginal likelihood involves integrals over the unobserved quantities $i$ and $M_2$,
 \begin{align}
-    p(\mf \given \bs{\theta}) &= \int_{-\infty}^\infty dM_2 \int_0^{\pi/2} di  \nonumber \\
+    p(\mf \given \bs{\theta}) &= \int_0^\infty dM_2 \int_0^{\pi/2} di  \nonumber \\
       & \qquad {} \times p(\mf \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
@@
 \begin{align}
-%    p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di \nonumber \\
-%    & \qquad {} \times \delta \left[\mf - f(M_1, M_2, i)\right]~\sin i\\
     p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta})  \nonumber \\
@@
 \begin{align}
-%	\sin i^* &= \alpha\\
-%	\alpha &= \frac{(\mf(M_1+M_2)^2)^{1/3}}{M_2}\\
 	\sin i^* &= \frac{ \left[\mf(M_1+M_2)^2 \right]^{1/3}}{M_2}\\
-%	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
-%	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
 	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \sin^2 i^* \sqrt{1 - \sin^2 i^*}
@@
 	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\sin i^* \left(\frac{\partial g}{\partial i}\bigg\rvert_{i^*}\right)^{-1}\\
-%	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
 	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, \mf, M_1) \label{eq:fullm2}
@@
 \begin{align}
-%	h(M_2, \mf, M_1) &= \frac{(M_1+M_2)^{4/3}}{3\mf^{1/3}M_2\sqrt{M_2^2 - \left[ \mf(M_1+M_2)^2 \right]^{2/3}}}\\
-%	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, \mf, M_1)\\
 	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] 
@@
 	\mu_{\rm NS} &= 1.4~\Msun\\
-	\sigma^2_{\rm NS} &= (0.05~\Msun)^2
+	\sigma_{\rm NS} &= 0.05~\Msun
 \end{align}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.05-2~\Msun$; finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
+For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
+Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
 
-%\setlength{\tabcolsep}{2pt}
 \renewcommand{\arraystretch}{1.405}
@@
 The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
-%Nevertheless, our model recovers the input parameters for the white dwarf companion population.
 
@@
 \subsection{Test 2: Two Gaussians (WD + NS)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$ and parameters described in Section~\ref{sec:experiments}.
+For our next test, we use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$.
 The middle row of Figure~\ref{fig:tests} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
@@
 However, many systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
-
-%Figure~\ref{fig:P_NS} indicates that some systems have near unity $P_{\rm NS}$ values; tick marks, which indicate ''true" NSs, indicate that our model correctly identifies these as true NSs.
-However, more than half of the systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
 
@@
 The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-Fitting the WDs' spectra to templates provides precisely determine $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.
+Fitting the WDs' spectra to templates provides precisely determined $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.
 
@@
 
-Our results are independent of astrophysical expectations, as they do not include any priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
-In principle, priors could be added based on population synthesis models, which suggest that there are two dominant companion populations to LMWDs composed of CO and He core WDs \citep{han98}.
-The ratio and distribution of these two populations depend on the exact stellar evolution prescriptions assumed \citep[see discussion in, e.g., ][]{toonen12}.
+Our results are independent of astrophysical expectations, as they do not include informative priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
+In principle, priors could be added based on population synthesis models, which suggest that there are two dominant companion populations to LMWDs composed of CO and He core WDs \citep{han98, toonen12}.
 Our results here suggest the companion sample is composed mainly of CO WDs.
-Our model could be expanded to include a two Gaussian model --- one for each WD population.
-The ratio of these populations could potentially place an important constraint on population synthesis models.
-However, we have found that there are not enough data to motivate adding additional freedom to the model in the form of a second WD component.
+With a larger sample, a more sophisticated LMWD companion model could place quantitative constraints on population synthesis predictions.
 
@@
 
-% Because it may be radio quiet or beamed away from us, a NS companion to these LMWDs may not be detectable \citep{vLeeuwen07}.
-All NSs give off blackbody radiation peaked in X-ray wavelengths, so X-ray follow-up provides a more stringent test on the potential for a NS companion \citep{agueros09a}.
-Previous searches for LMWDs with X-ray counterparts have all been non-detections \citep{ELMII,ELMIV,kilic13,kilic14}.
-However, based on our model, all of those sources have a low probability of hosting a NS companion.
-%If the two systems with the highest $P_{\rm NS}$, SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7, also lack X-ray counterparts, then even more stringent constraints can be placed on $f_{\rm NS}$.
-
-% It is worth noting that systems with NS companions cannot necessarily be differentiated from those with WD companions through the mass function and LMWD mass alone.
-Therefore there is a non-negligible probability that {\it any} LMWD could host a NS companion.
-
-%These systems are ideal candidates for radio and X-ray searches for NS companions. 
-%Radio observations of these objects are in progress, however
-
-%It is worth noting that the fourth panels in our test cases in Figure~\ref{fig:tests} shows that our model is fairly good at identifying those systems most likely to host NS's.
-However it also shows that roughly half of the LMWDs with NS companions may appear with a deceptively low $f_{\rm NS}$ due to the inclination angle.
-
 \section{Conclusions}
@@
 We then applied our model to the set of LMWDs from the ELM WD survey.
-It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the mass distribution of LMWD companions is well-described by our model.
+It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the companion mass distribution to the LMWDs in the ELM sample is well-described by our model.
 Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
 This is in contrast to predictions from population synthesis models, which find that the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
-Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\approx$16\% (within 1-$\sigma$).
+Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be as high as $\approx$16\% (within 1-$\sigma$).
 Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
-%and SDSS J174140.5$+$652638.7 
-% and suggest that X-ray and radio follow-up is warranted.
-We further suggest that the majority of ELM WDs have CO-core WD companions.
-This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
 
-%In particular, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
-
-To determine the probability of any particular LMWD of hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt Python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
+To determine the probability of any particular LMWD hosting a NS, we make our model posteriors publicly available on fig{\bf share}.\footnote{\url{http://dx.doi.org/10.6084/m9.figshare.1206621}} We further provide a {\tt Python} script that calculates $P_{\rm NS}$ and the mass distribution for a WD companion for any LMWD with a measured $M_1$ and $\mf$.
 This script can be applied to newly discovered LMWDs as well as those already in the ELM sample.
@@
 Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems, which could be included in our model.
-Furthermore, tighter constraints can be placed on $f_{\rm NS}$ by including radio and X-ray non-detection data.
+Furthermore, tighter constraints can be placed on $f_{\rm NS}$ by including radio and X-ray non-detection results.
 Finally, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
-
-%Our model is applicable to any arbitrary set of single-lined spectroscopic binaries.
-Applying this method to various populations can help to constrain the formation of particularly classes of binaries.
 

### 2014-11-11 documents/letter/response.txt
Updated .tex and .bib and added referee response

Dear Dr. de Grijs

We thank the two referees for their detailed comments. We have improved the paper, and included all the suggestions in the revised manuscript. Our response to the referees’ suggestions are below.

Please let me know if further improvements are required.

Sincerely,
Jeff J Andrews

>
>========================================================
>Report from Referee 1:
>
>The authors investigate the mass distribution of companions to
>low-mass white dwarfs. For this purpose they have developed a
>thorough statistical model, which has been applied to three mock data
>sets as well as to the real ELM white dwarf sample. They find that the
>companion mass distribution of the EML sample peaks at 0.71Msun (std
>of 0.26Msun), and that the NS fraction seems to be very low.
>
>The paper is well-written, goes to the point, and is well
>understood. Thus I highly recommend its publication in ApJ
>letters. However, before this I consider there are some points the
>authors should discuss/investigate further. 
>
>- Title. Since the sample of study is the ELM sample (defined as
>Mwd<~0.3Msun), instead of the low-mass sample (defined as
>Mwd<~0.45Msun), change the title to "The mass distribution of
>companions to extremely low-mass white dwarfs".
>
>- Abstract. "We then apply this model to a sample of low mass white
>dwarfs (LMWDs, M<~0.45 Msun)." Reading this gives the impression that
>the sample is an observed (real) one, which is not the case. Specify
>that the low-mass WD samples used are three, and that these are drawn
>from mock data.
>

We have fixed this in the abstract.

>
>- Introduction. The authors cite the seminal paper by Marsh et
>al. (1995) that demonstrated that a large fraction of low-mass white
>dwarfs are in binaries. However, several more and recent observational
>efforts have been performed that prove to high extent that indeed
>low-mass white dwarfs are formed due to binary interactions. Add 
>citations to e.g. Maxted et al. 2000MNRAS,319,305M, Rebassa-Mansergas 
>et al. 2011MNRAS,413,1121R.
>

These citations have been added to the introduction, along with a result from the SPY survey, searching for SN Ia progenitors, which identified two additional LMWDs in close binaries with unknown companions.

>
>- Introduction. The authors should state more clearly why identifying
>NS or WD companions to ELM white dwarfs is important. What important
>problems will be solved or can be addressed by knowing that NS are or
>are not likely to be the companions of ELM white dwarfs?
>

We have added a sentence explaining the importance of finding individual NS-LMWD systems in paragraph 2 in the introduction and a sentence explaining the importance of understanding the companion mass distribution to LMWDs in paragraph 4.

>
>- Section 2. Why using a logarithmic prior for sigma(WD)?

We choose a logarithmic prior for sigma(WD) since it is scale invariant. We have added this to the text.

>Why fixing sigma(NS) to 0.05Msun when sigma(WD) has a much wider range? Is it because the NS mass distribution peaks at ~1.35Msun with almost no tail towards lower and higher masses?

We wanted to build a simplistic model, with few parameters, therefore we set the NS distribution without allowing it to vary. From Kiziltan et al. (2013) and Smedley et al. (2014) it appears that NSs with WD companions may have a slightly higher mass tail, therefore we set the NS mass distribution higher than the canonical value of 1.35 Msun.

>According to the text, sigma(WD) ranges from 0.02-2Msun. However, in Table 1 I see sigma(WD) proportional to sigma^(-1), where 0.02 
>- Table 1. The prior of mu(WD) is written as U(0.2,1), but should not it be U(0.2,1.4)?

The prior on sigma(WD) should be U(0.2,2.0) and on mu(WD), 0.02 < mu < 1.0. Both the text and table have been fixed to reflect this. For the flexibility of our model, we allow sigma(WD) to vary greatly. We still truncate the mass distribution at [0.2,1.44], but we do not allow the center of the Gaussian to go above 1.0 Msun.

>
>- Figure 1. Why not adding the number and label in the y axis? Top
>left panel. It is interesting to see that the distribution is
>bi-modal, and that there is a large number of massive (~1Msun) white
>dwarfs. How realistic are the assumptions for this particular M2
>distribution?
>

The distribution in Figure 1 was drawn from a Gaussian with mu(WD)=0.7 Msun and sigma(WD) = 0.2. We tested this by drawing other random samples; the bimodal distribution is due to the randomness of drawing 100 WD samples. In other randomly drawn samples, this distribution appears as a single Gaussian.

>
>- I consider testing the statistical model using three samples of mock
>data is very useful. However, I believe the model should also be
>tested with real data. The sample of close white dwarf-M dwarf
>binaries with orbital periods and component masses measured is of the
>same order as the ELM survey and can be used for this purpose (see
>e.g. Nebot Gomez-Moran et al. 2011A&A,536A,43N; there are also several
>known eclipsing systems: see the work by S.G. Parsons et al.). In this
>case, K are known for the secondary stars so the distribution to test
>with the statistical model would be the white dwarf mass
>distribution. (Note that for this sample the spectral type of the
>secondary stars are provided, which can be converted into mass
>following a spectral type-mass relation: e.g. Baraffe & Chabrier
>1996ApJ,461L,51B).
>

Based on your suggestion, we have added a fourth test where we derive the resulting WD mass distribution of companions to the post-common envelope binary sample from SDSS. The description of this test is included in Section 3.4, and the results are included in Figure 4.

>
>- Section 4.1. "Fitting the WDs' spectra to templates provides
>precisely determined M1 values". I am not entirely convinced by this
>sentence. This is definitely the case when one of the stars is
>considerably more luminous than the other, but it might not be the
>case otherwise. Lets consider a white dwarf which contributes 30% to
>the total flux in the Hbeta to Hepsilon Balmer line regime (where the
>line profile fitting takes place), the other white dwarf contributing
>70%. The total flux will be the sum of the two flux contributions and
>a fit to the resulting spectrum may not give the mass of the more
>luminous white dwarf. I agree that assuming M1 to be the one obtained
>from the template fit is the best way to proceed, however a note of
>caution should be added in the text. A plausible way to check this
>would be to compare the accurate masses of the eclipsing systems with
>those provided from the spectral fitting, if available.
>

There is a distinct possibility that the companion WDs could contribute to the luminosity of the LMWD primaries in these systems. However, Gianninas et al. (2014) point out that because the systems are all single-lined spectra, they expect the companion’s “contribution to the observed spectra to be on the order of a few percent at most.” In investigating this possibility though, we found a bigger issue: For two of the three eclipsing systems, the spectroscopic mass measurements are in agreement with the expectation from the eclipse measurement. For the third system, NLTT 11748, there is a significant discrepancy. Gianninas et al. (2014) contribute this difference to the “high log g problem”, a manifestation of the problems with using 1-D WD atmospheric models. They suggest that only the spectroscopic masses of the seven WDs with temperatures below roughly 9500 K will be affected. We add a note of caution in the text to indicate there may be some unknown uncertainties in these mass measurements.

>
>- Section 4.2. "Our distribution is significantly wider (sigma ~ 0.26
>Msun compared with sigma~0.1 Msun), possibly due to mass transfer
>affecting the mass distribution of the unseen primary WDs as well." Do
>the authors mean on-going mass transfer? If that is the case, should
>we not see an accretion disk in the spectrum? It seems unlikely that a
>large fraction of these systems are currently undergoing mass transfer
>episodes. Or do the authors mean previous mass transfer episodes? When
>specifically?
>

We expect that all these systems are detached due to the lack of emission lines in the spectra as would be expected from an accretion disk. The text has been updated to specify that the companion masses may be more massive due to previous mass transfer phases.

>
>- Section 4.2. Since the ELM sample contains primaries of M<~0.3Msun
>and mu(WD)=0.71Msun, this seems to imply that the future mergers will
>not produce type Ia supernovae. I consider the authors should add a
>couple of sentences discussing this.
>

While most of these systems almost certainly have a combined mass less than 1.4 Msun, many of the combined masses of these systems are still ~1Msun. They may therefore evolve into underluminous supernova. We have included some discussion of this in Section 4.2.

>
>- Inspection of figure 3 and the right panel of figure 4 reveals that
>P(NS) increases with mf. Add an explanation why this is the case. Do
>these figures imply that an observer looking for a NS in orbit with a
>ELM white dwarf can focus specifically on targets with the highest mf?
>If so, add a sentence stating this in the text.
>

Systems with higher mf values are more likely to have NS companions through Equation 1. We added a note about this in the text.

>****
>Report from Referee 2:
>
>I provide here comments only on the statistical methodology of this manuscript, not on any scientific aspects. I have not checked the equations (8)-(15) in detail. 
>
>The procedure in section 2 focuses on the question raised in the Introduction: "1. Can the population as a whole be modeled using a simple description of the companion masses?" The setup of the likelihood seems reasonable. The normal mixture model for white dwarf and neutron star secondaries is also reasonable. The inference that the secondary WDs have similar mass distributions as primary WDs is unsurprising and adds confidence that the calculation is reasonable. I have two comments:
>
>A. Bayes' rule is only needed if significant priors are introduced. Are equations (7) and (19)-(20) relevant prior distributions? If so, please label them accordingly. Indeed, the authors state in 4.2/par2 that the "results are independent of astrophysical expectations as they do not include informative priors on ..."; but the entire point of the Bayesian approach is to introduce meaningful priors. Since the authors seek the MAP solution, I suspect the calculation is equivalent to a constrained maximum likelihood calculation (e.g. http://link.springer.com/article/10.1023/A:1008669208700 http://faculty.washington.edu/rons/cmlinf/cmlinf.html). There is no difficulty in using an MCMC approach, and the results are unchanged, but the authors should clarify that the calculation can be viewed from either perspective. Fortunately the authors do not emphasize `Bayesian' in the title, abstract or conclusions. 
>

The prior in equation 7 comes from the fact that the inclination angle is random. One of the advantages to this sample is that there is (nearly) no observational bias on the inclination angle, therefore this prior is appropriate. The priors on our NS model, listed in Equations 19-20, are reasonable based on NS mass measurements derived elsewhere, in Kiziltan et al. (2013) and Smedley et al. (2014).

We agree that there is no difference between our method and a maximum likelihood calculation. We have added a sentence clarifying this in the first paragraph of Section 2.

>
>B. Concerning the statement in 4.2 "Our distribution is significantly wider ....[physical explanation]. Couldn't this be a statistical effect: Wouldn't the posterior distribution appear wider just because the sample is small and the spread is thus poorly constrained? This can be checked with simulations of different sample sizes.
>
>

### 2014-11-11 documents/letter/ms.tex
Updated .tex and .bib and added referee response

@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to a sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
+We then apply this model to {\bf three mock} samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
 We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions.
-Our model successfully recovers the initial parameters of several mock data sets.
+Our model successfully recovers the initial parameters of {\bf these} mock data sets.
 We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey.
@@
 These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
-In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations.
+In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations, which has been followed by several other searches finding companions to LMWDs \citep{maxted00,nelemans05,rebassa11}.
 The ELM WD Survey \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$).
@@
 Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
+{\bf Finding even one additional system is extremely interesting since radial velocity measurements from optical spectra when combined with precise radio data give a NS mass measurement.} However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
 
@@
 
-The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained.
-In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
+The ELM sample is now large enough that the NS fraction and WD companion mass distribution can be statistically constrained.
+{\bf Constraints on the WD companion mass distribution to LMWDs provide a clear observable for population synthesis studies to match.} In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
@@
 \begin{center}
-\includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
+\includegraphics[angle=90,width=0.95\columnwidth]{f1.eps}
 \caption{The $M_1$ - $\period$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
@@
 and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified.
-We fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
+{\bf To reduce the number of parameters in our model} we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
 \begin{align}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
+For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; we use a logarithmic ({\bf scale-invariant}) prior for $\sigma_{\rm WD}$ over the range $0.02-1.0~\Msun$.
 Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
@@
 		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\propto \sigma^{-1}$  & $\mathcal{U}(0, 1)$ \\
-		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2)$ & \\
+		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2.0)$ & \\
 		\cutinhead{Test Cases}
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{many-panel.pdf}
+\includegraphics[width=0.75\textwidth]{f2.pdf}
 \caption{Results from the three tests described in Section~\ref{sec:tests}.
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{PNS.pdf}
+\includegraphics[width=0.75\textwidth]{f3.pdf}
 \caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks along the bottom show those systems that are true NSs.}
@@
 Fitting the WDs' spectra to templates provides precisely determined $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.
+{\bf These mass measurements are precisely determined, however the spectroscopic mass measurements may be affected by contamination from the less luminous companion or the ``high log $g$ problem'' due to inaccuracies in the 1-D WD atmospheric models \citep{tremblay13}.
+These limitations should only affect the coolest WDs in the ELM sample, therefore we suggest this effect is minor.}
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{real-data.pdf}
+\includegraphics[width=0.95\textwidth]{f4.pdf}
 \caption{Results from applying our model to the ELM WDs.
@@
 It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
+Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to {\bf past mass transfer phases increasing the masses of the unseen primary WDs.} {\bf Several of these systems will merge within a Hubble time \citep{ELMV}, however their sub-Chandrasekhar combined mass would suggest that they are more likely to be underluminous, .Ia supernova progenitors rather than type Ia supernova progenitors.
+}
 
@@
 Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are ongoing.
+{\bf Figure~\ref{fig:ELM_post} shows a general trend that systems with higher $\mf$'s have higher $P_{\rm NS}$ values.
+This is due to the effect of $M_2$ on $\mf$ in Equation~\ref{eq:massfunc}.
+Systems with higher $\mf$'s are therefore ideal targets to search for NS companions to LMWDs.}
 

### 2014-11-11 documents/letter/ms.tex
Updated .tex

@@
 We construct a statistical model to derive constraints on a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
-We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m_f}$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+{\bf Our model is based on a Bayesian approach, however the problem could also be viewed from a maximum likelihood perspective.} We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m_f}$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
 Using Bayes' rule,

### 2014-11-14 documents/letter/ms.tex
Updated .tex

--- 2014-11-05 documents/letter/ms.tex
@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to a sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$).
+We then apply this model to three mock samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a sample of post-common envelope binaries (PCEB).
 We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions.
-Our model successfully recovers the initial parameters of several mock data sets.
+Our model successfully recovers the initial parameters of these test data sets.
+%We focus on low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$), modeling the companion mass distribution with a mixture of two Gaussians to represent a WD and neutron star (NS) companion population.
+Our model successfully recovers the initial parameters of three mock samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a test sample of post-common envelope binaries (PCEB).
 We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey.
-Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.71~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$; the fraction of NS companions, $f_{\rm NS}$, is consistent with zero.
-However, the marginal posterior distribution over the NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$.
-We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered low mass WDs.
+Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.74~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.24~\Msun$.
+Our model constrains the fraction of NS companions,  $f_{\rm NS}$, to be less than 0.16 at 68\% confidence.
+We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered LMWDs.
 \end{abstract}
@@
 
-Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution.
-These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
-In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations.
-The ELM WD Survey \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$).
+Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single-star evolution.
+Instead, they form through interactions with another star and are expected to be in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
+%In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations. T
+Indeed, observationally, LMWDs have companions \citep{marsh95,maxted00,nelemans05,rebassa11}.
+Recently, the ELM WD Survey has searched for extremely LMWDs ($M\lesssim0.3~ \Msun$) in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere \citep{ELMI,ELMII, ELMIII, ELMIV, ELMV}.
+Fifty-five of their 61 identified LMWDs have a measured radial velocity (RV) and orbital period ($\period$); we refer to these 55 systems as the ELM sample.
+% \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$).
 After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
@@
 
-While the orbital periods and radial velocities indicate the companions to these LMWDs are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}.
-Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
+RV and $\period$ measurements indicate that the LMWDs companions are most likely WDs.
+However, since inclination angle $i$ is unknown, LMWDs could have NS companions \citep{vLeeuwen07}.
+Indeed, LMWDs are observed as companions to millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
+Finding even one NS companion to a spectroscopically characterized LMWD would be very valuable, since this system would constrain the NS mass.
+% TO ADD?: Also allows constraints on MSP age, braking index
+However, radio and X-ray searches for NS companions to LMWDs have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
 
-For each LMWD in the ELM sample, spectroscopic observations provide the orbital period ($\period$), primary WD mass ($M_1$), and projected orbital velocity ($K=v \sin i$), where $i$ is the unknown inclination angle.
-Using Kepler's third law, we can write the relation between these quantities and the companion mass ($M_2$) as:
+For each LMWD in the ELM sample, spectroscopy provides $\period$, the primary WD mass ($M_1$), and the projected orbital velocity ($K=v \sin i$). From Kepler's third law, we can write:
 \begin{equation}
-	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3 \label{eq:massfunc}
+	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3. \label{eq:massfunc}
 \end{equation}
-The righthand side of this equation is the mass function $\mf$.
-$M_2$ is minimized for an edge-on orbit with $i = 90\degree$.
+The righthand side is the mass function $\mf$.
+The companion mass, $M_2$, is minimized for an edge-on orbit ($i = 90\degree$).
 Because of this dependence on $i$, the nature of the companion cannot usually be determined based on $\mf$ alone.
@@
 
-The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained.
+Even if no NS companions to LMWDs are found, constraints on the WD companion mass distribution to LMWDs provide observations for population synthesis studies to match. 
+% TO ADD?: constraints on mass transfer physics?
+The ELM sample is now large enough that the NS fraction and WD companion mass distribution can be statistically constrained.
 In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
-We focus on several specific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses?
-2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?
-3.\ What is the rate of NS-LMWD binaries implied by our model?
-4.\ What are the resulting distributions of NS probabilities for individual systems in the ELM sample?
+We focus on several specific questions: Can the population as a whole be modeled using a simple description of the companion masses?
+How does the companion mass distribution compare to predictions from population synthesis simulations?
+What is the rate of NS-LMWD binaries implied by our model?
+What are the resulting distributions of NS probabilities for individual systems in the ELM sample?
 
-To answer these questions, we build the mathematical framework in Section 2, then test our resulting model in Section 3. We apply our model to the ELM WD sample in Section 4 and conclude in Section 5.
+To answer these questions, we build the mathematical framework (Section 2), then test our resulting model (Section 3).
+We apply our model to the ELM WD sample (Section 4) before concluding (Section 5).
 
@@
 
-We construct a statistical model to derive constraints on a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantities are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $\mf$ (\eqn~\ref{eq:massfunc}).
-We would like to derive posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m_f}$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$.
+We construct a statistical model to constrain a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{We represent vectors or sets of parameters or quantities by bold symbols.} For each system, we assume we have $K$, $T$, and $M_1$, and therefore know the value of $\mf$ (\eqn~\ref{eq:massfunc}).
+{\bf Our model is based on a Bayesian approach, but this problem could also be viewed from a maximum-likelihood perspective.} We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed $\mf$, $\bs{m_f}$, by deconvolving the distribution of $\mf$ from the unobserved $i$.
 Using Bayes' rule,
@@
 
-We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$.
-For all experiments -- including that with the real data -- we use a two-component Gaussian mixture model to fit the data.
-We generate mock data with different mixture component forms.
-We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$.
+We must now choose a functional form for the companion mass distribution, $p(M_2\given \bs{\theta})$, and 
+use a two-component Gaussian mixture model.
+We truncate the distributions using physically motivated bounds so that the WD component is restricted to $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$.
 We then have:
@@
 \end{align}
-and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified.
-We fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
+where $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified.
+To reduce the number of parameters in our model we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
 \begin{align}
@@
 \end{align}
-based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}.
+based on indications that NSs in certain binaries may have be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}.
 The probability of any particular system having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the companion mass distribution:
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
+For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; we use a logarithmic (scale-invariant) prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
 Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
@@
 		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\propto \sigma^{-1}$  & $\mathcal{U}(0, 1)$ \\
-		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2)$ & \\
+		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2.0)$ & \\
 		\cutinhead{Test Cases}
-		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
-		 & MAP & 0.74 & 0.18 & 0.0 \\
+		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0 \\
+		 & MAP & 0.72 & 0.20 & 0.0 \\
 		 \hline
-		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
-		 & MAP & 0.74 & 0.2 & 0.11 \\
+		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.10 \\
+		 & MAP & 0.74 & 0.19 & 0.11 \\
 		 \hline
-		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
-		 & MAP & 0.64 & 0.5 & 0.14 \\
+		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.10 \\
+		 & MAP & 0.63 & 0.52 & 0.14 \\
+		 \hline
+		\multirow{2}{*}{PCEB} & True & \nodata & \nodata & 0 \\
+		 & MAP & 0.58 & 0.16 & 0.0 \\
 		 \cutinhead{ELM Sample}
-		 & MAP & 0.71 & 0.26 & 0.0
+		 & MAP & 0.74 & 0.24 & 0.0
 	\enddata
 
-	\tablecomments{Parameter information for the form of the companion mass distribution used in the tests of Section~\ref{sec:tests}.
-$\mathcal{U}$ is the uniform distribution.
-There are three free parameters.
+	\tablecomments{Parameter information for the form of the companion mass distribution used in the tests of Section~\ref{sec:tests}. $\mathcal{U}$ is the uniform distribution. 
+%There are three free parameters. 
 We additionally fix the NS mass distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
@@
 
-We use an ensemble Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}} The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
-We run the walkers for an initial, burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
+We use a Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}} The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We run the walkers for a burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
 We then re-initialize the walkers from their positions at the end of this run and run again for 1000 steps.
-We throw out the burn-in samples to eliminate any effects from our choice of initial conditions.
+We remove the burn-in samples to eliminate any effects from our choice of initial conditions.
 
 \section{Testing Our Model} \label{sec:tests}
-To test the performance of this Gaussian mixture model, we first apply it to three separate sets of mock data (described in detail below), each with 100 ``observed'' systems.
-These mock data are generated by randomly drawing the companion mass from a particular distribution, then using a randomly drawn inclination angle and primary mass to compute the mass function.
+We test the performance of this Gaussian mixture model on four separate data sets: three mock data sets and the sample of SDSS PCEBs from \citet{nebot11}. 
+Each of the 100 systems in our three mock data sets are generated by computing $\mf$'s from randomly drawn
+$M_1$'s (from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$), $M_2$'s (from the distributions described below), and $i$'s. 
+%the companion mass from the particular distributions described below, then using a randomly drawn $i$ and $M_1$ to compute $\mf$.
 We draw $M_1$ from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$.
-We apply the same Gaussian mixture model to all mock datasets to infer the parameters of the WD mixture component and $f_{\rm NS}$.
+We apply the same Gaussian mixture model to all four tests to infer the parameters of the WD mixture component and $f_{\rm NS}$.
 
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{many-panel.pdf}
-\caption{Results from the three tests described in Section~\ref{sec:tests}.
+\includegraphics[width=0.75\textwidth]{f2.pdf}
+\caption{Results from testing the three mock data sets described in Section~\ref{sec:tests}.
 The leftmost column shows histograms of $M_2$ drawn from each of our test distributions.
 Overplotted as solid lines are the MAP models.
-The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
-The dashed lines in the top two panels show the true values that the sample systems were drawn from.
-Contours designate the 68\% and 95\% contours.
-Since the third model was not drawn from a Gaussian distribution, there is no true parameter set.
-The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; here again the dashed lines show the input values.
+The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, and the third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$.
+Contours designate the 68\% and 95\% confidence levels.
+Dashed lines in these panels show the true values from which the sample systems were drawn.
+Since the third model was drawn from a uniform distribution, there are no true $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ values.
 }
@@
 \subsection{Test 1: Single Gaussian (WD)} \label{sec:exp1}
+We first generate $M_2$ by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
+This mock sample contains no NSs.
+In the top row of Figure~\ref{fig:tests}, the leftmost panel shows that our model finds a maximum a posteriori (MAP) $M_2$ distribution (black line) that qualitatively matches the input distribution (grey histogram).
+The second and third panels show samples from the posterior distributions and contours containing 68\% and 95\% of the samples for our three model parameters.
+The input values (dashed lines) lie cleanly within the inner contour in both panels, however $f_{\rm NS}$ has a tail up to $\approx$10\%.
 
-As a first test, we generate $M_2$ by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
-This mock sample contains no NSs.
-In the top row of Figure~\ref{fig:tests}, the leftmost panel shows that the maximum a posteriori (MAP) $M_2$ distribution (black line) qualitatively matches the input distribution (grey histogram).
-The second panel shows samples from the posterior distribution and contours that contain 68\% and 95\% of the samples.
-The input values lie cleanly within the inner contour in both projections of the posterior shown; the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated mock sample.
-The third panel shows that although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\sim$10\%.
+%The second panel shows samples from the posterior distribution and contours containing 68\% and 95\% of the samples.
+The input values lie cleanly within the inner contour in both projections of the posterior.
+%the model preference toward higher masses and smaller standard deviations is due to statistical noise from our randomly generated mock sample. 
+%The third panel shows that, although the posterior $f_{\rm NS}$ distribution is consistent with 0\%, there is a tail up to $\approx$10\%.
 
-For any set of model parameters, Equation~\ref{eq:P_NS} gives the probability of an individual system hosting a NS.
+Equation~\ref{eq:P_NS} gives the probability of an individual system hosting a NS.
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
@@
 \subsection{Test 2: Two Gaussians (WD + NS)} \label{sec:exp2}
-For our next test, we use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$.
+We use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$.
 The middle row of Figure~\ref{fig:tests} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
-As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution.
+%As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution. 
 Importantly, the third panel shows that our model also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
@@
 Our model correctly assigns high $P_{\rm NS}$ to roughly half of these.
-However, many systems with NS companions have inclination angles too low to be statistically differentiated from those with WD companions.
+However, many systems with NS companions have $i$'s too low to be statistically differentiated from those with WD companions.
 
 \subsection{Test 3: Uniform (WD) + Gaussian (NS)} \label{sec:exp3}
-As a final test, we generate companion masses for the WDs by sampling from a uniform distribution over the range $[0.2,1.2]~\Msun$, again with $f_{\rm NS}=$10\%.
-The bottom row of Figure~\ref{fig:tests} shows the results of this test.
-The posterior distribution in the second panel shows that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained, as expected.
-The preference for larger $\sigma_{\rm WD}$ is expected as the model flattens the distribution to match it with the input uniform distribution.
-The third panel shows that the posterior distribution is spread out in $\sigma_{\rm WD}$.
-Interestingly, despite having a non-Gaussian input distribution for $M_2$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-Furthermore, the rightmost panel of Figure~\ref{fig:P_NS} shows that our model is still effective at identifying exactly which LMWDs host NS companions.
+We generate companion masses for the WDs by sampling from a uniform distribution over $[0.2,1.2]~\Msun$, again with $f_{\rm NS}=$10\%.
+The bottom row of Figure~\ref{fig:tests} shows the results.
+The posterior distribution in the second panel indicates that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained.
+The preference for larger $\sigma_{\rm WD}$ is expected as the model flattens the Gaussian model distribution to match it with the input uniform distribution.
+Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, and a poorly constrained $\sigma_{\rm WD}$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
+Furthermore, the rightmost panel of Figure~\ref{fig:P_NS} demonstrates that our model is effectively identifying which LMWDs host NS companions.
+
+\subsection{Test 4: Post-common envelope binaries} \label{sec:PCEB}
+Composed of WDs in close binaries with main-sequence stars, PCEBs are an ideal test sample for our model. 
+We use a sample of 54 SDSS PCEBs with spectroscopically derived $K$'s, $\period$'s, and main sequence masses from \citep{nebot11}.
+Our model uses the measurements of these three parameters to try and recover this sample's WD mass distribution, which we can then compare to the spectroscopically-determined WD masses.
+%Our model is ignorant of the spectroscopically measured WD masses and attempts to fit the WD mass distribution based on the measured main sequence mass, $K$, and $\period$.
+We use a sample of 54 SDSS PCEBs with spectroscopically derived $K$, $\period$, and main sequence masses \citep{nebot11}.
+Our MAP distribution (black line) in the leftmost panel of Figure~\ref{fig:ELM_post} shows that our model qualitatively recovers the true $M_{\rm WD}$ distribution (gray histogram).
+The third panel shows that the posterior $f_{\rm NS}$ distribution is very low, as expected since there are no NS companions in the PCEB sample.
+This is further seen in the rightmost panel, where every PCEB in the sample has low $P_{\rm NS}$ values.
 
@@
 \section{Applying our model}
+\subsection{The ELM Sample}
+The ELM WD Survey is based on the Hypervelocity Star Survey \citep{brown06}, and includes previously identified SDSS LMWDs \citep{eisenstein06,liebert04}.
+Objects are chosen for spectroscopic follow-up based on their $(u-g)$, $(g-r)$ colors, and this choice is independent of the mass and nature of any putative companions.
+Therefore, at least with regard to $i$ and companion mass, the population is unbiased.
 
-\subsection{The ELM Sample}
-
-The ELM WD Survey is based on the Hypervelocity Star Survey described in \citet{brown06}.
-The ELM sample also includes previously identified LMWDs in SDSS \citep{eisenstein06,liebert04}.
-Objects are identified for spectroscopic follow-up by their $u-g$ versus $g-r$ colors.
-Since the survey is designed to select low surface gravity WDs by color, the detection probability is independent of both the mass and nature of any putative companion.
-Therefore, at least with regard to the inclination angle and companion mass, the population is unbiased.
-
-The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-Fitting the WDs' spectra to templates provides precisely determined $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.
+The ELM WD sample includes 55 systems with RV variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
+WD masses in these systems are derived from fits to spectroscopic templates which are generally precise to $\sim10\%$ \citep{gianninas14}.
+The masses of cool LMWDs may suffer somewhat from
+%the ``high log $g$ problem'' due to 
+inaccuracies in the 1-D WD atmospheric models \citep{tremblay13}. However since these limitations should only affect the coolest WDs in the ELM sample, we expect any effect on our results to be minor.
 
@@
 
-The other six systems in the ELM WD sample show no evidence of orbital motion, with radial velocity upper limits of $\approx$20-50 km s$^{-1}$.
-Some of these systems may be in low inclination-angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}.
-These LMWDs could also have companions at systematically longer orbital periods, resulting in orbital velocities below the detection limit.
+The other six systems show no evidence of orbital motion, with RV upper limits of $\approx$20-50 km s$^{-1}$.
+Some of these systems may be in low $i$ binaries with RVs below the detection limit, or have $\period\approx24$ hr, which are difficult to detect \citep{ELMV}.
+These LMWDs could also have companions at systematically longer $\period$'s, resulting in orbital velocities below the detection limit.
 We do not include these systems in our analysis.
+% TO ADD?: They could also not have companions at all - reference goes here
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{real-data.pdf}
-\caption{Results from applying our model to the ELM WDs.
-The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines).
-The second panel shows posterior samples of $\mu$ and $\sigma$; the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
+\includegraphics[width=0.95\textwidth]{f4.pdf}
+\caption{Results from applying our model to the PCEBs (top row) and ELM WDs (bottom row). 
+The panels are the same as in Figure~\ref{fig:tests} and Figure~\ref{fig:P_NS}. 
+%The leftmost panel of the top row shows that the MAP model $M_{\rm WD}$ distribution matches the histogram of true masses in the PCEB sample. 
+%The second and third panels show the posterior distributions for our model parameters, while the fourth panel shows the $P_{\rm NS}$ values for each of the PCEBs (ordered by increasing $\mf$). 
+Here, however, the leftmost panel of the ELM sample shows both the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). 
+%The second panel shows that the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
 The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$.
-The last panel lists individual LMWDs in the ELM sample (ordered by increasing $\mf$) and shows each of their corresponding NS probabilities.
-The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.}
+The last panel indicates that several LMWDs in the ELM sample have high $P_{\rm NS}$.
+The three systems in the bottom right panel, with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.
+}
 \label{fig:ELM_post}
@@
 \subsection{Results and Discussion}
-
-The results from applying our model to the ELM sample are shown in Figure \ref{fig:ELM_post}.
-The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$.
+The results from applying our model to the ELM sample are shown in Figure~\ref{fig:ELM_post}.
+The MAP model gives $\mu_{\rm WD} = 0.74~\Msun$, $\sigma_{\rm WD} = 0.24~\Msun$, and $f_{\rm NS} = 0\%$.
 The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail toward larger $\sigma_{\rm WD}$, which could indicate that the true WD distribution may not be exactly Gaussian.
 It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.
-
-Our results are independent of astrophysical expectations, as they do not include informative priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
-In principle, priors could be added based on population synthesis models, which suggest that there are two dominant companion populations to LMWDs composed of CO and He core WDs \citep{han98, toonen12}.
-Our results here suggest the companion sample is composed mainly of CO WDs.
+Our distribution is significantly wider ($\sigma \approx 0.26~\Msun$, compared with $\sigma \approx 0.1~\Msun$), possibly due to past mass transfer phases increasing the masses of the unseen primary WDs.
+The low combined mass in these systems indicates that, although several of them will merge within a Hubble time \citep{ELMV}, the majority of ELM WDs are unlikely to be type Ia supernova progenitors.
+%Several of these systems will merge within a Hubble time \citep{ELMV}, but their sub-Chandrasekhar combined mass would suggest that they are more likely to be underluminous type .Ia, rather than Ia, supernova progenitors.
+%Our results are independent of astrophysical expectations, as they do not include informative priors on $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, apart from limits for $M_2$ of 0.2 \Msun\,(based on observations of LMWDs) and \wdupper~\Msun\,(based on the Chandrasekhar mass).
+In principle, priors could be added based on
+Our posterior distributions further suggest that the companions to LMWDs have predominantly CO cores.
+This is in contrast to population synthesis models which suggest that LMWDs should predominantly have He core WD companions \citep{toonen12}.
 With a larger sample, a more sophisticated LMWD companion model could place quantitative constraints on population synthesis predictions.
 
-The third panel in Figure~\ref{fig:ELM_post} shows a NS fraction strongly peaked toward 0\%.
+The third panel in Figure~\ref{fig:ELM_post} shows a $f_{\rm NS}$ strongly peaked toward 0\%.
 However, there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07}, based on the non-detection of radio emission from eight LMWD targets, and from \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, based on non-detections of radio emission from an expanded sample of 15 LMWDs.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07} and \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, both based on radio non-detections of LMWDs.
 
 The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7.
-X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}.
-Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are ongoing.
+However, X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}.
+Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are on-going.
+We note that Figure~\ref{fig:ELM_post} shows a general trend that systems with higher $\mf$ have higher $P_{\rm NS}$ values and are therefore ideal targets to search for NS companions to LMWDs.
 
 \section{Conclusions}
-
 We have developed a statistical model to infer the companion mass distribution for a sample of single-line, spectroscopic binaries.
 This model can be applied to any such sample with measured $M_1$ and $\mf$.
-When applied to three separate test cases with unseen WD and NS companions to LMWDs, our model recovers the input parameters.
+When tested on three separate mock data sets with unseen WD and NS companions to LMWDs, our model recovers the input parameters.
 Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction to within a few percent.
+We further apply our model to the sample of PCEB's from \citet{nebot11}; our model qualitatively recovers the independent, spectroscopically measured $M_{\rm WD}$ distribution.
 
@@
 It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the companion mass distribution to the LMWDs in the ELM sample is well-described by our model.
-Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
+Our model indicates a MAP $\mu_{\rm WD}$ of 0.74 \Msun\ and $\sigma_{\rm WD}$ of 0.24 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
 This is in contrast to predictions from population synthesis models, which find that the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
@@
 
+%Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
+Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems, which could be included in our model.
+
 There are several ways in which our model can be expanded.
-Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
-Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems, which could be included in our model.
+Based on modeling the photometric variability in these systems, \citet{hermes14} recently placed constraints on the inclination of 20 LMWDs in the ELM sample which could be included in our model.
 Furthermore, tighter constraints can be placed on $f_{\rm NS}$ by including radio and X-ray non-detection results.
@@
 \acknowledgements
-The authors wish to acknowledge David Hogg and DJ D'Orazio for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
+The authors wish to acknowledge David Hogg, DJ D'Orazio, and Josh Peek for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
 APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
@@
 
-\begin{thebibliography}{36}
+\begin{thebibliography}{41}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 
+\bibitem[{{Maxted} {et~al.}(2000){Maxted}, {Marsh}, \& {Moran}}]{maxted00}
+{Maxted}, P.~F.~L., {Marsh}, T.~R., \& {Moran}, C.~K.~J. 2000, \mnras, 319, 305
+
+\bibitem[{{Nebot G{\'o}mez-Mor{\'a}n} {et~al.}(2011){Nebot
+  G{\'o}mez-Mor{\'a}n}, {G{\"a}nsicke}, {Schreiber}, {Rebassa-Mansergas},
+  {Schwope}, {Southworth}, {Aungwerojwit}, {Bothe}, {Davis}, {Kolb},
+  {M{\"u}ller}, {Papadaki}, {Pyrzas}, {Rabitz}, {Rodr{\'{\i}}guez-Gil},
+  {Schmidtobreick}, {Schwarz}, {Tappert}, {Toloza}, {Vogel}, \&
+  {Zorotovic}}]{nebot11}
+{Nebot G{\'o}mez-Mor{\'a}n}, A. {et~al.} 2011, \aap, 536, A43
+
+\bibitem[{{Nelemans} {et~al.}(2005){Nelemans}, {Napiwotzki}, {Karl}, {Marsh},
+  {Voss}, {Roelofs}, {Izzard}, {Montgomery}, {Reerink}, {Christlieb}, \&
+  {Reimers}}]{nelemans05}
+{Nelemans}, G. {et~al.} 2005, \aap, 440, 1087
+
 \bibitem[{{Nelemans} {et~al.}(2000){Nelemans}, {Verbunt}, {Yungelson}, \&
@@
 
+\bibitem[{{Rebassa-Mansergas} {et~al.}(2011){Rebassa-Mansergas}, {Nebot
+  G{\'o}mez-Mor{\'a}n}, {Schreiber}, {Girven}, \& {G{\"a}nsicke}}]{rebassa11}
+{Rebassa-Mansergas}, A., {Nebot G{\'o}mez-Mor{\'a}n}, A., {Schreiber}, M.~R.,
+  {Girven}, J., \& {G{\"a}nsicke}, B.~T. 2011, \mnras, 413, 1121
+
 \bibitem[{{Smedley} {et~al.}(2014){Smedley}, {Tout}, {Ferrario}, \&
@@
 {Toonen}, S., {Nelemans}, G., \& {Portegies Zwart}, S. 2012, \aap, 546, A70
+
+\bibitem[{{Tremblay} {et~al.}(2013){Tremblay}, {Ludwig}, {Steffen}, \&
+  {Freytag}}]{tremblay13}
+{Tremblay}, P.-E., {Ludwig}, H.-G., {Steffen}, M., \& {Freytag}, B. 2013, \aap,
+  559, A104
 

### 2014-11-14 documents/letter/ms.tex
Newer version

@@
 We construct a statistical model to constrain a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{We represent vectors or sets of parameters or quantities by bold symbols.} For each system, we assume we have $K$, $T$, and $M_1$, and therefore know the value of $\mf$ (\eqn~\ref{eq:massfunc}).
-{\bf Our model is based on a Bayesian approach, but this problem could also be viewed from a maximum-likelihood perspective.} We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed $\mf$, $\bs{m_f}$, by deconvolving the distribution of $\mf$ from the unobserved $i$.
+Our model is based on a Bayesian approach, but this problem could also be viewed from a maximum-likelihood perspective.
+We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed $\mf$, $\bs{m_f}$, by deconvolving the distribution of $\mf$ from the unobserved $i$.
 Using Bayes' rule,

### 2014-11-15 documents/letter/ms.tex
Updated .tex

@@
 Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.74~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.24~\Msun$.
-Our model constrains the fraction of NS companions,  $f_{\rm NS}$, to be less than 0.16 at 68\% confidence.
+Our model constrains the NS companion fraction, $f_{\rm NS}$, $<16$\% at 68\% confidence.
 We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered LMWDs.
@@
 
-Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single-star evolution.
+Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs through single-star evolution.
 Instead, they form through interactions with another star and are expected to be in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
 %In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations. T
-Indeed, observationally, LMWDs have companions \citep{marsh95,maxted00,nelemans05,rebassa11}.
+Follow-up observations consistently find companions around LMWDs with few exceptions \citep{marsh95,maxted00,nelemans05,rebassa11}.
 Recently, the ELM WD Survey has searched for extremely LMWDs ($M\lesssim0.3~ \Msun$) in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere \citep{ELMI,ELMII, ELMIII, ELMIV, ELMV}.
@@
 RV and $\period$ measurements indicate that the LMWDs companions are most likely WDs.
-However, since inclination angle $i$ is unknown, LMWDs could have NS companions \citep{vLeeuwen07}.
+However, since the inclination angle ($i$) is unknown, LMWDs could have NS companions \citep{vLeeuwen07}.
 Indeed, LMWDs are observed as companions to millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
@@
 
-For each LMWD in the ELM sample, spectroscopy provides $\period$, the primary WD mass ($M_1$), and the projected orbital velocity ($K=v \sin i$). From Kepler's third law, we can write:
+For each LMWD in the ELM sample, spectroscopy provides $\period$, the primary WD mass ($M_1$), and the projected orbital velocity ($K=v \sin i$).
+From Kepler's third law, we can write (assuming circular orbits):
 \begin{equation}
@@
 Figure~\ref{fig:Porb-M1} shows that the population of LMWDs with pulsar companions occupies the same region in $M_1 - \period$ space as those with WD companions.
-Therefore, barring rare circumstances (such as an edge-on, eclipsing system), individual LMWDs with NS companions cannot be identified from optical observations alone.
+Therefore, barring rare circumstances (such as eclipsing systems), individual LMWDs with NS companions cannot be identified from optical observations alone.
 
-Even if no NS companions to LMWDs are found, constraints on the WD companion mass distribution to LMWDs provide observations for population synthesis studies to match. 
-% TO ADD?: constraints on mass transfer physics?
+The ELM sample is now large enough that $f_{\rm NS}$ and the companion mass distribution can be statistically constrained. These constraints provide important tests for population synthesis models.
+%Observational constraints on $f_{\rm NS}$ and the WD companion mass distribution make LMWDs an important benchmark population for population synthesis models.
+The ELM sample is now large enough these parameters can be statistically constrained.
+%Even if no NS companions to LMWDs are found, constraints on the WD companion mass distribution to LMWDs provide observations for population synthesis studies to match.
 The ELM sample is now large enough that the NS fraction and WD companion mass distribution can be statistically constrained.
@@
 Our model is based on a Bayesian approach, but this problem could also be viewed from a maximum-likelihood perspective.
-We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed $\mf$, $\bs{m_f}$, by deconvolving the distribution of $\mf$ from the unobserved $i$.
+We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed mass functions, $\bs{m_f}$, by deconvolving the distribution of $\mf$'s from the unobserved $i$'s.
 Using Bayes' rule,
@@
 \end{align}
-where $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified.
+where $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$, variance $\sigma^2$, and $f_{\rm NS}$ is the NS fraction, and the distributions are limited to the ranges specified.
 To reduce the number of parameters in our model we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
@@
 For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; we use a logarithmic (scale-invariant) prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
-Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$.
+Finally, we use a uniform prior over the dimensionless $f_{\rm NS}$ from $0-1$.
 The model parameters are summarized in Table~\ref{tbl:parameters}.
@@
 Each of the 100 systems in our three mock data sets are generated by computing $\mf$'s from randomly drawn
-$M_1$'s (from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$), $M_2$'s (from the distributions described below), and $i$'s. 
+$M_1$'s (from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$), $M_2$'s (from the distributions described below), and isotropic $i$'s. 
 %the companion mass from the particular distributions described below, then using a randomly drawn $i$ and $M_1$ to compute $\mf$.
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{f2.pdf}
-\caption{Results from testing the three mock data sets described in Section~\ref{sec:tests}.
-The leftmost column shows histograms of $M_2$ drawn from each of our test distributions.
-Overplotted as solid lines are the MAP models.
-The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, and the third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$.
+\includegraphics[width=0.95\textwidth]{f2.pdf}
+\caption{Results from testing our first two mock data sets described in Section~\ref{sec:tests}.
+The leftmost panels show the $M_2$'s (gray histogram) randomly drawn from each of our test distributions and our MAP models (black line).
+Panels in the second and third columns show samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, and $f_{\rm NS}$.
 Contours designate the 68\% and 95\% confidence levels.
 Dashed lines in these panels show the true values from which the sample systems were drawn.
-Since the third model was drawn from a uniform distribution, there are no true $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ values.
-}
-\label{fig:tests}
+The fourth panel shows individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ distribution.
+Tick marks along the bottom show those systems that are true NSs.}
+\label{fig:tests_1_2}
 \end{center}
@@
 \subsection{Test 1: Single Gaussian (WD)} \label{sec:exp1}
-We first generate $M_2$ by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
+We first generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
 This mock sample contains no NSs.
-In the top row of Figure~\ref{fig:tests}, the leftmost panel shows that our model finds a maximum a posteriori (MAP) $M_2$ distribution (black line) that qualitatively matches the input distribution (grey histogram).
+In the top row of Figure~\ref{fig:tests_1_2}, the leftmost panel shows that our model finds a maximum a posteriori (MAP) $M_2$ distribution (black line) that qualitatively matches the input distribution (grey histogram).
 The second and third panels show samples from the posterior distributions and contours containing 68\% and 95\% of the samples for our three model parameters.
@@
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
-The leftmost panel in Figure~\ref{fig:P_NS} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+The rightmost panel in Figure~\ref{fig:tests_1_2} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
 For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
@@
 We use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$.
-The middle row of Figure~\ref{fig:tests} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The middle row of Figure~\ref{fig:tests_1_2} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 %As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution. 
 Importantly, the third panel shows that our model also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
-Tick marks in the middle panel of Figure~\ref{fig:P_NS} indicate ``true" NSs in our mock data.
+Tick marks in the rightmost panel of Figure~\ref{fig:tests_1_2} indicate ``true" NSs in our mock data.
 Our model correctly assigns high $P_{\rm NS}$ to roughly half of these.
@@
 We generate companion masses for the WDs by sampling from a uniform distribution over $[0.2,1.2]~\Msun$, again with $f_{\rm NS}=$10\%.
-The bottom row of Figure~\ref{fig:tests} shows the results.
+The bottom row of Figure~\ref{fig:tests_3_4} shows the results.
 The posterior distribution in the second panel indicates that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained.
@@
 Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, and a poorly constrained $\sigma_{\rm WD}$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
-Furthermore, the rightmost panel of Figure~\ref{fig:P_NS} demonstrates that our model is effectively identifying which LMWDs host NS companions.
+Furthermore, the fourth panel of Figure~\ref{fig:tests_3_4} demonstrates that our model effectively identifies which LMWDs host NS companions.
 
 \subsection{Test 4: Post-common envelope binaries} \label{sec:PCEB}
-Composed of WDs in close binaries with main-sequence stars, PCEBs are an ideal test sample for our model. 
-We use a sample of 54 SDSS PCEBs with spectroscopically derived $K$'s, $\period$'s, and main sequence masses from \citep{nebot11}.
-Our model uses the measurements of these three parameters to try and recover this sample's WD mass distribution, which we can then compare to the spectroscopically-determined WD masses.
+PCEBs are composed of WDs in close orbits with Main Sequence companions.
+The sample of 54 SDSS PCEBs from \citet{nebot11} with precisely determined $K$, $\period$, and Main Sequence masses are an ideal test sample for our model.
+Our model uses these parameters to try and recover this sample's WD mass distribution, which we can then compare to the spectroscopically-determined WD masses.
 %Our model is ignorant of the spectroscopically measured WD masses and attempts to fit the WD mass distribution based on the measured main sequence mass, $K$, and $\period$.
 We use a sample of 54 SDSS PCEBs with spectroscopically derived $K$, $\period$, and main sequence masses \citep{nebot11}.
-Our MAP distribution (black line) in the leftmost panel of Figure~\ref{fig:ELM_post} shows that our model qualitatively recovers the true $M_{\rm WD}$ distribution (gray histogram).
+Our MAP distribution (black line) in the leftmost panel of Figure~\ref{fig:tests_3_4} shows that our model qualitatively recovers the true $M_{\rm WD}$ distribution (gray histogram).
 The third panel shows that the posterior $f_{\rm NS}$ distribution is very low, as expected since there are no NS companions in the PCEB sample.
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{f3.pdf}
-\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks along the bottom show those systems that are true NSs.}
-\label{fig:P_NS}
+\includegraphics[width=0.95\textwidth]{f3.pdf}
+\caption{ The results of our model when applied to Test 3 and 4 in Section~\ref{sec:tests}. The panels are in the same format as those in Figure~\ref{fig:tests_1_2}.}
+\label{fig:tests_3_4}
 \end{center}
@@
 \includegraphics[width=0.95\textwidth]{f4.pdf}
-\caption{Results from applying our model to the PCEBs (top row) and ELM WDs (bottom row). 
-The panels are the same as in Figure~\ref{fig:tests} and Figure~\ref{fig:P_NS}. 
+\caption{Results from applying our model to the ELM WDs. 
+The panels are in the same form as in Figure~\ref{fig:tests_1_2} and Figure~\ref{fig:tests_3_4}. 
 %The leftmost panel of the top row shows that the MAP model $M_{\rm WD}$ distribution matches the histogram of true masses in the PCEB sample. 
 %The second and third panels show the posterior distributions for our model parameters, while the fourth panel shows the $P_{\rm NS}$ values for each of the PCEBs (ordered by increasing $\mf$). 
-Here, however, the leftmost panel of the ELM sample shows both the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). 
+Here, the leftmost panel shows both the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). 
 %The second panel shows that the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
@@
 Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are on-going.
-We note that Figure~\ref{fig:ELM_post} shows a general trend that systems with higher $\mf$ have higher $P_{\rm NS}$ values and are therefore ideal targets to search for NS companions to LMWDs.
+We note that the $P_{\rm NS}$ distributions in each of our samples show a general trend that systems with higher $\mf$ have higher $P_{\rm NS}$ values and are therefore ideal targets to search for NS companions to LMWDs.
 
@@
 Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction to within a few percent.
-We further apply our model to the sample of PCEB's from \citet{nebot11}; our model qualitatively recovers the independent, spectroscopically measured $M_{\rm WD}$ distribution.
+We further apply our model to the sample of PCEB's from \citet{nebot11}, and our model qualitatively recovers the independent, spectroscopically measured $M_{\rm WD}$ distribution.
 

### 2014-11-15 documents/letter/ms.tex
Updated .tex

@@
 Our distribution is significantly wider ($\sigma \approx 0.26~\Msun$, compared with $\sigma \approx 0.1~\Msun$), possibly due to past mass transfer phases increasing the masses of the unseen primary WDs.
-The low combined mass in these systems indicates that, although several of them will merge within a Hubble time \citep{ELMV}, the majority of ELM WDs are unlikely to be type Ia supernova progenitors.
+The low combined mass in these systems indicates that, although several of them will merge within a Hubble time \citep{ELMV}, the majority of ELM WDs are unlikely to be type Ia SN progenitors.
+We cannot limit the possibility that some individual LMWD binaries may be massive enough to produce type Ia SNe \citep{justham09}.
 %Several of these systems will merge within a Hubble time \citep{ELMV}, but their sub-Chandrasekhar combined mass would suggest that they are more likely to be underluminous type .Ia, rather than Ia, supernova progenitors.
@@
 
-%Recently, \citet{hermes14} made high-speed photometric observations of 20 LMWDs in the ELM sample.
-Based on non-detection of eclipses and modeling of photometric variability, these authors set limits on the inclination angles of these systems, which could be included in our model.
-
 There are several ways in which our model can be expanded.
-Based on modeling the photometric variability in these systems, \citet{hermes14} recently placed constraints on the inclination of 20 LMWDs in the ELM sample which could be included in our model.
-Furthermore, tighter constraints can be placed on $f_{\rm NS}$ by including radio and X-ray non-detection results.
+By modeling photometric variability, \citet{hermes14} recently constrained the inclination of 20 LMWDs in the ELM sample which could be included in our model.
+Furthermore, our model can place tighter constraints on $f_{\rm NS}$ by including radio and X-ray non-detection results.
 Finally, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
@@
 
-\begin{thebibliography}{41}
+\begin{thebibliography}{43}
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 \bibitem[Goodman~\&\ Weare(2010)]{goodman10}
-Goodman,~J. \& Weare,\ J.,
+Goodman,~J. \& Weare,\ J.
 2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65
@@
 {Hermes}, J.~J. {et~al.} 2014, \apj, 792, 39
+
+\bibitem[{{Justham} {et~al.}(2009){Justham}, {Wolf}, {Podsiadlowski}, \&
+  {Han}}]{justham09}
+{Justham}, S., {Wolf}, C., {Podsiadlowski}, P., \& {Han}, Z. 2009, \aap, 493,
+  1081
 
@@
 %\bibitem[Goodman~\&\ Weare(2010)]{goodman10}
-%Goodman,~J. \& Weare,\ J.,
+%Goodman,~J. \& Weare,\ J.
 %2010, Comm.\ App.\ Math.\ Comp.\ Sci., 5, 65

### 2014-11-21 documents/letter/response.txt
Updated .tex and response

@@
-Dear Dr. de Grijs
+Dear Dr. de Grijs,
 
-We thank the two referees for their detailed comments. We have improved the paper, and included all the suggestions in the revised manuscript. Our response to the referees’ suggestions are below.
+We thank the two referees for their detailed comments.
 
-Please let me know if further improvements are required.
+We have updated the manuscript based on their suggestions. Below we detail how we addressed the referees' comments.
+
+Please let us know if further improvements are required.
 
@@
 
->
 >========================================================
 >Report from Referee 1:
->
->The authors investigate the mass distribution of companions to
->low-mass white dwarfs. For this purpose they have developed a
->thorough statistical model, which has been applied to three mock data
->sets as well as to the real ELM white dwarf sample. They find that the
->companion mass distribution of the EML sample peaks at 0.71Msun (std
->of 0.26Msun), and that the NS fraction seems to be very low.
->
->The paper is well-written, goes to the point, and is well
->understood. Thus I highly recommend its publication in ApJ
->letters. However, before this I consider there are some points the
->authors should discuss/investigate further. 
 >
@@
 >companions to extremely low-mass white dwarfs".
->
+
+Although the ELM survey is a search for WDs with masses <~0.3 Msun, a significant fraction (~20%) of the sample is composed of WDs with masses from 0.3-0.45 Msun.
+As a result we think it is more appropriate to keep "low-mass white dwarfs" in the title, particularly since for our purposes this distinction between low-mass and extremely low-mass is not critical.
+
 >- Abstract. "We then apply this model to a sample of low mass white
@@
 >from mock data.
->
 
-We have fixed this in the abstract.
+The abstract now reads "We apply this model to three mock samples of low-mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a sample of post-common-envelope binaries." The test using post-common-envelope binaries (PCEBs) was added in response to a later request from the referee.
 
->
 >- Introduction. The authors cite the seminal paper by Marsh et
@@
 >et al. 2011MNRAS,413,1121R.
->
 
-These citations have been added to the introduction, along with a result from the SPY survey, searching for SN Ia progenitors, which identified two additional LMWDs in close binaries with unknown companions.
+Because of space restrictions, we had to restructure the text somewhat to include the test with the PCEBs.
+So the introduction reads slightly differently; the relevant text is now "Indeed, with few exceptions, follow-up observations consistently find companions to LMWDs \citep{marsh95,maxted00,nelemans05,rebassa11}." In addition to the citations mentioned by the referee, we include a reference to the SPY survey, which identified two LMWDs in close binaries with unknown companions.
 
->
 >- Introduction. The authors should state more clearly why identifying
@@
 >are not likely to be the companions of ELM white dwarfs?
->
 
-We have added a sentence explaining the importance of finding individual NS-LMWD systems in paragraph 2 in the introduction and a sentence explaining the importance of understanding the companion mass distribution to LMWDs in paragraph 4.
+In the second paragraph of the introduction, we have added a sentence explaining the importance of finding even one NS companion to a spectroscopically characterized LMWD: "Finding even one NS companion to a spectroscopically characterized LMWD would be very valuable, since this system could constrain the NS mass."
 
->
 >- Section 2. Why using a logarithmic prior for sigma(WD)?
 
-We choose a logarithmic prior for sigma(WD) since it is scale invariant. We have added this to the text.
+We choose a logarithmic prior for sigma(WD) since it is scale-invariant. We have added this to the text, in the second paragraph of Section 2.1.
 
@@
 
-We wanted to build a simplistic model, with few parameters, therefore we set the NS distribution without allowing it to vary.
+We wanted to build a simplistic model, with few parameters, and therefore set the NS distribution without allowing it to vary.
 From Kiziltan et al.
 (2013) and Smedley et al.
-(2014) it appears that NSs with WD companions may have a slightly higher mass tail, therefore we set the NS mass distribution higher than the canonical value of 1.35 Msun.
+(2014) it appears that the mass distribution of NSs with WD companions may have a slightly higher-mass tail.
+We therefore set the NS mass distribution slightly higher than the canonical value of 1.35 Msun.
+It is not observed to vary much from this, so we made the distribution narrow by setting sigma(NS) to 0.05 Msun.
 
@@
 For the flexibility of our model, we allow sigma(WD) to vary greatly.
-We still truncate the mass distribution at [0.2,1.44], but we do not allow the center of the Gaussian to go above 1.0 Msun.
+We still truncate the mass distribution at [0.2,1.44], but we do not allow the center of the Gaussian, mu(WD), to go above 1.0 Msun.
 
->
 >- Figure 1. Why not adding the number and label in the y axis? Top
@@
 >distribution?
->
 
-The distribution in Figure 1 was drawn from a Gaussian with mu(WD)=0.7 Msun and sigma(WD) = 0.2.
+We have added labels and numbers to the y axes of our M_2 distributions.
+The distribution in Figure 1 was drawn from a Gaussian with mu(WD)=0.7 Msun and sigma(WD)=0.2.
 We tested this by drawing other random samples; the bimodal distribution is due to the randomness of drawing 100 WD samples.
 In other randomly drawn samples, this distribution appears as a single Gaussian.
+It may not be realistic to have so many WDs with masses above 1 Msun, but it is encouraging that our model can still fairly accurately determine that these systems don’t have NS companions.
 
->
 >- I consider testing the statistical model using three samples of mock
@@
 >1996ApJ,461L,51B).
->
 
-Based on your suggestion, we have added a fourth test where we derive the resulting WD mass distribution of companions to the post-common envelope binary sample from SDSS.
-The description of this test is included in Section 3.4, and the results are included in Figure 4.
+Based on this suggestion, we have added a fourth test where we derive the resulting WD mass distribution of companions to the SDSS PCEBs of Nebot Gomez-Moran et al.
+(2011).
+Instead of converting the provided spectral types into masses, we include the companion masses provided in this work.
+Parsons et al.
+(2012) list two of the systems in this PCEB sample as eclipsing.
+For one of them, J1348+1834, the value listed differs from the WD mass given by Drake et al.
+(2010).
+Because we cannot determine which is the correct mass, we do not include constraints in our analysis based on the fact that these two systems are eclipsing.
+Since there are only two systems and they do not have extreme masses, we expect that this will not affect the resulting posterior distributions.
+The description of this test is included in Section 3.4.
+The histogram of the WD masses in these systems is shown in the bottom left panel of Figure 3.
+The MAP value shows that our model does a good job of determining the mass distribution of these systems.
 
->
 >- Section 4.1. "Fitting the WDs' spectra to templates provides
@@
 >those provided from the spectral fitting, if available.
->
 
-There is a distinct possibility that the companion WDs could contribute to the luminosity of the LMWD primaries in these systems.
+It is possible that companion WDs could contribute to the luminosity of the LMWD primaries.
 However, Gianninas et al.
-(2014) point out that because the systems are all single-lined spectra, they expect the companion’s “contribution to the observed spectra to be on the order of a few percent at most.” In investigating this possibility though, we found a bigger issue: For two of the three eclipsing systems, the spectroscopic mass measurements are in agreement with the expectation from the eclipse measurement.
-For the third system, NLTT 11748, there is a significant discrepancy.
+(2014) point out that because these are all single-lined spectroscopic binaries, they expect the companions' “contribution to the observed spectra to be on the order of a few percent at most.” These authors' extremely high S/N coadded spectra would probably detect spectral lines from any luminous companion.
+In investigating this possibility, we did find a potentially larger source of uncertainty: for two of the three eclipsing systems, the spectroscopic mass measurements are in agreement with the expectation from the eclipse measurement.
+However, for the third system, NLTT 11748, there is a significant discrepancy.
 Gianninas et al.
-(2014) contribute this difference to the “high log g problem”, a manifestation of the problems with using 1-D WD atmospheric models.
-They suggest that only the spectroscopic masses of the seven WDs with temperatures below roughly 9500 K will be affected.
-We add a note of caution in the text to indicate there may be some unknown uncertainties in these mass measurements.
+(2014) attribute this difference to the “high log g problem,” one of the possible issues with using 1-D WD atmospheric models.
+They suggest that only the spectroscopic masses of the seven WDs with temperatures below ~9500 K will be (somewhat) affected.
+We add a note of caution in the text, in paragraph 2 of Section 3.4, to indicate this effect may lead to some uncertainties in these mass measurements.
 
->
 >- Section 4.2. "Our distribution is significantly wider (sigma ~ 0.26
@@
 >specifically?
->
 
-We expect that all these systems are detached due to the lack of emission lines in the spectra as would be expected from an accretion disk.
-The text has been updated to specify that the companion masses may be more massive due to previous mass transfer phases.
+We expect that all these systems are detached due to the lack of emission lines in the spectra, as would be expected from an accretion disk.
+Paragraph 2 of Section 4.2 has been updated to specify that the companion masses may be more massive due to previous mass-transfer phases.
 
->
 >- Section 4.2. Since the ELM sample contains primaries of M<~0.3Msun
@@
 >couple of sentences discussing this.
->
 
@@
 They may therefore evolve into underluminous supernova.
-We have included some discussion of this in Section 4.2.
+We can only constrain the population; a small subset of LMWDs may have high enough masses to be SNe Ia progenitors.
+We have included some discussion of this in the third paragraph of Section 4.2.
 
->
 >- Inspection of figure 3 and the right panel of figure 4 reveals that
@@
 >If so, add a sentence stating this in the text.
->
 
-Systems with higher mf values are more likely to have NS companions through Equation 1. We added a note about this in the text.
+Systems with higher mf values are more likely to have NS companions through Equation 1. We added a note about this in the last paragraph of Section 4.2.
 
@@
 >Report from Referee 2:
->
->I provide here comments only on the statistical methodology of this manuscript, not on any scientific aspects. I have not checked the equations (8)-(15) in detail. 
->
->The procedure in section 2 focuses on the question raised in the Introduction: "1.
-Can the population as a whole be modeled using a simple description of the companion masses?" The setup of the likelihood seems reasonable.
-The normal mixture model for white dwarf and neutron star secondaries is also reasonable.
-The inference that the secondary WDs have similar mass distributions as primary WDs is unsurprising and adds confidence that the calculation is reasonable.
-I have two comments:
->
+
 >A.
@@
 Fortunately the authors do not emphasize `Bayesian' in the title, abstract or conclusions.
->
 
@@
 
-We agree that there is no difference between our method and a maximum likelihood calculation. We have added a sentence clarifying this in the first paragraph of Section 2.
+While we could have approached this problem using a maximum likelihood technique, we would have had to use a regularization scheme to account for the prior on /sigma.
+Furthermore, we chose a Bayesian approach so that we can make our posterior distributions publicly available.
+Using these, the NS probabilities can be calculated for newly discovered LMWDs.
 
->
 >B.
@@
 This can be checked with simulations of different sample sizes.
->
->
+
+In Section 4.2, the statement about our distribution is referring to the companion distribution, not the posterior distribution.
+Our statistical model should provide an unbiased estimate of \sigma, since it is a model parameter.
+Therefore, it should not be affected by the sample size.

### 2014-11-21 documents/letter/ms.tex
Updated .tex and response

@@
 \title{The mass distribution of companions to low-mass white dwarfs}
-\author{Jeff J. Andrews\altaffilmark{\colum}, Adrian M. Price-Whelan\altaffilmark{\colum}, Marcel A. Ag\"ueros\altaffilmark{\colum}}
+\author{Jeff J.~Andrews\altaffilmark{\colum}, Adrian M.~Price-Whelan\altaffilmark{\colum}, Marcel A.~Ag\"ueros\altaffilmark{\colum}}
 
@@
 In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star.
-We then apply this model to three mock samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a sample of post-common envelope binaries (PCEB).
+We apply this model to three mock samples of low-mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a sample of post-common-envelope binaries.
 We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions.
 Our model successfully recovers the initial parameters of these test data sets.
-%We focus on low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$), modeling the companion mass distribution with a mixture of two Gaussians to represent a WD and neutron star (NS) companion population.
-Our model successfully recovers the initial parameters of three mock samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$) and a test sample of post-common envelope binaries (PCEB).
-We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey.
-Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.74~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.24~\Msun$.
-Our model constrains the NS companion fraction, $f_{\rm NS}$, $<16$\% at 68\% confidence.
+We then apply our model to 55 WDs in the extremely low-mass (ELM) WD Survey.
+Our maximum a posteriori model for the WD companion population has a mean mass $\mu_{\rm WD} = 0.74~\Msun$, with a standard deviation $\sigma_{\rm WD} = 0.24~\Msun$.
+Our model constrains the NS companion fraction $f_{\rm NS}$ to be $<$16\% at 68\% confidence.
 We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered LMWDs.
@@
 \section{Introduction}
+Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce low-mass white dwarfs (LMWDs) through single-star evolution.
+Instead, LMWDs are expected to form through interactions with another star \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
+Indeed, with few exceptions, follow-up observations consistently find companions to LMWDs \citep{marsh95,maxted00,nelemans05,rebassa11}.
+Recently, the ELM WD Survey has identified 61 extremely LMWDs ($M\lesssim0.3~ \Msun$) in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere \citep{ELMI,ELMII, ELMIII, ELMIV, ELMV}.
+We refer to the 55 WDs found by these authors that have a measured radial velocity (RV) and orbital period ($\period$) as the ELM sample.
 
-Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs through single-star evolution.
-Instead, they form through interactions with another star and are expected to be in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}.
-%In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations. T
-Follow-up observations consistently find companions around LMWDs with few exceptions \citep{marsh95,maxted00,nelemans05,rebassa11}.
-Recently, the ELM WD Survey has searched for extremely LMWDs ($M\lesssim0.3~ \Msun$) in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere \citep{ELMI,ELMII, ELMIII, ELMIV, ELMV}.
-Fifty-five of their 61 identified LMWDs have a measured radial velocity (RV) and orbital period ($\period$); we refer to these 55 systems as the ELM sample.
-% \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$).
-After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}.
-We refer to these 55 systems as the ELM sample.
+These RV and $\period$ measurements indicate that the LMWDs companions are most likely WDs.
+However, since the inclination angle $i$ is unknown, LMWDs could have neutron star (NS) companions.
+Indeed, LMWDs are known companions to millisecond pulsars, although these WDs are generally too faint for spectroscopy \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
+Finding even one NS companion to a spectroscopically characterized LMWD would be very valuable, since this system could constrain the NS mass.
+To date, unfortunately, radio and X-ray searches for NS companions to LMWDs have been unsuccessful \citep{vLeeuwen07,agueros09b,agueros09a,kilic13}.
 
-RV and $\period$ measurements indicate that the LMWDs companions are most likely WDs.
-However, since the inclination angle ($i$) is unknown, LMWDs could have NS companions \citep{vLeeuwen07}.
-Indeed, LMWDs are observed as companions to millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}.
-Finding even one NS companion to a spectroscopically characterized LMWD would be very valuable, since this system would constrain the NS mass.
-% TO ADD?: Also allows constraints on MSP age, braking index
-However, radio and X-ray searches for NS companions to LMWDs have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.
-
-For each LMWD in the ELM sample, spectroscopy provides $\period$, the primary WD mass ($M_1$), and the projected orbital velocity ($K=v \sin i$).
-From Kepler's third law, we can write (assuming circular orbits):
+For each LMWD in the ELM sample, spectroscopy provides $\period$, the primary WD mass $M_1$, and the projected orbital velocity $K=v \sin i$. Assuming circular orbits, we can write:
 \begin{equation}
-	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3. \label{eq:massfunc}
+	\frac{(M_2 \sin i)^3}{\left(M_1+M_2\right)^2} = \frac{\period}{2\pi G} K^3, \label{eq:massfunc}
 \end{equation}
-The righthand side is the mass function $\mf$.
+where the right side is the mass function $\mf$.
 The companion mass, $M_2$, is minimized for an edge-on orbit ($i = 90\degree$).
@@
 Figure~\ref{fig:Porb-M1} shows that the population of LMWDs with pulsar companions occupies the same region in $M_1 - \period$ space as those with WD companions.
-Therefore, barring rare circumstances (such as eclipsing systems), individual LMWDs with NS companions cannot be identified from optical observations alone.
+Therefore, barring rare circumstances such as eclipsing systems, individual LMWDs with NS companions cannot be identified from optical observations alone.
 
-The ELM sample is now large enough that $f_{\rm NS}$ and the companion mass distribution can be statistically constrained. These constraints provide important tests for population synthesis models.
-%Observational constraints on $f_{\rm NS}$ and the WD companion mass distribution make LMWDs an important benchmark population for population synthesis models.
-The ELM sample is now large enough these parameters can be statistically constrained.
-%Even if no NS companions to LMWDs are found, constraints on the WD companion mass distribution to LMWDs provide observations for population synthesis studies to match.
-The ELM sample is now large enough that the NS fraction and WD companion mass distribution can be statistically constrained.
-In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs.
+The ELM sample is now large enough that the $M_2$ distribution and NS companion fraction can be constrained statistically. %These constraints provide important tests for population synthesis models. 
+We have developed a probabilistic model to infer parameters of an assumed form for the $M_2$ distribution.
 Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters.
-We focus on several specific questions: Can the population as a whole be modeled using a simple description of the companion masses?
-How does the companion mass distribution compare to predictions from population synthesis simulations?
-What is the rate of NS-LMWD binaries implied by our model?
+We focus on the following questions: Can the companion population be modeled using a simple description of $M_2$?
+How does the $M_2$ distribution compare to predictions from population synthesis simulations?
+What is the rate of LMWD-NS binaries implied by our model?
 What are the resulting distributions of NS probabilities for individual systems in the ELM sample?
 
-To answer these questions, we build the mathematical framework (Section 2), then test our resulting model (Section 3).
-We apply our model to the ELM WD sample (Section 4) before concluding (Section 5).
+To answer these questions, we build the mathematical framework (Section 2), then test our resulting model (Section 3). We apply our model to the ELM sample (Section 4) before concluding (Section 5).
 
@@
 \includegraphics[angle=90,width=0.95\columnwidth]{f1.eps}
-\caption{The $M_1$ - $\period$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles).
-The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected radial velocity variations are shown by the arrows.
+\caption{The $M_1$ - $\period$ distribution of the ELM sample (circles) and the known WD-NS binaries (triangles).
+The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected RV variations are shown by the arrows.
 From $M_1$ and $\period$ alone, the two populations are indistinguishable.}
@@
 \section{Building our model}
-
-We construct a statistical model to constrain a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{We represent vectors or sets of parameters or quantities by bold symbols.} For each system, we assume we have $K$, $T$, and $M_1$, and therefore know the value of $\mf$ (\eqn~\ref{eq:massfunc}).
-Our model is based on a Bayesian approach, but this problem could also be viewed from a maximum-likelihood perspective.
-We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed mass functions, $\bs{m_f}$, by deconvolving the distribution of $\mf$'s from the unobserved $i$'s.
+We construct a statistical model to constrain a parametric model for the distribution of LMWD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{We represent vectors or sets of parameters or quantities by bold symbols.} For each system, we assume we have $K$, $T$, and $M_1$, and therefore know $\mf$.
+We wish to derive posterior constraints on the model parameters, $\bs{\theta}$, which describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given the set of observed mass functions, $\bs{m_f}$, by deconvolving the $\mf$ distribution from the unobserved inclinations.
 Using Bayes' rule,
 \begin{equation}
-    p(\bs{\theta} \given \bs{\mf}) = \frac{1}{\mathcal{Z}}~p(\bs{\mf} \given \bs{\theta})~p(\bs{\theta}).
+    p(\bs{\theta} \given \bs{\mf}) = \frac{1}{\mathcal{Z}}~p(\bs{\mf} \given \bs{\theta})~p(\bs{\theta}),
 \end{equation}
@@
 The likelihood, $p(\bs{\mf} \given \bs{\theta})$, can be split into a product over the likelihoods of individual systems:
-
 \begin{equation}
-p(\bs{\mf} \given \bs{\theta}) = \prod_j p(\mf \given \bs{\theta})
+p(\bs{\mf} \given \bs{\theta}) = \prod_j p(\mf \given \bs{\theta}),
 \end{equation}
@@
 \begin{equation}
-	p(\mf \given M_1, M_2, i) = \delta \left[\mf - f(M_1, M_2, i) \right]
+	p(\mf \given M_1, M_2, i) = \delta \left[\mf - f(M_1, M_2, i) \right],
 \end{equation}
@@
     p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2 ~p(M_2 \given \bs{\theta})  \nonumber \\
-    & \qquad {} \times \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
+    & \qquad {} \times \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta},
 \end{align}
@@
 \begin{equation}
-    \int dx~F(x)~\delta \left[ G(x) \right] = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
+    \int dx~F(x)~\delta \left[ G(x) \right] = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|},
 \end{equation}
@@
 \begin{align}
-	\sin i^* &= \frac{ \left[\mf(M_1+M_2)^2 \right]^{1/3}}{M_2}\\
-	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \sin^2 i^* \sqrt{1 - \sin^2 i^*}
+	\sin i^* &= \frac{ \left[\mf(M_1+M_2)^2 \right]^{1/3}}{M_2}, \\
+	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \sin^2 i^* \sqrt{1 - \sin^2 i^*}.
 \end{align}
@@
 	p(\mf \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\sin i^* \left(\frac{\partial g}{\partial i}\bigg\rvert_{i^*}\right)^{-1}\\
-	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, \mf, M_1) \label{eq:fullm2}
+	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~h(M_2, \mf, M_1). \label{eq:fullm2}
 \end{align}
-where the bottom bound in the integral in \eqn\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$ (determined by setting $i=90\degree$ in \eqn\ref{eq:massfunc} and solving for $M_2$), and
+The bottom bound in the integral in \eqn\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$, determined by setting $i=90\degree$ in \eqn\ref{eq:massfunc} and solving for $M_2$, and
 
 \begin{equation}
-h(M_2, \mf, M_1) = \frac{(M_1+M_2)^{4/3}}{3\ \mf^{1/3}M_2\sqrt{M_2^2 - \left[ \mf(M_1+M_2)^2 \right]^{2/3}}}
+h(M_2, \mf, M_1) = \frac{(M_1+M_2)^{4/3}}{3\ \mf^{1/3}M_2\sqrt{M_2^2 - \left[ \mf(M_1+M_2)^2 \right]^{2/3}}}.
 \end{equation}
@@
 \subsection{Our Model} \label{sec:experiments}
-
-We must now choose a functional form for the companion mass distribution, $p(M_2\given \bs{\theta})$, and 
-use a two-component Gaussian mixture model.
-We truncate the distributions using physically motivated bounds so that the WD component is restricted to $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$.
+We must now choose a functional form for the companion mass distribution, $p(M_2\given \bs{\theta})$.
+We use a two-component Gaussian mixture model.
+We truncate the distributions using physically motivated bounds: the WD component is restricted to $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$.
 We then have:
 \begin{align}
-	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] 
+	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right], 
 \end{align}
-where 
+where $f_{\rm NS}$ is the NS fraction and
 \begin{align}
 	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper, \\
-	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2,
+	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2.
 \end{align}
-where $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$, variance $\sigma^2$, and $f_{\rm NS}$ is the NS fraction, and the distributions are limited to the ranges specified.
-To reduce the number of parameters in our model we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
+$\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$, variance $\sigma^2$; the distributions are limited to the ranges specified.
+To reduce the number of parameters in our model we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$
+%$\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun$, 
+to:
 \begin{align}
-	\mu_{\rm NS} &= 1.4~\Msun\\
-	\sigma_{\rm NS} &= 0.05~\Msun
+	\mu_{\rm NS} &= 1.4~\Msun, \\
+	\sigma_{\rm NS} &= 0.05~\Msun,
 \end{align}
-based on indications that NSs in certain binaries may have be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}.
-The probability of any particular system having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the companion mass distribution:
+as some NSs in binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~\citep{kiziltan13,smedley14}.
+
+The probability of any particular WD having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the $M_2$ distribution:
 \begin{equation}
-P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{p(\mf \given \bs{\theta})}\label{eq:P_NS}
+P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{p(\mf \given \bs{\theta})}. \label{eq:P_NS}
 \end{equation}
@@
 Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.
-For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; we use a logarithmic (scale-invariant) prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$.
+For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; for $\sigma_{\rm WD}$, we use a logarithmic (scale-invariant) prior over the range $0.02-2.0~\Msun$.
 Finally, we use a uniform prior over the dimensionless $f_{\rm NS}$ from $0-1$.
@@
 
-	\tablecomments{Parameter information for the form of the companion mass distribution used in the tests of Section~\ref{sec:tests}. $\mathcal{U}$ is the uniform distribution. 
-%There are three free parameters. 
+	\tablecomments{Parameter information for the form of the $M_2$ distribution used in the tests described in Section~\ref{sec:tests}.
+$\mathcal{U}$ is the uniform distribution.
 We additionally fix the NS mass distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\
@@
 
-We use a Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}} The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
+We use a Markov Chain Monte Carlo algorithm \citep{goodman10} to draw samples from the posterior distribution, $p(\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS} \given \bs{m}_f, \bs{M}_1)$.\footnote{Our model uses {\tt emcee}, implemented in \texttt{Python} \citep{foremanmackey13}.} The algorithm uses an ensemble of individual ``walkers'' to naturally adapt to the geometry of the parameter-space being explored.
 We run the walkers for a burn-in period of 500 steps starting from randomly drawn initial conditions (sampled from the priors in Table~\ref{tbl:parameters}).
 We then re-initialize the walkers from their positions at the end of this run and run again for 1000 steps.
-We remove the burn-in samples to eliminate any effects from our choice of initial conditions.
+We remove the burn-in samples to eliminate any effects due to our choice of initial conditions.
 
 \section{Testing Our Model} \label{sec:tests}
-We test the performance of this Gaussian mixture model on four separate data sets: three mock data sets and the sample of SDSS PCEBs from \citet{nebot11}. 
-Each of the 100 systems in our three mock data sets are generated by computing $\mf$'s from randomly drawn
-$M_1$'s (from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$), $M_2$'s (from the distributions described below), and isotropic $i$'s. 
+We test the performance of this Gaussian mixture model on four separate data sets: three mock data sets and a sample of SDSS post-common-envelope binaries \citep[PCEBs;][]{nebot11}. 
+Each of the 100 systems in our three mock data sets is generated by computing a $\mf$ from a random $M_1$ (drawn from a uniform distribution, $\mathcal{U}(0.2,0.4)~\Msun$), $M_2$ (from the distributions described below), and $i$ (from an isotropic distribution).
 %the companion mass from the particular distributions described below, then using a randomly drawn $i$ and $M_1$ to compute $\mf$.
@@
 \includegraphics[width=0.95\textwidth]{f2.pdf}
-\caption{Results from testing our first two mock data sets described in Section~\ref{sec:tests}.
-The leftmost panels show the $M_2$'s (gray histogram) randomly drawn from each of our test distributions and our MAP models (black line).
-Panels in the second and third columns show samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$, and $f_{\rm NS}$.
+\caption{Results from testing the first two mock data sets described in Section~\ref{sec:tests}.
+The left-most panels show the companion masses (gray histogram) randomly drawn from each of our test distributions and our MAP models (black line).
+Panels in the second and third columns show samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ and $f_{\rm NS}$.
 Contours designate the 68\% and 95\% confidence levels.
 Dashed lines in these panels show the true values from which the sample systems were drawn.
-The fourth panel shows individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ distribution.
-Tick marks along the bottom show those systems that are true NSs.}
+The fourth panel shows individual mock LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ distribution.
+Tick marks along the bottom indicate inputed LMWD-NS systems.}
 \label{fig:tests_1_2}
@@
 \subsection{Test 1: Single Gaussian (WD)} \label{sec:exp1}
-We first generate $M_2$'s by drawing from a single, truncated Gaussian with parameters given in Table~\ref{tbl:parameters}.
+We first generate companion masses by drawing from a single, truncated Gaussian with the parameters given in Table~\ref{tbl:parameters}.
 This mock sample contains no NSs.
-In the top row of Figure~\ref{fig:tests_1_2}, the leftmost panel shows that our model finds a maximum a posteriori (MAP) $M_2$ distribution (black line) that qualitatively matches the input distribution (grey histogram).
+In the top row of Figure~\ref{fig:tests_1_2}, the left-most panel shows that our model finds a maximum a posteriori (MAP) $M_2$ distribution (black line) that qualitatively matches the input distribution (gray histogram).
 The second and third panels show samples from the posterior distributions and contours containing 68\% and 95\% of the samples for our three model parameters.
-The input values (dashed lines) lie cleanly within the inner contour in both panels, however $f_{\rm NS}$ has a tail up to $\approx$10\%.
+The input values (dashed lines) lie cleanly within the inner contour in both panels, although $f_{\rm NS}$ has a tail up to $\approx$10\%.
 
@@
 Using posterior samples, we can determine the distribution of $P_{\rm NS}$ for each system.
-The rightmost panel in Figure~\ref{fig:tests_1_2} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
+The right-most panel in Figure~\ref{fig:tests_1_2} includes all the individual systems, ordered by $\mf$, and shows the distributions of $P_{\rm NS}$ for each.
 For most systems, there is negligible probability above $P_{\rm NS}\sim 5\%$.
@@
 We use the same Gaussian distribution to generate companion masses for the WDs but add a NS component with $f_{\rm NS} = 10\%$.
-The middle row of Figure~\ref{fig:tests_1_2} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
+The bottom row of Figure~\ref{fig:tests_1_2} shows that our model again recovers the input values for $\mu_{\rm WD}$ and $\sigma_{\rm WD}$.
 %As in Test 1, the model preference for higher $\mu_{\rm WD}$ and lower $\sigma_{\rm WD}$ is due to our randomly generated mass distribution. 
 Importantly, the third panel shows that our model also recovers $f_{\rm NS}$, although the posterior shows a substantial tail toward higher $f_{\rm NS}$.
-Tick marks in the rightmost panel of Figure~\ref{fig:tests_1_2} indicate ``true" NSs in our mock data.
+Tick marks in the right-most panel of Figure~\ref{fig:tests_1_2} indicate ``true" NSs in our mock data.
 Our model correctly assigns high $P_{\rm NS}$ to roughly half of these.
-However, many systems with NS companions have $i$'s too low to be statistically differentiated from those with WD companions.
+However, many systems with NS companions have inclinations too low to be statistically differentiated from those with WD companions.
 
@@
 We generate companion masses for the WDs by sampling from a uniform distribution over $[0.2,1.2]~\Msun$, again with $f_{\rm NS}=$10\%.
-The bottom row of Figure~\ref{fig:tests_3_4} shows the results.
+The top row of Figure~\ref{fig:tests_3_4} shows the results.
 The posterior distribution in the second panel indicates that $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ are not well constrained.
-The preference for larger $\sigma_{\rm WD}$ is expected as the model flattens the Gaussian model distribution to match it with the input uniform distribution.
+The preference for larger $\sigma_{\rm WD}$ is expected, as the model flattens the Gaussian model distribution to match it with the input uniform distribution.
 Interestingly, the third panel shows that despite having a non-Gaussian input distribution for $M_2$, and a poorly constrained $\sigma_{\rm WD}$, our model still recovers $f_{\rm NS}$ approximately as accurately as in Test 2.
@@
 
-\subsection{Test 4: Post-common envelope binaries} \label{sec:PCEB}
-PCEBs are composed of WDs in close orbits with Main Sequence companions.
-The sample of 54 SDSS PCEBs from \citet{nebot11} with precisely determined $K$, $\period$, and Main Sequence masses are an ideal test sample for our model.
-Our model uses these parameters to try and recover this sample's WD mass distribution, which we can then compare to the spectroscopically-determined WD masses.
+\subsection{Test 4: PCEBs} \label{sec:PCEB}
+PCEBs are composed of WDs in close orbits with main-sequence companions.
+The \citet{nebot11} sample of 54 SDSS PCEBs, which have precisely determined $K$, $\period$, and masses for the main-sequence companions, are an ideal test sample for our model.
+Our model uses these parameters to try and recover the PCEBs WD mass distribution, which we can then compare to the spectroscopically determined WD masses.
 %Our model is ignorant of the spectroscopically measured WD masses and attempts to fit the WD mass distribution based on the measured main sequence mass, $K$, and $\period$.
 We use a sample of 54 SDSS PCEBs with spectroscopically derived $K$, $\period$, and main sequence masses \citep{nebot11}.
-Our MAP distribution (black line) in the leftmost panel of Figure~\ref{fig:tests_3_4} shows that our model qualitatively recovers the true $M_{\rm WD}$ distribution (gray histogram).
+Our MAP distribution (black line) is shown in the left-most panel in the bottom row of Figure~\ref{fig:tests_3_4}.
+Our model qualitatively recovers the true $M_{\rm WD}$ distribution (gray histogram).
 The third panel shows that the posterior $f_{\rm NS}$ distribution is very low, as expected since there are no NS companions in the PCEB sample.
-This is further seen in the rightmost panel, where every PCEB in the sample has low $P_{\rm NS}$ values.
+This is further illustrated in the right-most panel, where every PCEB in the sample has low $P_{\rm NS}$ values.
 
@@
 \includegraphics[width=0.95\textwidth]{f3.pdf}
-\caption{ The results of our model when applied to Test 3 and 4 in Section~\ref{sec:tests}. The panels are in the same format as those in Figure~\ref{fig:tests_1_2}.}
+\caption{ The results of our model when applied to our third mock data set and the SDSS PCEB sample. The panels are same as those in Figure~\ref{fig:tests_1_2}.}
 \label{fig:tests_3_4}
@@
 The ELM WD Survey is based on the Hypervelocity Star Survey \citep{brown06}, and includes previously identified SDSS LMWDs \citep{eisenstein06,liebert04}.
-Objects are chosen for spectroscopic follow-up based on their $(u-g)$, $(g-r)$ colors, and this choice is independent of the mass and nature of any putative companions.
-Therefore, at least with regard to $i$ and companion mass, the population is unbiased.
+Objects are chosen for spectroscopic follow-up based on their $ugr$ colors, and this choice is independent of the mass and nature of any putative companions.
+Therefore, at least with regard to $i$ and $M_2$, the population is unbiased.
 
 The ELM WD sample includes 55 systems with RV variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$.
-WD masses in these systems are derived from fits to spectroscopic templates which are generally precise to $\sim10\%$ \citep{gianninas14}.
-The masses of cool LMWDs may suffer somewhat from
-%the ``high log $g$ problem'' due to 
-inaccuracies in the 1-D WD atmospheric models \citep{tremblay13}. However since these limitations should only affect the coolest WDs in the ELM sample, we expect any effect on our results to be minor.
+WD masses in these systems are derived from fits to spectroscopic templates, which are generally precise to $\approx$10\% \citep{gianninas14}.
+The masses of cool LMWDs may suffer somewhat from inaccuracies in the one-dimensional WD atmospheric models \citep{tremblay13}.
+However, since this should only affect the coolest WDs in the ELM sample, we expect any impact on our results to be minor.
 
@@
 \begin{equation}
-p(\mf \given \theta) = (1-f_{\rm NS}) \mathcal{N}(M_2^* \given \mu_{\rm WD}, \sigma^2_{\rm WD})
+p(\mf \given \theta) = (1-f_{\rm NS}) \mathcal{N}(M_2^* \given \mu_{\rm WD}, \sigma^2_{\rm WD}),
 \end{equation}
-where $M_2^*$ is the mass of the WD companion in these three systems.
+where $M_2^*$ is the mass of the WD companion.
 
-The other six systems show no evidence of orbital motion, with RV upper limits of $\approx$20-50 km s$^{-1}$.
-Some of these systems may be in low $i$ binaries with RVs below the detection limit, or have $\period\approx24$ hr, which are difficult to detect \citep{ELMV}.
-These LMWDs could also have companions at systematically longer $\period$'s, resulting in orbital velocities below the detection limit.
+The other six ELM systems show no evidence of orbital motion, with RV upper limits of $\approx$20-50 km s$^{-1}$.
+Some of these systems may be in low $i$ binaries with RVs below the detection limit, or may have $\period\approx24$ hr, which is difficult to measure \citep{ELMV}.
+These LMWDs could also have companions at systematically longer $\period$, resulting in orbital velocities below the detection limit.
 We do not include these systems in our analysis.
@@
 \caption{Results from applying our model to the ELM WDs. 
-The panels are in the same form as in Figure~\ref{fig:tests_1_2} and Figure~\ref{fig:tests_3_4}. 
+The panels are the same as in Figures~\ref{fig:tests_1_2} and \ref{fig:tests_3_4}. 
 %The leftmost panel of the top row shows that the MAP model $M_{\rm WD}$ distribution matches the histogram of true masses in the PCEB sample. 
 %The second and third panels show the posterior distributions for our model parameters, while the fourth panel shows the $P_{\rm NS}$ values for each of the PCEBs (ordered by increasing $\mf$). 
-Here, the leftmost panel shows both the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). 
+The left-most panel shows both the MAP $M_2$ distribution (solid black) and random samples from the posterior (gray lines). 
 %The second panel shows that the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$.
@@
 The last panel indicates that several LMWDs in the ELM sample have high $P_{\rm NS}$.
-The three systems in the bottom right panel, with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.
+The three systems in the right-most panel with all $P_{\rm NS} = 0\%$ are the eclipsing systems with measured $M_2$.
 }
@@
 The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail toward larger $\sigma_{\rm WD}$, which could indicate that the true WD distribution may not be exactly Gaussian.
-It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}.
-Our distribution is significantly wider ($\sigma \approx 0.26~\Msun$, compared with $\sigma \approx 0.1~\Msun$), possibly due to past mass transfer phases increasing the masses of the unseen primary WDs.
-The low combined mass in these systems indicates that, although several of them will merge within a Hubble time \citep{ELMV}, the majority of ELM WDs are unlikely to be type Ia SN progenitors.
-We cannot limit the possibility that some individual LMWD binaries may be massive enough to produce type Ia SNe \citep{justham09}.
+
+It is interesting that the best-fit Gaussian for the companions to the ELM WDs is similar to that of the population of single hydrogen-atmosphere WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}.
+Our distribution is significantly wider: $\sigma \approx 0.26~\Msun$, compared to $\sigma \approx 0.1~\Msun$, possibly due to past mass transfer phases increasing the masses of the unseen primary WDs.
+
+The low combined mass in these systems indicates that, although several of them will merge within a Hubble time \citep{ELMV}, the majority of the ELM systems are unlikely to be type Ia SN progenitors.
+However, we cannot rule out the possibility that some individual LMWD binaries may be massive enough to produce type Ia SNe \citep{justham09}.
 %Several of these systems will merge within a Hubble time \citep{ELMV}, but their sub-Chandrasekhar combined mass would suggest that they are more likely to be underluminous type .Ia, rather than Ia, supernova progenitors.
@@
 In principle, priors could be added based on
+
 Our posterior distributions further suggest that the companions to LMWDs have predominantly CO cores.
-This is in contrast to population synthesis models which suggest that LMWDs should predominantly have He core WD companions \citep{toonen12}.
+This is in contrast to population synthesis models, which suggest that LMWDs should predominantly have He-core WD companions \citep{toonen12}.
 With a larger sample, a more sophisticated LMWD companion model could place quantitative constraints on population synthesis predictions.
@@
 However, there is a significant tail toward higher NS probabilities.
-Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07} and \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, both based on radio non-detections of LMWDs.
+Our model indicates $f_{\rm NS} <16\%$ at the 68\% confidence level, in agreement with independent constraints from \citet[][$f_{\rm NS}<18\pm5$\%]{vLeeuwen07} and \citet[][$f_{\rm NS}<10\substack{+4 \\ -2}~\%$]{agueros09b}, both based on radio non-detections of LMWD companions.
 
-The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7.
-However, X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}.
+The right-most panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and J174140.5$+$652638.7.
+However, the X-ray non-detection of SDSS J174140.5$+$652638.7 suggests its companion is unlikely to be a NS \citep{kilic14}.
 Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are on-going.
-We note that the $P_{\rm NS}$ distributions in each of our samples show a general trend that systems with higher $\mf$ have higher $P_{\rm NS}$ values and are therefore ideal targets to search for NS companions to LMWDs.
+We note that the $P_{\rm NS}$ distributions in each of our samples show a trend such that systems with higher $\mf$ have higher $P_{\rm NS}$ values.
+These high $\mf$ systems are therefore ideal targets to search for NS companions to LMWDs.
 
@@
 Even when the companion mass distribution is not drawn from a Gaussian distribution, our model still infers the input NS fraction to within a few percent.
-We further apply our model to the sample of PCEB's from \citet{nebot11}, and our model qualitatively recovers the independent, spectroscopically measured $M_{\rm WD}$ distribution.
+We further apply our model to the SDSS PCEBs \citep{nebot11}, and our model qualitatively recovers the independent, spectroscopically measured $M_{\rm WD}$ distribution.
 
-We then applied our model to the set of LMWDs from the ELM WD survey.
-It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the companion mass distribution to the LMWDs in the ELM sample is well-described by our model.
-Our model indicates a MAP $\mu_{\rm WD}$ of 0.74 \Msun\ and $\sigma_{\rm WD}$ of 0.24 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions.
+We applied our model to the set of LMWDs from the ELM WD survey.
+The resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the companion mass distribution to the LMWDs in the ELM sample is well-described by our model.
+Our model returns a MAP $\mu_{\rm WD} = 0.74\pm0.24\ \Msun$, suggesting that a majority of ELM WDs have CO-core WD companions.
 This is in contrast to predictions from population synthesis models, which find that the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
 Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be as high as $\approx$16\% (within 1-$\sigma$).
-Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
+Finally, our model identifies the LMWD SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
 
@@
 There are several ways in which our model can be expanded.
-By modeling photometric variability, \citet{hermes14} recently constrained the inclination of 20 LMWDs in the ELM sample which could be included in our model.
-Furthermore, our model can place tighter constraints on $f_{\rm NS}$ by including radio and X-ray non-detection results.
-Finally, we plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
+By modeling photometric variability, \citet{hermes14} recently constrained the inclination of 20 LMWDs in the ELM sample; we could include these constraints.
+Furthermore, our model can place tighter constraints on $f_{\rm NS}$ by factoring in radio and X-ray non-detections.
+We plan to develop our method to quantitatively compare our model to the results of population synthesis codes, potentially constraining the formation of LMWDs.
 
 \acknowledgements
-The authors wish to acknowledge David Hogg, DJ D'Orazio, and Josh Peek for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014). 
-APW is supported by a National Science Foundation Graduate Research Fellowship under Grant No.\ 11-44155. 
-This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}. \\
+The authors thank David Hogg, DJ D'Orazio, and Josh Peek for useful discussions, and the organizers of the \emph{AstroData Hack Week} (2014).
+We are grateful to the anonymous referees for comments that helped improve this paper.
+MAA acknowledges support provided by the NSF through grant AST-1255419.
+APW is supported by a NSF Graduate Research Fellowship under grant No.\ 11-44155.
+This research made use of Astropy, a community-developed core \texttt{Python} package for Astronomy \citep{astropy13}.
+\\
 
